### 2013-12-23 draft/ms.tex
Initialize makefile, ms.tex and references.tex for draft paper

% EOD Documentation Paper #3
% Project initiated Dec 22 2013

\documentclass{emulateapj}
\usepackage{amsmath,amssymb}
\usepackage{xspace}
\usepackage{graphicx}
\bibliographystyle{apj} 
\usepackage{epstopdf}  
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{verbatim}
\usepackage{morefloats} % somehow need this to have lots of figures
                        % and tables?
% for attractive links:
\usepackage[colorlinks,urlcolor=blue,citecolor=black,linkcolor=blue]{hyperref}
%\usepackage[nolists]{endfloat} % put floats at end - doesn't work
\interfootnotelinepenalty=10000 % Do not want cross-page footnote!

\usepackage{CJK}

% definition of symbols
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\ergcms{erg~cm$^{-2}$~s$^{-1}$}
\def\ergs{erg~s$^{-1}$}
\def\msun{M_{\odot}}
\def\lsun{L_{\odot}}
\def\etal{~et~al.~}
\def\degree{^{\circ}}
\def\leq{\leqslant}
\def\geq{\geqslant}
\def\micron{$\mu$m}
\def\percm2{{\rm cm^{-2}}}
\def\peryr{yr$^{-1}$}

\maxdeadcycles=1000 % need this to have bunch of figures on each page
                    % at end

\slugcomment{}
\shorttitle{}
\shortauthors{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{CJK*}{UTF8}{gbsn}

\title{}

% leading authors
\author{Eunkyu Han\altaffilmark{1,2}}
\author{Sharon X. Wang\altaffilmark{1,2,3}}
\author{Jason T. Wright\altaffilmark{1,2,3}}
\author{Ming Zhao\altaffilmark{1,2}}

\altaffiltext{1}{Department of Astronomy \& Astrophysics, 525 Davey
  Lab, The Pennsylvania State University, University Park, PA 16802, USA;
  Send correspondence to Eunkyu Han at hek90625@gmail.com.}
\altaffiltext{2}{Center for Exoplanets and Habitable Worlds, The
  Pennsylvania State University, University Park, PA 16802, USA}
\altaffiltext{3}{Astrobiology Research Center, The
  Pennsylvania State University, University Park, PA 16802, USA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}

The introduction Section...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References:
%\newpage
%\input{references.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BEGIN FIGURES AND STUFF
\begin{comment} % empty right now, so comment out
\newpage

%----------------------------------------------------------------
% Figure: 
\begin{figure*}[!th]
  \center
\includegraphics[angle=0.,scale=0.9]{f1.eps}  
\caption{
  \label{fig:f1}}
\end{figure*}
%----------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tables

%----------------------------------------------------------------
% Table: 
\renewcommand{\arraystretch}{1.3} % more row spacing for the table
\begin{turnpage}
\begin{center}
\begin{deluxetable*}{@{\hspace{-5mm}}c@{\hspace{-5mm}}llllccc}
%\rotate
\tabletypesize{\scriptsize}
\tablewidth{0pt}
\tablecaption{\label{tab:basic}}
\tablehead{
%-------------  
% FIRST ROW  
% submm stuff  
\colhead{} & \colhead{} &
\colhead{$S_{870 \mu{\rm m}}$} &
% xray stuff
\multicolumn{2}{c}{\xray\ Position\tablenotemark{b}}  & \colhead{\cdfs} & \colhead{\ecdfs} &
\colhead{$f_{X}/10^{-15}$} \\ \cline{4-5}
%-------------
% SECOND ROW
% submm stuff  
\colhead{ALESS SMG Full Name\tablenotemark{a}} & \colhead{ID\tablenotemark{a}} &
\colhead{(mJy)} &
% xray stuff
\colhead{$\alpha_{\rm J2000.0}$}  &  \colhead{$\delta_{\rm J2000.0}$}
& \colhead{Cat \& ID\tablenotemark{b}} & \colhead{Cat \& ID\tablenotemark{b}} &
\colhead{erg cm$^{-2}$ s$^{-1}$\tablenotemark{c}} 
}
\startdata
ALESS J$033213.85-275600.3  $ & 011.1 & $  7.3 \pm 0.4 $ & 03 32 13.85 & $ -27 $ 56 00.44 & M 197 & M 332 &  1.69 
\enddata
%
\tablenotetext{a}{}
%
\end{deluxetable*}
\end{center}
\end{turnpage}
%----------------------------------------------------------------

\end{comment}

\end{CJK*}

\end{document}

### 2013-12-23 draft/ms.tex
Modify ms.tex to be in aastex preprint style, per PASP requirement.
Update ms.tex and new_table_items.txt. Outline paper structure in ms.tex.

@@
 
-\documentclass{emulateapj}
+%\documentclass{emulateapj}
+% Requirement of PASP to use preprint and aastex
+\documentclass[12pt,preprint]{aastex}
 \usepackage{amsmath,amssymb}
@@
 
-\title{}
+\title{Updates on the Exoplanet Orbit Database}
 
@@
 \author{Ming Zhao\altaffilmark{1,2}}
+\author{and Friends}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Updates on the EOD}\label{sec:update}
+
+Restrict the updates in this section on EOD updates.
+
+Parameter updates, new table parameters etc. What other updates are there?
+
+Table: complete list of table parameters. Highlight the ones not
+included in Wright\etal2011
+
+Figure: Figure of single planet page, to show updated transit
+parameters and RV curves etc.?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Inclusion of the Kepler Planet Candidates and Other Exoplanets on Exoplanets.org}\label{sec:kepler}
+
+Figure: some comparison figures of Kepler candidate properties
+vs. EOD planet properties, such as mass-period, mass-radius?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}\label{sec:conclusion}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\acknowledgments
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % References:
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% BEGIN FIGURES AND STUFF
-\begin{comment} % empty right now, so comment out
-\newpage
-
-%----------------------------------------------------------------
-% Figure: 
-\begin{figure*}[!th]
-  \center
-\includegraphics[angle=0.,scale=0.9]{f1.eps}  
-\caption{
-  \label{fig:f1}}
-\end{figure*}
-%----------------------------------------------------------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Tables
-
-%----------------------------------------------------------------
-% Table: 
-\renewcommand{\arraystretch}{1.3} % more row spacing for the table
-\begin{turnpage}
-\begin{center}
-\begin{deluxetable*}{@{\hspace{-5mm}}c@{\hspace{-5mm}}llllccc}
-%\rotate
-\tabletypesize{\scriptsize}
-\tablewidth{0pt}
-\tablecaption{\label{tab:basic}}
-\tablehead{
-%-------------  
-% FIRST ROW  
-% submm stuff  
-\colhead{} & \colhead{} &
-\colhead{$S_{870 \mu{\rm m}}$} &
-% xray stuff
-\multicolumn{2}{c}{\xray\ Position\tablenotemark{b}}  & \colhead{\cdfs} & \colhead{\ecdfs} &
-\colhead{$f_{X}/10^{-15}$} \\ \cline{4-5}
-%-------------
-% SECOND ROW
-% submm stuff  
-\colhead{ALESS SMG Full Name\tablenotemark{a}} & \colhead{ID\tablenotemark{a}} &
-\colhead{(mJy)} &
-% xray stuff
-\colhead{$\alpha_{\rm J2000.0}$}  &  \colhead{$\delta_{\rm J2000.0}$}
-& \colhead{Cat \& ID\tablenotemark{b}} & \colhead{Cat \& ID\tablenotemark{b}} &
-\colhead{erg cm$^{-2}$ s$^{-1}$\tablenotemark{c}} 
-}
-\startdata
-ALESS J$033213.85-275600.3  $ & 011.1 & $  7.3 \pm 0.4 $ & 03 32 13.85 & $ -27 $ 56 00.44 & M 197 & M 332 &  1.69 
-\enddata
-%
-\tablenotetext{a}{}
-%
-\end{deluxetable*}
-\end{center}
-\end{turnpage}
-%----------------------------------------------------------------
-
-\end{comment}
-
 \end{CJK*}

### 2013-12-27 draft/ms.tex
Add parameter table and list all parameters

@@
 % Requirement of PASP to use preprint and aastex
-\documentclass[12pt,preprint]{aastex}
+\documentclass[11pt,preprint]{aastex}
 \usepackage{amsmath,amssymb}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Table
+\clearpage
+
+\begin{deluxetable}{llll}
+\tabletypesize{\scriptsize}
+\rotate
+\tablewidth{0pt}
+\tablecaption{Fields of Exoplanet Orbit Database}
+\tablehead{
+  \colhead{Field} & \colhead{Data Type} & \colhead{Meaning} &
+  \colhead{Related Fields\tablenotemark{a}}
+}
+\startdata
+\sidehead{\textbf{Planet Information}}
+NAME\dotfill & String & Name of planet &  \\
+OTHERNAME\dotfill & String & Other commonly used name of planet &  \\
+COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) &  \\
+HD\dotfill & String & &  \\
+HR\dotfill & String & &  \\
+HIPP\dotfill & String & & \\
+SAO\dotfill & & & \\
+GL\dotfill & & & \\
+BINARY\dotfill & & & BINARYREF BINARYURL \\
+RA, RA\_STRING\dotfill & & & \\
+DEC, DEC\_STRING\dotfill & & & \\
+KEPID\dotfill & & & \\
+KOI\dotfill & & & \\
+KDE\dotfill & & & \\
+EOD\dotfill & & & \\
+MICROLENSING\dotfill & & & \\ 
+IMAGING\dotfill & & & \\
+TIMING\dotfill & & & \\
+ASTROMETRY\dotfill & & & \\
+\sidehead{\textbf{Stellar Parameters}}
+BMV\dotfill & & & \\
+V\dotfill & & & VREF,VURL \\
+J\dotfill & & & \\
+H\dotfill & & & \\
+KS\dotfill & & & \\
+DIST\dotfill & & & DISTUPPER,DISTLOWER,UDIST,DISTREF,DISTURL \\
+PAR\dotfill & & & PARUPPER,PARLOWER,UPAR \\
+VSINI\dotfill & & & VSINIUPPER,VSINILOWER,UVSINI,VSINIREF,VSINIURL \\
+GAMMA\dotfill & & & GAMMAUPPER,GAMMALOWER,UGAMMA,GAMMAREF,GAMMAURL \\
+\sidehead{\textbf{Orbit Parameters}}
+PER\dotfill & & & PERUPPER,PERLOWER,UPER,PERREF,PERURL \\
+ECC\dotfill & & & ECCUPPER,ECCLOWER,UECC,ECCREF,ECCURL \\
+OM\dotfill & & & OMUPPER,OMLOWER,UOM,OMREF,OMURL \\
+K\dotfill & & & KUPPER,KLOWER,UK,KREF,KURL \\
+T0\dotfill & & & T0UPPER,T0LOWER,UT0,T0REF,T0URL \\
+DVDT\dotfill & & & DVDTUPPER,DVDTLOWER,UDVDT,DVDTREF,DVDTURL \\
+I\dotfill & & & IUPPER,ILOWER,UI,IREF,IURL \\
+MSINI\dotfill & & & MSINIUPPER,MSINILOWER,UMSINI,MSINIREF,MSINIURL \\
+A\dotfill & & & AUPPER,ALOWER,UA,AREF,AURL \\
+MASS\dotfill & & & MASSUPPER,MASSLOWER,UMASS,MASSREF,MASSURL \\
+SEP\dotfill & & & SEPUPPER,SEPLOWER,USEP,SEPREF,SEPURL \\
+TREND\dotfill  & & & \\
+LAMBDA\dotfill & & & LAMBDAUPPER,LAMBDALOWER,ULAMBDA,LAMBDAREF,LAMBDAURL \\
+BIGOM\dotfill & & & BIGOMUPPER,BIGOMLOWER,UBIGOM,BIGOMREF,BIGOMURL \\
+FREEZE\_ECC\dotfill & & & \\
+\sidehead{\textbf{Transit Parameters}}
+DEPTH\dotfill & & & DEPTHUPPER,DEPTHLOWER,UDEPTH,DEPTHREF,DEPTHURL \\
+T14\dotfill & & & T14UPPER,T14LOWER,UT14,T14REF,T14URL \\
+TT\dotfill & & & TTUPPER,TTLOWER,UTT,TTREF,TTURL \\
+R\dotfill & & & RUPPER,RLOWER,UR,RREF,RURL \\
+AR\dotfill & & & ARUPPER,ARLOWER,UAR,ARREF,ARURL \\
+B\dotfill & & & BUPPER,BLOWER,UB,BREF,BURL \\
+DENSITY\dotfill & & &
+DENSITYUPPER,DENSITYLOWER,UDENSITY,DENSITYREF,DENSITYURL \\
+GRAVITY\dotfill & & &
+GRAVITYUPPER,GRAVITYLOWER,UGRAVITY,GRAVITYREF,GRAVITYURL \\
+TRANSIT\dotfill & & & TRANSITREF,TRANSITURL \\
+DR\dotfill & & & DRUPPER,DRLOWER,UDR,DRREF,DRURL \\
+RR\dotfill & & & RRUPPER,RRLOWER,URR,RRREF,RRURL \\
+\sidehead{\textbf{Secondary Eclipse}}
+SE\dotfill & & & SEREF,SEURL \\
+SEDEPTHJ\dotfill & & &
+SEDEPTHJUPPER,SEDEPTHJLOWER,USEDEPTHJ,SEDEPTHJREF,SEDEPTHJURL \\
+SEDEPTHH\dotfill & & &
+SEDEPTHHUPPER,SEDEPTHHLOWER,USEDEPTHH,SEDEPTHHREF,SEDEPTHHURL \\
+SEDEPTHKS\dotfill & & &
+SEDEPTHKSUPPER,SEDEPTHKSLOWER,USEDEPTHKS,SEDEPTHKSREF,SEDEPTHKSURL \\
+SEDEPTHKP\dotfill & & &
+SEDEPTHKPUPPER,SEDEPTHKPLOWER,USEDEPTHKP,SEDEPTHKPREF,SEDEPTHKPURL \\
+SEDEPTH36\dotfill & & &
+SEDEPTH36UPPER,SEDEPTH36LOWER,USEDEPTH36,SEDEPTH36REF,SEDEPTH36URL \\
+SEDEPTH45\dotfill & & &
+SEDEPTH45UPPER,SEDEPTH45LOWER,USEDEPTH45,SEDEPTH45REF,SEDEPTH45URL \\
+SEDEPTH58\dotfill & & & 
+SEDEPTH58UPPER,SEDEPTH58LOWER,USEDEPTH58,SEDEPTH58REF,SEDEPTH58URL \\
+SEDEPTH80\dotfill & & &
+SEDEPTH80UPPER,SEDEPTH80LOWER,USEDEPTH80,SEDEPTH80REF,SEDEPTH80URL \\
+SET\dotfill & & & SETUPPER,SETLOWER,USET,SETREF,SETURL \\
+\sidehead{\textbf{Fit \& References}}
+RMS\dotfill & & & \\
+CHI2\dotfill & & & \\
+NOBS\dotfill & & & \\
+NCOMP\dotfill & & & \\
+MULT\dotfill & & & \\
+PLANETDISCMETH\dotfill & & & \\
+STARDISCMETH\dotfill & & & \\
+DATE\dotfill & & & \\
+FIRSTREF\dotfill & & & FIRSTURL \\
+ORBREF\dotfill & & & ORBURL \\
+\sidehead{\textbf{Stellar Properties}}
+STAR\dotfill & & & \\
+MSTAR\dotfill & & & MSTARUPPER,MSTARLOWER,UMSTAR,MSTARREF,MSTARURL \\
+RSTAR\dotfill & & & RSTARUPPER,RSTARLOWER,URSTAR,RSTARREF,RSTARURL \\
+TEFF\dotfill & & & TEFFUPPER,TEFFLOWER,UTEFF,TEFFREF,TEFFURL \\
+RHOSTAR\dotfill & & &
+RHOSTARUPPER,RHOSTARLOWER,URHOSTAR,RHOSTARREF,RHOSTARURL \\
+LOGG\dotfill & & & LOGGUPPER,LOGGLOWER,ULOGG,LOGGREF,LOGGURL \\
+FE\dotfill & & & FEUPPER,FELOWER,UFE,FEREF,FEURL \\
+SHK\dotfill & & & \\
+RHK\dotfill & & & \\
+KP\dotfill & & & \\
+SPECREF\dotfill & & & SPECURL \\
+\sidehead{\textbf{Links}}
+JSNAME\dotfill & & & EPEURL \\
+ETDNAME\dotfill & & & ETDURL \\
+SIMBADNAME\dotfill & & & SIMBADURL \\
+EANAME\dotfill & & & EAURL \\
+\enddata
+\tablenotetext{a}{XU, XUPPER, XLOWER, XREF, XURL etc.}
+\end{deluxetable}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{CJK*}

### 2013-12-27 draft/ms.tex
Add reference.tex. Fill in fields overlapped with Wright 2011 in table.

@@
 \def\ergs{erg~s$^{-1}$}
+\def\mps{m~s$^{-1}$}
 \def\msun{M_{\odot}}
@@
 Table: complete list of table parameters. Highlight the ones not
-included in Wright\etal2011
+included in \cite{Wright2011}.
 
@@
 %\newpage
-%\input{references.tex}
+\input{references.tex}
 
@@
 NAME\dotfill & String & Name of planet &  \\
-OTHERNAME\dotfill & String & Other commonly used name of planet &  \\
+OTHERNAME\tablenotemark{b}\dotfill & String & Other commonly used name of planet &  \\
 COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) &  \\
-HD\dotfill & String & &  \\
-HR\dotfill & String & &  \\
-HIPP\dotfill & String & & \\
-SAO\dotfill & & & \\
-GL\dotfill & & & \\
-BINARY\dotfill & & & BINARYREF BINARYURL \\
-RA, RA\_STRING\dotfill & & & \\
-DEC, DEC\_STRING\dotfill & & & \\
+HD\dotfill & Long Integer & Henry Draper number of sar &  \\
+HR\dotfill & Integer & Bright Star Catalog number of star &  \\
+HIPP\dotfill & Long Integer & \textit{Hipparcos} catalog number of star & \\
+SAO\dotfill & Long Integer & SAO catalog number of star & \\
+GL\dotfill & Float & GJ or Gliese catalog number of star & \\
+BINARY\dotfill & Boolean & Star known ot be binary? & BINARYREF BINARYURL \\
+RA, RA\_STRING\dotfill & Double, String & J2000 right ascension in decimal hours and in
+sexagesimal string & \\
+DEC, DEC\_STRING\dotfill & Double, String & J2000 declination in decimal degrees and in
+sexagesimal string & \\
 KEPID\dotfill & & & \\
@@
 \sidehead{\textbf{Stellar Parameters}}
-BMV\dotfill & & & \\
-V\dotfill & & & VREF,VURL \\
-J\dotfill & & & \\
-H\dotfill & & & \\
-KS\dotfill & & & \\
+BMV\dotfill & Float & $B-V$ color & \\
+V\dotfill & Float & $V$ magnitude & VREF,VURL \\
+J\dotfill & Float & $J$ magnitude & \\
+H\dotfill & Float & $H$ magnitude & \\
+KS\dotfill & Float & $K_S$ magnitude & \\
 DIST\dotfill & & & DISTUPPER,DISTLOWER,UDIST,DISTREF,DISTURL \\
-PAR\dotfill & & & PARUPPER,PARLOWER,UPAR \\
-VSINI\dotfill & & & VSINIUPPER,VSINILOWER,UVSINI,VSINIREF,VSINIURL \\
+PAR\dotfill & Float & Parallax in mas & PARUPPER,PARLOWER,UPAR \\
+VSINI\dotfill & Float & Projected equatorial rotational velocity of
+star & VSINIUPPER,VSINILOWER,UVSINI,VSINIREF,VSINIURL \\
 GAMMA\dotfill & & & GAMMAUPPER,GAMMALOWER,UGAMMA,GAMMAREF,GAMMAURL \\
 \sidehead{\textbf{Orbit Parameters}}
-PER\dotfill & & & PERUPPER,PERLOWER,UPER,PERREF,PERURL \\
-ECC\dotfill & & & ECCUPPER,ECCLOWER,UECC,ECCREF,ECCURL \\
-OM\dotfill & & & OMUPPER,OMLOWER,UOM,OMREF,OMURL \\
-K\dotfill & & & KUPPER,KLOWER,UK,KREF,KURL \\
-T0\dotfill & & & T0UPPER,T0LOWER,UT0,T0REF,T0URL \\
-DVDT\dotfill & & & DVDTUPPER,DVDTLOWER,UDVDT,DVDTREF,DVDTURL \\
-I\dotfill & & & IUPPER,ILOWER,UI,IREF,IURL \\
-MSINI\dotfill & & & MSINIUPPER,MSINILOWER,UMSINI,MSINIREF,MSINIURL \\
-A\dotfill & & & AUPPER,ALOWER,UA,AREF,AURL \\
+PER\dotfill & Double & Orbital period in days & PERUPPER,PERLOWER,UPER,PERREF,PERURL \\
+ECC\dotfill & Float & Orbital eccentricity & ECCUPPER,ECCLOWER,UECC,ECCREF,ECCURL \\
+OM\dotfill & Float & Argument of periastron in degrees & OMUPPER,OMLOWER,UOM,OMREF,OMURL \\
+K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps & KUPPER,KLOWER,UK,KREF,KURL \\
+T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{c} $-2,440,000$ & T0UPPER,T0LOWER,UT0,T0REF,T0URL \\
+DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & DVDTUPPER,DVDTLOWER,UDVDT,DVDTREF,DVDTURL \\
+I\dotfill & Float & Orbital inclination in degrees (ZZZ for transiting
+systems only ZZZ still true?) & IUPPER,ILOWER,UI,IREF,IURL \\
+MSINI\dotfill & Float & Minimum mass (as calculated from the mass
+function) in $M_{\rm Jup}$ & MSINIUPPER,MSINILOWER,UMSINI,MSINIREF,MSINIURL \\
+A\dotfill & Float & Orbital semimajor axis in AU & AUPPER,ALOWER,UA,AREF,AURL \\
 MASS\dotfill & & & MASSUPPER,MASSLOWER,UMASS,MASSREF,MASSURL \\
 SEP\dotfill & & & SEPUPPER,SEPLOWER,USEP,SEPREF,SEPURL \\
-TREND\dotfill  & & & \\
-LAMBDA\dotfill & & & LAMBDAUPPER,LAMBDALOWER,ULAMBDA,LAMBDAREF,LAMBDAURL \\
+TREND\dotfill  & Boolean & Linear trend in fit? & \\
+LAMBDA\dotfill & Float & Projected spin-orbit misalignment & LAMBDAUPPER,LAMBDALOWER,ULAMBDA,LAMBDAREF,LAMBDAURL \\
 BIGOM\dotfill & & & BIGOMUPPER,BIGOMLOWER,UBIGOM,BIGOMREF,BIGOMURL \\
-FREEZE\_ECC\dotfill & & & \\
+FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \\
 \sidehead{\textbf{Transit Parameters}}
-DEPTH\dotfill & & & DEPTHUPPER,DEPTHLOWER,UDEPTH,DEPTHREF,DEPTHURL \\
-T14\dotfill & & & T14UPPER,T14LOWER,UT14,T14REF,T14URL \\
-TT\dotfill & & & TTUPPER,TTLOWER,UTT,TTREF,TTURL \\
-R\dotfill & & & RUPPER,RLOWER,UR,RREF,RURL \\
-AR\dotfill & & & ARUPPER,ARLOWER,UAR,ARREF,ARURL \\
-B\dotfill & & & BUPPER,BLOWER,UB,BREF,BURL \\
-DENSITY\dotfill & & &
+DEPTH\dotfill & Float & $(R_p/R_*)^2$ & DEPTHUPPER,DEPTHLOWER,UDEPTH,DEPTHREF,DEPTHURL \\
+T14\dotfill & Float & Time of transit from first to fourth contact in days & T14UPPER,T14LOWER,UT14,T14REF,T14URL \\
+TT\dotfill & Float & Epoch of transit center in
+HJD\tablenotemark{c} $-2,440,000$ & TTUPPER,TTLOWER,UTT,TTREF,TTURL \\
+R\dotfill & Float & Radius of the planet in Jupiter radii & RUPPER,RLOWER,UR,RREF,RURL \\
+AR\dotfill & $(a/R_*)$ & & ARUPPER,ARLOWER,UAR,ARREF,ARURL \\
+B\dotfill & Float & Impact parameter of transit & BUPPER,BLOWER,UB,BREF,BURL \\
+DENSITY\dotfill & Float & Density of planet in g cc$^{-1}$ &
 DENSITYUPPER,DENSITYLOWER,UDENSITY,DENSITYREF,DENSITYURL \\
-GRAVITY\dotfill & & &
+GRAVITY\dotfill & Float & $\log{g}$ (surface gravity) of the planet
+calculated from transit parameters &
 GRAVITYUPPER,GRAVITYLOWER,UGRAVITY,GRAVITYREF,GRAVITYURL \\
-TRANSIT\dotfill & & & TRANSITREF,TRANSITURL \\
+TRANSIT\dotfill & Boolean & Is the planet known to transit? & TRANSITREF,TRANSITURL \\
 DR\dotfill & & & DRUPPER,DRLOWER,UDR,DRREF,DRURL \\
@@
 SET\dotfill & & & SETUPPER,SETLOWER,USET,SETREF,SETURL \\
+& & & \\
 \sidehead{\textbf{Fit \& References}}
-RMS\dotfill & & & \\
-CHI2\dotfill & & & \\
-NOBS\dotfill & & & \\
-NCOMP\dotfill & & & \\
-MULT\dotfill & & & \\
-PLANETDISCMETH\dotfill & & & \\
-STARDISCMETH\dotfill & & & \\
-DATE\dotfill & & & \\
-FIRSTREF\dotfill & & & FIRSTURL \\
-ORBREF\dotfill & & & ORBURL \\
+RMS\dotfill & Float & Root-mean-square residuals to orbital RV fit & \\
+CHI2\dotfill & Float & $\chi_{\nu}^2$ to orbital RV fit & \\
+NOBS\dotfill & Integer & Number of observations used in fit & \\
+NCOMP\dotfill & Integer & Number of planetary companions known & \\
+MULT\dotfill & Boolean & Multiple planets in system? & \\
+PLANETDISCMETH\dotfill & String & Method of discovery of planet & \\
+STARDISCMETH\dotfill & String & Method of discovery for the first
+planet in the system & \\
+DATE\dotfill & Integer & Year of publication of FIRSTREF & \\
+ZZZ MONTH ZZZ\dotfill & Integer & Month of publication of FIRSTREF & \\
+FIRSTREF\dotfill & String & First peer-reviewed publication of
+planetary orbit & FIRSTURL \\
+ORBREF\dotfill & String & Peer-reviewed origin of orbital parameters & ORBURL \\
 \sidehead{\textbf{Stellar Properties}}
 STAR\dotfill & & & \\
-MSTAR\dotfill & & & MSTARUPPER,MSTARLOWER,UMSTAR,MSTARREF,MSTARURL \\
+MSTAR\dotfill & Float & Mass of host star & MSTARUPPER,MSTARLOWER,UMSTAR,MSTARREF,MSTARURL \\
 RSTAR\dotfill & & & RSTARUPPER,RSTARLOWER,URSTAR,RSTARREF,RSTARURL \\
-TEFF\dotfill & & & TEFFUPPER,TEFFLOWER,UTEFF,TEFFREF,TEFFURL \\
+TEFF\dotfill & Float & Effective temperature of host star & TEFFUPPER,TEFFLOWER,UTEFF,TEFFREF,TEFFURL \\
 RHOSTAR\dotfill & & &
 RHOSTARUPPER,RHOSTARLOWER,URHOSTAR,RHOSTARREF,RHOSTARURL \\
-LOGG\dotfill & & & LOGGUPPER,LOGGLOWER,ULOGG,LOGGREF,LOGGURL \\
-FE\dotfill & & & FEUPPER,FELOWER,UFE,FEREF,FEURL \\
-SHK\dotfill & & & \\
-RHK\dotfill & & & \\
+LOGG\dotfill & Float & Spectroscopic $\log{g}$ (surface gravity) of
+host star & LOGGUPPER,LOGGLOWER,ULOGG,LOGGREF,LOGGURL \\
+FE\dotfill & Float & Iron abundance (or metallicity) of star & FEUPPER,FELOWER,UFE,FEREF,FEURL \\
+SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \\
+RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \\
 KP\dotfill & & & \\
@@
 \sidehead{\textbf{Links}}
-JSNAME\dotfill & & & EPEURL \\
-ETDNAME\dotfill & & & ETDURL \\
-SIMBADNAME\dotfill & & & SIMBADURL \\
+JSNAME\dotfill & String & Name of host star used in the Extrasolar
+Planets Encyclopaedia & EPEURL \\
+ETDNAME\dotfill & String & Name of host star used in the Exoplanet
+Transit Database & ETDURL \\
+SIMBADNAME\dotfill & String & Valid SIMBAD name of host star & SIMBADURL \\
 EANAME\dotfill & & & EAURL \\
@@
 \tablenotetext{a}{XU, XUPPER, XLOWER, XREF, XURL etc.}
+\tablenotetext{b}{Originally as other commonly used name for star in \cite{Wright2011};
+  changed to other commonly used name for planet.}
+\tablenotetext{c}{ZZZ Is this now consistent? ZZZ}
 \end{deluxetable}

### 2013-12-27 draft/references.tex
Add reference.tex. Fill in fields overlapped with Wright 2011 in table.

% List references here
\begin{thebibliography}

\bibitem[Wright et al.(2011)]{Wright2011} Wright, J.~T., et al.\ 2011, \pasp, 123, 412

\end{thebibliography}

### 2013-12-28 draft/ms.tex
Abbreviate related fields in table.

@@
 \tablewidth{0pt}
-\tablecaption{Fields of Exoplanet Orbit Database}
+\tablecaption{Fields of Exoplanet Orbit Database\label{tab:par}}
 \tablehead{
@@
 \startdata
+%
 \sidehead{\textbf{Planet Information}}
@@
 GL\dotfill & Float & GJ or Gliese catalog number of star & \\
-BINARY\dotfill & Boolean & Star known ot be binary? & BINARYREF BINARYURL \\
+BINARY\dotfill & Boolean & Star known ot be binary? & -REF, -URL \\
 RA, RA\_STRING\dotfill & Double, String & J2000 right ascension in decimal hours and in
@@
 ASTROMETRY\dotfill & & & \\
+%
 \sidehead{\textbf{Stellar Parameters}}
 BMV\dotfill & Float & $B-V$ color & \\
-V\dotfill & Float & $V$ magnitude & VREF,VURL \\
+V\dotfill & Float & $V$ magnitude & -REF,-URL \\
 J\dotfill & Float & $J$ magnitude & \\
@@
 KS\dotfill & Float & $K_S$ magnitude & \\
-DIST\dotfill & & & DISTUPPER,DISTLOWER,UDIST,DISTREF,DISTURL \\
-PAR\dotfill & Float & Parallax in mas & PARUPPER,PARLOWER,UPAR \\
+DIST\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
+PAR\dotfill & Float & Parallax in mas & -UPPER,-LOWER,U- \\
 VSINI\dotfill & Float & Projected equatorial rotational velocity of
-star & VSINIUPPER,VSINILOWER,UVSINI,VSINIREF,VSINIURL \\
-GAMMA\dotfill & & & GAMMAUPPER,GAMMALOWER,UGAMMA,GAMMAREF,GAMMAURL \\
+star & -UPPER,-LOWER,U-,-REF,-URL \\
+GAMMA\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
+%
 \sidehead{\textbf{Orbit Parameters}}
-PER\dotfill & Double & Orbital period in days & PERUPPER,PERLOWER,UPER,PERREF,PERURL \\
-ECC\dotfill & Float & Orbital eccentricity & ECCUPPER,ECCLOWER,UECC,ECCREF,ECCURL \\
-OM\dotfill & Float & Argument of periastron in degrees & OMUPPER,OMLOWER,UOM,OMREF,OMURL \\
-K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps & KUPPER,KLOWER,UK,KREF,KURL \\
-T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{c} $-2,440,000$ & T0UPPER,T0LOWER,UT0,T0REF,T0URL \\
-DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & DVDTUPPER,DVDTLOWER,UDVDT,DVDTREF,DVDTURL \\
+PER\dotfill & Double & Orbital period in days & -UP-,-LOWER,U-,-REF,-URL \\
+ECC\dotfill & Float & Orbital eccentricity & -UPPER,-LOWER,U-,-REF,-URL \\
+OM\dotfill & Float & Argument of periastron in degrees & -UPPER,-LOWER,U-,-REF,-URL \\
+K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps & -UPPER,-LOWER,U-,-REF,-URL \\
+T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{c} $-2,440,000$ & -UPPER,-LOWER,U-,-REF,-URL \\
+DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER,-LOWER,U-,-REF,-URL \\
 I\dotfill & Float & Orbital inclination in degrees (ZZZ for transiting
-systems only ZZZ still true?) & IUPPER,ILOWER,UI,IREF,IURL \\
+systems only ZZZ still true?) & -UPPER,-LOWER,U-,-REF,-URL \\
 MSINI\dotfill & Float & Minimum mass (as calculated from the mass
-function) in $M_{\rm Jup}$ & MSINIUPPER,MSINILOWER,UMSINI,MSINIREF,MSINIURL \\
-A\dotfill & Float & Orbital semimajor axis in AU & AUPPER,ALOWER,UA,AREF,AURL \\
-MASS\dotfill & & & MASSUPPER,MASSLOWER,UMASS,MASSREF,MASSURL \\
-SEP\dotfill & & & SEPUPPER,SEPLOWER,USEP,SEPREF,SEPURL \\
+function) in $M_{\rm Jup}$ & -UPPER,-LOWER,U-,-REF,-URL \\
+A\dotfill & Float & Orbital semimajor axis in AU & -UPPER,-LOWER,U-,-REF,-URL \\
+MASS\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
+SEP\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
 TREND\dotfill  & Boolean & Linear trend in fit? & \\
-LAMBDA\dotfill & Float & Projected spin-orbit misalignment & LAMBDAUPPER,LAMBDALOWER,ULAMBDA,LAMBDAREF,LAMBDAURL \\
-BIGOM\dotfill & & & BIGOMUPPER,BIGOMLOWER,UBIGOM,BIGOMREF,BIGOMURL \\
+LAMBDA\dotfill & Float & Projected spin-orbit misalignment & -UPPER,-LOWER,U-,-REF,-URL \\
+BIGOM\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
 FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \\
+%
 \sidehead{\textbf{Transit Parameters}}
-DEPTH\dotfill & Float & $(R_p/R_*)^2$ & DEPTHUPPER,DEPTHLOWER,UDEPTH,DEPTHREF,DEPTHURL \\
-T14\dotfill & Float & Time of transit from first to fourth contact in days & T14UPPER,T14LOWER,UT14,T14REF,T14URL \\
+DEPTH\dotfill & Float & $(R_p/R_*)^2$ & -UPPER,-LOWER,U-,-REF,-URL \\
+T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER,-LOWER,U-,-REF,-URL \\
 TT\dotfill & Float & Epoch of transit center in
-HJD\tablenotemark{c} $-2,440,000$ & TTUPPER,TTLOWER,UTT,TTREF,TTURL \\
-R\dotfill & Float & Radius of the planet in Jupiter radii & RUPPER,RLOWER,UR,RREF,RURL \\
-AR\dotfill & $(a/R_*)$ & & ARUPPER,ARLOWER,UAR,ARREF,ARURL \\
-B\dotfill & Float & Impact parameter of transit & BUPPER,BLOWER,UB,BREF,BURL \\
+HJD\tablenotemark{c} $-2,440,000$ & -UPPER,-LOWER,U-,-REF,-URL \\
+R\dotfill & Float & Radius of the planet in Jupiter radii & -UPPE-,-LOWE-,U-,-REF,-URL \\
+AR\dotfill & $(a/R_*)$ & & -UPPER,-LOWER,U-,-REF,-URL \\
+B\dotfill & Float & Impact parameter of transit & -UPPER,-LOWER,U-,-REF,-URL \\
 DENSITY\dotfill & Float & Density of planet in g cc$^{-1}$ &
-DENSITYUPPER,DENSITYLOWER,UDENSITY,DENSITYREF,DENSITYURL \\
+-UPPER,-LOWER,U-,-REF,-URL \\
 GRAVITY\dotfill & Float & $\log{g}$ (surface gravity) of the planet
 calculated from transit parameters &
-GRAVITYUPPER,GRAVITYLOWER,UGRAVITY,GRAVITYREF,GRAVITYURL \\
+-UPPER,-LOWER,U-,-REF,-URL \\
 TRANSIT\dotfill & Boolean & Is the planet known to transit? & TRANSITREF,TRANSITURL \\
-DR\dotfill & & & DRUPPER,DRLOWER,UDR,DRREF,DRURL \\
-RR\dotfill & & & RRUPPER,RRLOWER,URR,RRREF,RRURL \\
+DR\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
+RR\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
+%
 \sidehead{\textbf{Secondary Eclipse}}
-SE\dotfill & & & SEREF,SEURL \\
+SE\dotfill & & & -REF,-URL \\
 SEDEPTHJ\dotfill & & &
-SEDEPTHJUPPER,SEDEPTHJLOWER,USEDEPTHJ,SEDEPTHJREF,SEDEPTHJURL \\
+-UPPER,-LOWER,U-,-REF,-URL \\
 SEDEPTHH\dotfill & & &
-SEDEPTHHUPPER,SEDEPTHHLOWER,USEDEPTHH,SEDEPTHHREF,SEDEPTHHURL \\
+-UPPER,-LOWER,U-,-REF,-URL \\
 SEDEPTHKS\dotfill & & &
-SEDEPTHKSUPPER,SEDEPTHKSLOWER,USEDEPTHKS,SEDEPTHKSREF,SEDEPTHKSURL \\
+-UPPER,-LOWER,U-,-REF,-URL \\
 SEDEPTHKP\dotfill & & &
-SEDEPTHKPUPPER,SEDEPTHKPLOWER,USEDEPTHKP,SEDEPTHKPREF,SEDEPTHKPURL \\
+-UPPER,-LOWER,U-,-REF,-URL \\
 SEDEPTH36\dotfill & & &
-SEDEPTH36UPPER,SEDEPTH36LOWER,USEDEPTH36,SEDEPTH36REF,SEDEPTH36URL \\
+-UPPER,-LOWER,U-,-REF,-URL \\
 SEDEPTH45\dotfill & & &
-SEDEPTH45UPPER,SEDEPTH45LOWER,USEDEPTH45,SEDEPTH45REF,SEDEPTH45URL \\
+-UPPER,-LOWER,U-,-REF,-URL \\
 SEDEPTH58\dotfill & & & 
-SEDEPTH58UPPER,SEDEPTH58LOWER,USEDEPTH58,SEDEPTH58REF,SEDEPTH58URL \\
+-UPPER,-LOWER,U-,-REF,-URL \\
 SEDEPTH80\dotfill & & &
-SEDEPTH80UPPER,SEDEPTH80LOWER,USEDEPTH80,SEDEPTH80REF,SEDEPTH80URL \\
-SET\dotfill & & & SETUPPER,SETLOWER,USET,SETREF,SETURL \\
+-UPPER,-LOWER,U-,-REF,-URL \\
+SET\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
 & & & \\
+%
 \sidehead{\textbf{Fit \& References}}
@@
 ORBREF\dotfill & String & Peer-reviewed origin of orbital parameters & ORBURL \\
+%
 \sidehead{\textbf{Stellar Properties}}
 STAR\dotfill & & & \\
-MSTAR\dotfill & Float & Mass of host star & MSTARUPPER,MSTARLOWER,UMSTAR,MSTARREF,MSTARURL \\
-RSTAR\dotfill & & & RSTARUPPER,RSTARLOWER,URSTAR,RSTARREF,RSTARURL \\
-TEFF\dotfill & Float & Effective temperature of host star & TEFFUPPER,TEFFLOWER,UTEFF,TEFFREF,TEFFURL \\
+MSTAR\dotfill & Float & Mass of host star & -UPPER,-LOWER,U-,-REF,-URL \\
+RSTAR\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
+TEFF\dotfill & Float & Effective temperature of host star & -UPPER,-LOWER,U-,-REF,-URL \\
 RHOSTAR\dotfill & & &
-RHOSTARUPPER,RHOSTARLOWER,URHOSTAR,RHOSTARREF,RHOSTARURL \\
+-UPPER,-LOWER,U-,-REF,-URL \\
 LOGG\dotfill & Float & Spectroscopic $\log{g}$ (surface gravity) of
-host star & LOGGUPPER,LOGGLOWER,ULOGG,LOGGREF,LOGGURL \\
-FE\dotfill & Float & Iron abundance (or metallicity) of star & FEUPPER,FELOWER,UFE,FEREF,FEURL \\
+host star & -UPPER,-LOWER,U-,-REF,-URL \\
+FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER,-LOWER,U-,-REF,-URL \\
 SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \\
@@
 SPECREF\dotfill & & & SPECURL \\
+%
 \sidehead{\textbf{Links}}

### 2013-12-28 draft/ms.tex
Fill all table fields except for a few data types. Update makefile.

@@
 \def\peryr{yr$^{-1}$}
+\def\kepler{\textit{Kepler}}
+\def\spitzer{\textit{Spitzer}}
+\def\micron{$\mu$m}
 
@@
 \sidehead{\textbf{Planet Information}}
-NAME\dotfill & String & Name of planet &  \\
-OTHERNAME\tablenotemark{b}\dotfill & String & Other commonly used name of planet &  \\
-COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) &  \\
-HD\dotfill & Long Integer & Henry Draper number of sar &  \\
-HR\dotfill & Integer & Bright Star Catalog number of star &  \\
-HIPP\dotfill & Long Integer & \textit{Hipparcos} catalog number of star & \\
-SAO\dotfill & Long Integer & SAO catalog number of star & \\
-GL\dotfill & Float & GJ or Gliese catalog number of star & \\
+NAME\dotfill & String & Name of planet & \nodata \\
+OTHERNAME\tablenotemark{b}\dotfill & String & Other commonly used name of planet & \nodata \\
+COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) & \nodata \\
+HD\dotfill & Long Integer & Henry Draper number of sar & \nodata \\
+HR\dotfill & Integer & Bright Star Catalog number of star & \nodata \\
+HIPP\dotfill & Long Integer & \textit{Hipparcos} catalog number of
+star & \nodata \\
+SAO\dotfill & Long Integer & SAO catalog number of star & \nodata \\
+GL\dotfill & Float & GJ or Gliese catalog number of star & \nodata \\
 BINARY\dotfill & Boolean & Star known ot be binary? & -REF, -URL \\
 RA, RA\_STRING\dotfill & Double, String & J2000 right ascension in decimal hours and in
-sexagesimal string & \\
+sexagesimal string & \nodata  \\
 DEC, DEC\_STRING\dotfill & Double, String & J2000 declination in decimal degrees and in
-sexagesimal string & \\
-KEPID\dotfill & & & \\
-KOI\dotfill & & & \\
-KDE\dotfill & & & \\
-EOD\dotfill & & & \\
-MICROLENSING\dotfill & & & \\ 
-IMAGING\dotfill & & & \\
-TIMING\dotfill & & & \\
-ASTROMETRY\dotfill & & & \\
+sexagesimal string & \nodata \\
+KEPID\dotfill & & The unique \kepler\ star identifier & \nodata \\
+KOI\dotfill & & KOI object number & \nodata \\
+KDE\dotfill & Boolean & If true, then this planet appears in the
+\kepler\ archive & \nodata \\
+EOD\dotfill & Boolean & If true, then this planet has been vetted by the
+exoplanets.org team & \nodata \\
+MICROLENSING\dotfill & Boolean & If true, then this planet was detected via microlensing & \nodata \\ 
+IMAGING\dotfill & Boolean & If true, then this planet was detected via imaging
+& \nodata \\
+TIMING\dotfill & Boolean & If true, then this planet was detected via timing & \nodata \\
+ASTROMETRY\dotfill & Boolean & If true, then this planet was detected via
+astrometric motion & \nodata \\
 %
 \sidehead{\textbf{Stellar Parameters}}
-BMV\dotfill & Float & $B-V$ color & \\
+BMV\dotfill & Float & $B-V$ color & \nodata \\
 V\dotfill & Float & $V$ magnitude & -REF,-URL \\
-J\dotfill & Float & $J$ magnitude & \\
-H\dotfill & Float & $H$ magnitude & \\
-KS\dotfill & Float & $K_S$ magnitude & \\
-DIST\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
+J\dotfill & Float & $J$ magnitude & \nodata \\
+H\dotfill & Float & $H$ magnitude & \nodata \\
+KS\dotfill & Float & $K_S$ magnitude & \nodata \\
+DIST\dotfill & & Distance to planetary system based on parallax in parsecs & -UPPER, etc. \\
 PAR\dotfill & Float & Parallax in mas & -UPPER,-LOWER,U- \\
 VSINI\dotfill & Float & Projected equatorial rotational velocity of
-star & -UPPER,-LOWER,U-,-REF,-URL \\
-GAMMA\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
+star in k\mps & -UPPER, etc. \\
+GAMMA\dotfill & & Systemic radial velocity in k\mps & -UPPER, etc. \\
 %
 \sidehead{\textbf{Orbit Parameters}}
-PER\dotfill & Double & Orbital period in days & -UP-,-LOWER,U-,-REF,-URL \\
-ECC\dotfill & Float & Orbital eccentricity & -UPPER,-LOWER,U-,-REF,-URL \\
-OM\dotfill & Float & Argument of periastron in degrees & -UPPER,-LOWER,U-,-REF,-URL \\
-K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps & -UPPER,-LOWER,U-,-REF,-URL \\
-T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{c} $-2,440,000$ & -UPPER,-LOWER,U-,-REF,-URL \\
-DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER,-LOWER,U-,-REF,-URL \\
+PER\dotfill & Double & Orbital period in days & -UPPER, etc. \\
+ECC\dotfill & Float & Orbital eccentricity & -UPPER, etc. \\
+OM\dotfill & Float & Argument of periastron in degrees & -UPPER, etc. \\
+K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps & -UPPER, etc. \\
+T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{c}$-2,440,000$ & -UPPER, etc. \\
+DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER, etc. \\
 I\dotfill & Float & Orbital inclination in degrees (ZZZ for transiting
-systems only ZZZ still true?) & -UPPER,-LOWER,U-,-REF,-URL \\
+systems only ZZZ still true?) & -UPPER, etc. \\
 MSINI\dotfill & Float & Minimum mass (as calculated from the mass
-function) in $M_{\rm Jup}$ & -UPPER,-LOWER,U-,-REF,-URL \\
-A\dotfill & Float & Orbital semimajor axis in AU & -UPPER,-LOWER,U-,-REF,-URL \\
-MASS\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
-SEP\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
-TREND\dotfill  & Boolean & Linear trend in fit? & \\
-LAMBDA\dotfill & Float & Projected spin-orbit misalignment & -UPPER,-LOWER,U-,-REF,-URL \\
-BIGOM\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
-FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \\
+function) in $M_{\rm Jup}$ & -UPPER, etc. \\
+A\dotfill & Float & Orbital semimajor axis in AU & -UPPER, etc. \\
+MASS\dotfill & & & -UPPER, etc. \\
+SEP\dotfill & & & -UPPER, etc. \\
+TREND\dotfill  & Boolean & Linear trend in fit? & \nodata \\
+LAMBDA\dotfill & Float & Projected spin-orbit misalignment in degrees & -UPPER, etc. \\
+BIGOM\dotfill & & Longitude of ascending node in degrees & -UPPER, etc. \\
+FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \nodata \\
 %
 \sidehead{\textbf{Transit Parameters}}
-DEPTH\dotfill & Float & $(R_p/R_*)^2$ & -UPPER,-LOWER,U-,-REF,-URL \\
-T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER,-LOWER,U-,-REF,-URL \\
+DEPTH\dotfill & Float & $(R_p/R_*)^2$ & -UPPER, etc. \\
+T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER, etc. \\
 TT\dotfill & Float & Epoch of transit center in
-HJD\tablenotemark{c} $-2,440,000$ & -UPPER,-LOWER,U-,-REF,-URL \\
-R\dotfill & Float & Radius of the planet in Jupiter radii & -UPPE-,-LOWE-,U-,-REF,-URL \\
-AR\dotfill & $(a/R_*)$ & & -UPPER,-LOWER,U-,-REF,-URL \\
-B\dotfill & Float & Impact parameter of transit & -UPPER,-LOWER,U-,-REF,-URL \\
+HJD\tablenotemark{c}$-2,440,000$ & -UPPER, etc. \\
+R\dotfill & Float & Radius of the planet in Jupiter radii & -UPPER, etc. \\
+AR\dotfill & $(a/R_*)$ & & -UPPER, etc. \\
+B\dotfill & Float & Impact parameter of transit & -UPPER, etc. \\
 DENSITY\dotfill & Float & Density of planet in g cc$^{-1}$ &
--UPPER,-LOWER,U-,-REF,-URL \\
+-UPPER, etc. \\
 GRAVITY\dotfill & Float & $\log{g}$ (surface gravity) of the planet
-calculated from transit parameters &
--UPPER,-LOWER,U-,-REF,-URL \\
-TRANSIT\dotfill & Boolean & Is the planet known to transit? & TRANSITREF,TRANSITURL \\
-DR\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
-RR\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
+calculated from transit parameters in cgs unit &
+-UPPER, etc. \\
+TRANSIT\dotfill & Boolean & Is the planet known to transit? & -REF,-URL \\
+DR\dotfill & & Distance during transit in stellar radii & -UPPER, etc. \\
+RR\dotfill & & $(R_p/R_*)$ & -UPPER, etc. \\
 %
 \sidehead{\textbf{Secondary Eclipse}}
-SE\dotfill & & & -REF,-URL \\
-SEDEPTHJ\dotfill & & &
--UPPER,-LOWER,U-,-REF,-URL \\
-SEDEPTHH\dotfill & & &
--UPPER,-LOWER,U-,-REF,-URL \\
-SEDEPTHKS\dotfill & & &
--UPPER,-LOWER,U-,-REF,-URL \\
-SEDEPTHKP\dotfill & & &
--UPPER,-LOWER,U-,-REF,-URL \\
-SEDEPTH36\dotfill & & &
--UPPER,-LOWER,U-,-REF,-URL \\
-SEDEPTH45\dotfill & & &
--UPPER,-LOWER,U-,-REF,-URL \\
-SEDEPTH58\dotfill & & & 
--UPPER,-LOWER,U-,-REF,-URL \\
-SEDEPTH80\dotfill & & &
--UPPER,-LOWER,U-,-REF,-URL \\
-SET\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
-& & & \\
+SE\dotfill & Boolean & If true, at least one secondary eclipse has been detected in the wavelengths listed below & -REF,-URL \\
+SEDEPTHJ\dotfill & & The secondary eclipse depth measured in the near
+infrared J band centered at 1.25 \micron &
+-UPPER, etc. \\
+SEDEPTHH\dotfill & & The secondary eclipse depth measured in the near
+infrared H band centered at 1.65 \micron & 
+-UPPER, etc. \\
+SEDEPTHKS\dotfill & & The secondary eclipse depth measured in the near
+infrared Ks band centered at 2.15 \micron &
+-UPPER, etc. \\
+SEDEPTHKP\dotfill & & The secondary eclipse depth measured in the
+Kepler photometry band in the optical from 400 to 865 nm &
+-UPPER, etc. \\
+SEDEPTH36\dotfill & & The secondary eclipse depth measured by
+\spitzer\ in its IRAC1 band centered at 3.6 \micron &
+-UPPER, etc. \\
+SEDEPTH45\dotfill & & The secondary eclipse depth measured by \spitzer\
+in its IRAC2 band centered at 4.5 \micron &
+-UPPER, etc. \\
+SEDEPTH58\dotfill & & The secondary eclipse depth measured by \spitzer\
+in its IRAC2 band centered at 5.8 \micron & 
+-UPPER, etc. \\
+SEDEPTH80\dotfill & & The secondary eclipse depth measured by \spitzer\
+in its IRAC2 band centered at 8.0 \micron &
+-UPPER, etc. \\
+SET\dotfill & & ZZZ Epoch of secondary eclipse center in
+HJD\tablenotemark{c}$-2,440,000$ ZZZ & -UPPER, etc. \\
+& & & \\ % empty row so that next table section starts on new page
 %
 \sidehead{\textbf{Fit \& References}}
-RMS\dotfill & Float & Root-mean-square residuals to orbital RV fit & \\
-CHI2\dotfill & Float & $\chi_{\nu}^2$ to orbital RV fit & \\
-NOBS\dotfill & Integer & Number of observations used in fit & \\
-NCOMP\dotfill & Integer & Number of planetary companions known & \\
-MULT\dotfill & Boolean & Multiple planets in system? & \\
-PLANETDISCMETH\dotfill & String & Method of discovery of planet & \\
+RMS\dotfill & Float & Root-mean-square residuals to orbital RV fit & \nodata \\
+CHI2\dotfill & Float & $\chi_{\nu}^2$ to orbital RV fit & \nodata \\
+NOBS\dotfill & Integer & Number of observations used in fit & \nodata \\
+NCOMP\dotfill & Integer & Number of planetary companions known & \nodata \\
+MULT\dotfill & Boolean & Multiple planets in system? & \nodata \\
+PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata \\
 STARDISCMETH\dotfill & String & Method of discovery for the first
-planet in the system & \\
-DATE\dotfill & Integer & Year of publication of FIRSTREF & \\
-ZZZ MONTH ZZZ\dotfill & Integer & Month of publication of FIRSTREF & \\
+planet in the system & \nodata \\
+DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata \\
+ZZZ MONTH ZZZ\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\
 FIRSTREF\dotfill & String & First peer-reviewed publication of
@@
 \sidehead{\textbf{Stellar Properties}}
-STAR\dotfill & & & \\
-MSTAR\dotfill & Float & Mass of host star & -UPPER,-LOWER,U-,-REF,-URL \\
-RSTAR\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
-TEFF\dotfill & Float & Effective temperature of host star & -UPPER,-LOWER,U-,-REF,-URL \\
-RHOSTAR\dotfill & & &
--UPPER,-LOWER,U-,-REF,-URL \\
+STAR\dotfill & String & Standard name for host star & \nodata \\
+MSTAR\dotfill & Float & Mass of host star in solar mass & -UPPER, etc. \\
+RSTAR\dotfill & & Radius of host star in solar radii & -UPPER, etc. \\
+TEFF\dotfill & Float & Effective temperature of host star & -UPPER, etc. \\
+RHOSTAR\dotfill & & Density of host star & -UPPER, etc. \\
 LOGG\dotfill & Float & Spectroscopic $\log{g}$ (surface gravity) of
-host star & -UPPER,-LOWER,U-,-REF,-URL \\
-FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER,-LOWER,U-,-REF,-URL \\
-SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \\
-RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \\
-KP\dotfill & & & \\
-SPECREF\dotfill & & & SPECURL \\
+host star in cgs unit & -UPPER, etc. \\
+FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER, etc. \\
+SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \nodata \\
+RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \nodata \\
+KP\dotfill & & \kepler\ bandpass magnitude & \nodata \\
+SPECREF\dotfill & & Source of most of the spectroscopic parameters
+listed for convenience & SPECURL \\
 %
@@
 Planets Encyclopaedia & EPEURL \\
-ETDNAME\dotfill & String & Name of host star used in the Exoplanet
+ETDNAME\dotfill & String & Name of planet used in the Exoplanet
 Transit Database & ETDURL \\
-SIMBADNAME\dotfill & String & Valid SIMBAD name of host star & SIMBADURL \\
-EANAME\dotfill & & & EAURL \\
+SIMBADNAME\dotfill & String & Valid SIMBAD name of host star (or
+planet, if available) & SIMBADURL \\
+EANAME\dotfill & String & Name of planet used in the Exoplanet
+Archive database & EAURL \\
 \enddata

### 2013-12-29 draft/ms.tex
Refine table: double check units and make descriptions brief.

@@
 \def\micron{$\mu$m}
+\def\mjup{$M_{\rm Jup}$}
 
@@
 
-Table: complete list of table parameters. Highlight the ones not
-included in \cite{Wright2011}.
-
+%------------------------------------------------------------------------------
 Figure: Figure of single planet page, to show updated transit
 parameters and RV curves etc.?
+
+%------------------------------------------------------------------------------
+\subsection{Revised and Removed Fields}
+These include:
+OTHERNAME - This is now listed as other name of planet instead of star;
+DISCMETH - replaced by planetdiscmeth and stardiscmeth;
+S - changed to SHK;
+SPSTAR - stellar type of star (unvetted), gone;
+NSTEDID - replaced by EANAME (Exoplanet Archive).
 
@@
 \tabletypesize{\scriptsize}
-\rotate
+%\rotate
 \tablewidth{0pt}
@@
 \tablehead{
-  \colhead{Field} & \colhead{Data Type} & \colhead{Meaning} &
-  \colhead{Related Fields\tablenotemark{a}}
+  \colhead{Field\tablenotemark{a}} & \colhead{Data Type} & \colhead{Meaning} &
+  \colhead{Related Fields\tablenotemark{b}}
 }
@@
 NAME\dotfill & String & Name of planet & \nodata \\
-OTHERNAME\tablenotemark{b}\dotfill & String & Other commonly used name of planet & \nodata \\
+OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of planet & \nodata \\
 COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) & \nodata \\
@@
 BINARY\dotfill & Boolean & Star known ot be binary? & -REF, -URL \\
-RA, RA\_STRING\dotfill & Double, String & J2000 right ascension in decimal hours and in
-sexagesimal string & \nodata  \\
-DEC, DEC\_STRING\dotfill & Double, String & J2000 declination in decimal degrees and in
-sexagesimal string & \nodata \\
+RA\dotfill & Double & J2000 right ascension in decimal hours & \nodata \\
+RA\_STRING\dotfill & String & J2000 right ascension in sexagesimal string & \nodata  \\
+DEC\dotfill & Double & J2000 declination in decimal degrees & \nodata \\
+DEC\_STRING\dotfill & String & J2000 declination in sexagesimal string & \nodata \\
 KEPID\dotfill & & The unique \kepler\ star identifier & \nodata \\
 KOI\dotfill & & KOI object number & \nodata \\
-KDE\dotfill & Boolean & If true, then this planet appears in the
-\kepler\ archive & \nodata \\
-EOD\dotfill & Boolean & If true, then this planet has been vetted by the
-exoplanets.org team & \nodata \\
-MICROLENSING\dotfill & Boolean & If true, then this planet was detected via microlensing & \nodata \\ 
-IMAGING\dotfill & Boolean & If true, then this planet was detected via imaging
-& \nodata \\
-TIMING\dotfill & Boolean & If true, then this planet was detected via timing & \nodata \\
-ASTROMETRY\dotfill & Boolean & If true, then this planet was detected via
-astrometric motion & \nodata \\
+KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata \\
+EOD\dotfill & Boolean & If true, planet is included in the EOD & \nodata \\
+MICROLENSING\dotfill & Boolean & If true, planet was detected via microlensing & \nodata \\
+IMAGING\dotfill & Boolean & If true, planet was detected via imaging & \nodata \\
+TIMING\dotfill & Boolean & If true, planet was detected via timing & \nodata \\
+ASTROMETRY\dotfill & Boolean & If true, planet was detected via astrometric motion & \nodata \\
 %
@@
 KS\dotfill & Float & $K_S$ magnitude & \nodata \\
-DIST\dotfill & & Distance to planetary system based on parallax in parsecs & -UPPER, etc. \\
+DIST\dotfill & & Distance to host star based on parallax in parsecs & -UPPER, etc. \\
 PAR\dotfill & Float & Parallax in mas & -UPPER,-LOWER,U- \\
@@
 K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps & -UPPER, etc. \\
-T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{c}$-2,440,000$ & -UPPER, etc. \\
+T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{d}$-2,440,000$ & -UPPER, etc. \\
 DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER, etc. \\
 I\dotfill & Float & Orbital inclination in degrees (ZZZ for transiting
-systems only ZZZ still true?) & -UPPER, etc. \\
+systems only) & -UPPER, etc. \\
 MSINI\dotfill & Float & Minimum mass (as calculated from the mass
-function) in $M_{\rm Jup}$ & -UPPER, etc. \\
+function) in \mjup & -UPPER, etc. \\
 A\dotfill & Float & Orbital semimajor axis in AU & -UPPER, etc. \\
-MASS\dotfill & & & -UPPER, etc. \\
-SEP\dotfill & & & -UPPER, etc. \\
+MASS\dotfill & & Mass of planet in \mjup & -UPPER, etc. \\
+SEP\dotfill & & Separation between host star and planet in AU & -UPPER, etc. \\
 TREND\dotfill  & Boolean & Linear trend in fit? & \nodata \\
@@
 \sidehead{\textbf{Transit Parameters}}
-DEPTH\dotfill & Float & $(R_p/R_*)^2$ & -UPPER, etc. \\
+DEPTH\dotfill & Float & Transit depth, $(R_p/R_*)^2$ & -UPPER, etc. \\
 T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER, etc. \\
 TT\dotfill & Float & Epoch of transit center in
-HJD\tablenotemark{c}$-2,440,000$ & -UPPER, etc. \\
-R\dotfill & Float & Radius of the planet in Jupiter radii & -UPPER, etc. \\
-AR\dotfill & $(a/R_*)$ & & -UPPER, etc. \\
+HJD\tablenotemark{d}$-2,440,000$ & -UPPER, etc. \\
+R\dotfill & Float & Radius of planet in Jupiter radii & -UPPER, etc. \\
+AR\dotfill & & $(a/R_*)$ & -UPPER, etc. \\
 B\dotfill & Float & Impact parameter of transit & -UPPER, etc. \\
@@
 -UPPER, etc. \\
-GRAVITY\dotfill & Float & $\log{g}$ (surface gravity) of the planet
-calculated from transit parameters in cgs unit &
+GRAVITY\dotfill & Float & $\log{g}$ (surface gravity) of planet in cgs unit &
 -UPPER, etc. \\
@@
 \sidehead{\textbf{Secondary Eclipse}}
-SE\dotfill & Boolean & If true, at least one secondary eclipse has been detected in the wavelengths listed below & -REF,-URL \\
-SEDEPTHJ\dotfill & & The secondary eclipse depth measured in the near
-infrared J band centered at 1.25 \micron &
--UPPER, etc. \\
-SEDEPTHH\dotfill & & The secondary eclipse depth measured in the near
-infrared H band centered at 1.65 \micron & 
--UPPER, etc. \\
-SEDEPTHKS\dotfill & & The secondary eclipse depth measured in the near
-infrared Ks band centered at 2.15 \micron &
--UPPER, etc. \\
-SEDEPTHKP\dotfill & & The secondary eclipse depth measured in the
-Kepler photometry band in the optical from 400 to 865 nm &
--UPPER, etc. \\
-SEDEPTH36\dotfill & & The secondary eclipse depth measured by
-\spitzer\ in its IRAC1 band centered at 3.6 \micron &
--UPPER, etc. \\
-SEDEPTH45\dotfill & & The secondary eclipse depth measured by \spitzer\
-in its IRAC2 band centered at 4.5 \micron &
--UPPER, etc. \\
-SEDEPTH58\dotfill & & The secondary eclipse depth measured by \spitzer\
-in its IRAC2 band centered at 5.8 \micron & 
--UPPER, etc. \\
-SEDEPTH80\dotfill & & The secondary eclipse depth measured by \spitzer\
-in its IRAC2 band centered at 8.0 \micron &
--UPPER, etc. \\
+SE\dotfill & Boolean & If true, at least one secondary eclipse has
+been detected & -REF,-URL \\
+SEDEPTHJ\dotfill & & Secondary eclipse depth in $J$ band & -UPPER, etc. \\
+SEDEPTHH\dotfill & & Secondary eclipse depth in $H$ band & -UPPER, etc. \\
+SEDEPTHKS\dotfill & & Secondary eclipse depth in $K_{\rm S}$
+band & -UPPER, etc. \\
+SEDEPTHKP\dotfill & & Secondary eclipse depth in the
+\kepler\ photometry band & -UPPER, etc. \\
+SEDEPTH36\dotfill & & Secondary eclipse depth in
+\spitzer\ IRAC1 3.6 \micron\ band & -UPPER, etc. \\
+SEDEPTH45\dotfill & & Secondary eclipse depth in
+\spitzer\ IRAC2 4.5 \micron\ band & -UPPER, etc. \\
+SEDEPTH58\dotfill & & Secondary eclipse depth in
+\spitzer\ IRAC3 5.8 \micron\ band & -UPPER, etc. \\
+SEDEPTH80\dotfill & & Secondary eclipse depth in
+\spitzer\ IRAC4 8.0 \micron\ band & -UPPER, etc. \\
 SET\dotfill & & ZZZ Epoch of secondary eclipse center in
-HJD\tablenotemark{c}$-2,440,000$ ZZZ & -UPPER, etc. \\
-& & & \\ % empty row so that next table section starts on new page
+HJD\tablenotemark{d}$-2,440,000$ & -UPPER, etc. \\
 %
@@
 PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata \\
-STARDISCMETH\dotfill & String & Method of discovery for the first
-planet in the system & \nodata \\
+STARDISCMETH\dotfill & String & Method of discovery of first planet in system & \nodata \\
 DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata \\
@@
 KP\dotfill & & \kepler\ bandpass magnitude & \nodata \\
-SPECREF\dotfill & & Source of most of the spectroscopic parameters
-listed for convenience & SPECURL \\
+SPECREF\dotfill & & Source of most of the spectroscopic parameters & SPECURL \\
 %
@@
 \enddata
-\tablenotetext{a}{XU, XUPPER, XLOWER, XREF, XURL etc.}
-\tablenotetext{b}{Originally as other commonly used name for star in \cite{Wright2011};
+\tablenotetext{a}{Fields in bold are updates or new additions from
+  \cite{Wright2011}. See Section~\ref{sec:update} for more details.}
+\tablenotetext{b}{XU, XUPPER, XLOWER, XREF, XURL etc.}
+\tablenotetext{c}{Originally as other commonly used name for star in \cite{Wright2011};
   changed to other commonly used name for planet.}
-\tablenotetext{c}{ZZZ Is this now consistent? ZZZ}
+\tablenotetext{d}{ZZZ Is this now consistent? ZZZ}
 \end{deluxetable}

### 2013-12-29 draft/ms.tex
Refine structure of paper: add subsections and section outlines. Update new_table_items.txt: REF and URL and misc.

@@
   Lab, The Pennsylvania State University, University Park, PA 16802, USA;
-  Send correspondence to Eunkyu Han at hek90625@gmail.com.}
+  Send correspondence to datamaster@exoplanets.org.}
 \altaffiltext{2}{Center for Exoplanets and Habitable Worlds, The
@@
 
-Restrict the updates in this section on EOD updates.
+Restrict the updates in this section on EOD updates. We only report
+new additions and revised fields here. For details on other fields,
+see \cite{Wright2011}. We divide the fields into categories in
+consistency with the interactive table on exoplanets.org. Some fields
+are not explicitly included in the interactive table (e.g., the URLs), but are
+explicitly listed in the downloadable {\tt .csv} file.\footnote{The
+  entire dataset provided by exoplanets.org is available for download in a
+  single CSV file at \url{http://exoplanets.org/csv-files/exoplanets.csv}}
 
-Parameter updates, new table parameters etc. What other updates are there?
+%------------------------------------------------------------------------------
+\subsection{Planet Information}
+
+Added fields since \cite{Wright2011}:
+
+KEPID
+
+KOI
+
+KDE
+
+EOD
+
+MICROLENSING, IMAGING, TIMING and ASTROMETRY
+
+%------------------------------------------------------------------------------
+\subsection{Stellar Parameters}
+
+Added fields since \cite{Wright2011}:
+
+DIST
+
+GAMMA
+
+%------------------------------------------------------------------------------
+\subsection{Orbit Parameters}
+
+Added fields since \cite{Wright2011}:
+
+MASSS
+
+SEP
+
+BIGOM
+
+%------------------------------------------------------------------------------
+\subsection{Transit Parameters}
+
+Added fields since \cite{Wright2011}:
+
+DR
+
+RR
+
+%------------------------------------------------------------------------------
+\subsection{Secondary Eclipse}
+
+This is a entire new set of fields since \cite{Wright2011}:
+
+SE
+
+SEDEPTH J H KS KP 36 45 58 80
+
+SET
+
+%------------------------------------------------------------------------------
+\subsection{Stellar Properties}
+
+Difference from Stellar Parameters: these are derived parameters based
+on spectroscopy and stellar models.
+Added fields since \cite{Wright2011}:
+
+RSTAR
+
+RHOSTAR
+
+KP
+
+%------------------------------------------------------------------------------
+\subsection{Uncertainties}
+
+We now report uncertainties for a certain field X as XUPPER, XLOWER
+and UX. XUPPER and XLOWER store the upper and lower ZZZ 1$\sigma$ ZZZ
+uncertainties, and they are different when the error bars are
+asymmetric. UX contains the ZZZ 1$\sigma$ ZZZ uncertainty, and it
+equals to $({\rm XUPPER+XLOWER})/2$ in the case of asymmetric error
+bars. Fields that have XUPPER, XLOWER and UX are: (list of fields).
+
+%------------------------------------------------------------------------------
+\subsection{References}
+
+Added field: ZZZ MONTH ZZZ, PLANETDISCMETH, STARDISCMETH.
+
+The fields XREF and XURL store the peer-reviewed reference and link to
+the publication for the field X. The following fields now have XREF
+and XURL: (previously in \citealt{Wright2011}) DIST, TRANSIT, BINARY;
+(new) fields in stellar parameters: V\footnote{ZZZ VREF and VURL are
+  also for J, H, KS. ZZZ}, VSINI, GAMMA; all orbit pars except for
+trend and freeze\_ecc; all transit parameters; all SE parameters;
+fields for stellar properties: MSTAR, RSTAR, TEFF, RHOSTAR, LOGG, FE.
+
+Other general reference fields: In \cite{Wright2011}: FIRSTREF,
+FIRSTURL, ORBREF, ORBURL. New: SPECREF, SPECURL contain source of most
+of the spectroscopic parameters listed for convenience; actual
+references in the REF fields take precedence over this one.
+
+%------------------------------------------------------------------------------
+\subsection{Revised and Removed Fields}
+
+These include:
+
+OTHERNAME - This is now listed as other name of planet instead of star;
+
+DISCMETH - replaced by planetdiscmeth and stardiscmeth;
+
+S - changed to SHK;
+
+SPSTAR - stellar type of star (unvetted), gone;
+
+NSTEDID - replaced by EANAME (Exoplanet Archive).
+
+MASSREF, MASSURL - originally for stellar mass reference, now for planet mass.
 
@@
 
-%------------------------------------------------------------------------------
-\subsection{Revised and Removed Fields}
-These include:
-OTHERNAME - This is now listed as other name of planet instead of star;
-DISCMETH - replaced by planetdiscmeth and stardiscmeth;
-S - changed to SHK;
-SPSTAR - stellar type of star (unvetted), gone;
-NSTEDID - replaced by EANAME (Exoplanet Archive).
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Inclusion of the Kepler Planet Candidates and Other Exoplanets on Exoplanets.org}\label{sec:kepler}
+
+We now include \kepler\ candidates...
+
+We also include planets discovered microlensing, imaging, timing,
+astrometric motion. Some microlensing and imaging planets are not
+included in the EOD because of poorly characterized orbits...
 

### 2014-01-01 draft/ms.tex
Refine structure and details, add outline for introduction.

@@
 \author{Jason T. Wright\altaffilmark{1,2,3}}
+\author{Ying Feng\altaffilmark{1,2}}
 \author{Ming Zhao\altaffilmark{1,2}}
+\author{Onsi Fakhouri}
 \author{and Friends}
@@
 
-The introduction Section...
+Recent development of exoplanet discoveries, especially
+\kepler\ discoveries.
+
+The business of keeping track of exoplanet discoveries, where EOD
+stands, and a brief history of EOD.
+
+What this paper is about: an update on EOD and the services our
+website, exoplanets.org, provide.
 
@@
 
-Restrict the updates in this section on EOD updates. We only report
-new additions and revised fields here. For details on other fields,
-see \cite{Wright2011}. We divide the fields into categories in
-consistency with the interactive table on exoplanets.org. Some fields
-are not explicitly included in the interactive table (e.g., the URLs), but are
-explicitly listed in the downloadable {\tt .csv} file.\footnote{The
-  entire dataset provided by exoplanets.org is available for download in a
-  single CSV file at \url{http://exoplanets.org/csv-files/exoplanets.csv}}
+Scope of EOD has changed in the following ways:
+
+1. Definition of planets: not strictly smaller than 24 \mjup\ any
+more? Or still true?
+
+2. Host stars: not only `normal stars' any more?
+
+3. Change on definition of `well-determined' orbital parameters?
+
+4. Inclusion of planets discovered beyond RV and transit.
+
+Purposes of EOD have not changed?
+
+We only report new additions and revised fields here. For details on
+other fields, see \cite{Wright2011}. We divide the fields into
+categories in consistency with the interactive table on
+exoplanets.org. Some fields are not explicitly included in the
+interactive table (e.g., the URLs), but are explicitly listed in the
+downloadable {\tt .csv} file.\footnote{The entire dataset provided by
+  exoplanets.org is available for download in a single CSV file at
+  \url{http://exoplanets.org/csv-files/exoplanets.csv}}
 
@@
 and XURL: (previously in \citealt{Wright2011}) DIST, TRANSIT, BINARY;
-(new) fields in stellar parameters: V\footnote{ZZZ VREF and VURL are
-  also for J, H, KS. ZZZ}, VSINI, GAMMA; all orbit pars except for
+(new) fields in stellar parameters: V, VSINI, GAMMA; all orbit pars except for
 trend and freeze\_ecc; all transit parameters; all SE parameters;
@@
 
-S - changed to SHK;
+S - changed to SHK; What's the source for SHK and RHK? Still discovery
+paper and Butler 2006?
 
@@
 
-We now include \kepler\ candidates...
+We now include \kepler\ candidates... They can be displayed by
+checking the `Kepler' option for the interactive data table.
 
-We also include planets discovered microlensing, imaging, timing,
-astrometric motion. Some microlensing and imaging planets are not
-included in the EOD because of poorly characterized orbits...
+We also include robustly detected planets discovered microlensing,
+imaging, timing, astrometric motion. They can be displayed by check
+the `Other' option for the table. They are not included in the EOD
+(especially some microlensing and imaging planets) because of poorly
+characterized orbits...
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}\label{sec:conclusion}
+\section{Updates on the Website}
+
+Onsi? Essential updates on the website.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion and Future}\label{sec:conclusion}
+
+Any planned future improvements and updates?
 
@@
 \acknowledgments
+
+NSF funding?
+
+SXW acknowledges support from PSARC.
 
@@
 SEDEPTHH\dotfill & & Secondary eclipse depth in $H$ band & -UPPER, etc. \\
-SEDEPTHKS\dotfill & & Secondary eclipse depth in $K_{\rm S}$
+SEDEPTHKS\dotfill & & Secondary eclipse depth in $K_S$
 band & -UPPER, etc. \\
@@
   \cite{Wright2011}. See Section~\ref{sec:update} for more details.}
-\tablenotetext{b}{XU, XUPPER, XLOWER, XREF, XURL etc.}
+\tablenotetext{b}{-UPPER etc. means ``-UPPER, -LOWER, U-, -REF, -URL",
+where ``-" stands for the name of the field listed in the first
+column. They are...}
 \tablenotetext{c}{Originally as other commonly used name for star in \cite{Wright2011};

### 2014-01-24 draft/ms.tex
Minor content revisions, add references.
update

@@
 
-KOI
+KOI:
 
@@
 
-EOD
+EOD: Planets discovered by radial velocity and transit method are classified as EOD planets. They have robust orbital parameters such as PER, ECC, K, OM, and I.
 
-MICROLENSING, IMAGING, TIMING and ASTROMETRY
+MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENSING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by methods other than radial velocity and transit.
+These planets are categorized as ``Other Planets"  on exoplanets.org
 
@@
 
-DIST
+DIST: actually, DIST is not added since Wright 2011 (It was just left out)
 
@@
 
-MASSS
+MASS: Previously, we only reported the minimum mass (MSINI) of the planets.
+We now report mass of the planet in the unit of Jupiter mass.
+If a planet is discovered by transit, the planet mass is given by the literature.
+However, if a planet is detected by radial velocity method, the minimum mass is given in which case we calculate the mass by dividing the minimum mass by the orbit inclination.
+MASS is set to MSINI if the orbital inclination is not given and the MASSREF is set to``Set to MSINI; I unknown"
 
@@
 BIGOM
+
+LAMBDA: We report the projected spin-orbit misalignment of transiting systems. We follow the definition of Fabrycky and Winn 2009.
 
@@
 
-S - changed to SHK; What's the source for SHK and RHK? Still discovery
+S - changed to SHK; ZZZ What's the source for SHK and RHK? Still discovery
 paper and Butler 2006?
@@
 DEC\_STRING\dotfill & String & J2000 declination in sexagesimal string & \nodata \\
-KEPID\dotfill & & The unique \kepler\ star identifier & \nodata \\
-KOI\dotfill & & KOI object number & \nodata \\
+KEPID\dotfill & Long Integer & The unique \kepler\ star identifier & \nodata \\
+KOI\dotfill & Float & KOI object number & \nodata \\
 KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata \\
@@
 KS\dotfill & Float & $K_S$ magnitude & \nodata \\
-DIST\dotfill & & Distance to host star based on parallax in parsecs & -UPPER, etc. \\
+DIST\dotfill & Float & Distance to host star based on parallax in parsecs & -UPPER, etc. \\
 PAR\dotfill & Float & Parallax in mas & -UPPER,-LOWER,U- \\
@@
 A\dotfill & Float & Orbital semimajor axis in AU & -UPPER, etc. \\
-MASS\dotfill & & Mass of planet in \mjup & -UPPER, etc. \\
-SEP\dotfill & & Separation between host star and planet in AU & -UPPER, etc. \\
+MASS\dotfill & Float & Mass of planet in \mjup & -UPPER, etc. \\
+SEP\dotfill & Float & Separation between host star and planet in AU & -UPPER, etc. \\
 TREND\dotfill  & Boolean & Linear trend in fit? & \nodata \\
 LAMBDA\dotfill & Float & Projected spin-orbit misalignment in degrees & -UPPER, etc. \\
-BIGOM\dotfill & & Longitude of ascending node in degrees & -UPPER, etc. \\
+BIGOM\dotfill & Float & Longitude of ascending node in degrees & -UPPER, etc. \\
 FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \nodata \\
@@
 R\dotfill & Float & Radius of planet in Jupiter radii & -UPPER, etc. \\
-AR\dotfill & & $(a/R_*)$ & -UPPER, etc. \\
+AR\dotfill & Float & $(a/R_*)$ & -UPPER, etc. \\
 B\dotfill & Float & Impact parameter of transit & -UPPER, etc. \\
@@
 TRANSIT\dotfill & Boolean & Is the planet known to transit? & -REF,-URL \\
-DR\dotfill & & Distance during transit in stellar radii & -UPPER, etc. \\
-RR\dotfill & & $(R_p/R_*)$ & -UPPER, etc. \\
+DR\dotfill & Float & Distance during transit in stellar radii & -UPPER, etc. \\
+RR\dotfill & Float & $(R_p/R_*)$ & -UPPER, etc. \\
 %
@@
 been detected & -REF,-URL \\
-SEDEPTHJ\dotfill & & Secondary eclipse depth in $J$ band & -UPPER, etc. \\
-SEDEPTHH\dotfill & & Secondary eclipse depth in $H$ band & -UPPER, etc. \\
-SEDEPTHKS\dotfill & & Secondary eclipse depth in $K_S$
+SEDEPTHJ\dotfill & Double & Secondary eclipse depth in $J$ band & -UPPER, etc. \\
+SEDEPTHH\dotfill & Double & Secondary eclipse depth in $H$ band & -UPPER, etc. \\
+SEDEPTHKS\dotfill & Double & Secondary eclipse depth in $K_S$
 band & -UPPER, etc. \\
-SEDEPTHKP\dotfill & & Secondary eclipse depth in the
+SEDEPTHKP\dotfill & Double & Secondary eclipse depth in the
 \kepler\ photometry band & -UPPER, etc. \\
-SEDEPTH36\dotfill & & Secondary eclipse depth in
+SEDEPTH36\dotfill & Double & Secondary eclipse depth in
 \spitzer\ IRAC1 3.6 \micron\ band & -UPPER, etc. \\
-SEDEPTH45\dotfill & & Secondary eclipse depth in
+SEDEPTH45\dotfill & Double  & Secondary eclipse depth in
 \spitzer\ IRAC2 4.5 \micron\ band & -UPPER, etc. \\
-SEDEPTH58\dotfill & & Secondary eclipse depth in
+SEDEPTH58\dotfill & Double  & Secondary eclipse depth in
 \spitzer\ IRAC3 5.8 \micron\ band & -UPPER, etc. \\
-SEDEPTH80\dotfill & & Secondary eclipse depth in
+SEDEPTH80\dotfill & Double & Secondary eclipse depth in
 \spitzer\ IRAC4 8.0 \micron\ band & -UPPER, etc. \\
-SET\dotfill & & ZZZ Epoch of secondary eclipse center in
+SET\dotfill & Double & ZZZ Epoch of secondary eclipse center in
 HJD\tablenotemark{d}$-2,440,000$ & -UPPER, etc. \\
@@
 MSTAR\dotfill & Float & Mass of host star in solar mass & -UPPER, etc. \\
-RSTAR\dotfill & & Radius of host star in solar radii & -UPPER, etc. \\
+RSTAR\dotfill & Float & Radius of host star in solar radii & -UPPER, etc. \\
 TEFF\dotfill & Float & Effective temperature of host star & -UPPER, etc. \\
-RHOSTAR\dotfill & & Density of host star & -UPPER, etc. \\
+RHOSTAR\dotfill & Float & Density of host star & -UPPER, etc. \\
 LOGG\dotfill & Float & Spectroscopic $\log{g}$ (surface gravity) of
@@
 RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \nodata \\
-KP\dotfill & & \kepler\ bandpass magnitude & \nodata \\
-SPECREF\dotfill & & Source of most of the spectroscopic parameters & SPECURL \\
+KP\dotfill & Float & \kepler\ bandpass magnitude & \nodata \\
+SPECREF\dotfill & String & Source of most of the spectroscopic parameters & SPECURL \\
 %

### 2014-01-24 draft/ms.tex

--- 2014-01-01 draft/ms.tex
@@
 
+According to Google Analytics, $47,000$ people visited exoplanets.org
+in 2013.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We only report new additions and revised fields here. For details on
-other fields, see \cite{Wright2011}. We divide the fields into
-categories in consistency with the interactive table on
-exoplanets.org. Some fields are not explicitly included in the
+We only describe new additions and revised fields here, but list all
+fields. For details on other fields, see \cite{Wright2011}. We divide
+the fields into categories in consistency with the interactive table
+on exoplanets.org. Some fields are not explicitly included in the
 interactive table (e.g., the URLs), but are explicitly listed in the
@@
 
-MASSS
+MASS: we use mass-radius relation to get mass.
 
@@
 BIGOM
+
+LAMBDA: the literature has conflicted definitions of LAMBDA, and we
+sorted it out and made sure it is consistent in EOD.
+
+I: it used to be for transit systems only. Now sometimes for
+non-transiting systems the values of I are also available.
 
@@
 We now report uncertainties for a certain field X as XUPPER, XLOWER
-and UX. XUPPER and XLOWER store the upper and lower ZZZ 1$\sigma$ ZZZ
+and UX. XUPPER and XLOWER store the upper and lower 1$\sigma$
 uncertainties, and they are different when the error bars are
-asymmetric. UX contains the ZZZ 1$\sigma$ ZZZ uncertainty, and it
+asymmetric. UX contains the 1$\sigma$ uncertainty, and it
 equals to $({\rm XUPPER+XLOWER})/2$ in the case of asymmetric error
@@
 
-Added field: ZZZ MONTH ZZZ, PLANETDISCMETH, STARDISCMETH.
+Added field: MONTH, PLANETDISCMETH, STARDISCMETH.
 
@@
 fields for stellar properties: MSTAR, RSTAR, TEFF, RHOSTAR, LOGG, FE.
+
+VREF is not the same as REF for J H KS, which do not have XREF
+fields. See \cite{Wright2011} for references of J H KS mags -- I think
+he mentioned it there.
 
@@
 
-S - changed to SHK; What's the source for SHK and RHK? Still discovery
-paper and Butler 2006?
+S - changed to SHK; ZZZ What's the source for SHK and RHK? Still discovery
+paper and Butler 2006? ZZZ SHK is a poorly maintained field, and it is
+unreferenced at the moment though we plan to include propoer reference
+in the future.
 
@@
 DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER, etc. \\
-I\dotfill & Float & Orbital inclination in degrees (ZZZ for transiting
-systems only) & -UPPER, etc. \\
+I\dotfill & Float & Orbital inclination in degrees & -UPPER, etc. \\
 MSINI\dotfill & Float & Minimum mass (as calculated from the mass
@@
 \spitzer\ IRAC4 8.0 \micron\ band & -UPPER, etc. \\
-SET\dotfill & & ZZZ Epoch of secondary eclipse center in
+SET\dotfill & & Epoch of secondary eclipse center in
 HJD\tablenotemark{d}$-2,440,000$ & -UPPER, etc. \\
@@
 DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata \\
-ZZZ MONTH ZZZ\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\
+MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\
 FIRSTREF\dotfill & String & First peer-reviewed publication of
@@
   changed to other commonly used name for planet.}
-\tablenotetext{d}{ZZZ Is this now consistent? ZZZ}
+\tablenotetext{d}{The same as in \cite{Wright2011}, HJD/BJD etc.\ are
+  still not consistent.}
 \end{deluxetable}

### 2014-01-24 draft/ms.tex
Update

@@
 
-EOD
+EOD: Planets discovered by radial velocity and transit method are classified as EOD planets. They have robust orbital parameters such as PER, ECC, K, OM, and I.
 
-MICROLENSING, IMAGING, TIMING and ASTROMETRY
+MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENS- ING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by methods other than radial velocity and transit.
+These planets are categorized as ``Other Planets'' on exoplanets.org
 
@@
 
-MASS: we use mass-radius relation to get mass.
+MASS: Previously, we only reported the minimum mass (MSINI) of the planets.
+We now report mass of the planet in the unit of Jupiter mass.
+If a planet is discovered by transit, the planet mass is given by the literature.
+However, if a planet is detected by radial velocity method, the minimum mass is given in which case we calculate the mass by dividing the minimum mass by the orbit inclination.
+MASS is set to MSINI if the orbital inclination is not given and the MASSREF is set to ``Set to MSINI; I unknown''
+
+MASS: we use mass-radius relation to get mass. =>stellar mass?
 
@@
 sorted it out and made sure it is consistent in EOD.
+
+LAMBDA: We report the projected spin-orbit misalignment of transiting systems. We follow the definition of Fabrycky and Winn 2009.
 

### 2014-01-24 draft/ms.tex
Conflict test: modify MASS description.

@@
 
-MASS: Previously, we only reported the minimum mass (MSINI) of the planets.
-We now report mass of the planet in the unit of Jupiter mass.
-If a planet is discovered by transit, the planet mass is given by the literature.
-However, if a planet is detected by radial velocity method, the minimum mass is given in which case we calculate the mass by dividing the minimum mass by the orbit inclination.
-MASS is set to MSINI if the orbital inclination is not given and the MASSREF is set to ``Set to MSINI; I unknown''
+MASS: Previously, we only reported the minimum mass (MSINI) of the
+planets. We now report mass of the planet in the unit of Jupiter
+mass. If a planet is discovered by transit, the planet mass is given
+by the literature. However, if a planet is detected by radial velocity
+method, the minimum mass is given in which case we calculate the mass
+by dividing the minimum mass by the orbit inclination. MASS is set to
+MSINI if the orbital inclination is not given and the MASSREF is set
+to ``Set to MSINI; I unknown''.
 
-MASS: we use mass-radius relation to get mass. =>stellar mass?
+MASS: For KOIs without MSINI measured, Exoplanet Archive reports MASS
+based on converting radius into mass.
 

### 2014-01-24 draft/ms.tex
conflict test
Comments in Sec 2.1 and small notes in Sec 2 and 3

@@
 1. Definition of planets: not strictly smaller than 24 \mjup\ any
-more? Or still true?
+more? Or still true? We still require smaller than 24 \mjup.
 
-2. Host stars: not only `normal stars' any more?
+2. Host stars: not only `normal stars' any more? Not any more -
+neutron stars are there (at least)! This requirement is completely gone.
 
-3. Change on definition of `well-determined' orbital parameters?
+3. Change on definition of `well-determined' orbital parameters? No. Still
+qualitative, still the same as described in Section~2 of \cite{Wright2011}.
 
@@
   exoplanets.org is available for download in a single CSV file at
-  \url{http://exoplanets.org/csv-files/exoplanets.csv}}
+  \url{http://exoplanets.org/csv-files/exoplanets.csv}} Make a note
+here that though we focus on EOD in this Section, the fields apply to
+all planets on exoplanets.org.
 
@@
 
-KEPID
+KEPID: None of EOD planets has KEPID! This is just something we copied
+from Exoplanet Archive...
 
@@
 
-EOD: Planets discovered by radial velocity and transit method are classified as EOD planets. They have robust orbital parameters such as PER, ECC, K, OM, and I.
+EOD: Planets discovered by radial velocity and transit method are
+classified as EOD planets. They have robust orbital parameters such as
+PER, ECC, K, OM, and I. \textit{(Sharon's comments: You don't need to
+  describe why we include a planet in EOD -- this is covered at the
+  beginning of Section~\ref{sec:update} as we discuss the `scope of
+  EOD'. Just say what this flag is. Also, right now it includes RV,
+  Transit, and also some Timing planets. The first sentence sounds
+  like as long as a planet is discovered via RV and transit, it'll be
+  in EOD, which is not true, I think.)}
 
-MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENS- ING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by methods other than radial velocity and transit.
-These planets are categorized as ``Other Planets'' on exoplanets.org
+MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENS-
+ING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by
+methods other than radial velocity and transit. These planets are
+categorized as ``Other Planets'' on exoplanets.org. \textit{(Sharon's
+  comments: Instead of saying `discovered', we should say `detected'
+  -- some planets are detected by these methods but are not
+  necessarily discovered by them at the first place. Re-phrase the
+  last sentence -- not all of planets with any of these TRUE are in
+  `Other Planets', only some are, so maybe just note planets
+  discovered by these methods are not necessarily in EOD and direct
+  the reader to Section~\ref{sec:kepler} where we talk about `Other
+  Planets'. Remember Section~\ref{sec:update} is focuses on EOD
+  updates though the fields apply to all planets on
+  exoplanets.org. Need to note here that we require the detection to
+  be robust, as determined by the QUAlity Control Board of the
+  Exoplanet Database, QUACBED.)}
 
@@
 characterized orbits...
+
+Also add our criteria for vetting IMAGING planets, which can be found
+here: http://exoplanets.org/methodology.html; do we have any similar
+criteria for Microlensing, timing and astrometry planets? Like mass
+cut etc.?
 

### 2014-01-24 draft/ms.tex
Filled out the table and edited section 2.1

--- 2014-01-24 draft/ms.tex
@@
 
+We report basic planet information to give our users general information of when, by whom and how the planets were discovered.
+Since \cite{Wright2011}, as more planets were discovered by different methods other than radial velocity and transit, we have expanded this information to better ingest those planets into our database.
+
 Added fields since \cite{Wright2011}:
 
-KEPID
+KEPID: For KOIs, the Exoplanet Archive reports Kepler ID.
 
@@
 
-MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENS- ING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by methods other than radial velocity and transit.
+MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENSING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by methods other than radial velocity and transit.
 These planets are categorized as ``Other Planets'' on exoplanets.org
@@
 star in k\mps & -UPPER, etc. \\
-GAMMA\dotfill & & Systemic radial velocity in k\mps & -UPPER, etc. \\
+GAMMA\dotfill & Float & Systemic radial velocity in k\mps & -UPPER, etc. \\
 %
@@
 been detected & -REF,-URL \\
-SEDEPTHJ\dotfill & & Secondary eclipse depth in $J$ band & -UPPER, etc. \\
-SEDEPTHH\dotfill & & Secondary eclipse depth in $H$ band & -UPPER, etc. \\
-SEDEPTHKS\dotfill & & Secondary eclipse depth in $K_S$
+SEDEPTHJ\dotfill & Float & Secondary eclipse depth in $J$ band & -UPPER, etc. \\
+SEDEPTHH\dotfill & Float & Secondary eclipse depth in $H$ band & -UPPER, etc. \\
+SEDEPTHKS\dotfill & Float & Secondary eclipse depth in $K_S$
 band & -UPPER, etc. \\
-SEDEPTHKP\dotfill & & Secondary eclipse depth in the
+SEDEPTHKP\dotfill & Float & Secondary eclipse depth in the
 \kepler\ photometry band & -UPPER, etc. \\
-SEDEPTH36\dotfill & & Secondary eclipse depth in
+SEDEPTH36\dotfill & Float & Secondary eclipse depth in
 \spitzer\ IRAC1 3.6 \micron\ band & -UPPER, etc. \\
-SEDEPTH45\dotfill & & Secondary eclipse depth in
+SEDEPTH45\dotfill & Float & Secondary eclipse depth in
 \spitzer\ IRAC2 4.5 \micron\ band & -UPPER, etc. \\
-SEDEPTH58\dotfill & & Secondary eclipse depth in
+SEDEPTH58\dotfill & Float & Secondary eclipse depth in
 \spitzer\ IRAC3 5.8 \micron\ band & -UPPER, etc. \\
-SEDEPTH80\dotfill & & Secondary eclipse depth in
+SEDEPTH80\dotfill & Float & Secondary eclipse depth in
 \spitzer\ IRAC4 8.0 \micron\ band & -UPPER, etc. \\
-SET\dotfill & & Epoch of secondary eclipse center in
+SET\dotfill & Double & Epoch of secondary eclipse center in
 HJD\tablenotemark{d}$-2,440,000$ & -UPPER, etc. \\

### 2014-01-24 draft/ms.tex

@@
 
-KEPID: For KOIs, the Exoplanet Archive reports Kepler ID.
+KEPID: None of EOD planets has KEPID! This is just something we copied
+from Exoplanet Archive...
 
@@
 
-EOD: Planets discovered by radial velocity and transit method are classified as EOD planets. They have robust orbital parameters such as PER, ECC, K, OM, and I.
+EOD: Planets discovered by radial velocity and transit method are
+classified as EOD planets. They have robust orbital parameters such as
+PER, ECC, K, OM, and I. \textit{(Sharon's comments: You don't need to
+  describe why we include a planet in EOD -- this is covered at the
+  beginning of Section~\ref{sec:update} as we discuss the `scope of
+  EOD'. Just say what this flag is. Also, right now it includes RV,
+  Transit, and also some Timing planets. The first sentence sounds
+  like as long as a planet is discovered via RV and transit, it'll be
+  in EOD, which is not true, I think.)}
 
-MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENSING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by methods other than radial velocity and transit.
-These planets are categorized as ``Other Planets'' on exoplanets.org
+MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENS-
+ING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by
+methods other than radial velocity and transit. These planets are
+categorized as ``Other Planets'' on exoplanets.org. \textit{(Sharon's
+  comments: Instead of saying `discovered', we should say `detected'
+  -- some planets are detected by these methods but are not
+  necessarily discovered by them at the first place. Re-phrase the
+  last sentence -- not all of planets with any of these TRUE are in
+  `Other Planets', only some are, so maybe just note planets
+  discovered by these methods are not necessarily in EOD and direct
+  the reader to Section~\ref{sec:kepler} where we talk about `Other
+  Planets'. Remember Section~\ref{sec:update} is focuses on EOD
+  updates though the fields apply to all planets on
+  exoplanets.org. Need to note here that we require the detection to
+  be robust, as determined by the QUAlity Control Board of the
+  Exoplanet Database, QUACBED.)}
 

### 2014-02-03 draft/ms.tex
Test
Added descriptions for KOI, EOD, and etc

@@
 
+TEST!
+
 Scope of EOD has changed in the following ways:
@@
 
-KOI
+KOI: KOI represents `Kepler Objects of Interest', which are planet candidates that have not been confirmed.
 
@@
 
-EOD: Planets discovered by radial velocity and transit method are
-classified as EOD planets. They have robust orbital parameters such as
-PER, ECC, K, OM, and I. \textit{(Sharon's comments: You don't need to
+EOD: EOD flag indicates planets with good Keplerian orbits. They have robust orbital parameters such as PER, ECC, K, OM, and I.
+
+\textit{(Sharon's comments: You don't need to
   describe why we include a planet in EOD -- this is covered at the
@@
 MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENS-
-ING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by
-methods other than radial velocity and transit. These planets are
-categorized as ``Other Planets'' on exoplanets.org. \textit{(Sharon's
+ING, IMAGING, TIMING and ASTROMETRY fields for planets detected by
+methods other than radial velocity and transit.
+Since planets detected by these methods do not have robust orbital parameters, they are categorized as ``Other Planets'' on exoplanets.org.
+However, if planets have follow up radial velocity or transit observations and thus have good orbital parameters, they have EOD flags.
+See Section~\ref{sec:kepler} for more information about `Other Planets'.
+
+\textit{(Sharon's
   comments: Instead of saying `discovered', we should say `detected'
@@
 DIST: actually, DIST is not added since Wright 2011 (It was just left out)
+We report distance of the host star in the unit of pc.
 
@@
 
+We now report the month when the peer-reviewed paper is accepted to ApJ to better track of the trend in exoplanetary detections.
+Moreover, we report the discovery methods for the host star and the planet separately: STARDISCMETH and PLANETDISCMETH.
+See Section~ for more details.
+
 %------------------------------------------------------------------------------
@@
 
-DISCMETH - replaced by planetdiscmeth and stardiscmeth;
+DISCMETH - We have replaced DISCMETH with PLANETDISCMETH and STARDISCMETH to better report how the host star and the planet are detected.
 

### 2014-02-04 draft/ms.tex
Adds comments for Sec 2.1.

@@
 
-TEST!
-
 Scope of EOD has changed in the following ways:
@@
 
-We report basic planet information to give our users general information of when, by whom and how the planets were discovered.
-Since \cite{Wright2011}, as more planets were discovered by different methods other than radial velocity and transit, we have expanded this information to better ingest those planets into our database.
+We report basic planet information to give our users general
+information of when, by whom and how the planets were
+discovered. Since \cite{Wright2011}, as more planets were discovered
+by different methods other than radial velocity and transit, we have
+expanded this information to better ingest those planets into our
+database.
 
 Added fields since \cite{Wright2011}:
+
+\textit{Sharon: I don't think the first sentence is true... Looking at
+  the fields in the Planet Information section in the table, it
+  doesn't contain when who or how at all... The current way of
+  dividing fields into these categories is a bit weird, but we are
+  definitely not changing it in our paper or change the website any
+  time soon... I'm guessing you want to summarize what Planet
+  Information fields cover in the first sentence here, so maybe look
+  at the table and give a very general summary of what those fields
+  are.
+
+  I'm not sure what's the purpose of the second sentence... It sounds
+  like something we generally did for EOD. Maybe we should move it to
+  the paragraph above in the overview text for
+  Section~\ref{sec:update}. Think more about what the purpose of the
+  subsection overview should serve.}
 
@@
 
-KDE
+\textit{Sharon: you need to say what KOI stores. When writing each
+  field, keep in mind you need to cover the following so that the
+  reader will completely understand: (1) what the field stands for
+  (e.g., in case of an abbreviation like KOI); (2) what the field
+  physically means, like `KOI' means planet candidates that have transit
+  signals as detected by \kepler\ but have not been confirmed, and
+  make sure to be thorough at what you say -- sometimes things are not
+  that obvious to an outsider reader, e.g., think if a cosmologist
+  would understand what you're saying when reading it; (3) what the
+  field actually contains, e.g. KOI contains the KOI number designated
+  by the \kepler\ team (right?), it is a floating point number, and
+  sometimes maybe even worth giving an example, e.g. KOI 30.1 or
+  something...; (4) why we added this new field, if this information
+  is helpful, or if it's a revised field since \cite{Wright2011}, what
+  is changed.
 
-EOD: EOD flag indicates planets with good Keplerian orbits. They have robust orbital parameters such as PER, ECC, K, OM, and I.
+  Also, use \keper\ (which is a defined symbol in our ms.tex file),
+  instead of typing out Kepler, since you need italic.
 
-\textit{(Sharon's comments: You don't need to
-  describe why we include a planet in EOD -- this is covered at the
-  beginning of Section~\ref{sec:update} as we discuss the `scope of
-  EOD'. Just say what this flag is. Also, right now it includes RV,
-  Transit, and also some Timing planets. The first sentence sounds
-  like as long as a planet is discovered via RV and transit, it'll be
-  in EOD, which is not true, I think.)}
+  Don't be afraid to write more! Being concise is important, but it's
+  always easier to trim down things than to add things on, especially
+  for a documentation type of paper like this. Let's be thorough at
+  first, then try to reach optimal conciseness. }
+
+KDE:
+
+EOD: EOD flag indicates planets with good Keplerian orbits. They have
+robust orbital parameters such as PER, ECC, K, OM, and I.
+
+EOD: A planet with the EOD flag being true indicates that it has
+well-characterized orbital parameters such as PER, ECC, K, OM, and I
+and is thus included in the EOD. We added this field because
+exoplanets.org now also includes robustly discovered planets that do
+not have well-characterized orbits, and also \kepler\ planet
+candidates (see Section~\ref{sec:kepler} for more details).
+
+\textit{Sharon: I've provided my version here: the stuff I added on
+  top of your writing is what I think was missing and may make a
+  cosmologist wonder. ;)
+
+  Also, EOD doesn't require the orbit to be 'Keplerian', right? We do
+  include reported dynamic fits - they're definitely not
+  Keplerian. Am I right?
+
+  Note that I've covered all the 4 aspects I mentioned above. :)}
 
@@
 ING, IMAGING, TIMING and ASTROMETRY fields for planets detected by
-methods other than radial velocity and transit.
-Since planets detected by these methods do not have robust orbital parameters, they are categorized as ``Other Planets'' on exoplanets.org.
-However, if planets have follow up radial velocity or transit observations and thus have good orbital parameters, they have EOD flags.
-See Section~\ref{sec:kepler} for more information about `Other Planets'.
+methods other than radial velocity and transit. Since planets detected
+by these methods do not have robust orbital parameters, they are
+categorized as ``Other Planets'' on exoplanets.org. However, if
+planets have follow up radial velocity or transit observations and
+thus have good orbital parameters, they have EOD flags. See
+Section~\ref{sec:kepler} for more information about `Other Planets'.
 
-\textit{(Sharon's
+\textit{Sharon: you've changed `discovered' to `detected', but it's
+  still not an accurate description. Let's meet and discuss this in
+  person.
+
+  old: Sharon's
   comments: Instead of saying `discovered', we should say `detected'
@@
   be robust, as determined by the QUAlity Control Board of the
-  Exoplanet Database, QUACBED.)}
+  Exoplanet Database, QUACBED.}
 
@@
 
-We now report the month when the peer-reviewed paper is accepted to ApJ to better track of the trend in exoplanetary detections.
-Moreover, we report the discovery methods for the host star and the planet separately: STARDISCMETH and PLANETDISCMETH.
-See Section~ for more details.
+We now report the month when the peer-reviewed paper is accepted to
+ApJ to better track of the trend in exoplanetary detections. Moreover,
+we report the discovery methods for the host star and the planet
+separately: STARDISCMETH and PLANETDISCMETH. See Section~ for more
+details.
 

### 2014-02-10 draft/ms.tex
Stellar parameter and KOI sections update

@@
   are.
-
   I'm not sure what's the purpose of the second sentence... It sounds
@@
 
-KOI: KOI represents `Kepler Objects of Interest', which are planet candidates that have not been confirmed.
+KOI: KOI represents `Kepler Objects of Interest' which is a star suspected to host transiting exoplanet.
+Transit signals are detected by \kepler\ but have not been confirmed to be planets.
+KOI field contains floating points that is consisted of a whole number designated to the host star followed by a decimal number denoting candidate planets.
+For example, KOI 102 is a star suspected to host multiple exoplanets and KOI 102.01 is an inner and KOI 102.02 is an outer planet candidate.
+Once the candidates are confirmed to be planets, the host star is designated \kepler\ followed by a hyphen and an integer.
+\textit {I am not actually sure why we started reporting KOI numbers... maybe to better track of exoplanets?}
 
-\textit{Sharon: you need to say what KOI stores. When writing each
+\textit {Sharon: you need to say what KOI stores. When writing each
   field, keep in mind you need to cover the following so that the
@@
   is helpful, or if it's a revised field since \cite{Wright2011}, what
-  is changed.
-
-  Also, use \keper\ (which is a defined symbol in our ms.tex file),
+  is changed. Also, use \keper\ (which is a defined symbol in our ms.tex file),
   instead of typing out Kepler, since you need italic.
-
   Don't be afraid to write more! Being concise is important, but it's
@@
   for a documentation type of paper like this. Let's be thorough at
-  first, then try to reach optimal conciseness. }
+  first, then try to reach optimal conciseness.}
 
@@
 
-\textit{Sharon: I've provided my version here: the stuff I added on
+\textit {Sharon: I've provided my version here: the stuff I added on
   top of your writing is what I think was missing and may make a
   cosmologist wonder. ;)
-
   Also, EOD doesn't require the orbit to be 'Keplerian', right? We do
@@
   Keplerian. Am I right?
-
   Note that I've covered all the 4 aspects I mentioned above. :)}
@@
 
-\textit{Sharon: you've changed `discovered' to `detected', but it's
+\textit {Sharon: you've changed `discovered' to `detected', but it's
   still not an accurate description. Let's meet and discuss this in
   person. 
-
   old: Sharon's
@@
 \subsection{Stellar Parameters}
+Stellar parameters section is consisted of 3 parts: Stellar properties, Stellar magnitudes, and Coordinates and Catalog.
+This section is to provide our users detailed information about the exoplanet hosting stars.
+Stellar properties section contains name, mass, and consistent set of metalicities (FE) , effective temperature (TEFF), surface gravity (LOGG), projected rotational velocity (VSINI), and the systematic radial velocity (GAMMA).
+Stellar magnitudes section includes optical magnitudes of the star (V and BMV) as well as 2MASS infrared (J, H, and K) and Kepler bandpass magnitude (KP).
+Coordinates and Catalog section includes the right ascension (RA) and the declination (DEC) of the host star, parallax (PAR) and distance (DIST) and the integers designated by different catalogs.
 
@@
 
-DIST: actually, DIST is not added since Wright 2011 (It was just left out)
-We report distance of the host star in the unit of pc.
+DIST is the distance of the host star in the unit of pc. It sometimes is calculated from the parallax that come from the Hipparcos data set by van Leeuwen (200).
 
-GAMMA
+GAMMA is the newly added field under Stellar properties. It is the radial velocity of the center of mass of the planetary system and is reported in km/s.
+
+ZZZ KP added?
 
@@
 OTHERNAME - This is now listed as other name of planet instead of star;
+** OTHTERNAME has always been the name of the star I think...?
 

### 2014-02-12 draft/ms.tex
Typo fix and note on KDE.
Structure changed

@@
 
-\textit {Sharon: you need to say what KOI stores. When writing each
-  field, keep in mind you need to cover the following so that the
-  reader will completely understand: (1) what the field stands for
-  (e.g., in case of an abbreviation like KOI); (2) what the field
-  physically means, like `KOI' means planet candidates that have transit
-  signals as detected by \kepler\ but have not been confirmed, and
-  make sure to be thorough at what you say -- sometimes things are not
-  that obvious to an outsider reader, e.g., think if a cosmologist
-  would understand what you're saying when reading it; (3) what the
-  field actually contains, e.g. KOI contains the KOI number designated
-  by the \kepler\ team (right?), it is a floating point number, and
-  sometimes maybe even worth giving an example, e.g. KOI 30.1 or
-  something...; (4) why we added this new field, if this information
-  is helpful, or if it's a revised field since \cite{Wright2011}, what
-  is changed. Also, use \keper\ (which is a defined symbol in our ms.tex file),
-  instead of typing out Kepler, since you need italic.
-  Don't be afraid to write more! Being concise is important, but it's
-  always easier to trim down things than to add things on, especially
-  for a documentation type of paper like this. Let's be thorough at
-  first, then try to reach optimal conciseness.}
-
 KDE:
@@
   Exoplanet Database, QUACBED.}
-
-%------------------------------------------------------------------------------
-\subsection{Stellar Parameters}
-Stellar parameters section is consisted of 3 parts: Stellar properties, Stellar magnitudes, and Coordinates and Catalog.
-This section is to provide our users detailed information about the exoplanet hosting stars.
-Stellar properties section contains name, mass, and consistent set of metalicities (FE) , effective temperature (TEFF), surface gravity (LOGG), projected rotational velocity (VSINI), and the systematic radial velocity (GAMMA).
-Stellar magnitudes section includes optical magnitudes of the star (V and BMV) as well as 2MASS infrared (J, H, and K) and Kepler bandpass magnitude (KP).
-Coordinates and Catalog section includes the right ascension (RA) and the declination (DEC) of the host star, parallax (PAR) and distance (DIST) and the integers designated by different catalogs.
-
-Added fields since \cite{Wright2011}:
-
-DIST is the distance of the host star in the unit of pc. It sometimes is calculated from the parallax that come from the Hipparcos data set by van Leeuwen (200).
-
-GAMMA is the newly added field under Stellar properties. It is the radial velocity of the center of mass of the planetary system and is reported in km/s.
-
-ZZZ KP added?
 
@@
 %------------------------------------------------------------------------------
+
 \subsection{Stellar Properties}
+ZZZ Stellar parameters and stellar properties have been merged.
+
+Stellar parameters section is consisted of 3 parts: Stellar properties, Stellar magnitudes, and Coordinates and Catalog.
+This section is to provide our users detailed information about the exoplanet hosting stars.
+Stellar properties section contains name, mass, and consistent set of metalicities (FE) , effective temperature (TEFF), surface gravity (LOGG), projected rotational velocity (VSINI), and the systematic radial velocity (GAMMA).
+Stellar magnitudes section includes optical magnitudes of the star (V and BMV) as well as 2MASS infrared (J, H, and K) and Kepler bandpass magnitude (KP).
+Coordinates and Catalog section includes the right ascension (RA) and the declination (DEC) of the host star, parallax (PAR) and distance (DIST) and the integers designated by different catalogs.
+
+Added fields since \cite{Wright2011}:
+
+GAMMA is the newly added field under Stellar properties. It is the radial velocity of the center of mass of the planetary system and is reported in km/s.
 
@@
 on spectroscopy and stellar models. 
+==>> Not always true for RSTAR because some literatures give the value. 
 Added fields since \cite{Wright2011}:
 
-RSTAR
+RSTAR is the radius of the star in the solar radius.
 
-RHOSTAR
+RHOSTAR is the density of the star in the unit of $g/cm^3$
+
+%------------------------------------------------------------------------------
+\subsection {Stellar Magnitudes}
 
 KP
+
+%------------------------------------------------------------------------------
+\subsection{Coordinates and Catalogs}
+
+Added fields since \cite{Wright2011}:
+
+DIST is the distance of the host star in the unit of pc. It sometimes is calculated from the parallax that come from the Hipparcos data set by van Leeuwen (2009).
 

### 2014-02-12 draft/ms.tex

--- 2014-02-10 draft/ms.tex
@@
   is helpful, or if it's a revised field since \cite{Wright2011}, what
-  is changed. Also, use \keper\ (which is a defined symbol in our ms.tex file),
+  is changed. Also, use \kepler\ (which is a defined symbol in our ms.tex file),
   instead of typing out Kepler, since you need italic.
@@
 
-KDE:
+KDE: obselete field! Detele from the table.
 

### 2014-02-14 draft/ms.tex
planet information update

@@
 
-KEPID: None of EOD planets has KEPID! This is just something we copied
-from Exoplanet Archive...
+KEPID stands for KEPler ID which is the integer number assigned for Kepler host stars.
+KEPID is only available for the unconfirmed KOIs which we import directly from the Exoplanet Archive.
+Therefore, none of the EOD planets and the Kepler planets do not have KEPID.
 
-KOI: KOI represents `Kepler Objects of Interest' which is a star suspected to host transiting exoplanet.
+KOI stands for `Kepler Objects of Interest' which is a star suspected to host transiting exoplanet.
 Transit signals are detected by \kepler\ but have not been confirmed to be planets.
@@
 
-EOD: EOD flag indicates planets with good Keplerian orbits. They have
-robust orbital parameters such as PER, ECC, K, OM, and I.
-
 EOD: A planet with the EOD flag being true indicates that it has
@@
 
-\textit {Sharon: I've provided my version here: the stuff I added on
-  top of your writing is what I think was missing and may make a
-  cosmologist wonder. ;)
-  Also, EOD doesn't require the orbit to be 'Keplerian', right? We do
-  include reported dynamic fits - they're definitely not
-  Keplerian. Am I right?
-  Note that I've covered all the 4 aspects I mentioned above. :)}
-
-MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENS-
-ING, IMAGING, TIMING and ASTROMETRY fields for planets detected by
-methods other than radial velocity and transit. Since planets detected
+MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENSING, IMAGING, TIMING and ASTROMETRY flags which are boolean numbers.
+Any of these flag being true indicates that the planet is detected by the method.
+For example, MICROLENSING flag being 1 means the planet is detected by microlensing event.
+Planets primarily detected
 by these methods do not have robust orbital parameters, they are
-categorized as ``Other Planets'' on exoplanets.org. However, if
-planets have follow up radial velocity or transit observations and
+categorized as ``Other Planets'' on exoplanets.org. However, we require the detection to be robust, as determined by the QUAlity Control Board of the Exoplanet Database, QUACBED. 
+If planets have follow up radial velocity or transit observations and
 thus have good orbital parameters, they have EOD flags. See
@@
 
-SEP
+SEP is the projected separation between the host star and the planet in the unit of AU.
+For directly imaged planets, the literatures give the projected separation.
+If only the semi-major axis is given, then the separation is set to the semi-major axis and vice versa.
 
@@
 
-KP
+We provide the brightness of the host star measured in different wavelengths.
+We report optical magnitudes (V and B-V), 2MASS J,H, and K magnitudes centered at 1.2\micron, 1.7\micron, and 2.2\micron, respectively.
+
+Added field: 
+KP is the stellar magnitude measured through the Kepler bandpass which covers 4000 angstroms to 8500 angstroms.
 

### 2014-02-17 draft/ms.tex
First paragraph of instroduction and added references.

@@
 \section{Introduction}\label{sec:intro}
+
+Since the first peer-reviewed list of exoplanets with robust orbits
+\citep{Butler2002,Butler2006}, the count of exoplanets has increased
+from less than 200 to over 1000 today (exoplanets.org). Before the
+launch of NASA's \kepler\ mission \citep{Borucki2010}, most confirmed
+exoplanets were discovered via the precise radial velocity (RV)
+method. However, since 2009, \kepler\ has contributed over $\sim$ 400
+confirmed exoplanets (ZZZ need citation update once the $>300$
+\kepler\ release comes out) as well as over 3000 exoplanet candidates
+(\kepler\ Objects of Interest, KOIs; e.g.~\citealt{Batalha2013}).
 

### 2014-02-18 draft/ms.tex
Orbital parameter section update

--- 2014-02-14 draft/ms.tex
@@
 
-LAMBDA: the literature has conflicted definitions of LAMBDA, and we
-sorted it out and made sure it is consistent in EOD.
-
-LAMBDA: We report the projected spin-orbit misalignment of transiting systems. We follow the definition of Fabrycky and Winn 2009.
+LAMBDA: We report the projected spin-orbit misalignment of transiting systems.
+We follow the definition of Fabrycky and Winn 2009.
+The spin-orbit angle is defined to be the angle between the stellar spin axis and the orbital axis.
+However, since the spin-orbit angle is not directly measurable, and therefore lambda, the projected spin-orbit angle was introduced.
+In the observer-oriented frame, Z axis points toward the observer, X axis points along the intersection of the sky plane and the planet's orbital plane, and Y axis completes a right handed-triad.
+Lambda is measured clockwise on the sky from the Y axis to the projected stellar rotational axis.
+While maintaining LAMBDA in our database, we figured out that literatures have conflicted definitions of LAMBDA with $\beta$, which is equal to $\lambda$ = -$\beta$.
+We sorted these cases out and made sure that LABDA is following the definition of Fabrycky and Winn 2009.
 

### 2014-02-18 draft/references.tex
Minor content revisions, add references.

@@
 
-\bibitem[Wright et al.(2011)]{Wright2011} Wright, J.~T., et al.\ 2011, \pasp, 123, 412
+\bibitem[Akeson et al.(2013)]{Akeson2013} Akeson, R.~L., et al.\ 2013, 
+\pasp, 125, 989 % NASA Exoplanet Archive
+
+\bibitem[Batalha et al.(2013)]{Batalha2013} Batalha, N.~M., et al.\ 2013, 
+\apjs, 204, 24 % example of KOI release
+
+\bibitem[Borucki et al.(2010)]{Borucki2010} Borucki, W.~J., et al.\ 2010, 
+Science, 327, 977 % Kepler instroduction and first results
+
+\bibitem[Butler et al.(2002)]{Butler2002} Butler, R.~P., et al.\ 2002, 
+\apj, 578, 565 % first peer-reviewed list of planets with robust orbits
+
+\bibitem[Butler et al.(2006)]{Butler2006} Butler, R.~P., et al.\ 2006, 
+\apj, 646, 505 % EOD first paper
+
+\bibitem[Schneider et al.(2011)]{Schneider2011} Schneider, J., Dedieu, C., 
+Le Sidaner, P., Savalle, R., \& Zolotukhin, I.\ 2011, \aap, 532, A79
+% exoplanet.eu
+
+\bibitem[Wright et al.(2011)]{Wright2011} Wright, J.~T., et al.\ 2011,
+  \pasp, 123, 412 % EOD 2011 paper
 

### 2014-02-19 draft/ms.tex
Orbital parameters update

@@
 \subsection{Orbit Parameters}
+We report the orbit parameters that determine the shape of the planet's orbit.
+Depending on the detection methods, different parameters are given by the literatures.
+For instance, if a planet is detected by the radial velocity method, we get the semi-amplitude, whereas the transit method gives the inclination of the orbit.
 
@@
 
-MASS: Previously, we only reported the minimum mass (MSINI) of the
-planets. We now report mass of the planet in the unit of Jupiter
-mass. If a planet is discovered by transit, the planet mass is given
-by the literature. However, if a planet is detected by radial velocity
+MASS is the mass of the planet in the unit of Jupiter mass.
+Previously, we only reported the minimum mass (MSINI) of the planets.
+We now report mass as well.
+If a planet is discovered by transit, the planet mass is given by the literature.
+However, if a planet is detected by radial velocity
 method, the minimum mass is given in which case we calculate the mass
@@
 MSINI if the orbital inclination is not given and the MASSREF is set
-to ``Set to MSINI; I unknown''.
-
-MASS: For KOIs without MSINI measured, Exoplanet Archive reports MASS
-based on converting radius into mass.
+to ``Set to MSINI; I unknown''. For KOIs without MSINI measured, the Exoplanet Archive reports MASS which is derived from the mass-radius relation.
 
 SEP is the projected separation between the host star and the planet in the unit of AU.
-For directly imaged planets, the literatures give the projected separation.
-If only the semi-major axis is given, then the separation is set to the semi-major axis and vice versa.
+For directly imaged planets, the literatures give the projected separation and we report this value.
+There are cases where only the semi-major axis is given without the projected separation, then SEP is set to the semi-major axis.
+For the cases where only the projected separation is given such as imaged planets, then the semi-major axis is set to SEP.
 
-BIGOM
+BIGOM is the longitude of the ascending node, which together with other orbital parameters (PER, T0, K, OM, ECC and I) determines the the planet's orbit. 
+ZZ why did we start reporting this?
+We thought we would get them eventually but we haven't seen any paper that actually reports this.
 
@@
 non-transiting systems the values of I are also available.
+ZZZ I was not added I think... and if the system has a follow-up transit observation?
 

### 2014-02-25 draft/ms.tex
Updates on sec 2.4

@@
 
-\textit{Sharon: I don't think the first sentence is true... Looking at
-  the fields in the Planet Information section in the table, it
-  doesn't contain when who or how at all... The current way of
-  dividing fields into these categories is a bit weird, but we are
-  definitely not changing it in our paper or change the website any
-  time soon... I'm guessing you want to summarize what Planet
-  Information fields cover in the first sentence here, so maybe look
-  at the table and give a very general summary of what those fields
-  are.
-  I'm not sure what's the purpose of the second sentence... It sounds
-  like something we generally did for EOD. Maybe we should move it to
-  the paragraph above in the overview text for
-  Section~\ref{sec:update}. Think more about what the purpose of the
-  subsection overview should serve.}
-
 KEPID stands for KEPler ID which is the integer number assigned for Kepler host stars.
@@
   person. 
-  old: Sharon's
-  comments: Instead of saying `discovered', we should say `detected'
+  old: Sharon's comments: Instead of saying `discovered', we should say `detected'
   -- some planets are detected by these methods but are not
@@
 
-LAMBDA: We report the projected spin-orbit misalignment of transiting systems.
+LAMBDA is the projected spin-orbit misalignment in the unit of degree.
+We report the projected spin-orbit misalignment of transiting systems.
 We follow the definition of Fabrycky and Winn 2009.
@@
 
-I: it used to be for transit systems only. Now sometimes for
+I is the orbital inclination.
+This field is not newly added but we chose to describe it here since our database now has the inclination for planets detected by methods other than transit.
+Previously, only transiting systems used to have the inclination measured.
+However, now sometimes for
 non-transiting systems the values of I are also available.
-ZZZ I was not added I think... and if the system has a follow-up transit observation?
+For instance, if the system was first detected by radial velocity and has a follow-up transit observation, then the inclination can be measured.
+To sum up, all the transiting planets have measured orbital inclination and currently, we also have one microlensing planet with measured inclination.
+*** give the example!
+
+you can only measure inclination with transit and imaging but there is only one microlensing planet with the inclination
 
@@
 
-RR
+RR is the ratio of the planetary radius and the stellar radius. Previously, we only reported the transit depth, which is the square of the planetary radius and the stellar radius.
+=== Why did we add this field?
 
@@
 \subsection{Secondary Eclipse}
+We have added an entire new set of fields for the secondary eclipse. Since \cite{Wright2011},
 
@@
 
-SE
+SE flag indicates whether the system has detected secondary eclipse in any of the 2MASS J, H, and K$_s$, Kepler photometry band, and 4 Spitzer IRAC bands.
+SE is a boolean and being true indicates the system has detected secondary eclipse.
 
-SEDEPTH J H KS KP 36 45 58 80
+SEDEPTH J H KS KP 36 45 58 80 fields are the secondary eclipse depth measured in the corresponding wavelength band.
+J, K, and K$_s$ are the depth measured in the 2MASS wavelength band in near infrared each centered at 1.25\micron, 1.65\micron, and 2.15\micron, respectively.
+KP is the depth measured in the Kepler photometry band which is centered at
 
-SET
+SET is the epoch of secondary eclipse center in HJD.
 
@@
 We provide the brightness of the host star measured in different wavelengths.
-We report optical magnitudes (V and B-V), 2MASS J,H, and K magnitudes centered at 1.2\micron, 1.7\micron, and 2.2\micron, respectively.
+We report optical magnitudes (V and B-V), 2MASS J,H, and K magnitudes centered at 1.25\micron, 1.65\micron, and 2.15\micron, respectively.
 

### 2014-02-25 draft/ms.tex
Add paragraph to introduction.

--- 2014-02-19 draft/ms.tex
@@
 
+% Recent development in exoplanet discoveries
 Since the first peer-reviewed list of exoplanets with robust orbits
 \citep{Butler2002,Butler2006}, the count of exoplanets has increased
-from less than 200 to over 1000 today (exoplanets.org). Before the
-launch of NASA's \kepler\ mission \citep{Borucki2010}, most confirmed
-exoplanets were discovered via the precise radial velocity (RV)
-method. However, since 2009, \kepler\ has contributed over $\sim$ 400
-confirmed exoplanets (ZZZ need citation update once the $>300$
-\kepler\ release comes out) as well as over 3000 exoplanet candidates
-(\kepler\ Objects of Interest, KOIs; e.g.~\citealt{Batalha2013}).
+from less than 200 to over 1000 as of March 2014
+(exoplanets.org). Before the launch of NASA's \kepler\ mission
+\citep{Borucki2010}, most confirmed exoplanets were discovered via the
+precise radial velocity (RV) method. However, since 2009, \kepler\ has
+contributed over $\sim$ 400 confirmed exoplanets (ZZZ need citation
+update once the $>300$ \kepler\ release comes out) as well as over
+3000 exoplanet candidates (\kepler\ Objects of Interest, KOIs;
+e.g.~\citealt{Batalha2013}).
 
-Recent development of exoplanet discoveries, especially
-\kepler\ discoveries.
+% The business of tracking planet discoveries
+As the number of exoplanet discoveries keeps rising, it is important
+to keep tracking these discoveries and cataloging the orbital
+parameters and host star properties of exoplanet systems. There are
+several entities that are devoted to this effort, including the
+Exoplanet Orbit Database and Exoplanets Data Explorer\footnote{See
+  \url{http://exoplanets.org}.} \citep{Wright2011}, the Extrasolar
+Planets Encyclopaedia\footnote{See \url{http://exoplanet.eu}.}
+\citep{Schneider2011}, the NASA Exoplanet Archive\footnote{See
+  \url{http://exoplanetarchive.ipac.caltech.edu}.}
+\citep{Akeson2013}, and so on.
 
-The business of keeping track of exoplanet discoveries, where EOD
-stands, and a brief history of EOD.
+% A brief history of EOD
+
+According to Google Analytics, $47,000$ people visited exoplanets.org
+in 2013.
 
@@
 website, exoplanets.org, provide.
-
-According to Google Analytics, $47,000$ people visited exoplanets.org
-in 2013.
 

### 2014-02-25 draft/ms.tex

@@
 %------------------------------------------------------------------------------
-\subsection{Planet Information}
+\subsection{Discovery and References}
 
-We report basic planet information to give our users general
-information of when, by whom and how the planets were
-discovered. Since \cite{Wright2011}, as more planets were discovered
-by different methods other than radial velocity and transit, we have
-expanded this information to better ingest those planets into our
-database.
+We report general information of when, by whom and how the planets were
+discovered and provide the references. We describe the added fields since \cite{Wright2011} below. \\
 
-Added fields since \cite{Wright2011}:
+{\bf KEPID} stands for KEPler ID which is the integer number assigned for a Kepler host star.
+KEPID is only available for the unconfirmed KOI which we import directly from the Exoplanet Archive.
+Therefore, none of the EOD planets and the confirmed Kepler planets has KEPID.
 
-KEPID stands for KEPler ID which is the integer number assigned for Kepler host stars.
-KEPID is only available for the unconfirmed KOIs which we import directly from the Exoplanet Archive.
-Therefore, none of the EOD planets and the Kepler planets do not have KEPID.
+{\bf KOI} stands for Kepler Objects of Interest which is a star with transit signals detected by \kepler\ but have not been confirmed to due to exoplanets.
+The KOI field contains a floating point number that consist of a whole number designated to the host star followed by a decimal number denoting a candidate planet.
+For example, KOI 102 is a star suspected to host two exoplanets and KOI 102.01 is the inner planet candidate and KOI 102.02 is the outer one.
+Once a candidate is confirmed, the NAME field of the planet is replaced by the official \kepler\ ID ('Kepler' followed by a hyphen, an integer and a letter).
+The KOI number is used as OTHERNAME.
+None of the KOIs are in the EOD and for more information see Section~\ref{sec:kepler}.
 
-KOI stands for `Kepler Objects of Interest' which is a star suspected to host transiting exoplanet.
-Transit signals are detected by \kepler\ but have not been confirmed to be planets.
-KOI field contains floating points that is consisted of a whole number designated to the host star followed by a decimal number denoting candidate planets.
-For example, KOI 102 is a star suspected to host multiple exoplanets and KOI 102.01 is an inner and KOI 102.02 is an outer planet candidate.
-Once the candidates are confirmed to be planets, the host star is designated \kepler\ followed by a hyphen and an integer.
-\textit {I am not actually sure why we started reporting KOI numbers... maybe to better track of exoplanets?}
-
+\begin{comment}
 \textit {Sharon: you need to say what KOI stores. When writing each
@@
   first, then try to reach optimal conciseness.}
+ \end{comment}
 
@@
 
-EOD: A planet with the EOD flag being true indicates that it has
-well-characterized orbital parameters such as PER, ECC, K, OM, and I
-and is thus included in the EOD. We added this field because
-exoplanets.org now also includes robustly discovered planets that do
-not have well-characterized orbits, and also \kepler\ planet
-candidates (see Section~\ref{sec:kepler} for more details).
+{\bf EOD} is a flag which indicates whether an exoplanet has well-characterized orbital parameters (e.g.
+period (PER)).
+EOD equals 1 means the exoplanet is in the EOD.
+We added this field because exoplanets.org now also includes robustly discovered planets that do not have well-characterized orbits, and also \kepler\ planet candidates (see Section~\ref{sec:kepler} for more details).
 
-MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENSING, IMAGING, TIMING and ASTROMETRY flags which are boolean numbers.
-Any of these flag being true indicates that the planet is detected by the method.
-For example, MICROLENSING flag being 1 means the planet is detected by microlensing event.
-Planets primarily detected
-by these methods do not have robust orbital parameters, they are
-categorized as ``Other Planets'' on exoplanets.org. However, we require the detection to be robust, as determined by the QUAlity Control Board of the Exoplanet Database, QUACBED. 
-If planets have follow up radial velocity or transit observations and
-thus have good orbital parameters, they have EOD flags. See
-Section~\ref{sec:kepler} for more information about `Other Planets'.
-
-\textit {Sharon: you've changed `discovered' to `detected', but it's
-  still not an accurate description. Let's meet and discuss this in
-  person. 
-  old: Sharon's comments: Instead of saying `discovered', we should say `detected'
-  -- some planets are detected by these methods but are not
-  necessarily discovered by them at the first place. Re-phrase the
-  last sentence -- not all of planets with any of these TRUE are in
-  `Other Planets', only some are, so maybe just note planets
-  discovered by these methods are not necessarily in EOD and direct
-  the reader to Section~\ref{sec:kepler} where we talk about `Other
-  Planets'. Remember Section~\ref{sec:update} is focuses on EOD
-  updates though the fields apply to all planets on
-  exoplanets.org. Need to note here that we require the detection to
-  be robust, as determined by the QUAlity Control Board of the
-  Exoplanet Database, QUACBED.}
+{\bf MICROLENSING, IMAGING, TIMING and ASTROMETRY} are flags which indicate that a planet detected via theses methods.
+For example, MICROLENSING $=$ 1 means the planet is detected by a microlensing event.
+However, we require the detection to be robust, as determined by the QUAlity Control Board of the Exoplanet Database, QUACBED.
 
@@
 \section{Inclusion of the Kepler Planet Candidates and Other Exoplanets on Exoplanets.org}\label{sec:kepler}
+
+Since \cite{Wright2011}, as more planets were discovered
+by different methods other than radial velocity and transit, we have expanded this information to better ingest those planets into our database.
+
+Planets primarily detected by these methods do not have robust orbital parameters, they are categorized as ``Other Planets'' on exoplanets.org.
+
+If planets have follow up radial velocity or transit observations and
+thus have good orbital parameters, they have EOD flags. See
+Section~\ref{sec:kepler} for more information about `Other Planets'.
 

### 2014-02-26 draft/ms.tex
First draft of introduction.

@@
 several entities that are devoted to this effort, including the
-Exoplanet Orbit Database and Exoplanets Data Explorer\footnote{See
+Exoplanet Orbit Database (EOD) and Exoplanets Data Explorer\footnote{See
   \url{http://exoplanets.org}.} \citep{Wright2011}, the Extrasolar
@@
 
-% A brief history of EOD
+% What is this paper about
+This paper describes the continuing efforts since \cite{Wright2011} to
+maintain the EOD and the Exoplanets Data Explorer at
+exoplanets.org. The EOD has expanded to include all robustly-detected
+exoplanets (around {\it any} type of host star) with well-determined
+orbital parameters published in peer-reviewed literature. It has also
+ingested more parameters of the exoplanet systems and host stars, and
+some parameters are revised or deleted. We describe the updates with
+the EOD in Section~\ref{sec:update}.
 
-According to Google Analytics, $47,000$ people visited exoplanets.org
-in 2013.
-
-What this paper is about: an update on EOD and the services our
-website, exoplanets.org, provide.
+% also the website
+We also describe the updates to the website that hosts the EOD and the
+Exoplanet Data Explorer, exoplanets.org. As one of the mostly visited
+exoplanet database, exoplanets.org had $47,000$ visitors in 2013
+according to Google Analytics. The Exoplanet Data Explorer has
+expanded its scope and now includes the \kepler\ exoplanet
+candidates. We describe these changes in Section~\ref{sec:kepler}. The
+website has also gone through major back-end changes since
+\cite{Wright2011}, which is described in Section~\ref{sec:website}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Updates on the Website}
+\section{Updates on the Website}\label{sec:website}
 

### 2014-02-27 draft/ms.tex
Update for the rest

--- 2014-02-25 draft/ms.tex
@@
 
-MASS is the mass of the planet in the unit of Jupiter mass.
+{\bf MASS} is the mass of the planet in the unit of Jupiter mass.
 Previously, we only reported the minimum mass (MSINI) of the planets.
@@
 
-SEP is the projected separation between the host star and the planet in the unit of AU.
+{\bf SEP} is the projected separation between the host star and the planet in the unit of AU.
 For directly imaged planets, the literatures give the projected separation and we report this value.
@@
 
-BIGOM is the longitude of the ascending node, which together with other orbital parameters (PER, T0, K, OM, ECC and I) determines the the planet's orbit. 
+{\bf BIGOM} is the longitude of the ascending node, which together with other orbital parameters (PER, T0, K, OM, ECC and I) determines the the planet's orbit. 
 ZZ why did we start reporting this?
@@
 
-LAMBDA is the projected spin-orbit misalignment in the unit of degree.
-We report the projected spin-orbit misalignment of transiting systems.
+{\bf LAMBDA} is the projected spin-orbit misalignment in the unit of degree.
+We report the projected spin-orbit misalignment of transiting systems, which is measured by Rossiter-McLaughlin effect.
 We follow the definition of Fabrycky and Winn 2009.
@@
 
-I is the orbital inclination.
+{\bf I} is the orbital inclination.
 This field is not newly added but we chose to describe it here since our database now has the inclination for planets detected by methods other than transit.
@@
 
-you can only measure inclination with transit and imaging but there is only one microlensing planet with the inclination
-
 %------------------------------------------------------------------------------
 \subsection{Transit Parameters}
-
+We report the transit parameters of transiting planets. These parameters are available only when the planet has TRANSIT flag equal to 1. 
 Added fields since \cite{Wright2011}:
 
-DR
+{\bf DR} is the distance between the planet and the star during the transit in stellar radii.
+This is one of the parameters that goes into the transit light curve modeling and for more information, see Batalha 2013 for more details.
 
-RR is the ratio of the planetary radius and the stellar radius. Previously, we only reported the transit depth, which is the square of the planetary radius and the stellar radius.
-=== Why did we add this field?
+{\bf RR} is the ratio of the planetary radius and the stellar radius. Previously, we only reported the transit depth, which is the square of the planetary radius and the stellar radius.
+Why did we add this field?
 
@@
 \subsection{Secondary Eclipse}
-We have added an entire new set of fields for the secondary eclipse. Since \cite{Wright2011},
+We have added an entirely new set of fields for the secondary eclipse.
+To measure transits, astronomers need to have a precision of 1/100, whereas for the secondary eclipse (or transmission spectrum), precision of 1/10,000 is required, which means it is much harder to detect the secondary eclipse depths or transmission spectra compared to just transit.
+Previously, due to the limits of instrumentation, there were not much available measured secondary eclipse depths.
+However, since \cite{Wright2011}, as many different surveys have been launched, secondary eclipse depths at multiple bands are now available.
+Therefore, to better ingest this information, we added a new set of fields for the secondary eclipse.
 
@@
 
-SE flag indicates whether the system has detected secondary eclipse in any of the 2MASS J, H, and K$_s$, Kepler photometry band, and 4 Spitzer IRAC bands.
+{\bf SE} flag indicates whether the system has detected secondary eclipse in any of the 2MASS J, H, and K$_s$, Kepler photometry band, and 4 Spitzer IRAC bands.
 SE is a boolean and being true indicates the system has detected secondary eclipse.
 
-SEDEPTH J H KS KP 36 45 58 80 fields are the secondary eclipse depth measured in the corresponding wavelength band.
+{\bf SEDEPTH J H KS KP 36 45 58 80} fields are the secondary eclipse depth measured in the corresponding wavelength band.
 J, K, and K$_s$ are the depth measured in the 2MASS wavelength band in near infrared each centered at 1.25\micron, 1.65\micron, and 2.15\micron, respectively.
@@
 
-SET is the epoch of secondary eclipse center in HJD.
+{\bf SET} is the epoch of secondary eclipse center in HJD.
 
@@
 
-GAMMA is the newly added field under Stellar properties. It is the radial velocity of the center of mass of the planetary system and is reported in km/s.
+{\bf GAMMA} is the newly added field under Stellar properties. It is the radial velocity of the center of mass of the planetary system and is reported in km/s.
 
@@
 on spectroscopy and stellar models. 
-==>> Not always true for RSTAR because some literatures give the value. 
+Not always true for RSTAR because some literatures give the value. 
 Added fields since \cite{Wright2011}:
 
-RSTAR is the radius of the star in the solar radius.
+{\bf RSTAR} is the radius of the star in the solar radius.
 
-RHOSTAR is the density of the star in the unit of $g/cm^3$
+{\bf RHOSTAR} is the density of the star in the unit of $g/cm^3$
 
@@
 Added field: 
-KP is the stellar magnitude measured through the Kepler bandpass which covers 4000 angstroms to 8500 angstroms.
+{\bf KP} is the stellar magnitude measured through the Kepler bandpass which covers 4000 angstroms to 8500 angstroms.
 
@@
 \subsection{Coordinates and Catalogs}
-
+We report the coordinates of the host star as well as the stellar ID as designated by different catalogs. 
 Added fields since \cite{Wright2011}:
 
-DIST is the distance of the host star in the unit of pc. It sometimes is calculated from the parallax that come from the Hipparcos data set by van Leeuwen (2009).
+{\bf DIST} is the distance of the host star in the unit of pc. It sometimes is calculated from the parallax that come from the Hipparcos data set by van Leeuwen (2009).
 
@@
 
+The fields {\bf XREF} and {\bf XURL} store the peer-reviewed reference and link to
+the publication for the field X.
+
 Added field: MONTH, PLANETDISCMETH, STARDISCMETH.
-
-The fields XREF and XURL store the peer-reviewed reference and link to
-the publication for the field X. The following fields now have XREF
-and XURL: (previously in \citealt{Wright2011}) DIST, TRANSIT, BINARY;
-(new) fields in stellar parameters: V, VSINI, GAMMA; all orbit pars except for
-trend and freeze\_ecc; all transit parameters; all SE parameters;
-fields for stellar properties: MSTAR, RSTAR, TEFF, RHOSTAR, LOGG, FE.
+The following fields now have XREF and XURL: (previously in \cite{Wright2011}) DIST, TRANSIT, BINARY; (new) fields in stellar parameters: V, VSINI, GAMMA; all orbit pars except for trend and freeze\_ecc; all transit parameters; all SE parameters; fields for stellar properties: MSTAR, RSTAR, TEFF, RHOSTAR, LOGG, FE.
 
@@
 
-We now report the month when the peer-reviewed paper is accepted to
-ApJ to better track of the trend in exoplanetary detections. Moreover,
-we report the discovery methods for the host star and the planet
-separately: STARDISCMETH and PLANETDISCMETH. See Section~ for more
-details.
+{\bf MONTH} field reports an integer of the month when the peer-reviewed paper is accepted to the
+ApJ to better track of the trend in the exoplanet detections.
+
+{\bf PLANETDISCMENT} and {\bf STARDISCMETH} are the fields that report the discovery methods for the host star and the planet See Section~ for more details.
 
@@
 \subsection{Revised and Removed Fields}
+We have major updates by taking out some of the fields and by revising the existing fields. Here, we explain why we removed or revised such fields.
 
-These include:
-
-OTHERNAME - This is now listed as other name of planet instead of star;
+{\bf OTHERNAME} - This is now listed as other name of planet instead of star;
 ** OTHTERNAME has always been the name of the star I think...?
 
-DISCMETH - We have replaced DISCMETH with PLANETDISCMETH and STARDISCMETH to better report how the host star and the planet are detected.
+{\bf DISCMETH} field previously reported the mouthed of discovery, which was either radial velocity or transit.
+We have replaced DISCMETH with {\bf PLANETDISCMETH} and {\bf STARDISCMETH} to better report how the host star and the planet are detected.
+Furthermore, they now have value of one of the following: radial velocity, transit, imaging, microlensing, timing, or astrometry.
 
-S - changed to SHK; ZZZ What's the source for SHK and RHK? Still discovery
-paper and Butler 2006? ZZZ SHK is a poorly maintained field, and it is
-unreferenced at the moment though we plan to include propoer reference
+{\bf S} field previously reported the Mount Wilson Ca II S-value and now it is changed to SHK. 
+; ZZZ What's the source for SHK and RHK? Still discovery paper and Butler 2006? ZZZ SHK is a poorly maintained field, and it is unreferenced at the moment though we plan to include proper reference
 in the future.
 
-SPSTAR - stellar type of star (unvetted), gone;
+{\bf SPSTAR} field previously reported the stellar type of the host star. We choose to remove this field because....? - stellar type of star (unvetted), gone;
 
-NSTEDID - replaced by EANAME (Exoplanet Archive).
+{\bf NSTEDID} field reported ID of host star in NStED and now it is replaced by EANAME, which is the name of the star as appears on the Exoplanet Archive.
 
-MASSREF, MASSURL - originally for stellar mass reference, now for planet mass.
+{\bf MASSREF} and {\bf MASSURL} fields were used to report the reference and the url of stellar mass but now they are used for planet mass.
 

### 2014-02-28 draft/ms.tex
Orbital parameters section revision 1

@@
 We report general information of when, by whom and how the planets were
-discovered and provide the references. We describe the added fields since \cite{Wright2011} below. \\
+discovered and provide the references. We describe the added fields since \cite{Wright2011} below.
 
@@
 %------------------------------------------------------------------------------
-\subsection{Orbit Parameters}
-We report the orbit parameters that determine the shape of the planet's orbit.
-Depending on the detection methods, different parameters are given by the literatures.
-For instance, if a planet is detected by the radial velocity method, we get the semi-amplitude, whereas the transit method gives the inclination of the orbit.
+\subsection{Orbital Parameters}
+We report the orbital parameters that determine the shape of the planet's orbit.
+Depending on the detection methods, different sets of parameters are given by the literatures.
+For instance, if a planet is detected by the radial velocity method, the semiamplitude, $K$, is reported whereas the inclination of the orbit, $i$, is reported by the transit method.
 
-Added fields since \cite{Wright2011}:
+We describe the added fields since \cite{Wright2011} below.
 
 {\bf MASS} is the mass of the planet in the unit of Jupiter mass.
-Previously, we only reported the minimum mass (MSINI) of the planets.
-We now report mass as well.
-If a planet is discovered by transit, the planet mass is given by the literature.
-However, if a planet is detected by radial velocity
-method, the minimum mass is given in which case we calculate the mass
-by dividing the minimum mass by the orbit inclination. MASS is set to
-MSINI if the orbital inclination is not given and the MASSREF is set
-to ``Set to MSINI; I unknown''. For KOIs without MSINI measured, the Exoplanet Archive reports MASS which is derived from the mass-radius relation.
+Previously, we only reported the minimum mass, ($m\sin{i}$, MSINI) of the planets.
+We now report the mass as well.
+For example, if a planet is discovered by microlensing, we report the actual mass of the planet according to the literature.
+If a planet has both radial velocity and transit measurements, we calculate the mass from the minimum mass and the orbital inclination.
+MASS is set to MSINI if the orbital inclination is not given and the MASSREF is set to ``Set to MSINI; I unknown''.
+
+ZZZ For KOIs without MSINI measured, we import the MASS fields from the Exoplanet Archive, which are derived from the mass-radius relation in .
 

### 2014-03-03 draft/ms.tex
Add Kepler 715 planets reference and slight modification on intro.

@@
 \begin{abstract}
-
+Make sure to mention: data are available at exoplanets.org; KOIs are included.
 \end{abstract}
@@
 \citep{Butler2002,Butler2006}, the count of exoplanets has increased
-from less than 200 to over 1000 as of March 2014
+from less than 200 to over 1490 as of March 2014
 (exoplanets.org). Before the launch of NASA's \kepler\ mission
@@
 precise radial velocity (RV) method. However, since 2009, \kepler\ has
-contributed over $\sim$ 400 confirmed exoplanets (ZZZ need citation
-update once the $>300$ \kepler\ release comes out) as well as over
-3000 exoplanet candidates (\kepler\ Objects of Interest, KOIs;
-e.g.~\citealt{Batalha2013}).
+contributed over $\sim$ 800 confirmed exoplanets
+\citep[e.g.,][]{Rowe2014} as well as over 3000 exoplanet candidates
+(\kepler\ Objects of Interest, KOIs; e.g.~\citealt{Batalha2013}).
 
@@
 As the number of exoplanet discoveries keeps rising, it is important
-to keep tracking these discoveries and cataloging the orbital
+to keep track of these discoveries and cataloging the orbital
 parameters and host star properties of exoplanet systems. There are

### 2014-03-03 draft/references.tex
Add reference and notes in new_table_items.txt.
Add Kepler 715 planets reference and slight modification on intro.

@@
 
+\bibitem[Rowe et al.(2014)]{Rowe2014} Rowe, J.~F., et al.\ 2014, 
+arXiv:1402.6534 % 715 new Kepler planets (multis)
+
 \bibitem[Schneider et al.(2011)]{Schneider2011} Schneider, J., Dedieu, C., 
@@
 
+\bibitem[Wright \& Gaudi(2013)]{Wright2013} Wright, J.~T., \& Gaudi, B.~S.\ 2013,
+  Planets, Stars and Stellar Systems.~Volume 3: Solar and Stellar
+  Planetary Systems, 489 % Review article with definition of orbital elements
+
 \end{thebibliography}

### 2014-03-04 draft/references.tex
Add references on KOI mass calculation and lambda definition.

@@
 
+\bibitem[Fabrycky \& Winn(2009)]{Fabrycky2009} Fabrycky, D.~C., \&
+  Winn, J.~N.\ 2009, \apj, 696, 1230 % spin-orbit misalignment lambda definition
+
+\bibitem[Lissauer et al.(2011)]{Lissauer2011} Lissauer, J.~J., et al.\ 
+2011, \apjs, 197, 8 % Mass-Radius for 1 Re < R < 6 Re
+
+\bibitem[Mordasini et al.(2012)]{Mordasini2012} Mordasini, C., Alibert, Y., 
+Georgy, C., Dittkrist, K.-M., Klahr, H., \& Henning, T.\ 2012, \aap, 547, A112
+% Mass-Radius for 6 Re < R < 11.684 Re
+
 \bibitem[Rowe et al.(2014)]{Rowe2014} Rowe, J.~F., et al.\ 2014, 
@@
 % exoplanet.eu
+
+\bibitem[Sotin et al.(2007)]{Sotin2007} Sotin, C., Grasset, O., 
+\& Mocquet, A.\ 2007, \icarus, 191, 337 % Mass-Radius for M<1Me, R<1Re
+
+\bibitem[Weiss \& Marcy(2014)]{Weiss2014} Weiss, L.~M., \& Marcy,
+  G.~W.\ 2014, \apjl, 783, L6  % Mass-Radius for R < 4Re to be implemented
 

### 2014-03-04 draft/ms.tex

@@
 \section{Updates on the EOD}\label{sec:update}
+ZZZ make sure to cite Wright and Gaudi paper for the definition of orbital elements.
 
@@
 For instance, if a planet is detected by the radial velocity method, the semiamplitude, $K$, is reported whereas the inclination of the orbit, $i$, is reported by the transit method.
-
 We describe the added fields since \cite{Wright2011} below.
@@
 Previously, we only reported the minimum mass, ($m\sin{i}$, MSINI) of the planets.
-We now report the mass as well.
+We now report the mass as well when it is available.
 For example, if a planet is discovered by microlensing, we report the actual mass of the planet according to the literature.
@@
 
-{\bf SEP} is the projected separation between the host star and the planet in the unit of AU.
+{\bf SEP} is the projected separation on the sky between the host star and the planet in the unit of AU.
 For directly imaged planets, the literatures give the projected separation and we report this value.
-There are cases where only the semi-major axis is given without the projected separation, then SEP is set to the semi-major axis.
+If SEP is  not directly measured but the semi-major (A) is available, then SEP is set to A with the reference ``Set to A''.
 For the cases where only the projected separation is given such as imaged planets, then the semi-major axis is set to SEP.
 
-{\bf BIGOM} is the longitude of the ascending node, which together with other orbital parameters (PER, T0, K, OM, ECC and I) determines the the planet's orbit. 
-ZZ why did we start reporting this?
-We thought we would get them eventually but we haven't seen any paper that actually reports this.
+{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in the unit of degree and for now this is only measured for some of the directly imaged planets, which are not in the EOD.
 
-{\bf LAMBDA} is the projected spin-orbit misalignment in the unit of degree.
-We report the projected spin-orbit misalignment of transiting systems, which is measured by Rossiter-McLaughlin effect.
-We follow the definition of Fabrycky and Winn 2009.
-The spin-orbit angle is defined to be the angle between the stellar spin axis and the orbital axis.
-However, since the spin-orbit angle is not directly measurable, and therefore lambda, the projected spin-orbit angle was introduced.
-In the observer-oriented frame, Z axis points toward the observer, X axis points along the intersection of the sky plane and the planet's orbital plane, and Y axis completes a right handed-triad.
-Lambda is measured clockwise on the sky from the Y axis to the projected stellar rotational axis.
-While maintaining LAMBDA in our database, we figured out that literatures have conflicted definitions of LAMBDA with $\beta$, which is equal to $\lambda$ = -$\beta$.
-We sorted these cases out and made sure that LABDA is following the definition of Fabrycky and Winn 2009.
+{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in the unit of degree.
+We report the projected spin-orbit misalignment of transiting systems, which is measured by ZZZ Rossiter-McLaughlin effect.
+$\lambda$ is introduced because the true spin-orbit angle ($\phi$), defined as the angle between the stellar spin axis and the orbital axis, is normally not directly measurable.
+We follow the definition of $\lambda$ in Fabrycky and Winn 2009 where the coordinates are defined as follows; the $z$-axis points toward the observer, the $x$-axis points along the intersection of the sky plane and the planet's orbital plane with the ascending node of the planet having $x<0$, and the $y$-axis completes a right handed-triad.
+$\lambda$ is measured clockwise on the sky from the $y$-axis to the projected stellar rotational axis.
+Some literatures report $\beta = -\lambda$ instead.
+We sorted these cases out and made sure that our $\lambda$'s are following the definition of Fabrycky and Winn 2009.
 

### 2014-03-04 draft/ms.tex
Orbital parameters section done

@@
 \def\mjup{$M_{\rm Jup}$}
+\def\rearth{R_\oplus}
 
@@
 
-ZZZ For KOIs without MSINI measured, we import the MASS fields from the Exoplanet Archive, which are derived from the mass-radius relation in .
+ZZZ For KOIs without MSINI measured, we calculate their mass using the mass-radius relation from the literatures.
+For KOIs with $R<4\rearth$, we use \cite{Weiss2014} , with $4\rearth<R<6\rearth$, we use \cite{Lissauer2011}, and for KOIs with $6\rearth<R<17\rearth$ we use \cite{Mordasini2012}.
 
@@
 
-{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in the unit of degree.
-We report the projected spin-orbit misalignment of transiting systems, which is measured by ZZZ Rossiter-McLaughlin effect.
-$\lambda$ is introduced because the true spin-orbit angle ($\phi$), defined as the angle between the stellar spin axis and the orbital axis, is normally not directly measurable.
-We follow the definition of $\lambda$ in Fabrycky and Winn 2009 where the coordinates are defined as follows; the $z$-axis points toward the observer, the $x$-axis points along the intersection of the sky plane and the planet's orbital plane with the ascending node of the planet having $x<0$, and the $y$-axis completes a right handed-triad.
-$\lambda$ is measured clockwise on the sky from the $y$-axis to the projected stellar rotational axis.
-Some literatures report $\beta = -\lambda$ instead.
-We sorted these cases out and made sure that our $\lambda$'s are following the definition of Fabrycky and Winn 2009.
-
-{\bf I} is the orbital inclination.
-This field is not newly added but we chose to describe it here since our database now has the inclination for planets detected by methods other than transit.
-Previously, only transiting systems used to have the inclination measured.
-However, now sometimes for
-non-transiting systems the values of I are also available.
-For instance, if the system was first detected by radial velocity and has a follow-up transit observation, then the inclination can be measured.
-To sum up, all the transiting planets have measured orbital inclination and currently, we also have one microlensing planet with measured inclination.
-*** give the example!
-
 %------------------------------------------------------------------------------
 \subsection{Transit Parameters}
-We report the transit parameters of transiting planets. These parameters are available only when the planet has TRANSIT flag equal to 1. 
-Added fields since \cite{Wright2011}:
+We report the transit parameters, which are available only when the planet has TRANSIT flag equal to 1. We describe added fields since \cite{Wright2011} below.
 
 {\bf DR} is the distance between the planet and the star during the transit in stellar radii.
-This is one of the parameters that goes into the transit light curve modeling and for more information, see Batalha 2013 for more details.
+This is one of the parameters that goes into the transit light curve modeling (see e.g.
+\citealt{Batalha2013}).
 
-{\bf RR} is the ratio of the planetary radius and the stellar radius. Previously, we only reported the transit depth, which is the square of the planetary radius and the stellar radius.
-Why did we add this field?
+{\bf RR} is the ratio of the planetary radius and the stellar radius. If the transit depth (DEPTH) is not given, we calculate DEPTH by taking square of RR but we do not calculate RR from DEPTH.
 
@@
 We have major updates by taking out some of the fields and by revising the existing fields. Here, we explain why we removed or revised such fields.
+
+{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in the unit of degree.
+We report the projected spin-orbit misalignment of transiting systems, which is measured by ZZZ Rossiter-McLaughlin effect.
+$\lambda$ is introduced because the true spin-orbit angle ($\phi$), defined as the angle between the stellar spin axis and the orbital axis, is normally not directly measurable.
+We follow the definition of $\lambda$ in Fabrycky and Winn 2009 where the coordinates are defined as follows; the $z$-axis points toward the observer, the $x$-axis points along the intersection of the sky plane and the planet's orbital plane with the ascending node of the planet having $x<0$, and the $y$-axis completes a right handed-triad.
+$\lambda$ is measured clockwise on the sky from the $y$-axis to the projected stellar rotational axis.
+Some literatures report $\beta = -\lambda$ instead.
+We sorted these cases out and made sure that our $\lambda$'s are following the definition of Fabrycky and Winn 2009.
+
+{\bf I} is the orbital inclination.
+This field is not newly added but we chose to describe it here since our database now has the inclination for planets detected by methods other than transit.
+Previously, only transiting systems used to have the inclination measured.
+However, now sometimes for
+non-transiting systems the values of I are also available.
+For instance, if the system was first detected by radial velocity and has a follow-up transit observation, then the inclination can be measured.
+To sum up, all the transiting planets have measured orbital inclination and currently, we also have one microlensing planet with measured inclination.
+*** give the example!
 

### 2014-03-05 draft/ms.tex
Section 2.4 to 2.7 done

@@
 We have added an entirely new set of fields for the secondary eclipse.
-To measure transits, astronomers need to have a precision of 1/100, whereas for the secondary eclipse (or transmission spectrum), precision of 1/10,000 is required, which means it is much harder to detect the secondary eclipse depths or transmission spectra compared to just transit.
 Previously, due to the limits of instrumentation, there were not much available measured secondary eclipse depths.
-However, since \cite{Wright2011}, as many different surveys have been launched, secondary eclipse depths at multiple bands are now available.
-Therefore, to better ingest this information, we added a new set of fields for the secondary eclipse.
+Since \cite{Wright2011}, as many different surveys have been launched, secondary eclipse depths at multiple bands are now available.
+Therefore, we added this entire new set of fields since.
 
-This is a entire new set of fields since \cite{Wright2011}:
+{\bf SE} flag indicates whether the system has detected secondary eclipse in any of the two Micron All-Sky Survey (2MASS) $J$, $H$, and $K_s$, Kepler photometry band, and 4 Spitzer IRAC bands.
+SE is a boolean and being true indicates the system has at least one detected secondary eclipse.
+ZZZ add 2MASS reference!
 
-{\bf SE} flag indicates whether the system has detected secondary eclipse in any of the 2MASS J, H, and K$_s$, Kepler photometry band, and 4 Spitzer IRAC bands.
-SE is a boolean and being true indicates the system has detected secondary eclipse.
-
-{\bf SEDEPTH J H KS KP 36 45 58 80} fields are the secondary eclipse depth measured in the corresponding wavelength band.
-J, K, and K$_s$ are the depth measured in the 2MASS wavelength band in near infrared each centered at 1.25\micron, 1.65\micron, and 2.15\micron, respectively.
-KP is the depth measured in the Kepler photometry band which is centered at
+{\bf SEDEPTHX} whereas X stands for one of J H KS KP 36 45 58 80: these fields are the secondary eclipse depth measured in the corresponding wavelength band.
+SEDEPTHJ, H, and KS are the depths measured in the 2MASS wavelength band in near infrared each centered at 1.25~\micron, 1.65~\micron, and 2.15~\micron, respectively.
+KP is the depth measured in the \kepler\ photometry band which ranges from 400 to 865~nm.
+The rest four stand for the Spitzer bands centered at 3.6~\micron, 4.5~\micron, 5.8~\micron, and 8.0~\micron.
 
@@
 %------------------------------------------------------------------------------
+\subsection{Stellar Properties}
+This set of parameters is to provide users the physical parameters of the exoplanet host stars. 
+Most of the parameters are derived from the stellar models in the literatures and we provide the readers with the references. We describe added fields since \cite{Wright2011} below.
 
-\subsection{Stellar Properties}
-ZZZ Stellar parameters and stellar properties have been merged.
-
-Stellar parameters section is consisted of 3 parts: Stellar properties, Stellar magnitudes, and Coordinates and Catalog.
-This section is to provide our users detailed information about the exoplanet hosting stars.
-Stellar properties section contains name, mass, and consistent set of metalicities (FE) , effective temperature (TEFF), surface gravity (LOGG), projected rotational velocity (VSINI), and the systematic radial velocity (GAMMA).
-Stellar magnitudes section includes optical magnitudes of the star (V and BMV) as well as 2MASS infrared (J, H, and K) and Kepler bandpass magnitude (KP).
-Coordinates and Catalog section includes the right ascension (RA) and the declination (DEC) of the host star, parallax (PAR) and distance (DIST) and the integers designated by different catalogs.
-
-Added fields since \cite{Wright2011}:
-
-{\bf GAMMA} is the newly added field under Stellar properties. It is the radial velocity of the center of mass of the planetary system and is reported in km/s.
-
-Difference from Stellar Parameters: these are derived parameters based
-on spectroscopy and stellar models. 
-Not always true for RSTAR because some literatures give the value. 
-Added fields since \cite{Wright2011}:
+{\bf GAMMA} ($\gamma$) is the radial velocity of the center of mass of the planetary system and is reported in km/s.
 
@@
 
-{\bf RHOSTAR} is the density of the star in the unit of $g/cm^3$
+{\bf RHOSTAR} is the density of the star in the unit of g/cm$^3$.
 
@@
 We provide the brightness of the host star measured in different wavelengths.
-We report optical magnitudes (V and B-V), 2MASS J,H, and K magnitudes centered at 1.25\micron, 1.65\micron, and 2.15\micron, respectively.
-
-Added field: 
-{\bf KP} is the stellar magnitude measured through the Kepler bandpass which covers 4000 angstroms to 8500 angstroms.
+We report optical magnitudes ($V$ and $B-V$), 2MASS $J$, $H$, and $K_s$ magnitudes and we added {\bf KP} since \cite{Wright2011}, which is the stellar magnitude measured through the Kepler bandpass.
 
@@
 We report the coordinates of the host star as well as the stellar ID as designated by different catalogs. 
-Added fields since \cite{Wright2011}:
-
-{\bf DIST} is the distance of the host star in the unit of pc. It sometimes is calculated from the parallax that come from the Hipparcos data set by van Leeuwen (2009).
+We added {\bf DIST} since \cite{Wright2011}, which is the distance of the host star in the unit of pc.
+If only parallax (PAR) is given, we convert it to DIST and vice versa.
+If the literature does not report DIST or PAR, then we obtain PAR from the Hipparcos data set by van Leeuwen (2009).
+ZZZ add a reference for Leeuwen
 
@@
 K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps & -UPPER, etc. \\
-T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{d}$-2,440,000$ & -UPPER, etc. \\
+T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{d} & -UPPER, etc. \\
 DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER, etc. \\
@@
 TT\dotfill & Float & Epoch of transit center in
-HJD\tablenotemark{d}$-2,440,000$ & -UPPER, etc. \\
+HJD\tablenotemark{d} & -UPPER, etc. \\
 R\dotfill & Float & Radius of planet in Jupiter radii & -UPPER, etc. \\
@@
 SET\dotfill & Double & Epoch of secondary eclipse center in
-HJD\tablenotemark{d}$-2,440,000$ & -UPPER, etc. \\
+HJD\tablenotemark{d} & -UPPER, etc. \\
 %

### 2014-03-06 draft/ms.tex
Add several missing references in Sec 2.

@@
 \section{Updates on the EOD}\label{sec:update}
-ZZZ make sure to cite Wright and Gaudi paper for the definition of orbital elements.
+Make sure to cite \cite{Wright2013} for the definition of orbital elements.
 
@@
 
-We report general information of when, by whom and how the planets were
-discovered and provide the references. We describe the added fields since \cite{Wright2011} below.
+We report general information of when, by whom and how the planets
+were discovered and provide the references. We describe the added
+fields since \cite{Wright2011} below.
 
-{\bf KEPID} stands for KEPler ID which is the integer number assigned for a Kepler host star.
-KEPID is only available for the unconfirmed KOI which we import directly from the Exoplanet Archive.
-Therefore, none of the EOD planets and the confirmed Kepler planets has KEPID.
+{\bf KEPID} stands for KEPler ID which is the integer number assigned
+for a Kepler host star. KEPID is only available for the unconfirmed
+KOI which we import directly from the Exoplanet Archive. Therefore,
+none of the EOD planets and the confirmed Kepler planets has KEPID.
 
-{\bf KOI} stands for Kepler Objects of Interest which is a star with transit signals detected by \kepler\ but have not been confirmed to due to exoplanets.
-The KOI field contains a floating point number that consist of a whole number designated to the host star followed by a decimal number denoting a candidate planet.
-For example, KOI 102 is a star suspected to host two exoplanets and KOI 102.01 is the inner planet candidate and KOI 102.02 is the outer one.
-Once a candidate is confirmed, the NAME field of the planet is replaced by the official \kepler\ ID ('Kepler' followed by a hyphen, an integer and a letter).
-The KOI number is used as OTHERNAME.
-None of the KOIs are in the EOD and for more information see Section~\ref{sec:kepler}.
+{\bf KOI} stands for Kepler Objects of Interest which is a star with
+transit signals detected by \kepler\ but have not been confirmed to
+due to exoplanets. The KOI field contains a floating point number that
+consist of a whole number designated to the host star followed by a
+decimal number denoting a candidate planet. For example, KOI 102 is a
+star suspected to host two exoplanets and KOI 102.01 is the inner
+planet candidate and KOI 102.02 is the outer one. Once a candidate is
+confirmed, the NAME field of the planet is replaced by the official
+\kepler\ ID ('Kepler' followed by a hyphen, an integer and a
+letter). The KOI number is used as OTHERNAME. None of the KOIs are in
+the EOD and for more information see Section~\ref{sec:kepler}.
 
@@
   (e.g., in case of an abbreviation like KOI); (2) what the field
-  physically means, like `KOI' means planet candidates that have transit
-  signals as detected by \kepler\ but have not been confirmed, and
-  make sure to be thorough at what you say -- sometimes things are not
-  that obvious to an outsider reader, e.g., think if a cosmologist
+  physically means, like `KOI' means planet candidates that have
+  transit signals as detected by \kepler\ but have not been confirmed,
+  and make sure to be thorough at what you say -- sometimes things are
+  not that obvious to an outsider reader, e.g., think if a cosmologist
   would understand what you're saying when reading it; (3) what the
@@
   is helpful, or if it's a revised field since \cite{Wright2011}, what
-  is changed. Also, use \kepler\ (which is a defined symbol in our ms.tex file),
-  instead of typing out Kepler, since you need italic.
+  is changed. Also, use \kepler\ (which is a defined symbol in our
+  ms.tex file), instead of typing out Kepler, since you need italic.
   Don't be afraid to write more! Being concise is important, but it's
@@
 
-{\bf EOD} is a flag which indicates whether an exoplanet has well-characterized orbital parameters (e.g.
-period (PER)).
-EOD equals 1 means the exoplanet is in the EOD.
-We added this field because exoplanets.org now also includes robustly discovered planets that do not have well-characterized orbits, and also \kepler\ planet candidates (see Section~\ref{sec:kepler} for more details).
+{\bf EOD} is a flag which indicates whether an exoplanet has
+well-characterized orbital parameters (e.g. period (PER)). EOD equals
+1 means the exoplanet is in the EOD. We added this field because
+exoplanets.org now also includes robustly discovered planets that do
+not have well-characterized orbits, and also \kepler\ planet
+candidates (see Section~\ref{sec:kepler} for more details).
 
-{\bf MICROLENSING, IMAGING, TIMING and ASTROMETRY} are flags which indicate that a planet detected via theses methods.
-For example, MICROLENSING $=$ 1 means the planet is detected by a microlensing event.
-However, we require the detection to be robust, as determined by the QUAlity Control Board of the Exoplanet Database, QUACBED.
+{\bf MICROLENSING, IMAGING, TIMING and ASTROMETRY} are flags which
+indicate that a planet detected via theses methods. For example,
+MICROLENSING $=$ 1 means the planet is detected by a microlensing
+event. However, we require the detection to be robust, as determined
+by the QUAlity Control Board of the Exoplanet Database, QUACBED.
 
@@
 \subsection{Orbital Parameters}
-We report the orbital parameters that determine the shape of the planet's orbit.
-Depending on the detection methods, different sets of parameters are given by the literatures.
-For instance, if a planet is detected by the radial velocity method, the semiamplitude, $K$, is reported whereas the inclination of the orbit, $i$, is reported by the transit method.
-We describe the added fields since \cite{Wright2011} below.
+We report the orbital parameters that determine the shape of the
+planet's orbit. Depending on the detection methods, different sets of
+parameters are given by the literatures. For instance, if a planet is
+detected by the radial velocity method, the semiamplitude, $K$, is
+reported whereas the inclination of the orbit, $i$, is reported by the
+transit method. We describe the added fields since \cite{Wright2011}
+below.
 
-{\bf MASS} is the mass of the planet in the unit of Jupiter mass.
-Previously, we only reported the minimum mass, ($m\sin{i}$, MSINI) of the planets.
-We now report the mass as well when it is available.
-For example, if a planet is discovered by microlensing, we report the actual mass of the planet according to the literature.
-If a planet has both radial velocity and transit measurements, we calculate the mass from the minimum mass and the orbital inclination.
-MASS is set to MSINI if the orbital inclination is not given and the MASSREF is set to ``Set to MSINI; I unknown''.
+{\bf MASS} is the mass of the planet in the unit of Jupiter
+mass. Previously, we only reported the minimum mass, ($m\sin{i}$,
+MSINI) of the planets. We now report the mass as well when it is
+available. For example, if a planet is discovered by microlensing, we
+report the actual mass of the planet according to the literature. If a
+planet has both radial velocity and transit measurements, we calculate
+the mass from the minimum mass and the orbital inclination. MASS is
+set to MSINI if the orbital inclination is not given and the MASSREF
+is set to ``Set to MSINI; I unknown''.
 
-ZZZ For KOIs without MSINI measured, we calculate their mass using the mass-radius relation from the literatures.
-For KOIs with $R<4\rearth$, we use \cite{Weiss2014} , with $4\rearth<R<6\rearth$, we use \cite{Lissauer2011}, and for KOIs with $6\rearth<R<17\rearth$ we use \cite{Mordasini2012}.
+ZZZ For KOIs without MSINI measured, we calculate their mass using the
+mass-radius relation from the literatures. For KOIs with $R<4\rearth$,
+we use \cite{Weiss2014} , with $4\rearth<R<6\rearth$, we use
+\cite{Lissauer2011}, and for KOIs with $6\rearth<R<17\rearth$ we use
+\cite{Mordasini2012}.
 
-{\bf SEP} is the projected separation on the sky between the host star and the planet in the unit of AU.
-For directly imaged planets, the literatures give the projected separation and we report this value.
-If SEP is  not directly measured but the semi-major (A) is available, then SEP is set to A with the reference ``Set to A''.
-For the cases where only the projected separation is given such as imaged planets, then the semi-major axis is set to SEP.
+{\bf SEP} is the projected separation on the sky between the host star
+and the planet in the unit of AU. For directly imaged planets, the
+literatures give the projected separation and we report this value.
+If SEP is not directly measured but the semi-major (A) is available,
+then SEP is set to A with the reference ``Set to A''. For the cases
+where only the projected separation is given such as imaged planets,
+then the semi-major axis is set to SEP.
 
-{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in the unit of degree and for now this is only measured for some of the directly imaged planets, which are not in the EOD.
+{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in the
+unit of degree and for now this is only measured for some of the
+directly imaged planets, which are not in the EOD.
 
@@
 \subsection{Transit Parameters}
-We report the transit parameters, which are available only when the planet has TRANSIT flag equal to 1. We describe added fields since \cite{Wright2011} below.
+We report the transit parameters, which are available only when the
+planet has TRANSIT flag equal to 1. We describe added fields since
+\cite{Wright2011} below.
 
-{\bf DR} is the distance between the planet and the star during the transit in stellar radii.
-This is one of the parameters that goes into the transit light curve modeling (see e.g.
-\citealt{Batalha2013}).
+{\bf DR} is the distance between the planet and the star during the
+transit in stellar radii. This is one of the parameters that goes into
+the transit light curve modeling (see e.g. \citealt{Batalha2013}).
 
-{\bf RR} is the ratio of the planetary radius and the stellar radius. If the transit depth (DEPTH) is not given, we calculate DEPTH by taking square of RR but we do not calculate RR from DEPTH.
+{\bf RR} is the ratio of the planetary radius and the stellar
+radius. If the transit depth (DEPTH) is not given, we calculate DEPTH
+by taking square of RR but we do not calculate RR from DEPTH.
 
@@
 \subsection{Secondary Eclipse}
-We have added an entirely new set of fields for the secondary eclipse.
-Previously, due to the limits of instrumentation, there were not much available measured secondary eclipse depths.
-Since \cite{Wright2011}, as many different surveys have been launched, secondary eclipse depths at multiple bands are now available.
-Therefore, we added this entire new set of fields since.
 
-{\bf SE} flag indicates whether the system has detected secondary eclipse in any of the two Micron All-Sky Survey (2MASS) $J$, $H$, and $K_s$, Kepler photometry band, and 4 Spitzer IRAC bands.
-SE is a boolean and being true indicates the system has at least one detected secondary eclipse.
-ZZZ add 2MASS reference!
+We have added an entirely new set of fields for the secondary
+eclipse. Previously, due to the limits of instrumentation, there were
+not much available measured secondary eclipse depths. Since
+\cite{Wright2011}, as many different surveys have been launched,
+secondary eclipse depths at multiple bands are now
+available. Therefore, we added this entire new set of fields since.
 
-{\bf SEDEPTHX} whereas X stands for one of J H KS KP 36 45 58 80: these fields are the secondary eclipse depth measured in the corresponding wavelength band.
-SEDEPTHJ, H, and KS are the depths measured in the 2MASS wavelength band in near infrared each centered at 1.25~\micron, 1.65~\micron, and 2.15~\micron, respectively.
-KP is the depth measured in the \kepler\ photometry band which ranges from 400 to 865~nm.
-The rest four stand for the Spitzer bands centered at 3.6~\micron, 4.5~\micron, 5.8~\micron, and 8.0~\micron.
+{\bf SE} flag indicates whether the system has detected secondary
+eclipse in any of the two Micron All-Sky Survey (2MASS;
+\citealt{Skrustskie2006}) $J$, $H$, and $K_s$, Kepler photometry band,
+and 4 Spitzer IRAC bands. SE is a boolean and being true indicates the
+system has at least one detected secondary eclipse.
+
+{\bf SEDEPTHX} whereas X stands for one of J H KS KP 36 45 58 80:
+these fields are the secondary eclipse depth measured in the
+corresponding wavelength band. SEDEPTHJ, H, and KS are the depths
+measured in the 2MASS wavelength band in near infrared each centered
+at 1.25~\micron, 1.65~\micron, and 2.15~\micron, respectively. KP is
+the depth measured in the \kepler\ photometry band which ranges from
+400 to 865~nm. The rest four stand for the Spitzer bands centered at
+3.6~\micron, 4.5~\micron, 5.8~\micron, and 8.0~\micron.
 
@@
 \subsection{Stellar Properties}
-This set of parameters is to provide users the physical parameters of the exoplanet host stars. 
-Most of the parameters are derived from the stellar models in the literatures and we provide the readers with the references. We describe added fields since \cite{Wright2011} below.
+This set of parameters is to provide users the physical parameters of
+the exoplanet host stars.  Most of the parameters are derived from the
+stellar models in the literatures and we provide the readers with the
+references. We describe added fields since \cite{Wright2011} below.
 
-{\bf GAMMA} ($\gamma$) is the radial velocity of the center of mass of the planetary system and is reported in km/s.
+{\bf GAMMA} ($\gamma$) is the radial velocity of the center of mass of
+the planetary system and is reported in km/s.
 
@@
 
-We provide the brightness of the host star measured in different wavelengths.
-We report optical magnitudes ($V$ and $B-V$), 2MASS $J$, $H$, and $K_s$ magnitudes and we added {\bf KP} since \cite{Wright2011}, which is the stellar magnitude measured through the Kepler bandpass.
+We provide the brightness of the host star measured in different
+wavelengths. We report optical magnitudes ($V$ and $B-V$), 2MASS $J$,
+$H$, and $K_s$ magnitudes and we added {\bf KP} since
+\cite{Wright2011}, which is the stellar magnitude measured through the
+Kepler bandpass.
 
@@
 \subsection{Coordinates and Catalogs}
-We report the coordinates of the host star as well as the stellar ID as designated by different catalogs. 
-We added {\bf DIST} since \cite{Wright2011}, which is the distance of the host star in the unit of pc.
-If only parallax (PAR) is given, we convert it to DIST and vice versa.
-If the literature does not report DIST or PAR, then we obtain PAR from the Hipparcos data set by van Leeuwen (2009).
-ZZZ add a reference for Leeuwen
+We report the coordinates of the host star as well as the stellar ID
+as designated by different catalogs.  We added {\bf DIST} since
+\cite{Wright2011}, which is the distance of the host star in the unit
+of pc. If only parallax (PAR) is given, we convert it to DIST and vice
+versa. If the literature does not report DIST or PAR, then we obtain
+PAR from the Hipparcos data set by \cite{van Leeuwen2009}.
 
@@
 Added field: MONTH, PLANETDISCMETH, STARDISCMETH.
-The following fields now have XREF and XURL: (previously in \cite{Wright2011}) DIST, TRANSIT, BINARY; (new) fields in stellar parameters: V, VSINI, GAMMA; all orbit pars except for trend and freeze\_ecc; all transit parameters; all SE parameters; fields for stellar properties: MSTAR, RSTAR, TEFF, RHOSTAR, LOGG, FE.
+The following fields now have XREF and XURL: (previously in
+\cite{Wright2011}) DIST, TRANSIT, BINARY; (new) fields in stellar
+parameters: V, VSINI, GAMMA; all orbit pars except for trend and
+freeze\_ecc; all transit parameters; all SE parameters; fields for
+stellar properties: MSTAR, RSTAR, TEFF, RHOSTAR, LOGG, FE.
 
@@
 
-{\bf MONTH} field reports an integer of the month when the peer-reviewed paper is accepted to the
-ApJ to better track of the trend in the exoplanet detections.
+{\bf MONTH} field reports an integer of the month when the
+peer-reviewed paper is accepted to the ApJ to better track of the
+trend in the exoplanet detections.
 
-{\bf PLANETDISCMENT} and {\bf STARDISCMETH} are the fields that report the discovery methods for the host star and the planet See Section~ for more details.
+{\bf PLANETDISCMENT} and {\bf STARDISCMETH} are the fields that report
+the discovery methods for the host star and the planet See Section~
+for more details.
 
@@
 
-{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in the unit of degree.
-We report the projected spin-orbit misalignment of transiting systems, which is measured by ZZZ Rossiter-McLaughlin effect.
-$\lambda$ is introduced because the true spin-orbit angle ($\phi$), defined as the angle between the stellar spin axis and the orbital axis, is normally not directly measurable.
-We follow the definition of $\lambda$ in Fabrycky and Winn 2009 where the coordinates are defined as follows; the $z$-axis points toward the observer, the $x$-axis points along the intersection of the sky plane and the planet's orbital plane with the ascending node of the planet having $x<0$, and the $y$-axis completes a right handed-triad.
-$\lambda$ is measured clockwise on the sky from the $y$-axis to the projected stellar rotational axis.
-Some literatures report $\beta = -\lambda$ instead.
-We sorted these cases out and made sure that our $\lambda$'s are following the definition of Fabrycky and Winn 2009.
+{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
+the unit of degree. We report the projected spin-orbit misalignment of
+transiting systems, which is measured by ZZZ Rossiter-McLaughlin
+effect. $\lambda$ is introduced because the true spin-orbit angle
+($\phi$), defined as the angle between the stellar spin axis and the
+orbital axis, is normally not directly measurable. We follow the
+definition of $\lambda$ in Fabrycky and Winn 2009 where the
+coordinates are defined as follows; the $z$-axis points toward the
+observer, the $x$-axis points along the intersection of the sky plane
+and the planet's orbital plane with the ascending node of the planet
+having $x<0$, and the $y$-axis completes a right
+handed-triad. $\lambda$ is measured clockwise on the sky from the
+$y$-axis to the projected stellar rotational axis. Some literatures
+report $\beta = -\lambda$ instead. We sorted these cases out and made
+sure that our $\lambda$'s are following the definition of Fabrycky and
+Winn 2009.
 
-{\bf I} is the orbital inclination.
-This field is not newly added but we chose to describe it here since our database now has the inclination for planets detected by methods other than transit.
-Previously, only transiting systems used to have the inclination measured.
-However, now sometimes for
-non-transiting systems the values of I are also available.
-For instance, if the system was first detected by radial velocity and has a follow-up transit observation, then the inclination can be measured.
-To sum up, all the transiting planets have measured orbital inclination and currently, we also have one microlensing planet with measured inclination.
-*** give the example!
+{\bf I} is the orbital inclination. This field is not newly added but
+we chose to describe it here since our database now has the
+inclination for planets detected by methods other than
+transit. Previously, only transiting systems used to have the
+inclination measured. However, now sometimes for non-transiting
+systems the values of I are also available. For instance, if the
+system was first detected by radial velocity and has a follow-up
+transit observation, then the inclination can be measured. To sum up,
+all the transiting planets have measured orbital inclination and
+currently, we also have one microlensing planet with measured
+inclination. *** give the example!
 
-{\bf OTHERNAME} - This is now listed as other name of planet instead of star;
-** OTHTERNAME has always been the name of the star I think...?
+{\bf OTHERNAME} - This is now listed as other name of planet instead
+of star; ** OTHTERNAME has always been the name of the star I
+think...?
 
-{\bf DISCMETH} field previously reported the mouthed of discovery, which was either radial velocity or transit.
-We have replaced DISCMETH with {\bf PLANETDISCMETH} and {\bf STARDISCMETH} to better report how the host star and the planet are detected.
-Furthermore, they now have value of one of the following: radial velocity, transit, imaging, microlensing, timing, or astrometry.
+{\bf DISCMETH} field previously reported the mouthed of discovery,
+which was either radial velocity or transit. We have replaced DISCMETH
+with {\bf PLANETDISCMETH} and {\bf STARDISCMETH} to better report how
+the host star and the planet are detected. Furthermore, they now have
+value of one of the following: radial velocity, transit, imaging,
+microlensing, timing, or astrometry.
 
-{\bf S} field previously reported the Mount Wilson Ca II S-value and now it is changed to SHK. 
-; ZZZ What's the source for SHK and RHK? Still discovery paper and Butler 2006? ZZZ SHK is a poorly maintained field, and it is unreferenced at the moment though we plan to include proper reference
-in the future.
+{\bf S} field previously reported the Mount Wilson Ca II S-value and
+now it is changed to SHK.  ; ZZZ What's the source for SHK and RHK?
+Still discovery paper and Butler 2006? ZZZ SHK is a poorly maintained
+field, and it is unreferenced at the moment though we plan to include
+proper reference in the future.
 
-{\bf SPSTAR} field previously reported the stellar type of the host star. We choose to remove this field because....? - stellar type of star (unvetted), gone;
+{\bf SPSTAR} field previously reported the stellar type of the host
+star. We choose to remove this field because....? - stellar type of
+star (unvetted), gone;
 
-{\bf NSTEDID} field reported ID of host star in NStED and now it is replaced by EANAME, which is the name of the star as appears on the Exoplanet Archive.
+{\bf NSTEDID} field reported ID of host star in NStED and now it is
+replaced by EANAME, which is the name of the star as appears on the
+Exoplanet Archive.
 
-{\bf MASSREF} and {\bf MASSURL} fields were used to report the reference and the url of stellar mass but now they are used for planet mass.
+{\bf MASSREF} and {\bf MASSURL} fields were used to report the
+reference and the url of stellar mass but now they are used for planet
+mass.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Inclusion of the Kepler Planet Candidates and Other Exoplanets on Exoplanets.org}\label{sec:kepler}
 
-Since \cite{Wright2011}, as more planets were discovered
-by different methods other than radial velocity and transit, we have expanded this information to better ingest those planets into our database.
+Since \cite{Wright2011}, as more planets were discovered by different
+methods other than radial velocity and transit, we have expanded this
+information to better ingest those planets into our database.
 
-Planets primarily detected by these methods do not have robust orbital parameters, they are categorized as ``Other Planets'' on exoplanets.org.
+Planets primarily detected by these methods do not have robust orbital
+parameters, they are categorized as ``Other Planets'' on
+exoplanets.org.
 

### 2014-03-06 draft/ms.tex
Revision of Introduction with added references.

@@
 % Recent development in exoplanet discoveries
+Since the launch of NASA's \kepler\ mission \citep{Borucki2010}, the
+number of confirmed exoplanets has increased from about 300 to over
+1490 as of March 2014 (exoplanets.org). \kepler\ contributed to a vast
+majority of these new discoveries ($> 800$) while providing an
+additional sample of over 3000 exoplanet candidates(\kepler\ Objects
+of Interest, KOIs; e.g.~\citealt{Batalha2013}). The transit method has
+surpassed the radial velocity (RV) method and become the most fruitful
+mean for detecting exoplanets. Meanwhile, great promises lie within
+the new and future exoplanet surveys and instruments with direct
+imaging (e.g., the Gemini Planet Imager, GPI,
+\citealt{Macintosh2014}) and microlensing (e.g., the Wide-Field
+InfraRed Survey Telescope, WFIRST, \citealt{Green2012}), while the
+fronts of RV and transit exoplanet searches keep expanding (e.g., the
+MINiature Exoplanet RV Array, MINERVA, \citealt{Wright2014}; and the
+Transiting Exoplanet Survey Satellit, TESS, \citealt{Ricker2010}).
+
+% The business of tracking planet discoveries and EOD
+This paper describes the continuing efforts since \cite{Butler2006}
+and \cite{Wright2011} to maintain the Exoplanet Orbit Database (EOD)
+and the Exoplanets Data Explorer to keep track of the exoplanet
+discoveries and catalog their orbital parameters and host star
+properties. There are also other entities devoted to this effort,
+including the Extrasolar Planets Encyclopaedia\footnote{See
+  \url{http://exoplanet.eu}.}  \citep{Schneider2011}, the NASA
+Exoplanet Archive\footnote{See
+  \url{http://exoplanetarchive.ipac.caltech.edu}.}
+\citep{Akeson2013}. As described in \cite{Wright2011}, the EOD is
+dedicated to cataloging all \emph{robustly-detected} exoplanets with
+\emph{well-determined} orbital parameters published in
+\emph{peer-reviewed} literature.
+
+% data access and popularity
+The EOD is hosted by exoplanets.org, which also hosts the Exoplanets
+Data Explorer, an interactive table with plotting tools including all
+the EOD exoplanets as well as other confirmed exoplanets (and now also
+KOIs). The entire dataset of exoplanets.org is available for download
+as a single {\tt .csv} file at the website's front page.\footnote{At
+  \url{exoplanets.org/csv-files/exoplanets.csv}.} The EOD is widely
+used in exoplanet researches (e.g., \citealt{Dawson2013},
+\citealt{Howard2013}, \citealt{Kipping2013}, \citealt{Kane2014},
+\citealt{Weiss2014}), and the website exoplanets.org is among the most
+visited exoplanet databases, with over $47,000$ visitors in 2013
+according to Google Analytics.
+
+% updates on EOD and the website
+Since \cite{Wright2011}, the EOD has expanded its scope and we now do
+not require the host star of an exoplanet to be a normal star (e.g.,
+exoplanets around pulsars are now included). It has also ingested more
+parameters of the exoplanet systems and host stars, and some
+parameters are revised or deleted. We describe the updates with the
+EOD in Section~\ref{sec:update}. We also describe the updates to the
+hosting website, exoplanets.org. The Exoplanet Data Explorer at
+exoplanets.org has expanded its scope and now includes the
+\kepler\ exoplanet candidates (KOIs). We describe these changes in
+Section~\ref{sec:kepler}. The website has also gone through major
+back-end changes since \cite{Wright2011}, which is described in
+Section~\ref{sec:website}.
+
+%------------------------------------------------------------------
+% RECYCLE BIN
+\begin{comment}
 Since the first peer-reviewed list of exoplanets with robust orbits
@@
 precise radial velocity (RV) method. However, since 2009, \kepler\ has
-contributed over $\sim$ 800 confirmed exoplanets
-\citep[e.g.,][]{Rowe2014} as well as over 3000 exoplanet candidates
-(\kepler\ Objects of Interest, KOIs; e.g.~\citealt{Batalha2013}).
+contributed over $\sim$ 800 confirmed exoplanets (e.g.,
+\ciatealt{Marcy2014}, \citealt{Rowe2014}) as well as over 3000
+exoplanet candidates (\kepler\ Objects of Interest, KOIs;
+e.g.~\citealt{Batalha2013}).
 
-% The business of tracking planet discoveries
 As the number of exoplanet discoveries keeps rising, it is important
@@
 
-% What is this paper about
 This paper describes the continuing efforts since \cite{Wright2011} to
-maintain the EOD and the Exoplanets Data Explorer at
-exoplanets.org. The EOD has expanded to include all robustly-detected
-exoplanets (around {\it any} type of host star) with well-determined
-orbital parameters published in peer-reviewed literature. It has also
-ingested more parameters of the exoplanet systems and host stars, and
-some parameters are revised or deleted. We describe the updates with
-the EOD in Section~\ref{sec:update}.
+maintain the EOD and the Exoplanets Data Explorer at exoplanets.org.
 
-% also the website
-We also describe the updates to the website that hosts the EOD and the
-Exoplanet Data Explorer, exoplanets.org. As one of the mostly visited
-exoplanet database, exoplanets.org had $47,000$ visitors in 2013
-according to Google Analytics. The Exoplanet Data Explorer has
-expanded its scope and now includes the \kepler\ exoplanet
-candidates. We describe these changes in Section~\ref{sec:kepler}. The
-website has also gone through major back-end changes since
-\cite{Wright2011}, which is described in Section~\ref{sec:website}.
+The efforts of keeping track of exoplanet discoveries are being
+carried out by several entities, and most notably, the Extrasolar
+Planets Encyclopaedia\footnote{See \url{http://exoplanet.eu}.}
+\citep{Schneider2011}, the NASA Exoplanet Archive\footnote{See
+  \url{http://exoplanetarchive.ipac.caltech.edu}.}
+\citep{Akeson2013}, and the Exoplanet Orbit Database (EOD) and
+Exoplanets Data Explorer\footnote{See \url{http://exoplanets.org}.}
+\citep{Wright2011}.
+\end{comment}
+%------------------------------------------------------------------
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Updates on the EOD}\label{sec:update}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Updates on the Website}\label{sec:website}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion and Future}\label{sec:conclusion}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \acknowledgments
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % References:
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Table
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{CJK*}

### 2014-03-06 draft/references.tex
Add several missing references in Sec 2.
Add 2MASS reference.

@@
 
+\bibitem[Cosentino et al.(2012)]{Cosentino2012} Cosentino, R., et al.\ 
+2012, \procspie, 8446, 1V % HARPS-North
+
+\bibitem[Dawson \& Murray-Clay(2013)]{Dawson2013} Dawson, R.~I., \&
+  Murray-Clay, R.~A.\ 2013, \apjl, 767, L24  % use of EOD
+
 \bibitem[Fabrycky \& Winn(2009)]{Fabrycky2009} Fabrycky, D.~C., \&
   Winn, J.~N.\ 2009, \apj, 696, 1230 % spin-orbit misalignment lambda definition
+
+\bibitem[Green et al.(2012)]{Green2012} Green, J., et al.\ 2012, 
+arXiv:1208.4012   % WFIRST
+
+\bibitem[Howard(2013)]{Howard2013} Howard, A.~W.\ 2013, Science, 340,
+  572 % use of EOD
+
+\bibitem[Kane(2014)]{Kane2014} Kane, S.~R.\ 2014, \apj, 782, 111 % use
+                                % of EOD
+
+\bibitem[Kipping(2013)]{Kipping2013} Kipping, D.~M.\ 2013, \mnras,
+  434, L51 % use of EOD
 
@@
 
+\bibitem[Macintosh et al.(2014)]{Macintosh2014} Macintosh, B., Gemini 
+Planet Imager instrument team, Planet Imager Exoplanet Survey, G., 
+\& Observatory, G.\ 2014, American Astronomical Society Meeting
+Abstracts, 223, \#229.02  % GPI
+
+\bibitem[Marcy et al.(2014)]{Marcy2014} Marcy, G.~W., et al.\ 2014, \apjs, 
+210, 20 % 42 RV confirmed small Kepler planets
+
 \bibitem[Mordasini et al.(2012)]{Mordasini2012} Mordasini, C., Alibert, Y., 
@@
 % Mass-Radius for 6 Re < R < 11.684 Re
+
+\bibitem[Ricker et al.(2010)]{Ricker2010} Ricker, G.~R., et al.\ 2010, 
+Bulletin of the American Astronomical Society, 42, \#450.06 % TESS
 
@@
 
+\bibitem[Skrutskie et al.(2006)]{Skrutskie2006} Skrutskie, M.~F., et al.\ 
+2006, \aj, 131, 1163 % 2MASS
+
 \bibitem[Sotin et al.(2007)]{Sotin2007} Sotin, C., Grasset, O., 
 \& Mocquet, A.\ 2007, \icarus, 191, 337 % Mass-Radius for M<1Me, R<1Re
+
+\bibitem[van Leeuwen(2009)]{van Leeuwen2009} van Leeuwen, F.\ 2009, \aap, 
+497, 209 % Hipparcos catalog
 
@@
 
+\bibitem[Wright et al.(2014)]{Wright2014} Wright, J., et al.\ 2014, 
+American Astronomical Society Meeting Abstracts, 223, \#148.31
+
 \end{thebibliography}

### 2014-03-06 draft/ms.tex
Partial re-aranging of table.

@@
 
+% NEW ORGANIZATION ACCORDING TO INDIVIDUAL PLANET PAGE
 \begin{deluxetable}{llll}
@@
 %
-\sidehead{\textbf{Planet Information}}
+\sidehead{\textbf{Discovery and References}}
 NAME\dotfill & String & Name of planet & \nodata \\
 OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of planet & \nodata \\
+DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata \\
+MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\
+PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata \\
+STARDISCMETH\dotfill & String & Method of discovery of first planet in system & \nodata \\
+ORBREF\dotfill & String & Peer-reviewed origin of orbital parameters & ORBURL \\
+FIRSTREF\dotfill & String & First peer-reviewed publication of
+planetary orbit & FIRSTURL \\
+JSNAME\dotfill & String & Name of host star used in the Extrasolar
+Planets Encyclopaedia & EPEURL \\
+ETDNAME\dotfill & String & Name of planet used in the Exoplanet
+Transit Database & ETDURL \\
+EANAME\dotfill & String & Name of planet used in the Exoplanet
+Archive database & EAURL \\
+SIMBADNAME\dotfill & String & Valid SIMBAD name of host star (or
+planet, if available) & SIMBADURL \\
+KEPID\dotfill & Long Integer & The unique \kepler\ star identifier &
+\nodata \\
+KOI\dotfill & Float & KOI object number & \nodata \\
+KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata \\
+EOD\dotfill & Boolean & If true, planet is included in the EOD & \nodata \\
+MICROLENSING\dotfill & Boolean & If true, planet was detected via microlensing & \nodata \\
+IMAGING\dotfill & Boolean & If true, planet was detected via imaging & \nodata \\
+TIMING\dotfill & Boolean & If true, planet was detected via timing & \nodata \\
+ASTROMETRY\dotfill & Boolean & If true, planet was detected via astrometric motion & \nodata \\
+
+% STILL OLD SORTING BELOW
+
+%
+\sidehead{\textbf{Planet Information}}
 COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) & \nodata \\
@@
 DEC\_STRING\dotfill & String & J2000 declination in sexagesimal string & \nodata \\
-KEPID\dotfill & Long Integer & The unique \kepler\ star identifier & \nodata \\
-KOI\dotfill & Float & KOI object number & \nodata \\
-KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata \\
-EOD\dotfill & Boolean & If true, planet is included in the EOD & \nodata \\
-MICROLENSING\dotfill & Boolean & If true, planet was detected via microlensing & \nodata \\
-IMAGING\dotfill & Boolean & If true, planet was detected via imaging & \nodata \\
-TIMING\dotfill & Boolean & If true, planet was detected via timing & \nodata \\
-ASTROMETRY\dotfill & Boolean & If true, planet was detected via astrometric motion & \nodata \\
 %
@@
 MULT\dotfill & Boolean & Multiple planets in system? & \nodata \\
-PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata \\
-STARDISCMETH\dotfill & String & Method of discovery of first planet in system & \nodata \\
-DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata \\
-MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\
-FIRSTREF\dotfill & String & First peer-reviewed publication of
-planetary orbit & FIRSTURL \\
-ORBREF\dotfill & String & Peer-reviewed origin of orbital parameters & ORBURL \\
+
 %
@@
 \sidehead{\textbf{Links}}
-JSNAME\dotfill & String & Name of host star used in the Extrasolar
-Planets Encyclopaedia & EPEURL \\
-ETDNAME\dotfill & String & Name of planet used in the Exoplanet
-Transit Database & ETDURL \\
-SIMBADNAME\dotfill & String & Valid SIMBAD name of host star (or
-planet, if available) & SIMBADURL \\
-EANAME\dotfill & String & Name of planet used in the Exoplanet
-Archive database & EAURL \\
+
 \enddata

### 2014-03-06 draft/ms.tex
Uncertainties and Upper Limit section update

--- 2014-03-06 draft/ms.tex
@@
 %------------------------------------------------------------------------------
-\subsection{Uncertainties}
+\subsection{Uncertainties and Upper Limits}
 
@@
 equals to $({\rm XUPPER+XLOWER})/2$ in the case of asymmetric error
-bars. Fields that have XUPPER, XLOWER and UX are: (list of fields).
+bars.
+Fields that have XUPPER, XLOWER and UX are:  all the orbital parameters except for TREND and FREEZE\_ECC flags; all the transit parameters except for TRANSIT flags; all the secondary eclipse fields except for SE flag; and all the stellar properties except for STAR, SPECREF and BINARY flag; and DIST and PAR.
+We also report the upper limits for planet mass (MSINI), eccentricity (ECC), and the velocity semi-amplitude (K) when the literatures only provide the upper limits and not the actual values.
+The upper limits for ECC is reported when the orbit is circular, and the upper limits for K is reported when there is no radial velocity detection.
+If only upper limits are given, we set the field to 0, the uncertainty to half of the upper limit, and the upper limits to the upper limits.
+For example, if the literature reports the upper limit for ECC, then we put the value in ECCUL, set ECC to be 0, ECCUPPER to ECCUL, and UECC to ECCUL/2.
 
+ZZZ modify table to reflect MASSUL, ECCUL, KUL, fields
 %------------------------------------------------------------------------------
@@
 
-{\bf MONTH} field reports an integer of the month when the
+{\bf MONTH} field reports the month in integer when the
 peer-reviewed paper is accepted to the ApJ to better track of the
@@
 \subsection{Revised and Removed Fields}
+ZZZ CPSNAME?
+
 We have major updates by taking out some of the fields and by revising the existing fields. Here, we explain why we removed or revised such fields.

### 2014-03-06 draft/ms.tex
Re-arranged table according to new sortings same as individual planet page.

--- 2014-03-06 draft/ms.tex
@@
 %------------------------------------------------------------------------------
-\subsection{Uncertainties and Upper Limits}
+\subsection{Uncertainties}
 
@@
 equals to $({\rm XUPPER+XLOWER})/2$ in the case of asymmetric error
-bars.
-Fields that have XUPPER, XLOWER and UX are:  all the orbital parameters except for TREND and FREEZE\_ECC flags; all the transit parameters except for TRANSIT flags; all the secondary eclipse fields except for SE flag; and all the stellar properties except for STAR, SPECREF and BINARY flag; and DIST and PAR.
-We also report the upper limits for planet mass (MSINI), eccentricity (ECC), and the velocity semi-amplitude (K) when the literatures only provide the upper limits and not the actual values.
-The upper limits for ECC is reported when the orbit is circular, and the upper limits for K is reported when there is no radial velocity detection.
-If only upper limits are given, we set the field to 0, the uncertainty to half of the upper limit, and the upper limits to the upper limits.
-For example, if the literature reports the upper limit for ECC, then we put the value in ECCUL, set ECC to be 0, ECCUPPER to ECCUL, and UECC to ECCUL/2.
+bars. Fields that have XUPPER, XLOWER and UX are: (list of fields).
 
-ZZZ modify table to reflect MASSUL, ECCUL, KUL, fields
 %------------------------------------------------------------------------------
@@
 
-{\bf MONTH} field reports the month in integer when the
+{\bf MONTH} field reports an integer of the month when the
 peer-reviewed paper is accepted to the ApJ to better track of the
@@
 \subsection{Revised and Removed Fields}
-ZZZ CPSNAME?
-
 We have major updates by taking out some of the fields and by revising the existing fields. Here, we explain why we removed or revised such fields.
@@
 %
-\sidehead{\textbf{Planet Information}}
+\sidehead{\textbf{Discovery and References}}
 NAME\dotfill & String & Name of planet & \nodata \\
 OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of planet & \nodata \\
-COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) & \nodata \\
-HD\dotfill & Long Integer & Henry Draper number of sar & \nodata \\
-HR\dotfill & Integer & Bright Star Catalog number of star & \nodata \\
-HIPP\dotfill & Long Integer & \textit{Hipparcos} catalog number of
-star & \nodata \\
-SAO\dotfill & Long Integer & SAO catalog number of star & \nodata \\
-GL\dotfill & Float & GJ or Gliese catalog number of star & \nodata \\
-BINARY\dotfill & Boolean & Star known ot be binary? & -REF, -URL \\
-RA\dotfill & Double & J2000 right ascension in decimal hours & \nodata \\
-RA\_STRING\dotfill & String & J2000 right ascension in sexagesimal string & \nodata  \\
-DEC\dotfill & Double & J2000 declination in decimal degrees & \nodata \\
-DEC\_STRING\dotfill & String & J2000 declination in sexagesimal string & \nodata \\
-KEPID\dotfill & Long Integer & The unique \kepler\ star identifier & \nodata \\
+DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata \\
+MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\
+PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata \\
+STARDISCMETH\dotfill & String & Method of discovery of first planet in system & \nodata \\
+ORBREF\dotfill & String & Peer-reviewed origin of orbital parameters & ORBURL \\
+FIRSTREF\dotfill & String & First peer-reviewed publication of
+planetary orbit & FIRSTURL \\
+JSNAME\dotfill & String & Name of host star used in the Extrasolar
+Planets Encyclopaedia & EPEURL \\
+ETDNAME\dotfill & String & Name of planet used in the Exoplanet
+Transit Database & ETDURL \\
+EANAME\dotfill & String & Name of planet used in the Exoplanet
+Archive database & EAURL \\
+SIMBADNAME\dotfill & String & Valid SIMBAD name of host star (or
+planet, if available) & SIMBADURL \\
+KEPID\dotfill & Long Integer & The unique \kepler\ star identifier &
+\nodata \\
 KOI\dotfill & Float & KOI object number & \nodata \\
@@
 %
-\sidehead{\textbf{Stellar Parameters}}
-BMV\dotfill & Float & $B-V$ color & \nodata \\
-V\dotfill & Float & $V$ magnitude & -REF,-URL \\
-J\dotfill & Float & $J$ magnitude & \nodata \\
-H\dotfill & Float & $H$ magnitude & \nodata \\
-KS\dotfill & Float & $K_S$ magnitude & \nodata \\
-DIST\dotfill & Float & Distance to host star based on parallax in parsecs & -UPPER, etc. \\
-PAR\dotfill & Float & Parallax in mas & -UPPER,-LOWER,U- \\
-VSINI\dotfill & Float & Projected equatorial rotational velocity of
-star in k\mps & -UPPER, etc. \\
-GAMMA\dotfill & Float & Systemic radial velocity in k\mps & -UPPER, etc. \\
-%
-\sidehead{\textbf{Orbit Parameters}}
+\sidehead{\textbf{Orbital Parameters}}
+MSINI\dotfill & Float & Minimum mass (as calculated from the mass
+function) in \mjup & -UPPER, etc. \\
+MASS\dotfill & Float & Mass of planet in \mjup & -UPPER, etc. \\
+A\dotfill & Float & Orbital semimajor axis in AU & -UPPER, etc. \\
+SEP\dotfill & Float & Separation between host star and planet in AU & -UPPER, etc. \\
 PER\dotfill & Double & Orbital period in days & -UPPER, etc. \\
+K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps &
+-UPPER, etc. \\
 ECC\dotfill & Float & Orbital eccentricity & -UPPER, etc. \\
+I\dotfill & Float & Orbital inclination in degrees & -UPPER, etc. \\
 OM\dotfill & Float & Argument of periastron in degrees & -UPPER, etc. \\
-K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps & -UPPER, etc. \\
+BIGOM\dotfill & Float & Longitude of ascending node in degrees & -UPPER, etc. \\
 T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{d} & -UPPER, etc. \\
 DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER, etc. \\
-I\dotfill & Float & Orbital inclination in degrees & -UPPER, etc. \\
-MSINI\dotfill & Float & Minimum mass (as calculated from the mass
-function) in \mjup & -UPPER, etc. \\
-A\dotfill & Float & Orbital semimajor axis in AU & -UPPER, etc. \\
-MASS\dotfill & Float & Mass of planet in \mjup & -UPPER, etc. \\
-SEP\dotfill & Float & Separation between host star and planet in AU & -UPPER, etc. \\
-TREND\dotfill  & Boolean & Linear trend in fit? & \nodata \\
-LAMBDA\dotfill & Float & Projected spin-orbit misalignment in degrees & -UPPER, etc. \\
-BIGOM\dotfill & Float & Longitude of ascending node in degrees & -UPPER, etc. \\
-FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \nodata \\
+LAMBDA\dotfill & Float & Projected spin-orbit misalignment in degrees
+& -UPPER, etc. \\
+TRANSIT\dotfill & Boolean & Is the planet known to transit? & -REF,-URL \\
 %
 \sidehead{\textbf{Transit Parameters}}
-DEPTH\dotfill & Float & Transit depth, $(R_p/R_*)^2$ & -UPPER, etc. \\
-T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER, etc. \\
+R\dotfill & Float & Radius of planet in Jupiter radii & -UPPER,
+etc. \\
 TT\dotfill & Float & Epoch of transit center in
 HJD\tablenotemark{d} & -UPPER, etc. \\
-R\dotfill & Float & Radius of planet in Jupiter radii & -UPPER, etc. \\
+T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER, etc. \\
+B\dotfill & Float & Impact parameter of transit & -UPPER, etc. \\
 AR\dotfill & Float & $(a/R_*)$ & -UPPER, etc. \\
-B\dotfill & Float & Impact parameter of transit & -UPPER, etc. \\
+DEPTH\dotfill & Float & Transit depth, $(R_p/R_*)^2$ & -UPPER, etc. \\
 DENSITY\dotfill & Float & Density of planet in g cc$^{-1}$ &
@@
 -UPPER, etc. \\
-TRANSIT\dotfill & Boolean & Is the planet known to transit? & -REF,-URL \\
 DR\dotfill & Float & Distance during transit in stellar radii & -UPPER, etc. \\
@@
 %
-\sidehead{\textbf{Secondary Eclipse}}
+\sidehead{\textbf{Orbital Fit Properties}}
+CHI2\dotfill & Float & $\chi_{\nu}^2$ to orbital RV fit & \nodata \\
+NOBS\dotfill & Integer & Number of observations used in fit & \nodata \\
+RMS\dotfill & Float & Root-mean-square residuals to orbital RV fit &
+\nodata \\
+FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \nodata \\
+TREND\dotfill  & Boolean & Linear trend in fit? & \nodata \\
+NCOMP\dotfill & Integer & Number of planetary companions known & \nodata \\
+MULT\dotfill & Boolean & Multiple planets in system? & \nodata \\
+COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) & \nodata \\
+%
+\sidehead{\textbf{Secondary Eclipse Depth}}
 SE\dotfill & Boolean & If true, at least one secondary eclipse has
@@
 %
-\sidehead{\textbf{Fit \& References}}
-RMS\dotfill & Float & Root-mean-square residuals to orbital RV fit & \nodata \\
-CHI2\dotfill & Float & $\chi_{\nu}^2$ to orbital RV fit & \nodata \\
-NOBS\dotfill & Integer & Number of observations used in fit & \nodata \\
-NCOMP\dotfill & Integer & Number of planetary companions known & \nodata \\
-MULT\dotfill & Boolean & Multiple planets in system? & \nodata \\
-PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata \\
-STARDISCMETH\dotfill & String & Method of discovery of first planet in system & \nodata \\
-DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata \\
-MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\
-FIRSTREF\dotfill & String & First peer-reviewed publication of
-planetary orbit & FIRSTURL \\
-ORBREF\dotfill & String & Peer-reviewed origin of orbital parameters & ORBURL \\
-%
 \sidehead{\textbf{Stellar Properties}}
 STAR\dotfill & String & Standard name for host star & \nodata \\
+BINARY\dotfill & Boolean & Star known ot be binary? & -REF, -URL \\
 MSTAR\dotfill & Float & Mass of host star in solar mass & -UPPER, etc. \\
 RSTAR\dotfill & Float & Radius of host star in solar radii & -UPPER, etc. \\
+FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER, etc. \\
 TEFF\dotfill & Float & Effective temperature of host star & -UPPER, etc. \\
@@
 host star in cgs unit & -UPPER, etc. \\
-FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER, etc. \\
+VSINI\dotfill & Float & Projected equatorial rotational velocity of
+star in k\mps & -UPPER, etc. \\
+GAMMA\dotfill & Float & Systemic radial velocity in k\mps & -UPPER, etc. \\
+%
+\sidehead{\textbf{Stellar Magnitudes}}
+V\dotfill & Float & $V$ magnitude & -REF,-URL \\
+BMV\dotfill & Float & $B-V$ color & \nodata \\
+J\dotfill & Float & $J$ magnitude & \nodata \\
+H\dotfill & Float & $H$ magnitude & \nodata \\
+KS\dotfill & Float & $K_S$ magnitude & \nodata \\
 SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \nodata \\
@@
 %
-\sidehead{\textbf{Links}}
-JSNAME\dotfill & String & Name of host star used in the Extrasolar
-Planets Encyclopaedia & EPEURL \\
-ETDNAME\dotfill & String & Name of planet used in the Exoplanet
-Transit Database & ETDURL \\
-SIMBADNAME\dotfill & String & Valid SIMBAD name of host star (or
-planet, if available) & SIMBADURL \\
-EANAME\dotfill & String & Name of planet used in the Exoplanet
-Archive database & EAURL \\
+\sidehead{\textbf{Coordinates and Catalogs}}
+RA\dotfill & Double & J2000 right ascension in decimal hours & \nodata \\
+RA\_STRING\dotfill & String & J2000 right ascension in sexagesimal string & \nodata  \\
+DEC\dotfill & Double & J2000 declination in decimal degrees & \nodata \\
+DEC\_STRING\dotfill & String & J2000 declination in sexagesimal string & \nodata \\
+PAR\dotfill & Float & Parallax in mas & -UPPER,-LOWER,U- \\
+DIST\dotfill & Float & Distance to host star based on parallax in parsecs & -UPPER, etc. \\
+HIPP\dotfill & Long Integer & \textit{Hipparcos} catalog number of
+star & \nodata \\
+HD\dotfill & Long Integer & Henry Draper number of sar & \nodata \\
+GL\dotfill & Float & GJ or Gliese catalog number of star & \nodata \\
+HR\dotfill & Integer & Bright Star Catalog number of star & \nodata \\
+SAO\dotfill & Long Integer & SAO catalog number of star & \nodata \\
+%
 \enddata

### 2014-03-06 draft/ms.tex
Add ref in table, linking to sections or refer to W11.

@@
 %------------------------------------------------------------------------------
-\subsection{Discovery and References}
+\subsection{Discovery and References}\label{sec:disc}
 
@@
 %------------------------------------------------------------------------------
-\subsection{Orbital Parameters}
+\subsection{Orbital Parameters}\label{sec:orbit}
+
 We report the orbital parameters that determine the shape of the
@@
 %------------------------------------------------------------------------------
-\subsection{Transit Parameters}
+\subsection{Transit Parameters}\label{sec:transit}
+
 We report the transit parameters, which are available only when the
@@
 %------------------------------------------------------------------------------
-\subsection{Secondary Eclipse}
+\subsection{Secondary Eclipse}\label{sec:se}
 
@@
 %------------------------------------------------------------------------------
-\subsection{Stellar Properties}
+\subsection{Stellar Properties}\label{sec:stellarprop}
+
 This set of parameters is to provide users the physical parameters of
@@
 %------------------------------------------------------------------------------
-\subsection {Stellar Magnitudes}
+\subsection{Stellar Magnitudes}\label{sec:stellarmag}
 
@@
 %------------------------------------------------------------------------------
-\subsection{Coordinates and Catalogs}
+\subsection{Coordinates and Catalogs}\label{sec:coord}
 We report the coordinates of the host star as well as the stellar ID
@@
 %------------------------------------------------------------------------------
-\subsection{Uncertainties and Upper Limits}
+\subsection{Uncertainties and Upper Limits}\label{sec:unc}
 
@@
 uncertainties, and they are different when the error bars are
-asymmetric. UX contains the 1$\sigma$ uncertainty, and it
-equals to $({\rm XUPPER+XLOWER})/2$ in the case of asymmetric error
-bars.
-Fields that have XUPPER, XLOWER and UX are:  all the orbital parameters except for TREND and FREEZE\_ECC flags; all the transit parameters except for TRANSIT flags; all the secondary eclipse fields except for SE flag; and all the stellar properties except for STAR, SPECREF and BINARY flag; and DIST and PAR.
-We also report the upper limits for planet mass (MSINI), eccentricity (ECC), and the velocity semi-amplitude (K) when the literatures only provide the upper limits and not the actual values.
-The upper limits for ECC is reported when the orbit is circular, and the upper limits for K is reported when there is no radial velocity detection.
-If only upper limits are given, we set the field to 0, the uncertainty to half of the upper limit, and the upper limits to the upper limits.
-For example, if the literature reports the upper limit for ECC, then we put the value in ECCUL, set ECC to be 0, ECCUPPER to ECCUL, and UECC to ECCUL/2.
+asymmetric. UX contains the 1$\sigma$ uncertainty, and it equals to
+$({\rm XUPPER+XLOWER})/2$ in the case of asymmetric error bars. Fields
+that have XUPPER, XLOWER and UX are: all the orbital parameters except
+for TREND and FREEZE\_ECC flags; all the transit parameters except for
+TRANSIT flags; all the secondary eclipse fields except for SE flag;
+and all the stellar properties except for STAR, SPECREF and BINARY
+flag; and DIST and PAR.
 
-ZZZ modify table to reflect MASSUL, ECCUL, KUL, fields
+We also report the upper limits for planet mass (MSINI), eccentricity
+(ECC), and the velocity semi-amplitude (K) when the literatures only
+provide the upper limits and not the actual values. The upper limits
+for ECC is reported when the orbit is circular, and the upper limits
+for K is reported when there is no radial velocity detection. If only
+upper limits are given, we set the field to 0, the uncertainty to half
+of the upper limit, and the upper limits to the upper limits. For
+example, if the literature reports the upper limit for ECC, then we
+put the value in ECCUL, set ECC to be 0, ECCUPPER to ECCUL, and UECC
+to ECCUL/2.
+
 %------------------------------------------------------------------------------
-\subsection{References}
+\subsection{References}\label{sec:ref}
 
@@
 % NEW ORGANIZATION ACCORDING TO INDIVIDUAL PLANET PAGE
-\begin{deluxetable}{llll}
+\begin{deluxetable}{llllc}
+  \center
 \tabletypesize{\scriptsize}
@@
   \colhead{Field\tablenotemark{a}} & \colhead{Data Type} & \colhead{Meaning} &
-  \colhead{Related Fields\tablenotemark{b}}
+  \colhead{Related Fields\tablenotemark{b}} & \colhead{Ref.}
 }
@@
 \sidehead{\textbf{Discovery and References}}
-NAME\dotfill & String & Name of planet & \nodata \\
-OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of planet & \nodata \\
-DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata \\
-MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\
-PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata \\
-STARDISCMETH\dotfill & String & Method of discovery of first planet in system & \nodata \\
-ORBREF\dotfill & String & Peer-reviewed origin of orbital parameters & ORBURL \\
+NAME\dotfill & String & Name of planet & \nodata & W11 \\
+OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of planet & \nodata & \ref{sec:disc} \\
+DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata & W11 \\
+MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata & W11 \\
+PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata & \ref{sec:disc} \\
+STARDISCMETH\dotfill & String & Method of discovery of first planet in system & \nodata & \ref{sec:disc} \\
+ORBREF\dotfill & String & Peer-reviewed origin of orbital parameters & ORBURL & W11 \\
 FIRSTREF\dotfill & String & First peer-reviewed publication of
-planetary orbit & FIRSTURL \\
+planetary orbit & FIRSTURL & W11 \\
 JSNAME\dotfill & String & Name of host star used in the Extrasolar
-Planets Encyclopaedia & EPEURL \\
+Planets Encyclopaedia & EPEURL & W11 \\
 ETDNAME\dotfill & String & Name of planet used in the Exoplanet
-Transit Database & ETDURL \\
+Transit Database & ETDURL & W11 \\
 EANAME\dotfill & String & Name of planet used in the Exoplanet
-Archive database & EAURL \\
+Archive database & EAURL & \ref{sec:disc} \\
 SIMBADNAME\dotfill & String & Valid SIMBAD name of host star (or
-planet, if available) & SIMBADURL \\
+planet, if available) & SIMBADURL & W11 \\
 KEPID\dotfill & Long Integer & The unique \kepler\ star identifier &
-\nodata \\
-KOI\dotfill & Float & KOI object number & \nodata \\
-KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata \\
-EOD\dotfill & Boolean & If true, planet is included in the EOD & \nodata \\
-MICROLENSING\dotfill & Boolean & If true, planet was detected via microlensing & \nodata \\
-IMAGING\dotfill & Boolean & If true, planet was detected via imaging & \nodata \\
-TIMING\dotfill & Boolean & If true, planet was detected via timing & \nodata \\
-ASTROMETRY\dotfill & Boolean & If true, planet was detected via astrometric motion & \nodata \\
+\nodata & \ref{sec:disc} \\
+KOI\dotfill & Float & KOI object number & \nodata & \ref{sec:disc} \\
+KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata & \ref{sec:disc} \\
+EOD\dotfill & Boolean & If true, planet is included in the EOD & \nodata & \ref{sec:disc} \\
+MICROLENSING\dotfill & Boolean & If true, planet was detected via microlensing & \nodata & \ref{sec:disc} \\
+IMAGING\dotfill & Boolean & If true, planet was detected via imaging & \nodata & \ref{sec:disc} \\
+TIMING\dotfill & Boolean & If true, planet was detected via timing & \nodata & \ref{sec:disc} \\
+ASTROMETRY\dotfill & Boolean & If true, planet was detected via astrometric motion & \nodata & \ref{sec:disc} \\
 %
@@
 MSINI\dotfill & Float & Minimum mass (as calculated from the mass
-function) in \mjup & -UPPER, etc. \\
-MASS\dotfill & Float & Mass of planet in \mjup & -UPPER, etc. \\
-A\dotfill & Float & Orbital semimajor axis in AU & -UPPER, etc. \\
-SEP\dotfill & Float & Separation between host star and planet in AU & -UPPER, etc. \\
-PER\dotfill & Double & Orbital period in days & -UPPER, etc. \\
+function) in \mjup & -UL, -UPPER, etc. & W11 \\
+MASS\dotfill & Float & Mass of planet in \mjup & -UPPER, etc. & \ref{sec:orbit} \\
+A\dotfill & Float & Orbital semimajor axis in AU & -UPPER, etc. & W11 \\
+SEP\dotfill & Float & Separation between host star and planet in AU & -UPPER, etc. & \ref{sec:orbit} \\
+PER\dotfill & Double & Orbital period in days & -UPPER, etc. & W11 \\
 K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps &
--UPPER, etc. \\
-ECC\dotfill & Float & Orbital eccentricity & -UPPER, etc. \\
-I\dotfill & Float & Orbital inclination in degrees & -UPPER, etc. \\
-OM\dotfill & Float & Argument of periastron in degrees & -UPPER, etc. \\
-BIGOM\dotfill & Float & Longitude of ascending node in degrees & -UPPER, etc. \\
-T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{d} & -UPPER, etc. \\
-DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER, etc. \\
+-UL, -UPPER, etc. & W11 \\
+ECC\dotfill & Float & Orbital eccentricity & -UL, -UPPER, etc. & W11 \\
+I\dotfill & Float & Orbital inclination in degrees & -UPPER, etc. & \ref{sec:orbit} \\
+OM\dotfill & Float & Argument of periastron in degrees & -UPPER, etc. & W11 \\
+BIGOM\dotfill & Float & Longitude of ascending node in degrees & -UPPER, etc. & \ref{sec:orbit} \\
+T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{d} & -UPPER, etc. & W11 \\
+DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER, etc. & W11 \\
 LAMBDA\dotfill & Float & Projected spin-orbit misalignment in degrees
-& -UPPER, etc. \\
-TRANSIT\dotfill & Boolean & Is the planet known to transit? & -REF,-URL \\
+& -UPPER, etc. & \ref{sec:orbit} \\
+TRANSIT\dotfill & Boolean & Is the planet known to transit? & -REF,-URL & W11 \\
 %
@@
 R\dotfill & Float & Radius of planet in Jupiter radii & -UPPER,
-etc. \\
+etc. & W11 \\
 TT\dotfill & Float & Epoch of transit center in
-HJD\tablenotemark{d} & -UPPER, etc. \\
-T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER, etc. \\
-B\dotfill & Float & Impact parameter of transit & -UPPER, etc. \\
-AR\dotfill & Float & $(a/R_*)$ & -UPPER, etc. \\
-DEPTH\dotfill & Float & Transit depth, $(R_p/R_*)^2$ & -UPPER, etc. \\
+HJD\tablenotemark{d} & -UPPER, etc. & W11 \\
+T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER, etc. & W11 \\
+B\dotfill & Float & Impact parameter of transit & -UPPER, etc. & W11 \\
+AR\dotfill & Float & $(a/R_*)$ & -UPPER, etc. & W11 \\
+DEPTH\dotfill & Float & Transit depth, $(R_p/R_*)^2$ & -UPPER, etc. & W11 \\
 DENSITY\dotfill & Float & Density of planet in g cc$^{-1}$ &
--UPPER, etc. \\
+-UPPER, etc. & W11 \\
 GRAVITY\dotfill & Float & $\log{g}$ (surface gravity) of planet in cgs unit &
--UPPER, etc. \\
-DR\dotfill & Float & Distance during transit in stellar radii & -UPPER, etc. \\
-RR\dotfill & Float & $(R_p/R_*)$ & -UPPER, etc. \\
+-UPPER, etc. & W11 \\
+DR\dotfill & Float & Distance during transit in stellar radii & -UPPER, etc. & \ref{sec:transit} \\
+RR\dotfill & Float & $(R_p/R_*)$ & -UPPER, etc. & \ref{sec:transit} \\
 %
 \sidehead{\textbf{Orbital Fit Properties}}
-CHI2\dotfill & Float & $\chi_{\nu}^2$ to orbital RV fit & \nodata \\
-NOBS\dotfill & Integer & Number of observations used in fit & \nodata \\
+CHI2\dotfill & Float & $\chi_{\nu}^2$ to orbital RV fit & \nodata & W11 \\
+NOBS\dotfill & Integer & Number of observations used in fit & \nodata & W11 \\
 RMS\dotfill & Float & Root-mean-square residuals to orbital RV fit &
-\nodata \\
-FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \nodata \\
-TREND\dotfill  & Boolean & Linear trend in fit? & \nodata \\
-NCOMP\dotfill & Integer & Number of planetary companions known & \nodata \\
-MULT\dotfill & Boolean & Multiple planets in system? & \nodata \\
-COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) & \nodata \\
+\nodata & W11 \\
+FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \nodata & W11 \\
+TREND\dotfill  & Boolean & Linear trend in fit? & \nodata & W11 \\
+NCOMP\dotfill & Integer & Number of planetary companions known & \nodata & W11 \\
+MULT\dotfill & Boolean & Multiple planets in system? & \nodata & W11 \\
+COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) & \nodata & W11 \\
 %
@@
 SE\dotfill & Boolean & If true, at least one secondary eclipse has
-been detected & -REF,-URL \\
-SEDEPTHJ\dotfill & Float & Secondary eclipse depth in $J$ band & -UPPER, etc. \\
-SEDEPTHH\dotfill & Float & Secondary eclipse depth in $H$ band & -UPPER, etc. \\
+been detected & -REF,-URL & \ref{sec:se} \\
+SEDEPTHJ\dotfill & Float & Secondary eclipse depth in $J$ band & -UPPER, etc. & \ref{sec:se} \\
+SEDEPTHH\dotfill & Float & Secondary eclipse depth in $H$ band & -UPPER, etc. & \ref{sec:se} \\
 SEDEPTHKS\dotfill & Float & Secondary eclipse depth in $K_S$
-band & -UPPER, etc. \\
+band & -UPPER, etc. & \ref{sec:se} \\
 SEDEPTHKP\dotfill & Float & Secondary eclipse depth in the
-\kepler\ photometry band & -UPPER, etc. \\
+\kepler\ photometry band & -UPPER, etc. & \ref{sec:se} \\
 SEDEPTH36\dotfill & Float & Secondary eclipse depth in
-\spitzer\ IRAC1 3.6 \micron\ band & -UPPER, etc. \\
+\spitzer\ IRAC1 3.6 \micron\ band & -UPPER, etc. & \ref{sec:se} \\
 SEDEPTH45\dotfill & Float & Secondary eclipse depth in
-\spitzer\ IRAC2 4.5 \micron\ band & -UPPER, etc. \\
+\spitzer\ IRAC2 4.5 \micron\ band & -UPPER, etc. & \ref{sec:se} \\
 SEDEPTH58\dotfill & Float & Secondary eclipse depth in
-\spitzer\ IRAC3 5.8 \micron\ band & -UPPER, etc. \\
+\spitzer\ IRAC3 5.8 \micron\ band & -UPPER, etc. & \ref{sec:se} \\
 SEDEPTH80\dotfill & Float & Secondary eclipse depth in
-\spitzer\ IRAC4 8.0 \micron\ band & -UPPER, etc. \\
+\spitzer\ IRAC4 8.0 \micron\ band & -UPPER, etc. & \ref{sec:se} \\
 SET\dotfill & Double & Epoch of secondary eclipse center in
-HJD\tablenotemark{d} & -UPPER, etc. \\
+HJD\tablenotemark{d} & -UPPER, etc. & \ref{sec:se} \\
 %
 \sidehead{\textbf{Stellar Properties}}
-STAR\dotfill & String & Standard name for host star & \nodata \\
-BINARY\dotfill & Boolean & Star known ot be binary? & -REF, -URL \\
-MSTAR\dotfill & Float & Mass of host star in solar mass & -UPPER, etc. \\
-RSTAR\dotfill & Float & Radius of host star in solar radii & -UPPER, etc. \\
-FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER, etc. \\
-TEFF\dotfill & Float & Effective temperature of host star & -UPPER, etc. \\
-RHOSTAR\dotfill & Float & Density of host star & -UPPER, etc. \\
+STAR\dotfill & String & Standard name for host star & \nodata & W11 \\
+BINARY\dotfill & Boolean & Star known ot be binary? & -REF, -URL & W11 \\
+MSTAR\dotfill & Float & Mass of host star in solar mass & -UPPER, etc. & W11 \\
+RSTAR\dotfill & Float & Radius of host star in solar radii & -UPPER, etc. & \ref{sec:stellarprop} \\
+FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER, etc. & W11 \\
+TEFF\dotfill & Float & Effective temperature of host star & -UPPER, etc. & W11 \\
+RHOSTAR\dotfill & Float & Density of host star & -UPPER, etc. & \ref{sec:stellarprop} \\
 LOGG\dotfill & Float & Spectroscopic $\log{g}$ (surface gravity) of
-host star in cgs unit & -UPPER, etc. \\
+host star in cgs unit & -UPPER, etc. & W11 \\
 VSINI\dotfill & Float & Projected equatorial rotational velocity of
-star in k\mps & -UPPER, etc. \\
-GAMMA\dotfill & Float & Systemic radial velocity in k\mps & -UPPER, etc. \\
+star in k\mps & -UPPER, etc. & W11 \\
+GAMMA\dotfill & Float & Systemic radial velocity in k\mps & -UPPER, etc. & \ref{sec:stellarprop} \\
 %
 \sidehead{\textbf{Stellar Magnitudes}}
-V\dotfill & Float & $V$ magnitude & -REF,-URL \\
-BMV\dotfill & Float & $B-V$ color & \nodata \\
-J\dotfill & Float & $J$ magnitude & \nodata \\
-H\dotfill & Float & $H$ magnitude & \nodata \\
-KS\dotfill & Float & $K_S$ magnitude & \nodata \\
-SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \nodata \\
-RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \nodata \\
-KP\dotfill & Float & \kepler\ bandpass magnitude & \nodata \\
-SPECREF\dotfill & String & Source of most of the spectroscopic parameters & SPECURL \\
+V\dotfill & Float & $V$ magnitude & -REF,-URL & W11 \\
+BMV\dotfill & Float & $B-V$ color & \nodata & W11 \\
+J\dotfill & Float & $J$ magnitude & \nodata & W11 \\
+H\dotfill & Float & $H$ magnitude & \nodata & W11 \\
+KS\dotfill & Float & $K_S$ magnitude & \nodata & W11 \\
+SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \nodata & \ref{sec:stellarmag} \\
+RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \nodata & W11 \\
+KP\dotfill & Float & \kepler\ bandpass magnitude & \nodata & \ref{sec:stellarmag} \\
+SPECREF\dotfill & String & Source of most of the spectroscopic parameters & SPECURL & W11 \\
 %
 \sidehead{\textbf{Coordinates and Catalogs}}
-RA\dotfill & Double & J2000 right ascension in decimal hours & \nodata \\
-RA\_STRING\dotfill & String & J2000 right ascension in sexagesimal string & \nodata  \\
-DEC\dotfill & Double & J2000 declination in decimal degrees & \nodata \\
-DEC\_STRING\dotfill & String & J2000 declination in sexagesimal string & \nodata \\
-PAR\dotfill & Float & Parallax in mas & -UPPER,-LOWER,U- \\
-DIST\dotfill & Float & Distance to host star based on parallax in parsecs & -UPPER, etc. \\
+RA\dotfill & Double & J2000 right ascension in decimal hours & \nodata & W11 \\
+RA\_STRING\dotfill & String & J2000 right ascension in sexagesimal string & \nodata  & W11 \\
+DEC\dotfill & Double & J2000 declination in decimal degrees & \nodata & W11 \\
+DEC\_STRING\dotfill & String & J2000 declination in sexagesimal string & \nodata & W11 \\
+PAR\dotfill & Float & Parallax in mas & -UPPER,-LOWER,U- & W11 \\
+DIST\dotfill & Float & Distance to host star based on parallax in parsecs & -UPPER, etc. & \ref{sec:coord} \\
 HIPP\dotfill & Long Integer & \textit{Hipparcos} catalog number of
-star & \nodata \\
-HD\dotfill & Long Integer & Henry Draper number of sar & \nodata \\
-GL\dotfill & Float & GJ or Gliese catalog number of star & \nodata \\
-HR\dotfill & Integer & Bright Star Catalog number of star & \nodata \\
-SAO\dotfill & Long Integer & SAO catalog number of star & \nodata \\
+star & \nodata & W11 \\
+HD\dotfill & Long Integer & Henry Draper number of sar & \nodata & W11 \\
+GL\dotfill & Float & GJ or Gliese catalog number of star & \nodata & W11 \\
+HR\dotfill & Integer & Bright Star Catalog number of star & \nodata & W11 \\
+SAO\dotfill & Long Integer & SAO catalog number of star & \nodata & W11 \\
 %
@@
 where ``-" stands for the name of the field listed in the first
-column. They are...}
+column. They are... See Section~\ref{sec:unc} and \ref{sec:ref} for
+more details. -UL stands for upper limits for the fields (see
+Section~\ref{sec:unc} for details).}
 \tablenotetext{c}{Originally as other commonly used name for star in \cite{Wright2011};

### 2014-03-07 draft/ms.tex
Title changed
section 2.9 done and half of 2.10, need to start from SHK

@@
 
-\title{Updates on the Exoplanet Orbit Database}
+\title{The Exoplanet Orbit Database 2, 2014 updates}
 
@@
 
+{\bf DISCMETH} field previously reported the method of discovery,
+which was either radial velocity or transit. We have replaced DISCMETH
+with {\bf PLANETDISCMETH} and \mbox{{\bf STARDISCMETH}} to better report how
+the host star and the planet are detected.
+PLANETDISCMETH and STARDISCMETH are the fields that report the discovery methods for the planet and the first planet around the host star, respectively.
+Furthermore, they now have values of one of the following: radial velocity, transit, imaging,
+microlensing, timing, or astrometry.
+
+{\bf MONTH} field reports the month in integer when the
+peer-reviewed paper is accepted to the ApJ.
+
 {\bf KEPID} stands for KEPler ID which is the integer number assigned
@@
 
-ZZZ For KOIs without MSINI measured, we calculate their mass using the
+For KOIs without MSINI measured, we calculate their mass using the
 mass-radius relation from the literatures. For KOIs with $R<4\rearth$,
 we use \cite{Weiss2014} , with $4\rearth<R<6\rearth$, we use
-\cite{Lissauer2011}, and for KOIs with $6\rearth<R<17\rearth$ we use
+\cite{Lissauer2011}, and for KOIs with $6\rearth<R<11.7\rearth$ we use
 \cite{Mordasini2012}.
@@
 
+{\bf I} is the orbital inclination.
+Previously, only transiting systems have I measured but now, sometimes, non-transiting systems have I's reported too.
+ZZZ(add reference) For example, one microlensing system has I measured (OGLE-2006-BLG-109L).
+
 {\bf BIGOM} is the longitude of the ascending node ($\Omega$) in the
@@
 
+{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
+the unit of degree. We report the projected spin-orbit misalignment of
+transiting systems, which is measured by, e.g., the Rossiter-McLaughlin
+effect or planet transiting star spots ZZZ add references for RM effect and the star spot method. $\lambda$ is introduced because the true spin-orbit angle
+($\phi$), defined as the angle between the stellar spin axis and the
+orbital axis, is normally not directly measurable. We follow the
+definition of $\lambda$ in \cite{Fabrycky2009} where the
+coordinates are defined as follows; the $z$-axis points toward the
+observer, the $x$-axis points along the intersection of the sky plane
+and the planet's orbital plane with the ascending node of the planet
+having $x<0$, and the $y$-axis completes a right
+handed-triad. $\lambda$ is measured clockwise on the sky from the
+$y$-axis to the projected stellar rotational axis. $\lambda$ is not a newly added field but we describe it here because $\lambda$'s were not reported consistently since some literatures
+report $\beta = -\lambda$ instead. We sorted these cases out and made
+sure that our $\lambda$'s are following the definition of \cite{Fabrycky2009}.
 %------------------------------------------------------------------------------
@@
 
+{\bf SHK} is the Mount Wilson Ca II S-value and {\bf RHK} is the Chromospheric activity of star as $\log{R'_{HK}}$
+: field previously reported the  and
+now it is changed to SHK.  ; ZZZ What's the source for SHK and RHK?
+Still discovery paper and Butler 2006? ZZZ SHK is a poorly maintained
+field, and it is unreferenced at the moment though we plan to include
+proper reference in the future.
+
 %------------------------------------------------------------------------------
@@
 PAR from the Hipparcos data set by \cite{van Leeuwen2009}.
+
+We naively propagate the error in PAR to DIST.
 
@@
 
-We also report the upper limits for planet mass (MSINI), eccentricity
-(ECC), and the velocity semi-amplitude (K) when the literatures only
-provide the upper limits and not the actual values. The upper limits
-for ECC is reported when the orbit is circular, and the upper limits
-for K is reported when there is no radial velocity detection. If only
+We also report the upper limits (XUL) for planet mass (MSINI), eccentricity (ECC), and the velocity semi-amplitude (K) when the literatures report them.
+For example, the upper limits for ECC is reported when the orbit is circular, and the upper limits for K is reported when there is no radial velocity detection.
+If only
 upper limits are given, we set the field to 0, the uncertainty to half
@@
 put the value in ECCUL, set ECC to be 0, ECCUPPER to ECCUL, and UECC
-to ECCUL/2.
+to ECCUL/2. Since not all authors define the upper limits in the same way (e.g. 1$\sigma$ or some fixed percentile), we encourage the readers to refer to the literature for more information.
 
@@
 
-Added field: MONTH, PLANETDISCMETH, STARDISCMETH.
-The following fields now have XREF and XURL: (previously in
-\cite{Wright2011}) DIST, TRANSIT, BINARY; (new) fields in stellar
-parameters: V, VSINI, GAMMA; all orbit pars except for trend and
-freeze\_ecc; all transit parameters; all SE parameters; fields for
-stellar properties: MSTAR, RSTAR, TEFF, RHOSTAR, LOGG, FE.
+Previously, we only reported general references (e.g. FIRSTREF, FIRSTURL, ORBREF, and ORBURL), but now we report the references for most of the fields.
 
-VREF is not the same as REF for J H KS, which do not have XREF
-fields. See \cite{Wright2011} for references of J H KS mags -- I think
-he mentioned it there.
-
-Other general reference fields: In \cite{Wright2011}: FIRSTREF,
-FIRSTURL, ORBREF, ORBURL. New: SPECREF, SPECURL contain source of most
-of the spectroscopic parameters listed for convenience; actual
-references in the REF fields take precedence over this one.
-
-{\bf MONTH} field reports the month in integer when the
-peer-reviewed paper is accepted to the ApJ to better track of the
-trend in the exoplanet detections.
-
-{\bf PLANETDISCMENT} and {\bf STARDISCMETH} are the fields that report
-the discovery methods for the host star and the planet See Section~
-for more details.
+ZZZ RA, DEC, and PAR do not have references but they are from the \textit{Hipparcos} by \cite{van Leeuwen2009}.
+$B-V$ (BMV) field does not have a reference but the values are from the \textit{Hipparcos} catalog.
+The fields J H and KS do not have references as well but they are from the 2MASS \citep{Skrutskie2006}.
+The KP field do not have reference but the values are from the Exoplanet Archive \citep{Akeson2013}.
 
@@
 \subsection{Revised and Removed Fields}
-ZZZ CPSNAME?
 
 We have major updates by taking out some of the fields and by revising the existing fields. Here, we explain why we removed or revised such fields.
-
-{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
-the unit of degree. We report the projected spin-orbit misalignment of
-transiting systems, which is measured by ZZZ Rossiter-McLaughlin
-effect. $\lambda$ is introduced because the true spin-orbit angle
-($\phi$), defined as the angle between the stellar spin axis and the
-orbital axis, is normally not directly measurable. We follow the
-definition of $\lambda$ in Fabrycky and Winn 2009 where the
-coordinates are defined as follows; the $z$-axis points toward the
-observer, the $x$-axis points along the intersection of the sky plane
-and the planet's orbital plane with the ascending node of the planet
-having $x<0$, and the $y$-axis completes a right
-handed-triad. $\lambda$ is measured clockwise on the sky from the
-$y$-axis to the projected stellar rotational axis. Some literatures
-report $\beta = -\lambda$ instead. We sorted these cases out and made
-sure that our $\lambda$'s are following the definition of Fabrycky and
-Winn 2009.
-
-{\bf I} is the orbital inclination. This field is not newly added but
-we chose to describe it here since our database now has the
-inclination for planets detected by methods other than
-transit. Previously, only transiting systems used to have the
-inclination measured. However, now sometimes for non-transiting
-systems the values of I are also available. For instance, if the
-system was first detected by radial velocity and has a follow-up
-transit observation, then the inclination can be measured. To sum up,
-all the transiting planets have measured orbital inclination and
-currently, we also have one microlensing planet with measured
-inclination. *** give the example!
-
-{\bf OTHERNAME} - This is now listed as other name of planet instead
-of star; ** OTHTERNAME has always been the name of the star I
-think...?
-
-{\bf DISCMETH} field previously reported the mouthed of discovery,
-which was either radial velocity or transit. We have replaced DISCMETH
-with {\bf PLANETDISCMETH} and {\bf STARDISCMETH} to better report how
-the host star and the planet are detected. Furthermore, they now have
-value of one of the following: radial velocity, transit, imaging,
-microlensing, timing, or astrometry.
-
-{\bf S} field previously reported the Mount Wilson Ca II S-value and
-now it is changed to SHK.  ; ZZZ What's the source for SHK and RHK?
-Still discovery paper and Butler 2006? ZZZ SHK is a poorly maintained
-field, and it is unreferenced at the moment though we plan to include
-proper reference in the future.
 
@@
 NAME\dotfill & String & Name of planet & \nodata & W11 \\
-OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of planet & \nodata & \ref{sec:disc} \\
+OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of star & \nodata & \ref{sec:disc} \\
 DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata & W11 \\
@@
 KS\dotfill & Float & $K_S$ magnitude & \nodata & W11 \\
-SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \nodata & \ref{sec:stellarmag} \\
-RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \nodata & W11 \\
+SHK\dotfill & Float & Mount Wilson Ca {\sc{II}} $S$-value & \nodata & \ref{sec:stellarmag} \\
+RHK\dotfill & Float & Chromospheric activity of star as $\log{R'_{HK}}$ & \nodata & W11 \\
 KP\dotfill & Float & \kepler\ bandpass magnitude & \nodata & \ref{sec:stellarmag} \\

### 2014-03-10 draft/ms.tex
Done with section 2

@@
 sure that our $\lambda$'s are following the definition of \cite{Fabrycky2009}.
+
+{\bf MASSREF} and {\bf MASSURL} fields were used to report the
+reference and the URL of stellar mass but now they are used for planet
+mass.
 %------------------------------------------------------------------------------
@@
 
-{\bf SHK} is the Mount Wilson Ca II S-value and {\bf RHK} is the Chromospheric activity of star as $\log{R'_{HK}}$
-: field previously reported the  and
-now it is changed to SHK.  ; ZZZ What's the source for SHK and RHK?
-Still discovery paper and Butler 2006? ZZZ SHK is a poorly maintained
-field, and it is unreferenced at the moment though we plan to include
-proper reference in the future.
-
 %------------------------------------------------------------------------------
@@
 
+SHK and RHK are poorly maintained fields and they unreferenced at the moment though we plan to include
+proper reference in the future. Most of the values are from \cite{Butler2006}.
+
 %------------------------------------------------------------------------------
-\subsection{Revised and Removed Fields}
+\subsection{Removed Fields}
 
-We have major updates by taking out some of the fields and by revising the existing fields. Here, we explain why we removed or revised such fields.
+We removed 2 fields.
 
 {\bf SPSTAR} field previously reported the stellar type of the host
-star. We choose to remove this field because....? - stellar type of
-star (unvetted), gone;
+star but it is removed since it is not reliable.
 
@@
 replaced by EANAME, which is the name of the star as appears on the
-Exoplanet Archive.
-
-{\bf MASSREF} and {\bf MASSURL} fields were used to report the
-reference and the url of stellar mass but now they are used for planet
-mass.
+NASA's Exoplanet Archive \citep{Akeson2013}.
 
 %------------------------------------------------------------------------------
-Figure: Figure of single planet page, to show updated transit
+ZZZ Figure: Figure of single planet page, to show updated transit
 parameters and RV curves etc.?
@@
 \section{Inclusion of the Kepler Planet Candidates and Other Exoplanets on Exoplanets.org}\label{sec:kepler}
+
+We included KOIs and other planets and describe the criteria for other planets.
+
+KOI's are not counted as part of the EOD due to their status of being 'candidates', we include them in our website so that these KOIs are put into the context of all confirmed exoplanets.
+To display the KOIs in the EDE table, check the 'Kepler' option on the upper left of the table (default selection only includes 'Orbit Database' and 'Other').
+The KOIs listed in our table include two past Kepler data releases and the most up-to-date release from January 2013.
+The original data are from the NASA Exoplanet Archive.
 

### 2014-03-10 draft/ms.tex
Tiny revisions in Sec 2 and ref.

--- 2014-03-07 draft/ms.tex
@@
 
-{\bf I} is the orbital inclination.
-Previously, only transiting systems have I measured but now, sometimes, non-transiting systems have I's reported too.
-ZZZ(add reference) For example, one microlensing system has I measured (OGLE-2006-BLG-109L).
+{\bf I} is the orbital inclination. Previously, only transiting
+systems have I measured but now, sometimes, non-transiting systems
+have I's reported too. ZZZ(add reference) For example, one
+microlensing system has I measured (OGLE-2006-BLG-109L).
 
@@
 the unit of degree. We report the projected spin-orbit misalignment of
-transiting systems, which is measured by, e.g., the Rossiter-McLaughlin
-effect or planet transiting star spots ZZZ add references for RM effect and the star spot method. $\lambda$ is introduced because the true spin-orbit angle
-($\phi$), defined as the angle between the stellar spin axis and the
-orbital axis, is normally not directly measurable. We follow the
-definition of $\lambda$ in \cite{Fabrycky2009} where the
-coordinates are defined as follows; the $z$-axis points toward the
-observer, the $x$-axis points along the intersection of the sky plane
-and the planet's orbital plane with the ascending node of the planet
-having $x<0$, and the $y$-axis completes a right
-handed-triad. $\lambda$ is measured clockwise on the sky from the
-$y$-axis to the projected stellar rotational axis. $\lambda$ is not a newly added field but we describe it here because $\lambda$'s were not reported consistently since some literatures
-report $\beta = -\lambda$ instead. We sorted these cases out and made
-sure that our $\lambda$'s are following the definition of \cite{Fabrycky2009}.
+transiting systems, which is measured by, e.g., the
+Rossiter-McLaughlin effect or planet transiting star spots ZZZ add
+references for RM effect and the star spot method. $\lambda$ is
+introduced because the true spin-orbit angle ($\phi$), defined as the
+angle between the stellar spin axis and the orbital axis, is normally
+not directly measurable. We follow the definition of $\lambda$ in
+\cite{Fabrycky2009} where the coordinates are defined as follows; the
+$z$-axis points toward the observer, the $x$-axis points along the
+intersection of the sky plane and the planet's orbital plane with the
+ascending node of the planet having $x<0$, and the $y$-axis completes
+a right handed-triad. $\lambda$ is measured clockwise on the sky from
+the $y$-axis to the projected stellar rotational axis. $\lambda$ is
+not a newly added field but we describe it here because $\lambda$'s
+were not reported consistently since some literatures report $\beta =
+-\lambda$ instead. We sorted these cases out and made sure that our
+$\lambda$'s are following the definition of \cite{Fabrycky2009}.
+
 %------------------------------------------------------------------------------
@@
 
-{\bf SHK} is the Mount Wilson Ca II S-value and {\bf RHK} is the Chromospheric activity of star as $\log{R'_{HK}}$
-: field previously reported the  and
-now it is changed to SHK.  ; ZZZ What's the source for SHK and RHK?
-Still discovery paper and Butler 2006? ZZZ SHK is a poorly maintained
-field, and it is unreferenced at the moment though we plan to include
-proper reference in the future.
+{\bf SHK} is the Mount Wilson Ca II S-value and {\bf RHK} is the
+Chromospheric activity of star as $\log{R'_{HK}}$ : field previously
+reported the and now it is changed to SHK.  ; ZZZ What's the source
+for SHK and RHK?  Still discovery paper and Butler 2006? ZZZ SHK is a
+poorly maintained field, and it is unreferenced at the moment though
+we plan to include proper reference in the future.
 
@@
 
-We also report the upper limits (XUL) for planet mass (MSINI), eccentricity (ECC), and the velocity semi-amplitude (K) when the literatures report them.
-For example, the upper limits for ECC is reported when the orbit is circular, and the upper limits for K is reported when there is no radial velocity detection.
-If only
-upper limits are given, we set the field to 0, the uncertainty to half
-of the upper limit, and the upper limits to the upper limits. For
+We also report the upper limits (XUL) for planet mass (MSINI),
+eccentricity (ECC), and the velocity semi-amplitude (K) when the
+literatures report them. For example, the upper limits for ECC is
+reported when the orbit is circular, and the upper limits for K is
+reported when there is no radial velocity detection. If only upper
+limits are given, we set the field to 0, the uncertainty to half of
+the upper limit, and the upper limits to the upper limits. For
 example, if the literature reports the upper limit for ECC, then we
 put the value in ECCUL, set ECC to be 0, ECCUPPER to ECCUL, and UECC
-to ECCUL/2. Since not all authors define the upper limits in the same way (e.g. 1$\sigma$ or some fixed percentile), we encourage the readers to refer to the literature for more information.
+to ECCUL/2. Since not all authors define the upper limits in the same
+way (e.g. 1$\sigma$ or some fixed percentile), we encourage the
+readers to refer to the literature for more information.
 
@@
 
-The fields {\bf XREF} and {\bf XURL} store the peer-reviewed reference and link to
-the publication for the field X.
+The fields {\bf XREF} and {\bf XURL} store the peer-reviewed reference
+and link to the publication for the field X.
 
-Previously, we only reported general references (e.g. FIRSTREF, FIRSTURL, ORBREF, and ORBURL), but now we report the references for most of the fields.
+Previously, we only reported general references (e.g. FIRSTREF,
+FIRSTURL, ORBREF, and ORBURL), but now we report the references for
+most of the fields.
 
-ZZZ RA, DEC, and PAR do not have references but they are from the \textit{Hipparcos} by \cite{van Leeuwen2009}.
-$B-V$ (BMV) field does not have a reference but the values are from the \textit{Hipparcos} catalog.
-The fields J H and KS do not have references as well but they are from the 2MASS \citep{Skrutskie2006}.
-The KP field do not have reference but the values are from the Exoplanet Archive \citep{Akeson2013}.
+ZZZ RA, DEC, and PAR do not have references but they are from the
+\textit{Hipparcos} by \cite{van Leeuwen2009}. $B-V$ (BMV) field does
+not have a reference but the values are from the \textit{Hipparcos}
+catalog. The fields J H and KS do not have references as well but they
+are from the 2MASS \citep{Skrutskie2006}. The KP field do not have
+reference but the values are from the Exoplanet Archive
+\citep{Akeson2013}.
 
@@
 
-We have major updates by taking out some of the fields and by revising the existing fields. Here, we explain why we removed or revised such fields.
+We have major updates by taking out some of the fields and by revising
+the existing fields. Here, we explain why we removed or revised such
+fields.
 

### 2014-03-10 draft/ms.tex
Add missing references for Sec 2.

--- 2014-03-10 draft/ms.tex
@@
 
-{\bf I} is the orbital inclination.
-Previously, only transiting systems have I measured but now, sometimes, non-transiting systems have I's reported too.
-ZZZ(add reference) For example, one microlensing system has I measured (OGLE-2006-BLG-109L).
+{\bf I} is the orbital inclination. Previously, only transiting
+systems have I measured but now, sometimes, non-transiting systems
+have I's reported too. For example, one microlensing system has I
+measured (OGLE-2006-BLG-109L; \citealt{Bennet2010}).
 
@@
 the unit of degree. We report the projected spin-orbit misalignment of
-transiting systems, which is measured by, e.g., the Rossiter-McLaughlin
-effect or planet transiting star spots ZZZ add references for RM effect and the star spot method. $\lambda$ is introduced because the true spin-orbit angle
-($\phi$), defined as the angle between the stellar spin axis and the
-orbital axis, is normally not directly measurable. We follow the
-definition of $\lambda$ in \cite{Fabrycky2009} where the
-coordinates are defined as follows; the $z$-axis points toward the
-observer, the $x$-axis points along the intersection of the sky plane
-and the planet's orbital plane with the ascending node of the planet
-having $x<0$, and the $y$-axis completes a right
-handed-triad. $\lambda$ is measured clockwise on the sky from the
-$y$-axis to the projected stellar rotational axis. $\lambda$ is not a newly added field but we describe it here because $\lambda$'s were not reported consistently since some literatures
-report $\beta = -\lambda$ instead. We sorted these cases out and made
-sure that our $\lambda$'s are following the definition of \cite{Fabrycky2009}.
+transiting systems, which is measured by, e.g., the
+Rossiter-McLaughlin effect \citep[e.g.,][]{Winn2005} or planet
+transiting star spots \citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is
+introduced because the true spin-orbit angle ($\phi$), defined as the
+angle between the stellar spin axis and the orbital axis, is normally
+not directly measurable. We follow the definition of $\lambda$ in
+\cite{Fabrycky2009} where the coordinates are defined as follows; the
+$z$-axis points toward the observer, the $x$-axis points along the
+intersection of the sky plane and the planet's orbital plane with the
+ascending node of the planet having $x<0$, and the $y$-axis completes
+a right handed-triad. $\lambda$ is measured clockwise on the sky from
+the $y$-axis to the projected stellar rotational axis. $\lambda$ is
+not a newly added field but we describe it here because $\lambda$'s
+were not reported consistently since some literatures report $\beta =
+-\lambda$ instead. We sorted these cases out and made sure that our
+$\lambda$'s are following the definition of \cite{Fabrycky2009}.
 
@@
 mass.
+
 %------------------------------------------------------------------------------
@@
 
-The fields {\bf XREF} and {\bf XURL} store the peer-reviewed reference and link to
-the publication for the field X.
+The fields {\bf XREF} and {\bf XURL} store the peer-reviewed reference
+and link to the publication for the field X.
 
-Previously, we only reported general references (e.g. FIRSTREF, FIRSTURL, ORBREF, and ORBURL), but now we report the references for most of the fields.
+Previously, we only reported general references (e.g. FIRSTREF,
+FIRSTURL, ORBREF, and ORBURL), but now we report the references for
+most of the fields.
 
-ZZZ RA, DEC, and PAR do not have references but they are from the \textit{Hipparcos} by \cite{van Leeuwen2009}.
-$B-V$ (BMV) field does not have a reference but the values are from the \textit{Hipparcos} catalog.
-The fields J H and KS do not have references as well but they are from the 2MASS \citep{Skrutskie2006}.
-The KP field do not have reference but the values are from the Exoplanet Archive \citep{Akeson2013}.
+RA, DEC, and PAR do not have references but they are from the
+\textit{Hipparcos} by \cite{van Leeuwen2009}. $B-V$ (BMV) field does
+not have a reference but the values are from the \textit{Hipparcos}
+catalog by \cite{Perryman1997}. The fields J H and KS do not have
+references as well but they are from the 2MASS
+\citep{Skrutskie2006}. The KP field do not have reference but the
+values are from the Exoplanet Archive \citep{Akeson2013}.
 
-SHK and RHK are poorly maintained fields and they unreferenced at the moment though we plan to include
-proper reference in the future. Most of the values are from \cite{Butler2006}.
+SHK and RHK are poorly maintained fields and they unreferenced at the
+moment though we plan to include proper reference in the future. Most
+of the values are from \cite{Butler2006}.
 

### 2014-03-10 draft/references.tex
Tiny revisions in Sec 2 and ref.
Add missing references for Sec 2.

@@
 
+\bibitem[Bennett et al.(2010)]{Bennett2010} Bennett, D.~P., et al.\ 2010, 
+\apj, 713, 837 % OGLE microlensing planet with inclination measured
+
 \bibitem[Borucki et al.(2010)]{Borucki2010} Borucki, W.~J., et al.\ 2010, 
@@
 \apj, 646, 505 % EOD first paper
+
+\bibitem[Collier Cameron et al.(2010)]{Collier Cameron2010} Collier 
+Cameron, A., et al.\ 2010, \mnras, 407, 507 % WASP-33b having no RV
+                                % detection and K upper limit
 
@@
   572 % use of EOD
+
+\bibitem[Johnson et al.(2011)]{Johnson2011} Johnson, J.~A., et al.\ 2011, 
+\apjs, 197, 26 % HD 116029B having ECC upper limit (circular orbit)
 
@@
 
+\bibitem[Perryman \& ESA(1997)]{Perryman1997} Perryman, M.~A.~C., \&
+  ESA 1997, ESA Special Publication, 1200 % Hipparcos B-V reference
+
 \bibitem[Ricker et al.(2010)]{Ricker2010} Ricker, G.~R., et al.\ 2010, 
@@
 arXiv:1402.6534 % 715 new Kepler planets (multis)
+
+\bibitem[Sanchis-Ojeda et al.(2012)]{Sanchis-Ojeda2012} Sanchis-Ojeda, R., 
+et al.\ 2012, \nat, 487, 449 % Kepler 30 system lambda measurement
+                             % with star spot transit
 
@@
 
+\bibitem[Winn et al.(2005)]{Winn2005} Winn, J.~N., et al.\ 2005, \apj, 631, 
+1215 % HD 209458b, the first Rossiter-McLaughlin lambda measurement
+
 \bibitem[Wright et al.(2011)]{Wright2011} Wright, J.~T., et al.\ 2011,

### 2014-03-10 draft/ms.tex
Section 3 update

--- 2014-03-10 draft/ms.tex
@@
 
-We included KOIs and other planets and describe the criteria for other planets.
+Since \cite{Wright2011}, as more planets were discovered by different methods other than radial velocity and transit, we have expanded this information to better ingest those planets into our database.
+We are going to explain what they are and the criteria we used to put them into the EOD.
 
-KOI's are not counted as part of the EOD due to their status of being 'candidates', we include them in our website so that these KOIs are put into the context of all confirmed exoplanets.
+{\bf KOI}'s: Although KOI's are not counted as part of the EOD due to their status of being `candidates', we include them in our website so that these KOIs are put into the context of all confirmed exoplanets.
 To display the KOIs in the EDE table, check the 'Kepler' option on the upper left of the table (default selection only includes 'Orbit Database' and 'Other').
-The KOIs listed in our table include two past Kepler data releases and the most up-to-date release from January 2013.
+The KOIs listed in our table include two past Kepler data releases and the most up-to-date release from February 2014.
 The original data are from the NASA Exoplanet Archive.
 
-Since \cite{Wright2011}, as more planets were discovered by different
-methods other than radial velocity and transit, we have expanded this
-information to better ingest those planets into our database.
+ZZZ Ask Jason about their criteria. \\
+We also included robustly detected imaging, microlensing, and timing planets and the criteria are the following (as set by the QUACBED):
 
-Planets primarily detected by these methods do not have robust orbital
-parameters, they are categorized as ``Other Planets'' on
+\begin{itemize}
+\item Imaging planets: 
+\begin{enumerate}
+\item Planet-star mass ratio $q < 0.024$ ($< 24\ $\mjup\ for a solar mass star); and in general we require ($q+\sigma_q$) $< 0.024$, where $\sigma_q$ is the uncertainty in $q$.
+\item SEP $<$ 100 AU $\times$ ($M_*/M_\odot$), where SEP is the semi-major axis a if a is known, and the projected separation otherwise.
+\item Confidently detected: the detection is clearly of a real astrophysical source, and will unlikely later be found to have been spurious.
+\item Confidently bound: in opinion of the QUACBED the object will not be later found to be unbound or a chance alignment.
+
+\end{enumerate}
+\item Microlensing planets
+
+\item Timing planets
+
+\end{itemize}
+Planets primarily detected by these methods do not have robust orbital parameters and they are categorized as ``Other Planets'' on
 exoplanets.org.
-
-If planets have follow up radial velocity or transit observations and
-thus have good orbital parameters, they have EOD flags. See
-Section~\ref{sec:kepler} for more information about `Other Planets'.
-
-We now include \kepler\ candidates... They can be displayed by
-checking the `Kepler' option for the interactive data table.
-
-We also include robustly detected planets discovered microlensing,
-imaging, timing, astrometric motion. They can be displayed by check
-the `Other' option for the table. They are not included in the EOD
-(especially some microlensing and imaging planets) because of poorly
-characterized orbits...
+If planets have follow up radial velocity or transit observations and thus have good orbital parameters, they have the EOD flags.
+See Section~\ref{sec:kepler} for more information about `Other Planets'.
+These other planets can be displayed by check the `Other' option for the table.
+They are not included in the EOD (especially some microlensing and imaging planets) because of poorly characterized orbits.
 

### 2014-03-11 draft/ms.tex
Section 2 intro

@@
 \section{Updates on the EOD}\label{sec:update}
-Make sure to cite \cite{Wright2013} for the definition of orbital elements.
+
+The scope of the EOD has not been changed much but there was a major change in the category of host star.
+Previously, we only included exoplanets orbiting the `normal stars', but exoplanets orbiting neutron stars are also in our database.
+Furthermore, we only had exoplanets that were discovered by RV and transit but as more exoplanets are discovered by various methods such as microlensing and imaging, we have included those exoplanets as well into our database.
+
+We still require the ``planets" to be smaller than 24 \mjup\ and the robust detection, which although is not strictly quantitative.
+
+The purpose of the EOD has not changed; we aim to provide the readers with comprehensive database for exoplanets that are discovered up-to-date.
+However, we just do not put all the announced exoplanets as we are not trying to do ``an encyclopedic presentation of every claimed detection of an exoplanet" as mentioned in \cite{Wright2011}.
 
@@
 all planets on exoplanets.org.
-
+Make sure to cite \cite{Wright2013} for the definition of orbital elements. 
 %------------------------------------------------------------------------------

### 2014-03-11 draft/ms.tex
Revision of Sec 3 and other misc revisions.

--- 2014-03-10 draft/ms.tex
@@
 and \cite{Wright2011} to maintain the Exoplanet Orbit Database (EOD)
-and the Exoplanets Data Explorer to keep track of the exoplanet
+and the Exoplanets Data Explorer (EDE) to keep track of the exoplanet
 discoveries and catalog their orbital parameters and host star
@@
 % data access and popularity
-The EOD is hosted by exoplanets.org, which also hosts the Exoplanets
-Data Explorer, an interactive table with plotting tools including all
-the EOD exoplanets as well as other confirmed exoplanets (and now also
-KOIs). The entire dataset of exoplanets.org is available for download
-as a single {\tt .csv} file at the website's front page.\footnote{At
+The EOD is hosted by exoplanets.org, which also hosts the EDE, an
+interactive table with plotting tools including all the EOD exoplanets
+as well as other confirmed exoplanets (and now also KOIs). The entire
+dataset of exoplanets.org is available for download as a single {\tt
+  .csv} file at the website's front page.\footnote{At
   \url{exoplanets.org/csv-files/exoplanets.csv}.} The EOD is widely
@@
 EOD in Section~\ref{sec:update}. We also describe the updates to the
-hosting website, exoplanets.org. The Exoplanet Data Explorer at
-exoplanets.org has expanded its scope and now includes the
-\kepler\ exoplanet candidates (KOIs). We describe these changes in
-Section~\ref{sec:kepler}. The website has also gone through major
-back-end changes since \cite{Wright2011}, which is described in
-Section~\ref{sec:website}.
+hosting website, exoplanets.org. The EDE at exoplanets.org has
+expanded its scope and now includes the \kepler\ exoplanet candidates
+(KOIs). We describe these changes in Section~\ref{sec:kepler}. The
+website has also gone through major back-end changes since
+\cite{Wright2011}, which is described in Section~\ref{sec:website}.
 
@@
 
-KDE: obselete field! Detele from the table.
+%KDE: obselete field! Detele from the table.
 
@@
 
-Since \cite{Wright2011}, as more planets were discovered by different methods other than radial velocity and transit, we have expanded this information to better ingest those planets into our database.
-We are going to explain what they are and the criteria we used to put them into the EOD.
+Since \cite{Wright2011}, as more planets were robustly discovered by
+different methods other than radial velocity and transit, we have
+expanded our database at exoplanets.org to better ingest those
+planets.
 
-{\bf KOI}'s: Although KOI's are not counted as part of the EOD due to their status of being `candidates', we include them in our website so that these KOIs are put into the context of all confirmed exoplanets.
-To display the KOIs in the EDE table, check the 'Kepler' option on the upper left of the table (default selection only includes 'Orbit Database' and 'Other').
-The KOIs listed in our table include two past Kepler data releases and the most up-to-date release from February 2014.
-The original data are from the NASA Exoplanet Archive.
+% KOIs
+First, we now include the KOIs discovered by \kepler in the
+EDE. Although KOIs are not counted as part of the EOD due to their
+status of being `candidates', we include them in our website so that
+these KOIs are put into the context of all confirmed exoplanets. The
+KOIs listed in our table include three Kepler data releases (as of
+March 2014), and we always keep up with the most up-to-date
+releases. The original data are from the NASA Exoplanet Archive.
 
-ZZZ Ask Jason about their criteria. \\
-We also included robustly detected imaging, microlensing, and timing planets and the criteria are the following (as set by the QUACBED):
+To display the KOIs in the EDE table, check the 'Kepler' option on the
+upper left of the table (default selection only includes 'Orbit
+Database', i.e.~the EOD, and 'Other'). They can also be displayed on
+plots with the interactive plotting tool of EDE.
+
+% Other Planets
+ZZZ Ask Jason about their criteria. \\ Second, we now also include
+robustly detected imaging, microlensing, and timing planets, and our
+criteria for a `robust detection' are the following (as set by the
+QUACBED):
 
@@
 \begin{enumerate}
-\item Planet-star mass ratio $q < 0.024$ ($< 24\ $\mjup\ for a solar mass star); and in general we require ($q+\sigma_q$) $< 0.024$, where $\sigma_q$ is the uncertainty in $q$.
-\item SEP $<$ 100 AU $\times$ ($M_*/M_\odot$), where SEP is the semi-major axis a if a is known, and the projected separation otherwise.
-\item Confidently detected: the detection is clearly of a real astrophysical source, and will unlikely later be found to have been spurious.
-\item Confidently bound: in opinion of the QUACBED the object will not be later found to be unbound or a chance alignment.
+\item Planet-star mass ratio $q < 0.024$ ($< 24\ $\mjup\ for a solar
+  mass star); and in general we require ($q+\sigma_q$) $< 0.024$,
+  where $\sigma_q$ is the uncertainty in $q$.
+\item SEP $<$ 100 AU $\times$ ($M_*/M_\odot$), where SEP is the
+  semi-major axis a if a is known, and the projected separation
+  otherwise.
+\item Confidently detected: the detection is clearly of a real
+  astrophysical source, and will unlikely later be found to have been
+  spurious.
+\item Confidently bound: in opinion of the QUACBED the object will not
+  be later found to be unbound or a chance alignment.
 
@@
 \end{itemize}
-Planets primarily detected by these methods do not have robust orbital parameters and they are categorized as ``Other Planets'' on
-exoplanets.org.
-If planets have follow up radial velocity or transit observations and thus have good orbital parameters, they have the EOD flags.
-See Section~\ref{sec:kepler} for more information about `Other Planets'.
-These other planets can be displayed by check the `Other' option for the table.
-They are not included in the EOD (especially some microlensing and imaging planets) because of poorly characterized orbits.
+Some of the exoplanets primarily detected by these methods do not have
+well-determined orbital parameters, and thus they are categorized as
+``Other Planets'' on exoplanets.org instead of being in the EOD. These
+planets can be displayed by check the `Other' option for the EDE
+table. As of March 2014, no microlensing or imaging planets are in the
+EOD, while several timing exoplanets have well-determined orbital
+parameters and are included in the EOD.
 
-Also add our criteria for vetting IMAGING planets, which can be found
-here: http://exoplanets.org/methodology.html; do we have any similar
-criteria for Microlensing, timing and astrometry planets? Like mass
-cut etc.?
-
-Figure: some comparison figures of Kepler candidate properties
-vs. EOD planet properties, such as mass-period, mass-radius?
+ZZZ Figure: some comparison figures of Kepler candidate properties vs. EOD
+planet properties, such as mass-period, mass-radius?
 
@@
 KOI\dotfill & Float & KOI object number & \nodata & \ref{sec:disc} \\
-KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata & \ref{sec:disc} \\
+%KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata & \ref{sec:disc} \\
 EOD\dotfill & Boolean & If true, planet is included in the EOD & \nodata & \ref{sec:disc} \\

### 2014-03-11 draft/ms.tex
Done!!!!!!!

--- 2014-03-11 draft/ms.tex
@@
 \section{Updates on the EOD}\label{sec:update}
-Make sure to cite \cite{Wright2013} for the definition of orbital elements.
 
-Scope of EOD has changed in the following ways:
+The scope of the EOD has not been changed much but there were two major changes in the EOD.
+Previously, we only included exoplanets orbiting the `normal stars', but now we are not limiting the type of the host star (e.g.
+we included exoplanets orbiting neutron stars).
+Furthermore, we only had exoplanets that were discovered by RV and transit but as more exoplanets are discovered by various methods such as timing are now in the EOD.
+For the future, exoplanets discovered by other methods with good orbital parameters may also be included in the EOD.
 
-1. Definition of planets: not strictly smaller than 24 \mjup\ any
-more? Or still true? We still require smaller than 24 \mjup.
+The rest of the criteria remain unchanged. We still require the planets to be smaller than 24 \mjup\ and with robust detection (though not strictly quantitative; see \citealt{Wright2011}).
 
-2. Host stars: not only `normal stars' any more? Not any more -
-neutron stars are there (at least)! This requirement is completely gone.
-
-3. Change on definition of `well-determined' orbital parameters? No. Still
-qualitative, still the same as described in Section~2 of \cite{Wright2011}.
-
-4. Inclusion of planets discovered beyond RV and transit.
-
-Purposes of EOD have not changed?
+The purpose of the EOD has not changed; we aim to provide the readers with comprehensive database for exoplanets that are discovered up-to-date.
+However, we do not report \textit{all} the announced exoplanets as we are not trying to do ``an encyclopedic presentation of every claimed detection of an exoplanet" \citep{Wright2011}.
 
 We only describe new additions and revised fields here, but list all
-fields. For details on other fields, see \cite{Wright2011}. We divide
-the fields into categories in consistency with the interactive table
-on exoplanets.org. Some fields are not explicitly included in the
-interactive table (e.g., the URLs), but are explicitly listed in the
-downloadable {\tt .csv} file.\footnote{The entire dataset provided by
-  exoplanets.org is available for download in a single CSV file at
-  \url{http://exoplanets.org/csv-files/exoplanets.csv}} Make a note
-here that though we focus on EOD in this Section, the fields apply to
-all planets on exoplanets.org.
-
+fields in Table~\ref{tab:par}. We divide the fields into categories in consistency with the individual planet page
+on exoplanets.org.
+Some fields are not explicitly included on the page (e.g., the URLs), but are explicitly listed in the downloadable {\tt .csv} file.\footnote{At \url{http://exoplanets.org/csv-files/exoplanets.csv}.} Though we focus on EOD in this section, the fields apply to all planets on exoplanets.org.
+For the definition of orbital elements see \cite{Wright2013} .
 %------------------------------------------------------------------------------
@@
 % KOIs
-First, we now include the KOIs discovered by \kepler in the
+First, we now include the KOIs discovered by \kepler\ in the
 EDE. Although KOIs are not counted as part of the EOD due to their
-status of being `candidates', we include them in our website so that
+status of being ``candidates", we include them in our website so that
 these KOIs are put into the context of all confirmed exoplanets. The
@@
 
-To display the KOIs in the EDE table, check the 'Kepler' option on the
-upper left of the table (default selection only includes 'Orbit
-Database', i.e.~the EOD, and 'Other'). They can also be displayed on
+To display the KOIs in the EDE table, check the ``Kepler" option on the
+upper left of the table (default selection only includes ``Orbit
+Database", i.e.~the EOD, and ``Other"). They can also be displayed on
 plots with the interactive plotting tool of EDE.

### 2014-03-12 draft/ms.tex
First finalized table content and note.

@@
 \tablehead{
-  \colhead{Field\tablenotemark{a}} & \colhead{Data Type} & \colhead{Meaning} &
-  \colhead{Related Fields\tablenotemark{b}} & \colhead{Ref.}
+  \colhead{Field} & \colhead{Data Type} & \colhead{Meaning} &
+  \colhead{Related Fields\tablenotemark{a}} & \colhead{Ref.\tablenotemark{b}}
 }
@@
 NAME\dotfill & String & Name of planet & \nodata & W11 \\
-OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of star & \nodata & \ref{sec:disc} \\
+OTHERNAME\dotfill & String & Other commonly used name of star & \nodata & \ref{sec:disc} \\
 DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata & W11 \\
@@
 BIGOM\dotfill & Float & Longitude of ascending node in degrees & -UPPER, etc. & \ref{sec:orbit} \\
-T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{d} & -UPPER, etc. & W11 \\
+T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{c} & -UPPER, etc. & W11 \\
 DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER, etc. & W11 \\
@@
 TT\dotfill & Float & Epoch of transit center in
-HJD\tablenotemark{d} & -UPPER, etc. & W11 \\
+HJD\tablenotemark{c} & -UPPER, etc. & W11 \\
 T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER, etc. & W11 \\
@@
 SET\dotfill & Double & Epoch of secondary eclipse center in
-HJD\tablenotemark{d} & -UPPER, etc. & \ref{sec:se} \\
+HJD\tablenotemark{c} & -UPPER, etc. & \ref{sec:se} \\
 %
@@
 \enddata
-\tablenotetext{a}{Fields in bold are updates or new additions from
-  \cite{Wright2011}. See Section~\ref{sec:update} for more details.}
-\tablenotetext{b}{-UPPER etc. means ``-UPPER, -LOWER, U-, -REF, -URL",
-where ``-" stands for the name of the field listed in the first
-column. They are... See Section~\ref{sec:unc} and \ref{sec:ref} for
-more details. -UL stands for upper limits for the fields (see
+\tablenotetext{a}{``-UPPER etc." means ``-UPPER, -LOWER, U-, -REF,
+  -URL", where ``-" stands for the name of the field listed in the
+  first column. These fields store the uncertainties and
+  references. See Section~\ref{sec:unc} and \ref{sec:ref} for more
+  details. ``-UL" stands for upper limits for the fields (see
   Section~\ref{sec:unc} for details).}
-\tablenotetext{c}{Originally as other commonly used name for star in \cite{Wright2011};
-  changed to other commonly used name for planet.}
-\tablenotetext{d}{The same as in \cite{Wright2011}, HJD/BJD etc.\ are
-  still not consistent.}
+\tablenotetext{b}{Fields that remain unchanged are referenced to
+  \cite{Wright2011}, abbreviated as ``W11". Fields that are new or
+  revised since \cite{Wright2011} are referenced to the relevant
+  section in this paper.}
+\tablenotetext{c}{As noted in \cite{Wright2011}, we do not report the
+  epoches of periastron, transit center, and secondary eclipse center
+  all consistently as HJD. We simply record what the original articles
+  report, which are in varies formats (JD, BJD, HJD etc.).}
 \end{deluxetable}

### 2014-03-12 draft/ms.tex
Section 5 update and comments from Jason are included

--- 2014-03-11 draft/ms.tex
@@
 
+ZZZ (1) We have a list of criteria for 'robustly detected' imaging planets (on our methodology web page) - do we have similar lists of criteria regarding 'robust detections' for microlensing, timing, and astrometry planets?
+
+No, not really.
+As I think we discuss in the last EOD paper (check) we relax some conditions for transiting planets (we don't have to have a measured RV amplitude, for instance).
+There have been no astrometric planets.
+Timing planets must have dynamically stable orbits and, ideally, show multiple complete orbits (see Jackson Norris's paper for a discussion of difficulties with timing planets, also cite recent papers by Rob Wittenmyer).
+In general, we accept microlensing planets that are appear in refereed journals as having unambiguously planetary masses.
+
 ZZZ Figure: some comparison figures of Kepler candidate properties vs. EOD
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion and Future}\label{sec:conclusion}
+\section{Summary and Future Work}\label{sec:conclusion}
 
-Any planned future improvements and updates?
+We have had two major updates since \cite{Wright2011}.
+We included Kepler planet candidates and other planets on exoplanets.org.
+Although they are not included in the EOD, we reported them on our website to help the users explore them and use them easily.
+We also have added some new fields, removed obsolete fields and revised them as necessary.
+
+ZZZ Any planned future improvements and updates?
+I hesitate to promise here, lest we overpromise.  We do hope to include images of directly imaged planets (where allowed under copyright law) and perhaps light curves for transits.
 

### 2014-03-12 draft/ms.tex
Minor fix on table refs.
Modify ref for SHK and RHK fields in table.

@@
 %------------------------------------------------------------------------------
-\subsection{Removed Fields}
+\subsection{Removed Fields}\label{sec:removed}
 
@@
 DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata & W11 \\
-MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata & W11 \\
+MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata & \ref{sec:disc} \\
 PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata & \ref{sec:disc} \\
@@
 EANAME\dotfill & String & Name of planet used in the Exoplanet
-Archive database & EAURL & \ref{sec:disc} \\
+Archive database & EAURL & \ref{sec:removed} \\
 SIMBADNAME\dotfill & String & Valid SIMBAD name of host star (or
@@
 KS\dotfill & Float & $K_S$ magnitude & \nodata & W11 \\
-SHK\dotfill & Float & Mount Wilson Ca {\sc{II}} $S$-value & \nodata & \ref{sec:stellarmag} \\
-RHK\dotfill & Float & Chromospheric activity of star as $\log{R'_{HK}}$ & \nodata & W11 \\
+SHK\dotfill & Float & Mount Wilson Ca {\sc{II}} $S$-value & \nodata & \ref{sec:ref} \\
+RHK\dotfill & Float & Chromospheric activity of star as $\log{R'_{HK}}$ & \nodata & \ref{sec:ref} \\
 KP\dotfill & Float & \kepler\ bandpass magnitude & \nodata & \ref{sec:stellarmag} \\

### 2014-03-13 draft/ms.tex
Summary written

--- 2014-03-12 draft/ms.tex
@@
 % Other Planets
-ZZZ Ask Jason about their criteria. \\ Second, we now also include
+Second, we now also include
 robustly detected imaging, microlensing, and timing planets, and our
@@
 \end{enumerate}
-\item Microlensing planets
+\item Microlensing planets:\\
+We accept microlensing planets that appear in refereed journals as having unambiguously planetary masses (planet host mass ratio, $q<0.024$). In case of ambiguity, we consult with QUACBED.
 
-\item Timing planets
+\item Timing planets:\\
+ Timing planets must have dynamically stable orbits and, ideally, show multiple complete orbits. 
+ ZZZ (see Jackson Norris's paper for a discussion of difficulties with timing planets, also cite recent papers by Rob Wittenmyer).
 
@@
 
-ZZZ (1) We have a list of criteria for 'robustly detected' imaging planets (on our methodology web page) - do we have similar lists of criteria regarding 'robust detections' for microlensing, timing, and astrometry planets?
-
-No, not really.
-As I think we discuss in the last EOD paper (check) we relax some conditions for transiting planets (we don't have to have a measured RV amplitude, for instance).
-There have been no astrometric planets.
-Timing planets must have dynamically stable orbits and, ideally, show multiple complete orbits (see Jackson Norris's paper for a discussion of difficulties with timing planets, also cite recent papers by Rob Wittenmyer).
-In general, we accept microlensing planets that are appear in refereed journals as having unambiguously planetary masses.
-
-ZZZ Figure: some comparison figures of Kepler candidate properties vs. EOD
-planet properties, such as mass-period, mass-radius?
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Summary and Future Work}\label{sec:conclusion}
+We have had two major updates since \cite{Wright2011}.
+First, we changed the scope of the EOD.
+We removed the limit on the type of the host star.
+We included the planets discovered by various methods (e.g.
+timing) in the EOD.
+We also have added some new fields, removed obsolete fields and revised them as necessary.
 
-We have had two major updates since \cite{Wright2011}.
-We included Kepler planet candidates and other planets on exoplanets.org.
+Second, we included Kepler planet candidates and other planets on exoplanets.org.
 Although they are not included in the EOD, we reported them on our website to help the users explore them and use them easily.
-We also have added some new fields, removed obsolete fields and revised them as necessary.
+
+ZZZ add summary for Onsi's section.
 

### 2014-03-13 draft/ms.tex
Add two figures and captions.

--- 2014-03-12 draft/ms.tex
@@
 
-The scope of the EOD has not been changed much but there were two major changes in the EOD.
-Previously, we only included exoplanets orbiting the `normal stars', but now we are not limiting the type of the host star (e.g.
-we included exoplanets orbiting neutron stars).
-Furthermore, we only had exoplanets that were discovered by RV and transit but as more exoplanets are discovered by various methods such as timing are now in the EOD.
-For the future, exoplanets discovered by other methods with good orbital parameters may also be included in the EOD.
+The scope of the EOD has not been changed much but there were two
+major changes in the EOD. Previously, we only included exoplanets
+orbiting the `normal stars', but now we are not limiting the type of
+the host star (e.g. we included exoplanets orbiting neutron
+stars). Furthermore, we only had exoplanets that were discovered by RV
+and transit but as more exoplanets are discovered by various methods
+such as timing are now in the EOD. For the future, exoplanets
+discovered by other methods with good orbital parameters may also be
+included in the EOD.
 
-The rest of the criteria remain unchanged. We still require the planets to be smaller than 24 \mjup\ and with robust detection (though not strictly quantitative; see \citealt{Wright2011}).
+The rest of the criteria remain unchanged. We still require the
+planets to be smaller than 24 \mjup\ and with robust detection (though
+not strictly quantitative; see \citealt{Wright2011}).
 
-The purpose of the EOD has not changed; we aim to provide the readers with comprehensive database for exoplanets that are discovered up-to-date.
-However, we do not report \textit{all} the announced exoplanets as we are not trying to do ``an encyclopedic presentation of every claimed detection of an exoplanet" \citep{Wright2011}.
+The purpose of the EOD has not changed; we aim to provide the readers
+with comprehensive database for exoplanets that are discovered
+up-to-date. However, we do not report \textit{all} the announced
+exoplanets as we are not trying to do ``an encyclopedic presentation
+of every claimed detection of an exoplanet" \citep{Wright2011}.
 
 We only describe new additions and revised fields here, but list all
-fields in Table~\ref{tab:par}. We divide the fields into categories in consistency with the individual planet page
-on exoplanets.org.
-Some fields are not explicitly included on the page (e.g., the URLs), but are explicitly listed in the downloadable {\tt .csv} file.\footnote{At \url{http://exoplanets.org/csv-files/exoplanets.csv}.} Though we focus on EOD in this section, the fields apply to all planets on exoplanets.org.
-For the definition of orbital elements see \cite{Wright2013} .
+fields in Table~\ref{tab:par}. We divide the fields into categories in
+consistency with the individual planet page on
+exoplanets.org. Figure~\ref{fig:individual} is an example of
+individual planet page. Some fields are not explicitly included on the
+page (e.g., the URLs), but are explicitly listed in the downloadable
+{\tt .csv} file.\footnote{At
+  \url{http://exoplanets.org/csv-files/exoplanets.csv}.} Though we
+focus on EOD in this section, the fields apply to all planets on
+exoplanets.org. For the definition of orbital elements see
+\cite{Wright2013} .
 %------------------------------------------------------------------------------
@@
 which was either radial velocity or transit. We have replaced DISCMETH
-with {\bf PLANETDISCMETH} and \mbox{{\bf STARDISCMETH}} to better report how
-the host star and the planet are detected.
-PLANETDISCMETH and STARDISCMETH are the fields that report the discovery methods for the planet and the first planet around the host star, respectively.
-Furthermore, they now have values of one of the following: radial velocity, transit, imaging,
-microlensing, timing, or astrometry.
+with {\bf PLANETDISCMETH} and \mbox{{\bf STARDISCMETH}} to better
+report how the host star and the planet are detected. PLANETDISCMETH
+and STARDISCMETH are the fields that report the discovery methods for
+the planet and the first planet around the host star,
+respectively. Furthermore, they now have values of one of the
+following: radial velocity, transit, imaging, microlensing, timing, or
+astrometry.
 
-{\bf MONTH} field reports the month in integer when the
-peer-reviewed paper is accepted to the ApJ.
+{\bf MONTH} field reports the month in integer when the peer-reviewed
+paper is accepted to the ApJ.
 
@@
 %------------------------------------------------------------------------------
-ZZZ Figure: Figure of single planet page, to show updated transit
-parameters and RV curves etc.?
+% Figure: single planet page
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=\textwidth]{../fig/wasp-14b.eps}
+\caption{An example page for an individual exoplanet (WASP-14b in this
+  case). The numbers listed in each field contain links to the
+  reference on ADS. In this example for WASP-14b, we provide the plot
+  for the phased RVs, but we are yet to implement such feature for all
+  planets with available RV data.}
+\label{fig:individual}
+\end{figure}
 
@@
 
-To display the KOIs in the EDE table, check the ``Kepler" option on the
-upper left of the table (default selection only includes ``Orbit
+To display the KOIs in the EDE table, check the ``Kepler" option on
+the upper left of the table (default selection only includes ``Orbit
 Database", i.e.~the EOD, and ``Other"). They can also be displayed on
-plots with the interactive plotting tool of EDE.
+plots with the interactive plotting tool of EDE (see
+Figure~\ref{fig:koi} for an example plot).
 
@@
 
-ZZZ Figure: some comparison figures of Kepler candidate properties vs. EOD
-planet properties, such as mass-period, mass-radius?
+%------------------------------------------------------------------------------
+% Figure: single planet page
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=\textwidth]{../fig/mass-per-color.eps}
+\caption{An example plot produced by the interactive plotting tools of
+  EDE on exoplanets.org. The $x$-axis is planet orbital period in days
+  and $y$-axis is planet mass in Earth's mass. The exoplanet samples
+  being plotted are the ones in the EOD, including transit planets
+  (blue large dots), RV planets (red triangles), and timing planets
+  (magenta squares). The KOIs are plotted as black small dots, and
+  their masses are calculated using their radii based on mass-radius
+  relations from the literature (see Section~\ref{sec:orbit}).}
+\label{fig:koi}
+\end{figure}
 

### 2014-03-13 draft/ms.tex

@@
   case). The numbers listed in each field contain links to the
-  reference on ADS. In this example for WASP-14b, we provide the plot
+  reference on NASA ADS. In this example for WASP-14b, we provide the plot
   for the phased RVs, but we are yet to implement such feature for all
@@
 \end{enumerate}
-\item Microlensing planets
+\item Microlensing planets:\\
+We accept microlensing planets that appear in refereed journals as
+having unambiguously planetary masses (planet host mass ratio,
+$q<0.024$). In cases of ambiguity, we consult with QUACBED.
 
-\item Timing planets
+\item Timing planets:\\
+ Timing planets must have dynamically stable orbits and, ideally, show
+ multiple complete orbits (e.g., see \citealt{Wittenmyer2012},
+ \citealt{Horner2012}, and \citealt{Wittenmyer2013}).
 
@@
 
-ZZZ (1) We have a list of criteria for 'robustly detected' imaging planets (on our methodology web page) - do we have similar lists of criteria regarding 'robust detections' for microlensing, timing, and astrometry planets?
-
-No, not really.
-As I think we discuss in the last EOD paper (check) we relax some conditions for transiting planets (we don't have to have a measured RV amplitude, for instance).
-There have been no astrometric planets.
-Timing planets must have dynamically stable orbits and, ideally, show multiple complete orbits (see Jackson Norris's paper for a discussion of difficulties with timing planets, also cite recent papers by Rob Wittenmyer).
-In general, we accept microlensing planets that are appear in refereed journals as having unambiguously planetary masses.
+ZZZ mention there have been no astrometry planets so far, but we do
+plan to include them if any robust detections occur.
 
@@
 
-We have had two major updates since \cite{Wright2011}.
-We included Kepler planet candidates and other planets on exoplanets.org.
-Although they are not included in the EOD, we reported them on our website to help the users explore them and use them easily.
-We also have added some new fields, removed obsolete fields and revised them as necessary.
+We have had two major updates since \cite{Wright2011}. First, we
+changed the scope of the EOD. We removed the limit on the type of the
+host star. We included the planets discovered by various methods
+(e.g. timing) in the EOD. We also have added some new fields, removed
+obsolete fields and revised them as necessary.
 
-ZZZ Any planned future improvements and updates?
-I hesitate to promise here, lest we overpromise.  We do hope to include images of directly imaged planets (where allowed under copyright law) and perhaps light curves for transits.
+Second, we included Kepler planet candidates and other planets on
+exoplanets.org. Although they are not included in the EOD, we reported
+them on our website to help the users explore them and use them
+easily.
+
+ZZZ add summary for Onsi's section.
+
+ZZZ Any planned future improvements and updates?  I hesitate to
+promise here, lest we overpromise.  We do hope to include images of
+directly imaged planets (where allowed under copyright law) and
+perhaps light curves for transits.
 
@@
 
-SXW acknowledges support from PSARC.
+SXW acknowledges support from PSARC. This research has made use of
+NASA's Astrophysics Data System Bibliographic Services (ADS).
 

### 2014-03-13 draft/references.tex

@@
 arXiv:1208.4012   % WFIRST
+
+\bibitem[Horner et al.(2012)]{Horner2012} Horner, J., Wittenmyer, R.~A., 
+Hinse, T.~C., \& Tinney, C.~G.\ 2012, \mnras, 425, 749 % dynamic
+                                % analysis on timing planet
 
@@
 
+\bibitem[Wittenmyer et al.(2012)]{Wittenmyer2012} Wittenmyer, R.~A., 
+Horner, J., Marshall, J.~P., Butters, O.~W., 
+\& Tinney, C.~G.\ 2012, \mnras, 419, 3258 % dynamic analysis on timing
+                                % planets
+
+\bibitem[Wittenmyer et al.(2013)]{Wittenmyer2013} Wittenmyer, R.~A., 
+Horner, J., \& Marshall, J.~P.\ 2013, \mnras, 431, 2150 % dynamic
+                                % analysis on timing planets
+
 \bibitem[Wright et al.(2011)]{Wright2011} Wright, J.~T., et al.\ 2011,

### 2014-03-14 draft/ms.tex
Section 3 and 5 update and random notes for abstract

@@
 Make sure to mention: data are available at exoplanets.org; KOIs are included.
+ZZZ Also mention the number of confirmed planets? and maybe the scope of the EOD (what are in our database)
 \end{abstract}
@@
 EOD, while several timing exoplanets have well-determined orbital
-parameters and are included in the EOD.
-
-ZZZ mention there have been no astrometry planets so far, but we do
-plan to include them if any robust detections occur.
+parameters and are included in the EOD. Moreover, there have been no astrometry planets in the EOD but we plan to include them if any robust detections occur.
 
@@
 
-ZZZ Any planned future improvements and updates?  I hesitate to
-promise here, lest we overpromise.  We do hope to include images of
-directly imaged planets (where allowed under copyright law) and
-perhaps light curves for transits.
+We hope to include images of directly imaged planets (where allowed under copyright law) and
+light curves for transits in the future.
 

### 2014-03-15 draft/ms.tex
Proofread and revisions from sec 1 through sec 2.1.

--- 2014-03-13 draft/ms.tex
@@
 majority of these new discoveries ($> 800$) while providing an
-additional sample of over 3000 exoplanet candidates(\kepler\ Objects
+additional sample of over 3000 exoplanet candidates (\kepler\ Objects
 of Interest, KOIs; e.g.~\citealt{Batalha2013}). The transit method has
@@
 and the Exoplanets Data Explorer (EDE) to keep track of the exoplanet
-discoveries and catalog their orbital parameters and host star
+discoveries and to catalog their orbital parameters and host star
 properties. There are also other entities devoted to this effort,
 including the Extrasolar Planets Encyclopaedia\footnote{See
-  \url{http://exoplanet.eu}.}  \citep{Schneider2011}, the NASA
+  \url{http://exoplanet.eu}.}  \citep{Schneider2011} and the NASA
 Exoplanet Archive\footnote{See
@@
 % updates on EOD and the website
-Since \cite{Wright2011}, the EOD has expanded its scope and we now do
+Since \cite{Wright2011}, the EOD has expanded its scope: we now do
 not require the host star of an exoplanet to be a normal star (e.g.,
 exoplanets around pulsars are now included). It has also ingested more
-parameters of the exoplanet systems and host stars, and some
+parameters describing the exoplanet systems and their host stars, and some
 parameters are revised or deleted. We describe the updates with the
-EOD in Section~\ref{sec:update}. We also describe the updates to the
-hosting website, exoplanets.org. The EDE at exoplanets.org has
+EOD in Section~\ref{sec:update}. The EDE at exoplanets.org has also
 expanded its scope and now includes the \kepler\ exoplanet candidates
 (KOIs). We describe these changes in Section~\ref{sec:kepler}. The
-website has also gone through major back-end changes since
-\cite{Wright2011}, which is described in Section~\ref{sec:website}.
+website exoplanets.org has gone through major back-end changes since
+\cite{Wright2011}, which is described in Section~\ref{sec:website}. We
+summarize the updates and possible future improvements in
+Section~\ref{sec:summary}.
 
@@
 
-The scope of the EOD has not been changed much but there were two
-major changes in the EOD. Previously, we only included exoplanets
-orbiting the `normal stars', but now we are not limiting the type of
-the host star (e.g. we included exoplanets orbiting neutron
-stars). Furthermore, we only had exoplanets that were discovered by RV
-and transit but as more exoplanets are discovered by various methods
-such as timing are now in the EOD. For the future, exoplanets
-discovered by other methods with good orbital parameters may also be
-included in the EOD.
+The scope of the EOD has expanded, and there are two major changes
+from what was described in \cite{Wright2011}. Previously, we only
+included exoplanets orbiting the ``normal stars", but now we are not
+limiting the type of host stars (e.g. we included exoplanets orbiting
+neutron stars). Furthermore, in \cite{Wright2011}, we only had
+exoplanets that were discovered by the RV and transit methods in the
+EOD, but now we also have planets discovered via timing. For the
+future, exoplanets discovered by any other methods with robust
+detections and good orbital parameters will also be included in the
+EOD.
 
-The rest of the criteria remain unchanged. We still require the
-planets to be smaller than 24 \mjup\ and with robust detection (though
-not strictly quantitative; see \citealt{Wright2011}).
+The rest of the selection criteria for the EOD remain unchanged. We
+still require the planets to be smaller than 24 \mjup\ and to have
+robust detections and well-determined orbits (though these are not
+strictly quantitative; see Section~2 of \citealt{Wright2011}).
 
-The purpose of the EOD has not changed; we aim to provide the readers
-with comprehensive database for exoplanets that are discovered
-up-to-date. However, we do not report \textit{all} the announced
-exoplanets as we are not trying to do ``an encyclopedic presentation
-of every claimed detection of an exoplanet" \citep{Wright2011}.
+The purpose of the EOD has not changed: we aim to provide the readers
+with a comprehensive, reliable, and up-to-date database of exoplanets
+with good orbital parameters and host star properties. We do not
+report \textit{all} the announced exoplanets as we are not trying to
+do ``an encyclopedic presentation of every claimed detection of an
+exoplanet" \citep{Wright2011}.
 
-We only describe new additions and revised fields here, but list all
-fields in Table~\ref{tab:par}. We divide the fields into categories in
+In the following subsections, we describe the newly added and revised
+fields since \cite{Wright2011}, but list all fields in
+Table~\ref{tab:par}. We divide the fields into categories in
 consistency with the individual planet page on
 exoplanets.org. Figure~\ref{fig:individual} is an example of
-individual planet page. Some fields are not explicitly included on the
-page (e.g., the URLs), but are explicitly listed in the downloadable
-{\tt .csv} file.\footnote{At
-  \url{http://exoplanets.org/csv-files/exoplanets.csv}.} Though we
-focus on EOD in this section, the fields apply to all planets on
-exoplanets.org. For the definition of orbital elements see
-\cite{Wright2013} .
+individual planet page. Some fields are not explicitly tabulated on
+the page (e.g., the URLs), but are explicitly listed in the
+downloadable {\tt .csv} file (see Section~\ref{sec:intro}). Though we
+focus on the EOD in this section, the fields apply to all planets on
+exoplanets.org. We follow the definition of orbital elements in
+\cite{Wright2013} unless indicated otherwise.
+
 %------------------------------------------------------------------------------
@@
 We report general information of when, by whom and how the planets
-were discovered and provide the references. We describe the added
-fields since \cite{Wright2011} below.
+were discovered and provide the references. We describe the added or
+revised fields since \cite{Wright2011} below.
 
@@
 with {\bf PLANETDISCMETH} and \mbox{{\bf STARDISCMETH}} to better
-report how the host star and the planet are detected. PLANETDISCMETH
-and STARDISCMETH are the fields that report the discovery methods for
-the planet and the first planet around the host star,
-respectively. Furthermore, they now have values of one of the
-following: radial velocity, transit, imaging, microlensing, timing, or
-astrometry.
+report how exoplanet systems and individual exoplanets are first
+discovered. PLANETDISCMETH reports the discovery method for the
+planet, wihle STARDISCMETH reports the discovery method for the first
+discovered planet around the host star. Furthermore, they are stored
+in string formats and have values of one of the following: RV,
+Transit, Imaging, Microlensing, Timing, or Astrometry.
 
-{\bf MONTH} field reports the month in integer when the peer-reviewed
-paper is accepted to the ApJ.
+{\bf MONTH} field reports the month in integer of when the
+peer-reviewed paper is accepted by the journal.
 
-{\bf KEPID} stands for KEPler ID which is the integer number assigned
+{\bf KEPID} stands for KEPler ID, which is the integer number assigned
 for a Kepler host star. KEPID is only available for the unconfirmed
@@
 
-{\bf KOI} stands for Kepler Objects of Interest which is a star with
-transit signals detected by \kepler\ but have not been confirmed to
-due to exoplanets. The KOI field contains a floating point number that
-consist of a whole number designated to the host star followed by a
-decimal number denoting a candidate planet. For example, KOI 102 is a
-star suspected to host two exoplanets and KOI 102.01 is the inner
-planet candidate and KOI 102.02 is the outer one. Once a candidate is
-confirmed, the NAME field of the planet is replaced by the official
-\kepler\ ID ('Kepler' followed by a hyphen, an integer and a
-letter). The KOI number is used as OTHERNAME. None of the KOIs are in
-the EOD and for more information see Section~\ref{sec:kepler}.
+{\bf KOI} stands for Kepler Objects of Interest, which is an object
+with transit signals detected by \kepler\ but have not been confirmed
+to be due to exoplanets. The KOI field contains a floating point
+number that consist of a whole number designated to the host star
+followed by a decimal number denoting a candidate planet. For example,
+KOI 102 is a star suspected to host two exoplanets, and KOI 102.01 is
+the inner planet candidate and KOI 102.02 is the outer one. Once a
+candidate is confirmed, the NAME field of the planet is replaced by
+the official \kepler\ ID (``Kepler" followed by a hyphen, an integer
+and an lower case letter). The KOI number is then used as
+OTHERNAME. None of the KOIs are in the EOD. For more information, see
+Section~\ref{sec:kepler}.
 
-\begin{comment}
-\textit {Sharon: you need to say what KOI stores. When writing each
-  field, keep in mind you need to cover the following so that the
-  reader will completely understand: (1) what the field stands for
-  (e.g., in case of an abbreviation like KOI); (2) what the field
-  physically means, like `KOI' means planet candidates that have
-  transit signals as detected by \kepler\ but have not been confirmed,
-  and make sure to be thorough at what you say -- sometimes things are
-  not that obvious to an outsider reader, e.g., think if a cosmologist
-  would understand what you're saying when reading it; (3) what the
-  field actually contains, e.g. KOI contains the KOI number designated
-  by the \kepler\ team (right?), it is a floating point number, and
-  sometimes maybe even worth giving an example, e.g. KOI 30.1 or
-  something...; (4) why we added this new field, if this information
-  is helpful, or if it's a revised field since \cite{Wright2011}, what
-  is changed. Also, use \kepler\ (which is a defined symbol in our
-  ms.tex file), instead of typing out Kepler, since you need italic.
-  Don't be afraid to write more! Being concise is important, but it's
-  always easier to trim down things than to add things on, especially
-  for a documentation type of paper like this. Let's be thorough at
-  first, then try to reach optimal conciseness.}
- \end{comment}
-
-%KDE: obselete field! Detele from the table.
-
-{\bf EOD} is a flag which indicates whether an exoplanet has
-well-characterized orbital parameters (e.g. period (PER)). EOD equals
-1 means the exoplanet is in the EOD. We added this field because
-exoplanets.org now also includes robustly discovered planets that do
-not have well-characterized orbits, and also \kepler\ planet
-candidates (see Section~\ref{sec:kepler} for more details).
+{\bf EOD} is a flag which indicates whether an exoplanet is included
+in the EOD for having robust detection and well-characterized orbital
+parameters such as the orbital period (PER). EOD equals 1 means the
+exoplanet is in the EOD. We added this field because exoplanets.org
+now also includes robustly discovered planets that do not have
+well-characterized orbits, and also \kepler\ planet candidates (see
+Section~\ref{sec:kepler} for more details).
 
@@
 indicate that a planet detected via theses methods. For example,
-MICROLENSING $=$ 1 means the planet is detected by a microlensing
+MICROLENSING $=$ 1 means the planet is detected in a microlensing
 event. However, we require the detection to be robust, as determined
-by the QUAlity Control Board of the Exoplanet Database, QUACBED.
+by the QUAlity Control Board of the Exoplanet Database, QUACBED (see
+Section~\ref{sec:kepler}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary and Future Work}\label{sec:conclusion}
+\section{Summary and Future Work}\label{sec:summary}
 

### 2014-03-17 draft/ms.tex
Summary section done and abstract

@@
 
-\title{The Exoplanet Orbit Database 2, 2014 updates}
+\title{The Exoplanet Orbit Database \textsc{II}: 2014 updates}
 
@@
 \begin{abstract}
+We made an effort to put robustly detected exoplanets together with over 3000 sample of exoplanet candidates (\kepler\ Objects of Interest, KOIs) in the Exoplanet Orbit Database (EOD).
+The EOD is available at exoplanets.org and we have ZZZ number of confirmed exoplanets as of March 2014.
+
  Make sure to mention: data are available at exoplanets.org; KOIs are included.
@@
 We have had two major updates since \cite{Wright2011}. First, we
-changed the scope of the EOD. We removed the limit on the type of the
-host star. We included the planets discovered by various methods
-(e.g. timing) in the EOD. We also have added some new fields, removed
-obsolete fields and revised them as necessary.
+expanded the scope of the EOD.
+We removed the requirement for the host star being normal and included the planets discovered not only by RV and transit but also by various other methods (e.g.
+timing) in the EOD.
+We also have added some new fields, most notably, we now report the secondary eclipse depths.
+We removed obsolete fields and revised some fields as necessary.
 
-Second, we included Kepler planet candidates and other planets on
-exoplanets.org. Although they are not included in the EOD, we reported
-them on our website to help the users explore them and use them
-easily.
+Second, we included KOIs and other planets (the ones detected by microlensing, imaging, timing, and in the future, astrometry) on exoplanets.org.
+Although they are not included in the EOD, we reported them on our website since the users might find them useful for purposes of statistical studies and comparison.
 
@@
 
-We hope to include images of directly imaged planets (where allowed under copyright law) and
-light curves for transits in the future.
+In the future, we hope to include images of directly imaged planets (where allowed under copyright law) and
+light curves for transits. We also plan to display RV curves whenever their RV data are available.
 

### 2014-03-17 draft/ms.tex
Refine Sec 2.2.

--- 2014-03-15 draft/ms.tex
@@
 robust detections and well-determined orbits (though these are not
-strictly quantitative; see Section~2 of \citealt{Wright2011}).
+strictly quantitative; see Section~2 of \citealt{Wright2011}). When
+new evidence comes to light and we are no longer confident about the
+planet, we remove it from EOD, even if the evidence is not peer
+reviewed.
 
@@
 by the QUAlity Control Board of the Exoplanet Database, QUACBED (see
-Section~\ref{sec:kepler}.
+Section~\ref{sec:kepler}).
 
@@
 planet has both radial velocity and transit measurements, we calculate
-the mass from the minimum mass and the orbital inclination. MASS is
-set to MSINI if the orbital inclination is not given and the MASSREF
-is set to ``Set to MSINI; I unknown''.
+the mass from the minimum mass $m\sin{i}$ and the orbital inclination
+$i$. MASS is set to MSINI if the orbital inclination is not given and
+the reference for MASS, MASSREF is set to ``Set to MSINI; I unknown''.
 
@@
 mass-radius relation from the literatures. For KOIs with $R<4\rearth$,
-we use \cite{Weiss2014} , with $4\rearth<R<6\rearth$, we use
-\cite{Lissauer2011}, and for KOIs with $6\rearth<R<11.7\rearth$ we use
+we follow \cite{Weiss2014}; for $4\rearth<R<6\rearth$, we follow
+\cite{Lissauer2011}; and for $6\rearth<R<11.7\rearth$ we follow
 \cite{Mordasini2012}.
@@
 and the planet in the unit of AU. For directly imaged planets, the
-literatures give the projected separation and we report this value.
-If SEP is not directly measured but the semi-major (A) is available,
-then SEP is set to A with the reference ``Set to A''. For the cases
-where only the projected separation is given such as imaged planets,
-then the semi-major axis is set to SEP.
+literatures usually report the projected separation and we report the
+value accordingly.  If SEP is not directly measured but the semi-major
+axis ($a$, A) is available, then SEP is set to A with its reference,
+SEPREF, set to ``Set to A''. For the cases where only the projected
+separation is given but A is not available (e.g., the directly imaged
+planets), then A is set to SEP.
 
 {\bf I} is the orbital inclination. Previously, only transiting
-systems have I measured but now, sometimes, non-transiting systems
-have I's reported too. For example, one microlensing system has I
-measured (OGLE-2006-BLG-109L; \citealt{Bennet2010}).
+systems have I measured, but now some non-transiting systems
+have I's reported too. For example, one microlensing system,
+OGLE-2006-BLG-109L, has I measured \citep{Bennett2010}.
 
 {\bf BIGOM} is the longitude of the ascending node ($\Omega$) in the
-unit of degree and for now this is only measured for some of the
+unit of degree. At the moment, this is only measured for some of the
 directly imaged planets, which are not in the EOD.
@@
 {\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
-the unit of degree. We report the projected spin-orbit misalignment of
-transiting systems, which is measured by, e.g., the
-Rossiter-McLaughlin effect \citep[e.g.,][]{Winn2005} or planet
-transiting star spots \citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is
-introduced because the true spin-orbit angle ($\phi$), defined as the
-angle between the stellar spin axis and the orbital axis, is normally
-not directly measurable. We follow the definition of $\lambda$ in
-\cite{Fabrycky2009} where the coordinates are defined as follows; the
+the plane of the sky in the unit of degree. At the moment, $\lambda$
+values are only available for the transiting systems, which are
+measured by either the Rossiter-McLaughlin effect
+\citep[e.g.,][]{Winn2005} or planet transiting star spots
+\citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is introduced because
+the true spin-orbit angle ($\phi$), defined as the angle between the
+stellar spin axis and the orbital axis, is normally not directly
+measurable. We follow the definition of $\lambda$ in
+\cite{Fabrycky2009} where the coordinates are defined as follows: the
 $z$-axis points toward the observer, the $x$-axis points along the
@@
 the $y$-axis to the projected stellar rotational axis. $\lambda$ is
-not a newly added field but we describe it here because $\lambda$'s
-were not reported consistently since some literatures report $\beta =
--\lambda$ instead. We sorted these cases out and made sure that our
-$\lambda$'s are following the definition of \cite{Fabrycky2009}.
+not a newly added field but we describe it here because it was not
+reported consistently since some literatures report the ``projected
+spin-orbit misalignment" as $\beta = -\lambda$ instead. We have sorted
+these cases out and made sure that our $\lambda$'s are following the
+definition of \cite{Fabrycky2009}.
 

### 2014-03-17 draft/ms.tex
Abstract sturcture

@@
 \begin{abstract}
+The Exoplanet Orbit Database (EOD) is
+
 We made an effort to put robustly detected exoplanets together with over 3000 sample of exoplanet candidates (\kepler\ Objects of Interest, KOIs) in the Exoplanet Orbit Database (EOD).
+
+What does our  website go?
 The EOD is available at exoplanets.org and we have ZZZ number of confirmed exoplanets as of March 2014.
+
+What has been updated?
 
@@
 ZZZ Also mention the number of confirmed planets? and maybe the scope of the EOD (what are in our database)
+
 \end{abstract}

### 2014-03-18 draft/ms.tex
Comments from the group meeting
Revisions and proofreading up to before Sec 3.

@@
 axis ($a$, A) is available, then SEP is set to A with its reference,
-SEPREF, set to ``Set to A''. For the cases where only the projected
-separation is given but A is not available (e.g., the directly imaged
-planets), then A is set to SEP.
+SEPREF, set to ``Set to A''.
 
@@
 We have added an entirely new set of fields for the secondary
-eclipse. Previously, due to the limits of instrumentation, there were
-not much available measured secondary eclipse depths. Since
-\cite{Wright2011}, as many different surveys have been launched,
-secondary eclipse depths at multiple bands are now
-available. Therefore, we added this entire new set of fields since.
+eclipse. Previously, due to the limits of instrumentation and limited
+sample of exoplanets, there were not much secondary eclipse depth data
+available. Since \cite{Wright2011}, as many different surveys have
+been launched, more and more secondary eclipse depths at multiple
+bands become available for more and more planets. Therefore, we added
+this entire new set of fields.
 
@@
 eclipse in any of the two Micron All-Sky Survey (2MASS;
-\citealt{Skrustskie2006}) $J$, $H$, and $K_s$, Kepler photometry band,
-and 4 Spitzer IRAC bands. SE is a boolean and being true indicates the
+\citealt{Skrutskie2006}) $J$, $H$, and $K_s$, Kepler photometry band,
+and 4 Spitzer IRAC bands. SE is a boolean and SE $=$ 1 indicates the
 system has at least one detected secondary eclipse.
@@
 
-{\bf SET} is the epoch of secondary eclipse center in HJD.
+{\bf SET} is the epoch of secondary eclipse center (normally in HJD).
 
@@
 We provide the brightness of the host star measured in different
-wavelengths. We report optical magnitudes ($V$ and $B-V$), 2MASS $J$,
-$H$, and $K_s$ magnitudes and we added {\bf KP} since
+wavelengths. We report optical magnitude and color ($V$ and $B-V$),
+2MASS $J$, $H$, and $K_s$ magnitudes and we added {\bf KP} since
 \cite{Wright2011}, which is the stellar magnitude measured through the
-Kepler bandpass.
+\kepler\ bandpass.
 
@@
 \subsection{Coordinates and Catalogs}\label{sec:coord}
-We report the coordinates of the host star as well as the stellar ID
-as designated by different catalogs.  We added {\bf DIST} since
-\cite{Wright2011}, which is the distance of the host star in the unit
-of pc. If only parallax (PAR) is given, we convert it to DIST and vice
-versa. If the literature does not report DIST or PAR, then we obtain
-PAR from the Hipparcos data set by \cite{van Leeuwen2009}.
 
-We naively propagate the error in PAR to DIST.
+We report the coordinates of the host star as well as the host star's
+ID as designated by different catalogs.  We added {\bf DIST} since
+\cite{Wright2011}, which is the distance to the host star in the unit
+of pc. If only parallax (PAR) is given, we calculate DIST based on PAR
+and vice versa. If the literature does not report DIST or PAR, then we
+obtain PAR from the Hipparcos dataset by \cite{van Leeuwen2009}. We
+naively propagate the error in PAR to DIST and vice versa.
 
@@
 
-We now report uncertainties for a certain field X as XUPPER, XLOWER
-and UX. XUPPER and XLOWER store the upper and lower 1$\sigma$
-uncertainties, and they are different when the error bars are
-asymmetric. UX contains the 1$\sigma$ uncertainty, and it equals to
-$({\rm XUPPER+XLOWER})/2$ in the case of asymmetric error bars. Fields
-that have XUPPER, XLOWER and UX are: all the orbital parameters except
-for TREND and FREEZE\_ECC flags; all the transit parameters except for
-TRANSIT flags; all the secondary eclipse fields except for SE flag;
-and all the stellar properties except for STAR, SPECREF and BINARY
-flag; and DIST and PAR.
+We have changed the way of reporting uncertainties, especially
+asymmetric error bars since \cite{Wright2011}. We now report
+uncertainties for a certain field X as XUPPER, XLOWER and UX. XUPPER
+and XLOWER store the upper and lower 1$\sigma$ uncertainties, and they
+are different when the error bars are asymmetric. UX contains the
+1$\sigma$ uncertainty, and it equals to $({\rm XUPPER+XLOWER})/2$ in
+the case of asymmetric error bars. Fields that have XUPPER, XLOWER and
+UX are: all the orbital parameters except for TREND and FREEZE\_ECC
+flags; all the transit parameters except for TRANSIT flags; all the
+secondary eclipse fields except for SE flag; and all the stellar
+properties except for STAR, SPECREF and BINARY flag; and DIST and PAR.
 
-We also report the upper limits (XUL) for planet mass (MSINI),
-eccentricity (ECC), and the velocity semi-amplitude (K) when the
-literatures report them. For example, the upper limits for ECC is
-reported when the orbit is circular, and the upper limits for K is
-reported when there is no radial velocity detection. If only upper
-limits are given, we set the field to 0, the uncertainty to half of
-the upper limit, and the upper limits to the upper limits. For
-example, if the literature reports the upper limit for ECC, then we
-put the value in ECCUL, set ECC to be 0, ECCUPPER to ECCUL, and UECC
+We also report the upper limits (XUL) for planet minimum mass (MSINI),
+eccentricity (ECC), and the radial velocity semi-amplitude (K) when
+the literatures report them. For example, the upper limits for ECC is
+reported when the orbit is consistent with a circular one, and the
+upper limits for K is reported when there is only upper-limit radial
+velocity detection. If only upper limits are given, we set the
+parameter field X to 0, the uncertainty XU to half of the upper limit,
+and the upper error bar XUPPER to the upper limits (same as XUL). For
+example, if the literature reports the upper limit for ECC, which we
+report in ECCUL, then we set ECC to be 0, ECCUPPER to ECCUL, and UECC
 to ECCUL/2. Since not all authors define the upper limits in the same
 way (e.g. 1$\sigma$ or some fixed percentile), we encourage the
-readers to refer to the literature for more information.
+readers to refer to the original references for more information.
 
@@
 The fields {\bf XREF} and {\bf XURL} store the peer-reviewed reference
-and link to the publication for the field X.
+and link to the publication for the field X. Previously, we only
+reported general references for certain sets of fields (e.g. FIRSTREF,
+FIRSTURL, ORBREF, and ORBURL), but now we report the references for
+most of the fields on an individual basis.
 
-Previously, we only reported general references (e.g. FIRSTREF,
-FIRSTURL, ORBREF, and ORBURL), but now we report the references for
-most of the fields.
+The following fields do not have associated REF or URL fields, and we
+list their references here: RA, DEC, and PAR are from the
+\textit{Hipparcos} by \cite{van Leeuwen2009}; the $B-V$ (BMV) values
+are from the \textit{Hipparcos} catalog by \cite{Perryman1997};
+stellar magnitudes J H and KS are from the 2MASS
+\citep{Skrutskie2006}; the KP magnitudes are from the Exoplanet
+Archive \citep{Akeson2013}.
 
-RA, DEC, and PAR do not have references but they are from the
-\textit{Hipparcos} by \cite{van Leeuwen2009}. $B-V$ (BMV) field does
-not have a reference but the values are from the \textit{Hipparcos}
-catalog by \cite{Perryman1997}. The fields J H and KS do not have
-references as well but they are from the 2MASS
-\citep{Skrutskie2006}. The KP field do not have reference but the
-values are from the Exoplanet Archive \citep{Akeson2013}.
-
-SHK and RHK are poorly maintained fields and they unreferenced at the
-moment though we plan to include proper reference in the future. Most
-of the values are from \cite{Butler2006}.
+SHK and RHK are poorly maintained fields, and they unreferenced at the
+moment. We plan to include proper reference in the future. Most of the
+SHK and RHK values are from \cite{Butler2006}.
 
@@
 
-We removed 2 fields.
+We removed 2 fields since \cite{Wright2011}:
 
 {\bf SPSTAR} field previously reported the stellar type of the host
-star but it is removed since it is not reliable.
+star, but it is removed since it is not reliable.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Inclusion of the Kepler Planet Candidates and Other Exoplanets on Exoplanets.org}\label{sec:kepler}
+\section{Inclusion of the Kepler Planet Candidates \\
+  and Other Exoplanets on Exoplanets.org}\label{sec:kepler}
 
@@
 We have had two major updates since \cite{Wright2011}. First, we
-expanded the scope of the EOD.
-We removed the requirement for the host star being normal and included the planets discovered not only by RV and transit but also by various other methods (e.g.
-timing) in the EOD.
-We also have added some new fields, most notably, we now report the secondary eclipse depths.
-We removed obsolete fields and revised some fields as necessary.
+expanded the scope of the EOD. We removed the requirement for the host
+star being normal and included the planets discovered not only by RV
+and transit but also by various other methods (e.g. timing) in the
+EOD. We also have added some new fields, most notably, we now report
+the secondary eclipse depths. We removed obsolete fields and revised
+some fields as necessary.
 
-Second, we included KOIs and other planets (the ones detected by microlensing, imaging, timing, and in the future, astrometry) on exoplanets.org.
-Although they are not included in the EOD, we reported them on our website since the users might find them useful for purposes of statistical studies and comparison.
+Second, we included KOIs and other planets (the ones detected by
+microlensing, imaging, timing, and in the future, astrometry) on
+exoplanets.org. Although they are not included in the EOD, we reported
+them on our website since the users might find them useful for
+purposes of statistical studies and comparison.
 
@@
 
-In the future, we hope to include images of directly imaged planets (where allowed under copyright law) and
-light curves for transits. We also plan to display RV curves whenever their RV data are available.
+In the future, we hope to include images of directly imaged planets
+(where allowed under copyright law) and light curves for transits. We
+also plan to display RV curves whenever their RV data are available.
 

### 2014-03-19 draft/ms.tex
abstract update

@@
 \begin{abstract}
-The Exoplanet Orbit Database (EOD) is
+The Exoplanet Orbit Database (EOD) collects orbital and stellar parameters of all known exoplanets reported in the peer-reviewed literature.
+The EOD can be navigated through the Exoplanet Data Explorer (EDE) Plotter and Table, available at exoplanets.org.
+We have ZZZ number of confirmed exoplanets as of March 2014.
+Since \cite{Wright2011}, we made an effort to put robustly detected exoplanets together with over 3000 sample of exoplanet candidates (\kepler\ Objects of Interest, KOIs) and other planets (the ones detected by microlensing, imaging, timing) on exoplanets.org.
+We also added some new fields (e.g.
+the secondary eclipse depths), removed obsolete fields, and revised some fields as necessary.
 
-We made an effort to put robustly detected exoplanets together with over 3000 sample of exoplanet candidates (\kepler\ Objects of Interest, KOIs) in the Exoplanet Orbit Database (EOD).
-
-What does our  website go?
-The EOD is available at exoplanets.org and we have ZZZ number of confirmed exoplanets as of March 2014.
-
+What  is the EOD?
+What does our  website do?
 What has been updated?
-
 Make sure to mention: data are available at exoplanets.org; KOIs are included.
@@
 
+ZZZ orbital mass vs orbital distance
+
+ZZZ screen shots of what it looks like in the browser
+
+ZZZ add SE plots from Ming
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-03-19 draft/ms.tex
Minor notes and change fig:koi.

--- 2014-03-18 draft/ms.tex
@@
 \begin{abstract}
+
 The Exoplanet Orbit Database (EOD) is
 
-We made an effort to put robustly detected exoplanets together with over 3000 sample of exoplanet candidates (\kepler\ Objects of Interest, KOIs) in the Exoplanet Orbit Database (EOD).
+We made an effort to put robustly detected exoplanets together with
+over 3000 sample of exoplanet candidates (\kepler\ Objects of
+Interest, KOIs) in the Exoplanet Orbit Database (EOD).
 
-What does our  website go?
-The EOD is available at exoplanets.org and we have ZZZ number of confirmed exoplanets as of March 2014.
+What does our website go?  The EOD is available at exoplanets.org and
+we have ZZZ number of confirmed exoplanets as of March 2014.
 
@@
 
- Make sure to mention: data are available at exoplanets.org; KOIs are included.
-ZZZ Also mention the number of confirmed planets? and maybe the scope of the EOD (what are in our database)
+Make sure to mention: data are available at exoplanets.org; KOIs are
+ included.  ZZZ Also mention the number of confirmed planets? and
+ maybe the scope of the EOD (what are in our database)
 
@@
 bands become available for more and more planets. Therefore, we added
-this entire new set of fields.
+this entire new set of fields. ZZZ Refer to Ming's SE plot.
 
@@
 EOD, while several timing exoplanets have well-determined orbital
-parameters and are included in the EOD. Moreover, there have been no astrometry planets in the EOD but we plan to include them if any robust detections occur.
+parameters and are included in the EOD. Moreover, there have been no
+astrometry planets in the EOD but we plan to include them if any
+robust detections occur.
 
@@
 \centering
-\includegraphics[width=\textwidth]{../fig/mass-per-color.eps}
-\caption{An example plot produced by the interactive plotting tools of
-  EDE on exoplanets.org. The $x$-axis is planet orbital period in days
-  and $y$-axis is planet mass in Earth's mass. The exoplanet samples
-  being plotted are the ones in the EOD, including transit planets
-  (blue large dots), RV planets (red triangles), and timing planets
-  (magenta squares). The KOIs are plotted as black small dots, and
-  their masses are calculated using their radii based on mass-radius
-  relations from the literature (see Section~\ref{sec:orbit}).}
+\includegraphics[width=\textwidth]{../fig/mass-per-interactive.eps}
+\caption{ZZZ will change to mass-SEP plot once KOIs have SEP ZZZ
+  An example plot produced by the interactive plotting tools of
+  EDE on exoplanets.org. The interactive plotting interface is shown
+  on the left, with the mass-period plot shown on the right. The
+  $x$-axis is planet orbital period in days and $y$-axis is planet
+  mass in Earth's mass. The exoplanet samples being plotted are the
+  ones in the EOD, including transit planets (blue large dots), RV
+  planets (red triangles), and timing planets (magenta squares). The
+  KOIs are plotted as black small dots, and their masses are
+  calculated using their radii based on mass-radius relations from the
+  literature (see Section~\ref{sec:orbit}).}
 \label{fig:koi}
 \end{figure}
+
+ZZZ add SE plots from Ming
 

### 2014-03-19 draft/ms.tex

--- 2014-03-19 draft/ms.tex
@@
 \begin{abstract}
-The Exoplanet Orbit Database (EOD) collects orbital and stellar parameters of all known exoplanets reported in the peer-reviewed literature.
-The EOD can be navigated through the Exoplanet Data Explorer (EDE) Plotter and Table, available at exoplanets.org.
-We have ZZZ number of confirmed exoplanets as of March 2014.
-Since \cite{Wright2011}, we made an effort to put robustly detected exoplanets together with over 3000 sample of exoplanet candidates (\kepler\ Objects of Interest, KOIs) and other planets (the ones detected by microlensing, imaging, timing) on exoplanets.org.
-We also added some new fields (e.g.
-the secondary eclipse depths), removed obsolete fields, and revised some fields as necessary.
+
+The Exoplanet Orbit Database (EOD) collects orbital and stellar
+parameters of all known exoplanets reported in the peer-reviewed
+literature. The EOD can be navigated through the Exoplanet Data
+Explorer (EDE) Plotter and Table, available at exoplanets.org. We have
+ZZZ number of confirmed exoplanets as of March 2014.  
+Since \cite{Wright2011}, we made an effort to put robustly detected
+exoplanets together with over 3000 sample of exoplanet candidates
+(\kepler\ Objects of Interest, KOIs) and other planets (the ones
+detected by microlensing, imaging, timing) on exoplanets.org. We also
+added some new fields (e.g. the secondary eclipse depths), removed
+obsolete fields, and revised some fields as necessary.
 
@@
 ZZZ Also mention the number of confirmed planets? and maybe the scope of the EOD (what are in our database)
+
+Make sure to mention: data are available at exoplanets.org; KOIs are
+ included.  ZZZ Also mention the number of confirmed planets? and
+ maybe the scope of the EOD (what are in our database)
 
@@
 \centering
-\includegraphics[width=\textwidth]{../fig/mass-per-color.eps}
-\caption{An example plot produced by the interactive plotting tools of
-  EDE on exoplanets.org. The $x$-axis is planet orbital period in days
-  and $y$-axis is planet mass in Earth's mass. The exoplanet samples
-  being plotted are the ones in the EOD, including transit planets
-  (blue large dots), RV planets (red triangles), and timing planets
-  (magenta squares). The KOIs are plotted as black small dots, and
-  their masses are calculated using their radii based on mass-radius
-  relations from the literature (see Section~\ref{sec:orbit}).}
+\includegraphics[width=\textwidth]{../fig/mass-per-interactive.eps}
+\caption{ZZZ will change to mass-SEP plot once KOIs have SEP ZZZ
+  An example plot produced by the interactive plotting tools of
+  EDE on exoplanets.org. The interactive plotting interface is shown
+  on the left, with the mass-period plot shown on the right. The
+  $x$-axis is planet orbital period in days and $y$-axis is planet
+  mass in Earth's mass. The exoplanet samples being plotted are the
+  ones in the EOD, including transit planets (blue large dots), RV
+  planets (red triangles), and timing planets (magenta squares). The
+  KOIs are plotted as black small dots, and their masses are
+  calculated using their radii based on mass-radius relations from the
+  literature (see Section~\ref{sec:orbit}).}
 \label{fig:koi}
 \end{figure}
-
-ZZZ orbital mass vs orbital distance
-
-ZZZ screen shots of what it looks like in the browser
 

### 2014-03-19 draft/ms.tex
abstract update 2

@@
 The Exoplanet Orbit Database (EOD) collects orbital and stellar
-parameters of all known exoplanets reported in the peer-reviewed
+parameters of all known robustly dected exoplanets reported in the peer-reviewed
 literature. The EOD can be navigated through the Exoplanet Data
@@
 ZZZ number of confirmed exoplanets as of March 2014.  
-Since \cite{Wright2011}, we made an effort to put robustly detected
-exoplanets together with over 3000 sample of exoplanet candidates
-(\kepler\ Objects of Interest, KOIs) and other planets (the ones
-detected by microlensing, imaging, timing) on exoplanets.org. We also
-added some new fields (e.g. the secondary eclipse depths), removed
-obsolete fields, and revised some fields as necessary.
+The first complete documentation for the EOD and the EDE was \cite{Wright2011} and since then, we have expanded the scope of the EOD and incorporated the sample of over 3000  \kepler\ Objects of Interest, (KOIs) and other planets (the ones detected by microlensing, imaging, and timing) on exoplanets.org.
+We also added some new fields (e.g.
+the secondary eclipse depths), removed obsolete fields, and revised some fields as necessary.
 

### 2014-03-20 draft/ms.tex
Paper done!

@@
 ZZZ number of confirmed exoplanets as of March 2014.  
-The first complete documentation for the EOD and the EDE was \cite{Wright2011} and since then, we have expanded the scope of the EOD and incorporated the sample of over 3000  \kepler\ Objects of Interest, (KOIs) and other planets (the ones detected by microlensing, imaging, and timing) on exoplanets.org.
-We also added some new fields (e.g.
+The first complete documentation for the EOD and the EDE was \cite{Wright2011} and since then, we have expanded the scope of the EOD.
+We also incorporated the sample of over 3000 \kepler\ Objects of Interest (KOIs) and other planets (the ones detected by microlensing, imaging, and timing) on exoplanets.org.
+We added some new fields (e.g.
 the secondary eclipse depths), removed obsolete fields, and revised some fields as necessary.
-
-What is the EOD?
-What does our  website do?
-What has been updated?
-Make sure to mention: data are available at exoplanets.org; KOIs are included.
-ZZZ Also mention the number of confirmed planets? and maybe the scope of the EOD (what are in our database)
-
-Make sure to mention: data are available at exoplanets.org; KOIs are
- included.  ZZZ Also mention the number of confirmed planets? and
- maybe the scope of the EOD (what are in our database)
+The website also has gone through some backend changes.
+The users can download the whole dataset as a single .csv file from the front page of exoplanets.org.
 
@@
 
-Onsi? Essential updates on the website.
+The software stack powering the EOD remains largely unchanged from \cite{Wright2011}.
+The backend server is now written in Ruby, instead of Python, but the thin role it plays is largely unchanged.
+The JavaScript frontend that runs on the browser has recently been optimized to support the larger datasets arising from the Kepler missions.
+In particular, the EOD table now only renders cells that are visible on-screen.
 
@@
 Second, we included KOIs and other planets (the ones detected by
-microlensing, imaging, timing, and in the future, astrometry) on
+microlensing, imaging, timing, and in the future, astrometry but do not have well characterized orbits) on
 exoplanets.org. Although they are not included in the EOD, we reported
@@
 purposes of statistical studies and comparison.
-
-ZZZ add summary for Onsi's section.
 

### 2014-03-20 draft/ms.tex
Proofread complete.

@@
 ZZZ number of confirmed exoplanets as of March 2014.  
-The first complete documentation for the EOD and the EDE was \cite{Wright2011} and since then, we have expanded the scope of the EOD.
-We also incorporated the sample of over 3000 \kepler\ Objects of Interest (KOIs) and other planets (the ones detected by microlensing, imaging, and timing) on exoplanets.org.
-We added some new fields (e.g.
-the secondary eclipse depths), removed obsolete fields, and revised some fields as necessary.
-The website also has gone through some backend changes.
-The users can download the whole dataset as a single .csv file from the front page of exoplanets.org.
+The first complete documentation for the EOD and the EDE was
+\cite{Wright2011} and since then, we have expanded the scope of the
+EOD. We also incorporated the sample of over 3000 \kepler\ Objects of
+Interest (KOIs) and other planets (the ones detected by microlensing,
+imaging, and timing) on exoplanets.org. We added some new fields
+(e.g. the secondary eclipse depths), removed obsolete fields, and
+revised some fields as necessary. The website also has gone through
+some backend changes. The users can download the whole dataset as a
+single .csv file from the front page of exoplanets.org.
 
@@
 
-Since \cite{Wright2011}, as more planets were robustly discovered by
-different methods other than radial velocity and transit, we have
-expanded our database at exoplanets.org to better ingest those
-planets.
+Since \cite{Wright2011}, as \kepler\ has discovered many exoplanet
+candidates, and more planets were robustly discovered by various
+methods though not having very well characterized orbits, we have
+expanded exoplanets.org to ingest those planets for the convenience of
+the users and also to keep our database complete in terms of confirmed
+exoplanets.
 
@@
 these KOIs are put into the context of all confirmed exoplanets. The
-KOIs listed in our table include three Kepler data releases (as of
+KOIs listed in our table include three \kepler\ data releases (as of
 March 2014), and we always keep up with the most up-to-date
-releases. The original data are from the NASA Exoplanet Archive.
+release. The original data are from the NASA Exoplanet Archive.
 
@@
 % Other Planets
-Second, we now also include
-robustly detected imaging, microlensing, and timing planets, and our
-criteria for a `robust detection' are the following (as set by the
-QUACBED):
+Second, we now also include robustly detected imaging, microlensing,
+and timing planets, and our criteria for a `robust detection' are the
+following (as set by the QUACBED):
 
@@
 \end{itemize}
-Some of the exoplanets primarily detected by these methods do not have
-well-determined orbital parameters, and thus they are categorized as
-``Other Planets'' on exoplanets.org instead of being in the EOD. These
-planets can be displayed by check the `Other' option for the EDE
-table. As of March 2014, no microlensing or imaging planets are in the
-EOD, while several timing exoplanets have well-determined orbital
-parameters and are included in the EOD. Moreover, there have been no
-astrometry planets in the EOD but we plan to include them if any
-robust detections occur.
+Some of the exoplanets that are primarily detected by these methods do
+not have well-determined orbital parameters, and thus they are
+categorized as ``Other Planets'' on exoplanets.org instead of being in
+the EOD. These planets can be displayed by check the `Other' option
+for the EDE table. As of March 2014, no microlensing or imaging
+planets are in the EOD, while several timing exoplanets have
+well-determined orbital parameters and are included in the
+EOD. Moreover, there have been no astrometry planets in the EOD but we
+plan to include them if any robust detections occur.
 
@@
 
-The software stack powering the EOD remains largely unchanged from \cite{Wright2011}.
-The backend server is now written in Ruby, instead of Python, but the thin role it plays is largely unchanged.
-The JavaScript frontend that runs on the browser has recently been optimized to support the larger datasets arising from the Kepler missions.
-In particular, the EOD table now only renders cells that are visible on-screen.
+The software stack powering the EOD remains largely unchanged from
+\cite{Wright2011}. The backend server is now written in Ruby, instead
+of Python, but the thin role it plays is largely unchanged.  The
+JavaScript frontend that runs on the browser has recently been
+optimized to support the larger datasets arising from the Kepler
+missions.  In particular, the EOD table now only renders cells that
+are visible on-screen.
 

### 2014-03-20 draft/ms.tex
Add note on mass cut criterion of EOD.

@@
 The rest of the selection criteria for the EOD remain unchanged. We
-still require the planets to be smaller than 24 \mjup\ and to have
-robust detections and well-determined orbits (though these are not
-strictly quantitative; see Section~2 of \citealt{Wright2011}). When
-new evidence comes to light and we are no longer confident about the
-planet, we remove it from EOD, even if the evidence is not peer
-reviewed.
+still require the planets to be smaller than (ZZZ change to mass
+ratio) 24 \mjup\ and to have robust detections and well-determined
+orbits (though these are not strictly quantitative; see Section~2 of
+\citealt{Wright2011}). When new evidence comes to light and we are no
+longer confident about the planet, we remove it from EOD, even if the
+evidence is not peer reviewed.
 

### 2014-03-21 draft/ms.tex
24 Jup mass criteria

@@
 
-The scope of the EOD has expanded, and there are two major changes
+The scope of the EOD has expanded, and there are three major changes
 from what was described in \cite{Wright2011}. Previously, we only
@@
 exoplanets that were discovered by the RV and transit methods in the
-EOD, but now we also have planets discovered via timing. For the
-future, exoplanets discovered by any other methods with robust
-detections and good orbital parameters will also be included in the
-EOD.
+EOD, but now we also have planets discovered via timing. For the future, exoplanets discovered by any other methods with robust detections and good orbital parameters will also be included in the
+EOD. Previously, we required the planets to be smaller than 24 \mjup\ but now we require the mass ratio to be smaller than 24 \mjup$/\msun$.
 
 The rest of the selection criteria for the EOD remain unchanged. We
-still require the planets to be smaller than (ZZZ change to mass
-ratio) 24 \mjup\ and to have robust detections and well-determined
+still require the planets to have robust detections and well-determined
 orbits (though these are not strictly quantitative; see Section~2 of

### 2014-03-21 draft/ms.tex
Modify mass ratio cut q<0.024 to q<0.023, ie. 24Mjup/Msun.

@@
 exoplanets that were discovered by the RV and transit methods in the
-EOD, but now we also have planets discovered via timing. For the future, exoplanets discovered by any other methods with robust detections and good orbital parameters will also be included in the
-EOD. Previously, we required the planets to be smaller than 24 \mjup\ but now we require the mass ratio to be smaller than 24 \mjup$/\msun$.
+EOD, but now we also have planets discovered via timing. For the
+future, exoplanets discovered by any other methods with robust
+detections and good orbital parameters will also be included in the
+EOD. Previously, we required the planets to be smaller than 24
+\mjup, but now we require the mass ratio to be smaller than 24
+\mjup$/\msun$ ($< 0.023)$.
 
@@
 \begin{enumerate}
-\item Planet-star mass ratio $q < 0.024$ ($< 24\ $\mjup\ for a solar
-  mass star); and in general we require ($q+\sigma_q$) $< 0.024$,
+\item Planet-star mass ratio $q < 0.023$ ($< 24\ $\mjup\ for a solar
+  mass star); and in general we require ($q+\sigma_q$) $< 0.023$,
   where $\sigma_q$ is the uncertainty in $q$.
@@
   having unambiguously planetary masses (planet host mass ratio,
-  $q<0.024$). In cases of ambiguity, we consult with QUACBED.
+  $q<0.023$). In cases of ambiguity, we consult with QUACBED.
 

### 2014-03-25 draft/ms.tex
Revision 1

@@
 \def\rearth{R_\oplus}
+\def\mearth{M_\oplus}
 
@@
 
-\title{The Exoplanet Orbit Database \textsc{II}: 2014 updates}
+\title{The Exoplanet Orbit Database \textsc{II}: updates for 2014}
 
@@
 \author{Ming Zhao\altaffilmark{1,2}}
-\author{Onsi Fakhouri}
 \author{and Friends}
@@
   Lab, The Pennsylvania State University, University Park, PA 16802, USA;
-  Send correspondence to datamaster@exoplanets.org.}
+  Send correspondence to jtwright@astro.psu.edu.}
 \altaffiltext{2}{Center for Exoplanets and Habitable Worlds, The
   Pennsylvania State University, University Park, PA 16802, USA}
-\altaffiltext{3}{Astrobiology Research Center, The
+\altaffiltext{3}{Penn State Astrobiology Research Center, The
   Pennsylvania State University, University Park, PA 16802, USA}
@@
 
-The Exoplanet Orbit Database (EOD) collects orbital and stellar
-parameters of all known robustly dected exoplanets reported in the peer-reviewed
+The Exoplanet Orbit Database (EOD) compiles orbital, transit, host star, and other
+parameters of robustly dected exoplanets reported in the peer-reviewed
 literature. The EOD can be navigated through the Exoplanet Data
-Explorer (EDE) Plotter and Table, available at exoplanets.org. We have
-ZZZ number of confirmed exoplanets as of March 2014.  
-The first complete documentation for the EOD and the EDE was
-\cite{Wright2011} and since then, we have expanded the scope of the
-EOD. We also incorporated the sample of over 3000 \kepler\ Objects of
-Interest (KOIs) and other planets (the ones detected by microlensing,
-imaging, and timing) on exoplanets.org. We added some new fields
-(e.g. the secondary eclipse depths), removed obsolete fields, and
-revised some fields as necessary. The website also has gone through
-some backend changes. The users can download the whole dataset as a
-single .csv file from the front page of exoplanets.org.
+Explorer (EDE) Plotter and Table, available on the world wide web at exoplanets.org. The EOD contains data for 1490 confirmed exoplanets as of March 2014.  
+The EOD drives from the Catalog of Nearby Exoplanets \citep{Butler2006}, and the first complete documentation for the EOD and the EDE was presented in 
+\cite{Wright2011}. Since then, we have expanded the scope of the
+EOD to include secondary eclipse parameters, asymmetric uncertainties and etc. The EOD also incorporats the sample of over 3000 \kepler\ Objects of
+Interest (KOIs) and other real planets without good orbital parameters such as those detected by microlensing and imaging. Users can download the latest version of the in tire EOD as a
+single comma separated value file from the front page of exoplanets.org.
 
@@
 number of confirmed exoplanets has increased from about 300 to over
-1490 as of March 2014 (exoplanets.org). \kepler\ contributed to a vast
+1490 as of March 2014. \kepler\ contributed to a vast
 majority of these new discoveries ($> 800$) while providing an
 additional sample of over 3000 exoplanet candidates (\kepler\ Objects
-of Interest, KOIs; e.g.~\citealt{Batalha2013}). The transit method has
-surpassed the radial velocity (RV) method and become the most fruitful
-mean for detecting exoplanets. Meanwhile, great promises lie within
+of Interest, KOIs; e.g.~\citealt{Batalha2013}). The transit method has thus surpassed the radial velocity (RV) method to become the most fruitful
+means of detecting exoplanets. Meanwhile, great promise lies within
 the new and future exoplanet surveys and instruments with direct
@@
 fronts of RV and transit exoplanet searches keep expanding (e.g., the
-MINiature Exoplanet RV Array, MINERVA, \citealt{Wright2014}; and the
+MINiature Exoplanet RV Array, MINERVA, \citealt{Wright2014}; Habitable-zone Planet Finder, HPF, \cite{Mahadevan2012} and the
 Transiting Exoplanet Survey Satellit, TESS, \citealt{Ricker2010}).
@@
 % The business of tracking planet discoveries and EOD
-This paper describes the continuing efforts since \cite{Butler2006}
-and \cite{Wright2011} to maintain the Exoplanet Orbit Database (EOD)
-and the Exoplanets Data Explorer (EDE) to keep track of the exoplanet
-discoveries and to catalog their orbital parameters and host star
-properties. There are also other entities devoted to this effort,
+This paper describes our continuing efforts since \cite{Butler2006}
+and \cite{Wright2011} to maintain the Exoplanet Orbit Database\footnote{See http://expoplanets.org}(EOD)
+and the Exoplanets Data Explorer (EDE), to keep track of the exoplanet
+discoveries, and to catalog their orbital parameters and host star
+properties. There are also other entities devoted to similar efforts,
 including the Extrasolar Planets Encyclopaedia\footnote{See
@@
 \citep{Akeson2013}. As described in \cite{Wright2011}, the EOD is
-dedicated to cataloging all \emph{robustly-detected} exoplanets with
+dedicated to cataloging properties of all \emph{robustly-detected} exoplanets with
 \emph{well-determined} orbital parameters published in
@@
 % data access and popularity
-The EOD is hosted by exoplanets.org, which also hosts the EDE, an
-interactive table with plotting tools including all the EOD exoplanets
-as well as other confirmed exoplanets (and now also KOIs). The entire
-dataset of exoplanets.org is available for download as a single {\tt
-  .csv} file at the website's front page.\footnote{At
-  \url{exoplanets.org/csv-files/exoplanets.csv}.} The EOD is widely
-used in exoplanet researches (e.g., \citealt{Dawson2013},
+The EOD is hosted at exoplanets.org, which also hosts the EDE, an
+interactive table with plotting tools for all the EOD exoplanets
+as well as confirmed exoplanets, without good orbital parameters and KOIs. The plottable
+dataset of exoplanets.org is available for download as a single comma separated value file from the Website front page.\footnote{At
+  \url{htt://exoplanets.org/csv-files/exoplanets.csv}.} The EOD is widely
+used in exoplanet research (e.g., \citealt{Dawson2013},
 \citealt{Howard2013}, \citealt{Kipping2013}, \citealt{Kane2014},
 \citealt{Weiss2014}), and the website exoplanets.org is among the most
-visited exoplanet databases, with over $47,000$ visitors in 2013
-according to Google Analytics.
+visited exoplanet databases, with over $47,000$ visits in 2013\footnote{Measured as "visits" by Google Analytics}.
 
 % updates on EOD and the website
-Since \cite{Wright2011}, the EOD has expanded its scope: we now do
+Since the documentation described in \cite{Wright2011}, the EOD has expanded its scope: we now do
 not require the host star of an exoplanet to be a normal star (e.g.,
-exoplanets around pulsars are now included). It has also ingested more
+exoplanets around pulsars are now included). It now ingestes more
 parameters describing the exoplanet systems and their host stars, and some
-parameters are revised or deleted. We describe the updates with the
+parameters have been revised or deleted. We describe our updates to the
 EOD in Section~\ref{sec:update}. The EDE at exoplanets.org has also
@@
 website exoplanets.org has gone through major back-end changes since
-\cite{Wright2011}, which is described in Section~\ref{sec:website}. We
+\cite{Wright2011}, which are described in Section~\ref{sec:website}. We
 summarize the updates and possible future improvements in
@@
 limiting the type of host stars (e.g. we included exoplanets orbiting
-neutron stars). Furthermore, in \cite{Wright2011}, we only had
+neutron stars). Furthermore, in \cite{Wright2011}, we only included
 exoplanets that were discovered by the RV and transit methods in the
-EOD, but now we also have planets discovered via timing. For the
+EOD, but now we also included planets discovered via timing including pulsar planets and those discovered by eclipse timing. In the
 future, exoplanets discovered by any other methods with robust
 detections and good orbital parameters will also be included in the
-EOD. Previously, we required the planets to be smaller than 24
-\mjup, but now we require the mass ratio to be smaller than 24
+EOD including astrometric planets such as beta Pic b.
+Previously, we required the planets have minimum mass (m$\sin{i}$) smaller than 24\mjup, but now we require the measured mass ratio to be smaller than 24
 \mjup$/\msun$ ($< 0.023)$.
@@
 still require the planets to have robust detections and well-determined
-orbits (though these are not strictly quantitative; see Section~2 of
-\citealt{Wright2011}). When new evidence comes to light and we are no
-longer confident about the planet, we remove it from EOD, even if the
-evidence is not peer reviewed.
+orbits (though these are not strictly quantitative and sometimes subjective; see Section~2 of
+\citealt{Wright2011}). If new evidence comes to light and we are no
+longer confident about the planet, we may remove it from EOD, even if the new evidence is not peer reviewed.
 
@@
 report \textit{all} the announced exoplanets as we are not trying to
-do ``an encyclopedic presentation of every claimed detection of an
+provide ``an encyclopedic presentation of every claimed detection of an
 exoplanet" \citep{Wright2011}.
@@
 In the following subsections, we describe the newly added and revised
-fields since \cite{Wright2011}, but list all fields in
-Table~\ref{tab:par}. We divide the fields into categories in
-consistency with the individual planet page on
-exoplanets.org. Figure~\ref{fig:individual} is an example of
-individual planet page. Some fields are not explicitly tabulated on
-the page (e.g., the URLs), but are explicitly listed in the
+fields since \cite{Wright2011}, and list all fields in
+Table~\ref{tab:par}. We divide the fields into categories consistent with the individual planet page on
+exoplanets.org. (Figure~\ref{fig:individual} is an example of
+individual planet page, which is presented to website users who click on a planet's name). Some fields are not explicitly tabulated on
+the page (e.g., the URLs for ADS pages for papers providing the underlying data), but are explicitly listed in the
 downloadable {\tt .csv} file (see Section~\ref{sec:intro}). Though we
@@
 We report general information of when, by whom and how the planets
-were discovered and provide the references. We describe the added or
+were discovered and first reported and provide the references for underlying data. We describe the added or
 revised fields since \cite{Wright2011} below.
@@
 planet, wihle STARDISCMETH reports the discovery method for the first
-discovered planet around the host star. Furthermore, they are stored
-in string formats and have values of one of the following: RV,
-Transit, Imaging, Microlensing, Timing, or Astrometry.
+discovered planet around the host star. These fields are stored
+in string format and have one of the following values: "RV",
+"Transit", "Imaging", "Microlensing", "Timing", or "Astrometry" (no planets have "astrometry" yet).
 
-{\bf MONTH} field reports the month in integer of when the
-peer-reviewed paper is accepted by the journal.
+The {\bf MONTH} field reports the integer month of the
+peer-reviewed paper publication date.
 
 {\bf KEPID} stands for KEPler ID, which is the integer number assigned
-for a Kepler host star. KEPID is only available for the unconfirmed
-KOI which we import directly from the Exoplanet Archive. Therefore,
-none of the EOD planets and the confirmed Kepler planets has KEPID.
+for a Kepler host star. KEPID is only available for unconfirmed
+KOI's imported directly from the Exoplanet Archive by the exoplanet.org backend. Therefore,
+none of the EOD planets including confirmed Kepler planets has a KEPID, yet.
 
 {\bf KOI} stands for Kepler Objects of Interest, which is an object
-with transit signals detected by \kepler\ but have not been confirmed
-to be due to exoplanets. The KOI field contains a floating point
-number that consist of a whole number designated to the host star
+with transit signals detected by \kepler\ but have not been validated to be due to exoplanets. The KOI field defined by the \kepler\ team and showed on the Exoplanet Archive, contains a floating point
+number that consists of a whole number designated to the host star
 followed by a decimal number denoting a candidate planet. For example,
@@
 and an lower case letter). The KOI number is then used as
-OTHERNAME. None of the KOIs are in the EOD. For more information, see
+OTHERNAME. For more information, see
 Section~\ref{sec:kepler}.
 
-{\bf EOD} is a flag which indicates whether an exoplanet is included
-in the EOD for having robust detection and well-characterized orbital
-parameters such as the orbital period (PER). EOD equals 1 means the
-exoplanet is in the EOD. We added this field because exoplanets.org
+{\bf EOD} is a boolean which indicates whether an exoplanet is included
+in the EOD for having well-characterized orbital
+parameters, such as the orbital period (PER). We added this field because exoplanets.org
 now also includes robustly discovered planets that do not have
@@
 {\bf MICROLENSING, IMAGING, TIMING and ASTROMETRY} are flags which
-indicate that a planet detected via theses methods. For example,
+indicate that a planet detected via theses method. For example,
 MICROLENSING $=$ 1 means the planet is detected in a microlensing
-event. However, we require the detection to be robust, as determined
-by the QUAlity Control Board of the Exoplanet Database, QUACBED (see
-Section~\ref{sec:kepler}).
+event. Note that planets may be detected with multiple methods.
 
 %------------------------------------------------------------------------------
-\subsection{Orbital Parameters}\label{sec:orbit}
+\subsection{Orbital Parameters (e.g. RV and Transit)}\label{sec:orbit}
 
@@
 planet's orbit. Depending on the detection methods, different sets of
-parameters are given by the literatures. For instance, if a planet is
+parameters are given by the literature. For instance, if a planet is
 detected by the radial velocity method, the semiamplitude, $K$, is
-reported whereas the inclination of the orbit, $i$, is reported by the
-transit method. We describe the added fields since \cite{Wright2011}
+reported, whereas the inclination of the orbit, $i$, is usually only known via the
+transit method (although planet-planet interactions and astrometry can also determine it). We describe the added fields since \cite{Wright2011}
 below.
@@
 the mass from the minimum mass $m\sin{i}$ and the orbital inclination
-$i$. MASS is set to MSINI if the orbital inclination is not given and
+$i$. For convenience of plotting RV and other planets on a common mass scale (see Section~\ref{sec:kepler}, MASS is set to MSINI if the orbital inclination is not known and
 the reference for MASS, MASSREF is set to ``Set to MSINI; I unknown''.
 
-For KOIs without MSINI measured, we calculate their mass using the
-mass-radius relation from the literatures. For KOIs with $R<4\rearth$,
-we follow \cite{Weiss2014}; for $4\rearth<R<6\rearth$, we follow
-\cite{Lissauer2011}; and for $6\rearth<R<11.7\rearth$ we follow
-\cite{Mordasini2012}.
+Also for plotting convenience, for KOIs without $m\sin{i}$ measured, we estimate their mass using the
+mass-radius relation from the literature. For KOIs with $R<4\rearth$, we follow $M_{p}/\mearth=2.69(R_{p}/\rearth)$
+from \cite{Weiss2014}; for $4\rearth<R<6\rearth$, we follow $M_{p}/\mearth=(R_{p}/\rearth)^2.06$ from
+\cite{Lissauer2011}; and for $6\rearth<R<11.7\rearth$ we follow $M_{p}/\mearth=1756.7*10^{(-1.646*(11.684/(R_{p}/\rearth)-1)^{(1/2.489)})}$
+from \cite{Mordasini2012}.
 
-{\bf SEP} is the projected separation on the sky between the host star
-and the planet in the unit of AU. For directly imaged planets, the
-literatures usually report the projected separation and we report the
+{\bf SEP} is a separation between the host star
+and the planet in units of AU. For directly imaged planets, the
+literature usually reports the projected separation and we report the
 value accordingly.  If SEP is not directly measured but the semi-major
-axis ($a$, A) is available, then SEP is set to A with its reference,
+axis ($a$, A) is available, then we set SEP to A with its reference,
 SEPREF, set to ``Set to A''.
@@
 have I's reported too. For example, one microlensing system,
-OGLE-2006-BLG-109L, has I measured \citep{Bennett2010}.
+OGLE-2006-BLG-109L, has I measured \citep{Bennett2010}. Also, one imaging system, $\beta$ Pic, has I measured \citep{Lagrange2009}
 
-{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in the
-unit of degree. At the moment, this is only measured for some of the
-directly imaged planets, which are not in the EOD.
+{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in units of degrees. At the moment, no planets have this quantity measured, but astrometric orbits (e.g. from GPI) will .
 
 {\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
-the plane of the sky in the unit of degree. At the moment, $\lambda$
+the plane of the sky in units of degrees. At the moment, $\lambda$
 values are only available for the transiting systems, which are
@@
 \citep[e.g.,][]{Winn2005} or planet transiting star spots
-\citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is introduced because
-the true spin-orbit angle ($\phi$), defined as the angle between the
+\citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is used because
+the true spin-orbit angle, defined as the angle between the
 stellar spin axis and the orbital axis, is normally not directly
-measurable. We follow the definition of $\lambda$ in
-\cite{Fabrycky2009} where the coordinates are defined as follows: the
+measurable. We follow \cite{Fabrycky2009} where the coordinates are defined as follows: the
 $z$-axis points toward the observer, the $x$-axis points along the
@@
 the $y$-axis to the projected stellar rotational axis. $\lambda$ is
-not a newly added field but we describe it here because it was not
-reported consistently since some literatures report the ``projected
-spin-orbit misalignment" as $\beta = -\lambda$ instead. We have sorted
+not a newly added field to the EOD but we describe it here because we did not
+previously report it consistently, since some literature report the ``projected
+spin-orbit misalignment" as $\beta = -\lambda$ instead\footnote{e.g. \cite{Moutou2011}, }. We have sorted
 these cases out and made sure that our $\lambda$'s are following the
@@
 We report the transit parameters, which are available only when the
-planet has TRANSIT flag equal to 1. We describe added fields since
-\cite{Wright2011} below.
+planet has TRANSIT Boolean equal to true. We describe two added fields since
+\cite{Wright2011} below, which are used for KOI's incorporated from the Exoplanet Archive.
 
@@
 radius. If the transit depth (DEPTH) is not given, we calculate DEPTH
-by taking square of RR but we do not calculate RR from DEPTH.
+by taking square of RR, but we do not calculate RR from DEPTH.
 
@@
 
-We have added an entirely new set of fields for the secondary
-eclipse. Previously, due to the limits of instrumentation and limited
-sample of exoplanets, there were not much secondary eclipse depth data
+We have added an entirely new set of fields for secondary
+eclipse depths. Previously, due to the limits of instrumentation and limited
+sample of exoplanets, there was not much secondary eclipse depth data
 available. Since \cite{Wright2011}, as many different surveys have
 been launched, more and more secondary eclipse depths at multiple
-bands become available for more and more planets. Therefore, we added
+bands have become available for more and more planets. Therefore, we added
 this entire new set of fields. ZZZ Refer to Ming's SE plot.
 
-{\bf SE} flag indicates whether the system has detected secondary
+The {\bf SE} Boolean indicates whether the system has detected secondary
 eclipse in any of the two Micron All-Sky Survey (2MASS;
 \citealt{Skrutskie2006}) $J$, $H$, and $K_s$, Kepler photometry band,
-and 4 Spitzer IRAC bands. SE is a boolean and SE $=$ 1 indicates the
-system has at least one detected secondary eclipse.
+and 4 Spitzer IRAC bands. Truth indicates the
+system has at least one secondary eclipse measurement in the EOD.
 
-{\bf SEDEPTHX} whereas X stands for one of J H KS KP 36 45 58 80:
+{\bf SEDEPTHX} whereas X stands for one of ``J", ``H", ``KS", ``KP", ``36", ``45", ``58", ``80":
 these fields are the secondary eclipse depth measured in the
 corresponding wavelength band. SEDEPTHJ, H, and KS are the depths
-measured in the 2MASS wavelength band in near infrared each centered
+measured in the 2MASS wavelength bands in the near infrared, centered
 at 1.25~\micron, 1.65~\micron, and 2.15~\micron, respectively. KP is
-the depth measured in the \kepler\ photometry band which ranges from
-400 to 865~nm. The rest four stand for the Spitzer bands centered at
+the depth measured in the \kepler\ photometric band which spans 400 to 865~nm. The other four represent the Spitzer IRAC and MIPS bands centered at
 3.6~\micron, 4.5~\micron, 5.8~\micron, and 8.0~\micron.
 
-{\bf SET} is the epoch of secondary eclipse center (normally in HJD).
+{\bf SET} is the epoch of secondary eclipse center, normally given in HJD but (as with other fields) when the literature reports HJD or UTC JD, we do not attempt a conversion to BJD.
 
@@
 
-This set of parameters is to provide users the physical parameters of
+This set of parameters provides users the physical parameters of
 the exoplanet host stars.  Most of the parameters are derived from the
-stellar models in the literatures and we provide the readers with the
+stellar models in the literature and we provide the readers with the
 references. We describe added fields since \cite{Wright2011} below.
@@
 {\bf GAMMA} ($\gamma$) is the radial velocity of the center of mass of
-the planetary system and is reported in km/s.
+the planetary system with respect to the barycentric frame and is reported in km/s.
 
-{\bf RSTAR} is the radius of the star in the solar radius.
+{\bf RSTAR} is the radius of the star in the solar units.
 
-{\bf RHOSTAR} is the density of the star in the unit of g/cm$^3$.
+{\bf RHOSTAR} is the density of the star in g/cm$^3$.
 
@@
 We provide the brightness of the host star measured in different
-wavelengths. We report optical magnitude and color ($V$ and $B-V$),
-2MASS $J$, $H$, and $K_s$ magnitudes and we added {\bf KP} since
-\cite{Wright2011}, which is the stellar magnitude measured through the
-\kepler\ bandpass.
+filters. We report optical magnitude and color ($V$ and $B-V$),
+2MASS $J$, $H$, and $K_s$ magnitudes and, we have added {\bf KP}. Notes that the definitions of V and B in the literature vary, and are often Hipparcos values
+(the stellar magnitude measured through the \kepler\ bandpass).
 
@@
 We report the coordinates of the host star as well as the host star's
-ID as designated by different catalogs.  We added {\bf DIST} since
+ID as designated by different catalogs.  We added the {\bf DIST} field since
 \cite{Wright2011}, which is the distance to the host star in the unit
@@
 and vice versa. If the literature does not report DIST or PAR, then we
-obtain PAR from the Hipparcos dataset by \cite{van Leeuwen2009}. We
+obtain PAR from the Hipparcos dataset by \cite{van Leeuwen2009} for stars with Hipparcos numbers. We
 naively propagate the error in PAR to DIST and vice versa.
@@
 We have changed the way of reporting uncertainties, especially
-asymmetric error bars since \cite{Wright2011}. We now report
+asymmetric ones since \cite{Wright2011}. We now report
 uncertainties for a certain field X as XUPPER, XLOWER and UX. XUPPER
@@
 are different when the error bars are asymmetric. UX contains the
-1$\sigma$ uncertainty, and it equals to $({\rm XUPPER+XLOWER})/2$ in
+1$\sigma$ uncertainty, and it equals $({\rm XUPPER+XLOWER})/2$ in
 the case of asymmetric error bars. Fields that have XUPPER, XLOWER and
-UX are: all the orbital parameters except for TREND and FREEZE\_ECC
-flags; all the transit parameters except for TRANSIT flags; all the
-secondary eclipse fields except for SE flag; and all the stellar
-properties except for STAR, SPECREF and BINARY flag; and DIST and PAR.
+UX are: all the orbital parameters, all the transit parameters, all the
+secondary eclipse fields, and all the stellar
+properties and DIST and PAR.
 
@@
 eccentricity (ECC), and the radial velocity semi-amplitude (K) when
-the literatures report them. For example, the upper limits for ECC is
+the literature reports them. For example, the upper limits for ECC is
 reported when the orbit is consistent with a circular one, and the
@@
 way (e.g. 1$\sigma$ or some fixed percentile), we encourage the
-readers to refer to the original references for more information.
+readers to refer to the original references for more information. Note that as of this writing, limits have not been incorporated into the EDE (see Section~\ref{sec:}
 
@@
 The fields {\bf XREF} and {\bf XURL} store the peer-reviewed reference
-and link to the publication for the field X. Previously, we only
+and link to the publication for the data in field X. Previously, we only
 reported general references for certain sets of fields (e.g. FIRSTREF,
@@
 
-The following fields do not have associated REF or URL fields, and we
-list their references here: RA, DEC, and PAR are from the
-\textit{Hipparcos} by \cite{van Leeuwen2009}; the $B-V$ (BMV) values
+The following fields do not have associated REF or URL fields.
+Except where we record these values directly from discovery papers, RA, DEC, and PAR are usually from the \textit{Hipparcos} re-reduction of \cite{van Leeuwen2009}; the $B-V$ (BMV) values
 are from the \textit{Hipparcos} catalog by \cite{Perryman1997};
 stellar magnitudes J H and KS are from the 2MASS
-\citep{Skrutskie2006}; the KP magnitudes are from the Exoplanet
+\citep{Skrutskie2006} (as reduced from SIMBAD) and the KP magnitudes are from the Exoplanet
 Archive \citep{Akeson2013}.
 
-SHK and RHK are poorly maintained fields, and they unreferenced at the
+SHK and RHK are poorly maintained fields representing chromospheric emission measures and they unreferenced at the
 moment. We plan to include proper reference in the future. Most of the
-SHK and RHK values are from \cite{Butler2006}.
+SHK and RHK values are from \cite{Butler2006}, and individual discovery papers.
 
@@
 {\bf SPSTAR} field previously reported the stellar type of the host
-star, but it is removed since it is not reliable.
+star, but it is removed since it is not well maintained.
 
@@
   reference on NASA ADS. In this example for WASP-14b, we provide the plot
-  for the phased RVs, but we are yet to implement such feature for all
+  for the phased RVs, but we have yet to implement such feature for all
   planets with available RV data.}
@@
 
-Since \cite{Wright2011}, as \kepler\ has discovered many exoplanet
+Since \cite{Wright2011}, \kepler\ has discovered many exoplanet
 candidates, and more planets were robustly discovered by various
 methods though not having very well characterized orbits, we have
-expanded exoplanets.org to ingest those planets for the convenience of
+expanded the EDE to include those planets for the convenience of
 the users and also to keep our database complete in terms of confirmed
@@
 % KOIs
-First, we now include the KOIs discovered by \kepler\ in the
+We have used broad definitions for SEP and MASS for this purpose. First, we now include the KOIs discovered by \kepler\ in the
 EDE. Although KOIs are not counted as part of the EOD due to their
@@
 
-To display the KOIs in the EDE table, check the ``Kepler" option on
-the upper left of the table (default selection only includes ``Orbit
+To display the KOIs in the EDE table, users can check the ``Kepler" option on
+the upper left of the table (the default selection only includes ``Orbit
 Database", i.e.~the EOD, and ``Other"). They can also be displayed on
@@
   spurious.
-\item Confidently bound: in opinion of the QUACBED the object will not
+\item Confidently bound: object will clearly not
   be later found to be unbound or a chance alignment.
@@
   having unambiguously planetary masses (planet host mass ratio,
-  $q<0.023$). In cases of ambiguity, we consult with QUACBED.
+  $q<0.023$).
 
@@
 well-determined orbital parameters and are included in the
-EOD. Moreover, there have been no astrometry planets in the EOD but we
+EOD. Moreover, there have been no astrometric planets in the EOD but we
 plan to include them if any robust detections occur.
@@
   EDE on exoplanets.org. The interactive plotting interface is shown
-  on the left, with the mass-period plot shown on the right. The
+  on the right, with the mass-period plot shown on the left. The
   $x$-axis is planet orbital period in days and $y$-axis is planet
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Updates on the Website}\label{sec:website}
+\section{Updates to the Website software}\label{sec:website}
 
@@
 are visible on-screen. 
+\begin{enumerate}
+\item Plot parameters may be saved with browser cookies, so plots may be custom reproduced easily with updated data later.
+\item Tables may be generated and exported with custom fields computed.
+\item Plots may be exported with a variety of resolutions and aspects, including publication-quality vector graphics (SVG format). 
+\end{enumerate}
 
@@
 the secondary eclipse depths. We removed obsolete fields and revised
-some fields as necessary.
+some fields as necessary. We have included SEP and MASS with broad definitions so all planets may be plotted on common axes.
 
@@
 In the future, we hope to include images of directly imaged planets
-(where allowed under copyright law) and light curves for transits. We
-also plan to display RV curves whenever their RV data are available.
+(where allowed under copyright law) and light curves for transits and microlensing planets. We
+also plan to display RV curves whenever their RV data are available and include better incorporation of Kepler parameters in the EOD (such as KEPID).
+We also want upper limits in the EDE table and plotter.
 

### 2014-03-25 draft/references.tex
Revision 1

@@
 
+\bibitem[Lagrange et al.(2009)]{Lagrange2009} Lagrange, A.-M., Gratadour, D., Chauvin, G., et al.\ 2009, \aap, 493, L21 %beta Pic b, imaging planet with I measured
+
 \bibitem[Lissauer et al.(2011)]{Lissauer2011} Lissauer, J.~J., et al.\ 
@@
 
+\bibitem[Mahadevan et al.(2012)]{Mahadevan2012} Mahadevan, S., 
+Ramsey, L., Bender, C., et al.\ 2012, \procspie, 8446, %HPF
+
 \bibitem[Mordasini et al.(2012)]{Mordasini2012} Mordasini, C., Alibert, Y., 
@@
 % Mass-Radius for 6 Re < R < 11.684 Re
+
+\bibitem[Moutou et al.(2011)]{Moutou2011} Moutou, C., D{\'{\i}}az, R.~F., Udry, S., et al.\ 2011, \aap, 533, A113  %Lambda example
 

### 2014-03-26 draft/ms.tex
Revision 2

@@
 
-{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in units of degrees. At the moment, no planets have this quantity measured, but astrometric orbits (e.g. from GPI) will .
+{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in units of degrees. At the moment, no planets have this quantity measured, but astrometric orbits (e.g. from GPI) will reveal it.
 
@@
 previously report it consistently, since some literature report the ``projected
-spin-orbit misalignment" as $\beta = -\lambda$ instead\footnote{e.g. \cite{Moutou2011}, }. We have sorted
+spin-orbit misalignment" as $\beta = -\lambda$ instead\footnote{In some cases, e.g. \cite{Moutou2011}, other conventions entirely appear to be used.}. We have sorted
 these cases out and made sure that our $\lambda$'s are following the
@@
 way (e.g. 1$\sigma$ or some fixed percentile), we encourage the
-readers to refer to the original references for more information. Note that as of this writing, limits have not been incorporated into the EDE (see Section~\ref{sec:}
+readers to refer to the original references for more information. Note that as of this writing, limits have not been incorporated into the EDE (see Section~\ref{sec:website}
 
@@
 and timing planets, and our criteria for a `robust detection' are the
-following (as set by the QUACBED):
+following:
 
@@
 
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=\textwidth]{../fig/senew.eps}
+\caption{An example plot that demonstrates the current secondary eclipse measurements.
+Each planet has a set of circles that stand for its available secondary eclipse measurements in the database, including Spitzer 8.0, 5.8, 4.5, \& 3.6 $\mu m$, and  ground-based $J$, $H$, and $Ks$ bands.
+\kepler\ secondary eclipse measurements are labeled as solid black dots.
+A few representative planets are also annotated.}
+\label{fig:se}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In the future, we hope to include images of directly imaged planets
-(where allowed under copyright law) and light curves for transits and microlensing planets. We
-also plan to display RV curves whenever their RV data are available and include better incorporation of Kepler parameters in the EOD (such as KEPID).
-We also want upper limits in the EDE table and plotter.
+(where allowed under copyright law) and light curves for transits and microlensing planets.
+We plan to display RV curves whenever their RV data are available and include better incorporation of Kepler parameters in the EOD (such as KEPID).
+We also hope to include upper limits in the EDE table and plotter.
 
@@
 
-NSF funding?
+NSF funding? ZZZ will be added by Jason
 
@@
 NASA's Astrophysics Data System Bibliographic Services (ADS).
+
+CEHW, SIMBAD, EA, and JS acknowledgement
 

### 2014-07-22 draft/ms.tex
Including secondary plot
Jason's revision of the draft with first round of comments incorporated.

@@
 \def\mjup{$M_{\rm Jup}$}
+\def\rjup{$R_{\rm Jup}$}
 \def\rearth{R_\oplus}
@@
 
-\title{The Exoplanet Orbit Database \textsc{II}: updates for 2014}
+\title{The Exoplanet Orbit Database \textsc{II}: Updates to
+  exoplanets.org}
 
@@
 \author{Eunkyu Han\altaffilmark{1,2}}
-\author{Sharon X. Wang\altaffilmark{1,2,3}}
-\author{Jason T. Wright\altaffilmark{1,2,3}}
-\author{Ying Feng\altaffilmark{1,2}}
+\author{Sharon X.\ Wang\altaffilmark{1,2,3}}
+\author{Jason T.\ Wright\altaffilmark{1,2,3}}
+\author{Y.\ Katherina Feng\altaffilmark{1,2}}
 \author{Ming Zhao\altaffilmark{1,2}}
-\author{and Friends}
+\author{Onsi Fakhouri\altaffilmark{4}}
+\author{Jacob I.\ Brown\altaffilmark{1,2}}
+\author{Colin Hancock\altaffilmark{1,2}}
 
@@
   Pennsylvania State University, University Park, PA 16802, USA} 
+\altaffiltext{4}{Pivotal Labs, Cloud Foundry, 875 Howard St., Fourth
+  Floor, San Francisco, CA 94103}
 
@@
 The Exoplanet Orbit Database (EOD) compiles orbital, transit, host star, and other
-parameters of robustly dected exoplanets reported in the peer-reviewed
+parameters of robustly detected exoplanets reported in the peer-reviewed
 literature. The EOD can be navigated through the Exoplanet Data
-Explorer (EDE) Plotter and Table, available on the world wide web at exoplanets.org. The EOD contains data for 1490 confirmed exoplanets as of March 2014.  
-The EOD drives from the Catalog of Nearby Exoplanets \citep{Butler2006}, and the first complete documentation for the EOD and the EDE was presented in 
-\cite{Wright2011}. Since then, we have expanded the scope of the
-EOD to include secondary eclipse parameters, asymmetric uncertainties and etc. The EOD also incorporats the sample of over 3000 \kepler\ Objects of
-Interest (KOIs) and other real planets without good orbital parameters such as those detected by microlensing and imaging. Users can download the latest version of the in tire EOD as a
-single comma separated value file from the front page of exoplanets.org.
+Explorer (EDE) Plotter and Table, available on the World Wide Web at exoplanets.org. The EOD contains data for 1490 confirmed exoplanets as of March 2014.  
+The EOD descends from a table in \citet{Butler2002} and the Catalog of Nearby Exoplanets \citep{Butler2006}, and the first complete documentation for the EOD and the EDE was presented in 
+\cite{Wright2011}. In this work, we describe our work since then.  We have expanded the scope of the
+EOD to include secondary eclipse parameters, asymmetric uncertainties,
+and expanded the EDE to include
+the sample of over 3000 \kepler\ Objects of Interest (KOIs), and other
+real planets without good orbital parameters (such as many of those
+those detected by microlensing and imaging.) Users can download the
+latest version of the entire EOD as a single comma separated value
+file from the front page of exoplanets.org.
 
@@
 number of confirmed exoplanets has increased from about 300 to over
-1490 as of March 2014. \kepler\ contributed to a vast
-majority of these new discoveries ($> 800$) while providing an
-additional sample of over 3000 exoplanet candidates (\kepler\ Objects
+1490 as of March 2014. \kepler\ contributed to a majority of these new discoveries ($> 800$) while providing an
+additional sample of over 4,000 exoplanet candidates (\kepler\ Objects
 of Interest, KOIs; e.g.~\citealt{Batalha2013}). The transit method has thus surpassed the radial velocity (RV) method to become the most fruitful
@@
 fronts of RV and transit exoplanet searches keep expanding (e.g., the
-MINiature Exoplanet RV Array, MINERVA, \citealt{Wright2014}; Habitable-zone Planet Finder, HPF, \cite{Mahadevan2012} and the
-Transiting Exoplanet Survey Satellit, TESS, \citealt{Ricker2010}).
+MINiature Exoplanet Radial Velocity Array, MINERVA,
+\citep{Wright2014}; the Habitable-zone Planet Finder, HPF, \cite{Mahadevan2012} and the
+Transiting Exoplanet Survey Satellit, TESS, \citealt{Ricker2014}).
 
@@
 This paper describes our continuing efforts since \cite{Butler2006}
-and \cite{Wright2011} to maintain the Exoplanet Orbit Database\footnote{See http://expoplanets.org}(EOD)
-and the Exoplanets Data Explorer (EDE), to keep track of the exoplanet
-discoveries, and to catalog their orbital parameters and host star
-properties. There are also other entities devoted to similar efforts,
+and \cite{Wright2011} to maintain the Exoplanet Orbit Database\footnote{See \url{http://expoplanets.org}}(EOD)
+and the Exoplanets Data Explorer (EDE), to keep track of exoplanet
+discoveries, and to better catalog orbital parameters and host star
+properties.
+
+There are other entities devoted to similar efforts,
 including the Extrasolar Planets Encyclopaedia\footnote{See
@@
   \url{http://exoplanetarchive.ipac.caltech.edu}.}
-\citep{Akeson2013}. As described in \cite{Wright2011}, the EOD is
+\citep{Akeson2013}.  The natures of these efforts are complementary, and to the
+degree that they are redundant provide important cross-checking and
+validation.  As described in \cite{Wright2011}, the EOD is
 dedicated to cataloging properties of all \emph{robustly-detected} exoplanets with
 \emph{well-determined} orbital parameters published in
-\emph{peer-reviewed} literature.
+\emph{peer-reviewed} literature, and providing outstanding data
+exploration and visualization tools for these planets.
 
 % data access and popularity
-The EOD is hosted at exoplanets.org, which also hosts the EDE, an
-interactive table with plotting tools for all the EOD exoplanets
-as well as confirmed exoplanets, without good orbital parameters and KOIs. The plottable
-dataset of exoplanets.org is available for download as a single comma separated value file from the Website front page.\footnote{At
-  \url{htt://exoplanets.org/csv-files/exoplanets.csv}.} The EOD is widely
+The EOD is hosted at the Web domain exoplanets.org, which also hosts the EDE, an
+interactive table with plotting tools for all the EOD exoplanets, in
+addition to other confirmed exoplanets without good orbital
+parameters, and KOIs (except for those with a ``FALSE POSITIVE''
+disposition at the Exoplanet Archive). The entire dataset of exoplanets.org is available for download as a single comma separated value file from the Website front page.\footnote{At
+  \url{http://exoplanets.org/csv-files/exoplanets.csv}.}  An example
+of this CSV file is available with the electronic version of this paper.
+
+The EOD is widely
 used in exoplanet research (e.g., \citealt{Dawson2013},
 \citealt{Howard2013}, \citealt{Kipping2013}, \citealt{Kane2014},
-\citealt{Weiss2014}), and the website exoplanets.org is among the most
-visited exoplanet databases, with over $47,000$ visits in 2013\footnote{Measured as "visits" by Google Analytics}.
+\citealt{Weiss2014}), and the website exoplanets.org had over $47,000$ visits in
+2013\footnote{Measured as ``visits" by Google Analytics}.
 
@@
 not require the host star of an exoplanet to be a normal star (e.g.,
-exoplanets around pulsars are now included). It now ingestes more
+exoplanets around pulsars are now included). We now ingest more
 parameters describing the exoplanet systems and their host stars, and some
@@
 exoplanets that were discovered by the RV and transit methods in the
-EOD, but now we also included planets discovered via timing including pulsar planets and those discovered by eclipse timing. In the
-future, exoplanets discovered by any other methods with robust
-detections and good orbital parameters will also be included in the
-EOD including astrometric planets such as beta Pic b.
-Previously, we required the planets have minimum mass (m$\sin{i}$) smaller than 24\mjup, but now we require the measured mass ratio to be smaller than 24
-\mjup$/\msun$ ($< 0.023)$.
+EOD, but now we also include planets discovered via timing (including
+pulsar planets and those discovered by eclipse timing). We now include
+exoplanets discovered by any other methods with robust detections and
+good orbital parameters, such as $\beta$ Pictoris $b$ \citep{Chauvin2012,Nielsen2014,Macintosh2014}.
+
+Previously, we used a generous mass cutoff, recognizing that any
+definition of ``exoplanet'' will not necessarily track with the
+formation mechanism for an object (which may, after all, be unknown or
+unknowable).  Our previous mass cutoff was a minimum mass (m$\sin{i}$)
+smaller than 24\mjup; to make this cutoff more relevant to a wide
+range of stellar masses and detection methods, we now require the measured
+planet-star mass ratio to be smaller than 24 \mjup$/\msun$ ($< 0.023)$.
 
@@
 \citealt{Wright2011}). If new evidence comes to light and we are no
-longer confident about the planet, we may remove it from EOD, even if the new evidence is not peer reviewed.
-
-The purpose of the EOD has not changed: we aim to provide the readers
-with a comprehensive, reliable, and up-to-date database of exoplanets
-with good orbital parameters and host star properties. We do not
-report \textit{all} the announced exoplanets as we are not trying to
-provide ``an encyclopedic presentation of every claimed detection of an
-exoplanet" \citep{Wright2011}.
+longer confident about a planet, we may remove it from EOD, even if the
+new evidence is not peer reviewed.  The rationale for this scheme is,
+as it has been since the CNE, that the EOD represents our best, expert effort to produce a clean set of
+trustworthy parameters.  We do not report \textit{all} the announced
+exoplanets as we are not trying to provide ``an encyclopedic
+presentation of every claimed detection of an 
+exoplanet" \citep{Wright2011}.  More comprehensive sets of planet parameters
+are available from other exoplanet compendia on the Web.
 
@@
 
-{\bf DISCMETH} field previously reported the method of discovery,
-which was either radial velocity or transit. We have replaced DISCMETH
-with {\bf PLANETDISCMETH} and \mbox{{\bf STARDISCMETH}} to better
+The DISCMETH field previously reported the method of discovery,
+which was either ``radial velocity'' or ``transit''. We have replaced DISCMETH
+with {\bf PLANETDISCMETH} and {\bf STARDISCMETH} to better
 report how exoplanet systems and individual exoplanets are first
 discovered. PLANETDISCMETH reports the discovery method for the
-planet, wihle STARDISCMETH reports the discovery method for the first
-discovered planet around the host star. These fields are stored
-in string format and have one of the following values: "RV",
-"Transit", "Imaging", "Microlensing", "Timing", or "Astrometry" (no planets have "astrometry" yet).
+planet, while STARDISCMETH reports the discovery method for the {\it
+  planetary system} (i.e. the {\it first}
+discovered planet around the host star). These fields are stored
+in string format and have one of the following values: ``RV",
+``Transit", ``Imaging", ``Microlensing", ``Timing", or ``Astrometry"
+(no planets have a value of ``Astrometry" yet since no planet has yet
+been {\it discovered} via astrometry).
 
@@
 for a Kepler host star. KEPID is only available for unconfirmed
-KOI's imported directly from the Exoplanet Archive by the exoplanet.org backend. Therefore,
-none of the EOD planets including confirmed Kepler planets has a KEPID, yet.
+KOI's imported directly from the Exoplanet Archive by the
+exoplanets.org backend.
 
 {\bf KOI} stands for Kepler Objects of Interest, which is an object
-with transit signals detected by \kepler\ but have not been validated to be due to exoplanets. The KOI field defined by the \kepler\ team and showed on the Exoplanet Archive, contains a floating point
-number that consists of a whole number designated to the host star
-followed by a decimal number denoting a candidate planet. For example,
+with transit signals detected by \kepler\ that have not been validated
+as being due to exoplanets.  The KOI field defined by the \kepler\
+team and shown on the Exoplanet Archive is stored as a floating point
+number, consisting of a whole number designated to the host star
+followed by a decimal portion denoting a candidate planet. For example,
 KOI 102 is a star suspected to host two exoplanets, and KOI 102.01 is
 the inner planet candidate and KOI 102.02 is the outer one. Once a
-candidate is confirmed, the NAME field of the planet is replaced by
-the official \kepler\ ID (``Kepler" followed by a hyphen, an integer
-and an lower case letter). The KOI number is then used as
-OTHERNAME. For more information, see
+candidate is confirmed, the {\bf NAME} field of the planet is replaced by
+the official \kepler\ ID (``Kepler" followed by a hyphen, an integer,
+a space, and finally a lower case letter). The KOI number is then used as
+{\bf OTHERNAME}. For more information, see
 Section~\ref{sec:kepler}.
 
-{\bf EOD} is a boolean which indicates whether an exoplanet is included
+{\bf EOD} is a Boolean which indicates whether an exoplanet is included
 in the EOD for having well-characterized orbital
@@
 well-characterized orbits, and also \kepler\ planet candidates (see
-Section~\ref{sec:kepler} for more details).
+Section~\ref{sec:kepler} for more details).  Planets on exoplanets.org
+and appearing in the EDE that are not part of the EOD have EOD set to
+FALSE (i.e.\ zero).
 
-{\bf MICROLENSING, IMAGING, TIMING and ASTROMETRY} are flags which
-indicate that a planet detected via theses method. For example,
+{\bf MICROLENSING, IMAGING, TIMING} and {\bf ASTROMETRY} are Boolean flags which
+indicate that a planet has been detected via these methods. For example,
 MICROLENSING $=$ 1 means the planet is detected in a microlensing
@@
 %------------------------------------------------------------------------------
-\subsection{Orbital Parameters (e.g. RV and Transit)}\label{sec:orbit}
+\subsection{Orbital Parameters}\label{sec:orbit}
 
@@
 mass. Previously, we only reported the minimum mass, ($m\sin{i}$,
-MSINI) of the planets. We now report the mass as well when it is
-available. For example, if a planet is discovered by microlensing, we
+MSINI) of the planets.  We now, additionally, report the best estimate
+of the true mass in a heterogeneous way.  For example, if a planet is discovered by microlensing, we
 report the actual mass of the planet according to the literature. If a
@@
 the mass from the minimum mass $m\sin{i}$ and the orbital inclination
-$i$. For convenience of plotting RV and other planets on a common mass scale (see Section~\ref{sec:kepler}, MASS is set to MSINI if the orbital inclination is not known and
-the reference for MASS, MASSREF is set to ``Set to MSINI; I unknown''.
+$i$. For convenience of plotting RV and other planets on a common mass
+scale (see Section~\ref{sec:kepler}), MASS is set to MSINI if the
+orbital inclination is not known and the reference for MASS ({\bf
+  MASSREF}) is set to ``Set to MSINI; I unknown''.
 
-Also for plotting convenience, for KOIs without $m\sin{i}$ measured, we estimate their mass using the
-mass-radius relation from the literature. For KOIs with $R<4\rearth$, we follow $M_{p}/\mearth=2.69(R_{p}/\rearth)$
-from \cite{Weiss2014}; for $4\rearth<R<6\rearth$, we follow $M_{p}/\mearth=(R_{p}/\rearth)^2.06$ from
-\cite{Lissauer2011}; and for $6\rearth<R<11.7\rearth$ we follow $M_{p}/\mearth=1756.7*10^{(-1.646*(11.684/(R_{p}/\rearth)-1)^{(1/2.489)})}$
-from \cite{Mordasini2012}.
+Also for plotting convenience, for transiting $Kepler$ planets without $m\sin{i}$ measured, we estimate their mass using 
+mass-radius relations from the literature. We follow a series of
+relations given by \footnote{As of the writing of this manuscript,
+  Kepler planet candidates on exoplanets.org ingested
+  from the Exoplanet Archive have their masses estimated in a slightly
+  different manner.  The Website uses the \citeauthor{Mordasini2012} relation for
+  planets with 6$\rearth < R < 1 $ \rjup, the \citeauthor{Lissauer2011}
+  relation between $1 \rearth < R < 6\rearth$, and $M = (1/R)^{0.306}$ in
+  Earth units for planets smaller than $\rearth$.  Updating this
+  relation to be consistent with the EOD (and updating the
+  corresponding MASSREF fields for these candidates) is a priority
+  upgrade for exoplanets.org.}
+
+\[
+M_p=
+\begin{cases}
+M_{\rm WM} &  R<\rearth \\
+(1-x)M_{\rm WM} + xM_L  &  \rearth \leq R<4\rearth \\
+M_L & 4 \rearth \leq R < 6 \rearth \\
+M_M &  6\rearth \leq R < b \\
+{\text \mjup} &  R \geq b
+\end{cases}
+\]
+
+\noindent where $b$ is defined
+below, and we use the weight $x=\left(R_{p}/\rearth-1\right)/3$ to
+smoothly transition between $M_{\rm WM}$ and $M_L$ in their
+overlapping regions of validity. $M_{\rm WM}$ is from \cite{Weiss2014} and is given by 
+\[
+\frac{M_{\rm WM}}{\mearth}=
+\begin{cases}
+2.69\left(\frac{R_{p}}{\rearth}\right)^{0.93} &  \rearth \leq R<1.5\rearth \\
+0.582\left(0.717+\frac{R_{p}}{\rearth}\right)\left(\frac{R_{p}}{\rearth}\right)^3 &  1.5\rearth\leq R<4\rearth
+\end{cases}
+\]
+
+$M_L$ is given by $M_{p}/\mearth=\left(R_{p}/\rearth\right)^{2.06}$ from \cite{Lissauer2011}, and $M_M$ is given by 
+\[
+\log_{10}\left(\frac{M_{p}}{M_0}\right)=-w\left(\frac{b}{\left(R_{p}/\rearth\right)}-1\right)^{1/p}
+\]
+
+\noindent from \cite{Mordasini2012}, where
+\[
+\begin{tabular}{ c c c }
+  & $0.1<a/{\rm AU}$ & $0.1<a/{\rm AU} \leq 1$  \\ \hline $M_0[\mearth]$ & 1756.7 & 1308.7 \\
+$b[\rearth]$ & 11.684 & 11.858 \\ $w$ & 1.646 & 1.635 \\ $p$ & 2.489 & 2.849 \\ 
+\end{tabular}
+\]
+
+Planets with masses estimated in this manner are so noted in the
+MASSREF field.
 
 {\bf SEP} is a separation between the host star
-and the planet in units of AU. For directly imaged planets, the
+and the planet in units of AU. For directly imaged and microlensing planets, the
 literature usually reports the projected separation and we report the
 value accordingly.  If SEP is not directly measured but the semi-major
-axis ($a$, A) is available, then we set SEP to A with its reference,
+axis ({\bf A}) is available, then we set SEP to A with its reference,
 SEPREF, set to ``Set to A''.
 
-{\bf I} is the orbital inclination. Previously, only transiting
-systems have I measured, but now some non-transiting systems
-have I's reported too. For example, one microlensing system,
-OGLE-2006-BLG-109L, has I measured \citep{Bennett2010}. Also, one imaging system, $\beta$ Pic, has I measured \citep{Lagrange2009}
+{\bf I} reports the orbital inclination of the planet. Previously, only transiting
+systems had $i$ measured, but now some non-transiting systems have
+dynamical or astrometric constraints on $i$ (for example, the
+microlensing system OGLE-2006-BLG-109L \citep{Bennett2010} and the imaged system, $\beta$ Pictoris \citep{Lagrange2009}).
 
-{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in units of degrees. At the moment, no planets have this quantity measured, but astrometric orbits (e.g. from GPI) will reveal it.
+{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in units
+of degrees. At the moment, only $\beta$ Pictoris $b$ has this quantity listed.
 
@@
 measured by either the Rossiter-McLaughlin effect
-\citep[e.g.,][]{Winn2005} or planet transiting star spots
+\citep[e.g.,][]{Winn2005} or planetary transits of star spots
 \citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is used because
@@
 stellar spin axis and the orbital axis, is normally not directly
-measurable. We follow \cite{Fabrycky2009} where the coordinates are defined as follows: the
+measurable. We follow \cite{Fabrycky2009} who defined the quantity as follows: the
 $z$-axis points toward the observer, the $x$-axis points along the
@@
 previously report it consistently, since some literature report the ``projected
-spin-orbit misalignment" as $\beta = -\lambda$ instead\footnote{In some cases, e.g. \cite{Moutou2011}, other conventions entirely appear to be used.}. We have sorted
+spin-orbit misalignment" as $\beta = -\lambda$ instead\footnote{In some cases, \citep[e.g.][]{Moutou2011}, other conventions entirely appear to be used.}. We have sorted
 these cases out and made sure that our $\lambda$'s are following the
@@
 
-{\bf MASSREF} and {\bf MASSURL} fields were used to report the
-reference and the URL of stellar mass but now they are used for planet
-mass.
+The {\bf MASSREF} and {\bf MASSURL} fields were used to report the
+reference and the URL of stellar mass but now they are used for the planet's
+mass; {\bf MSTARREF} and {\bf MSTARURL} are now used for the stellar
+mass, {\bf MSTAR}.
 
@@
 
-We report the transit parameters, which are available only when the
-planet has TRANSIT Boolean equal to true. We describe two added fields since
-\cite{Wright2011} below, which are used for KOI's incorporated from the Exoplanet Archive.
+We have added two fields since \cite{Wright2011}, which are used for
+KOI's incorporated from the Exoplanet Archive.
 
@@
 available. Since \cite{Wright2011}, as many different surveys have
-been launched, more and more secondary eclipse depths at multiple
-bands have become available for more and more planets. Therefore, we added
-this entire new set of fields. ZZZ Refer to Ming's SE plot.
-
-The {\bf SE} Boolean indicates whether the system has detected secondary
-eclipse in any of the two Micron All-Sky Survey (2MASS;
-\citealt{Skrutskie2006}) $J$, $H$, and $K_s$, Kepler photometry band,
-and 4 Spitzer IRAC bands. Truth indicates the
-system has at least one secondary eclipse measurement in the EOD.
+been launched, secondary eclipse depths at multiple
+bands have become available for many planets. Therefore, we added
+this entire new set of fields (see Figure~\ref{fig:se}).
 
@@
 
-{\bf SET} is the epoch of secondary eclipse center, normally given in HJD but (as with other fields) when the literature reports HJD or UTC JD, we do not attempt a conversion to BJD.
+The {\bf SE} Boolean indicates whether the system has secondary
+eclipse depths measured in any band.  Truth indicates the
+system has at least one secondary eclipse measurement in the EOD.
+
+{\bf SET} is the epoch of secondary eclipse center, normally given in BJD but (as with other fields) when the literature reports HJD or UTC JD, we do not attempt a conversion to BJD.
 
@@
 {\bf GAMMA} ($\gamma$) is the radial velocity of the center of mass of
-the planetary system with respect to the barycentric frame and is reported in km/s.
+the planetary system with respect to the barycentric frame and is
+reported in km/s.  It is typically known to far less precision than
+$K$, because it requires an absolute measurement of velocity.
 
@@
 filters. We report optical magnitude and color ($V$ and $B-V$),
-2MASS $J$, $H$, and $K_s$ magnitudes and, we have added {\bf KP}. Notes that the definitions of V and B in the literature vary, and are often Hipparcos values
-(the stellar magnitude measured through the \kepler\ bandpass).
+2MASS $J$, $H$, and $K_s$ magnitudes and, we have added {\bf KP} for
+the \kepler\ photometric band. Notes that the definitions of $V$ and $B$ in the literature vary, and are often Hipparcos magnitudes.
 
@@
 We report the coordinates of the host star as well as the host star's
-ID as designated by different catalogs.  We added the {\bf DIST} field since
+ID as designated by different catalogs.  We have added the {\bf DIST} field since
 \cite{Wright2011}, which is the distance to the host star in the unit
@@
 and vice versa. If the literature does not report DIST or PAR, then we
-obtain PAR from the Hipparcos dataset by \cite{van Leeuwen2009} for stars with Hipparcos numbers. We
-naively propagate the error in PAR to DIST and vice versa.
+obtain PAR from the Hipparcos dataset by \cite{van Leeuwen2009} for
+stars with Hipparcos numbers. We na\"ively translate the 1-$\sigma$ errors in each into asymmetric
+uncertainties in the other.
 
@@
 are different when the error bars are asymmetric. UX contains the
-1$\sigma$ uncertainty, and it equals $({\rm XUPPER+XLOWER})/2$ in
-the case of asymmetric error bars. Fields that have XUPPER, XLOWER and
-UX are: all the orbital parameters, all the transit parameters, all the
-secondary eclipse fields, and all the stellar
+1$\sigma$ uncertainty, and it equals $({\rm XUPPER+XLOWER})/2$. Fields
+that have XUPPER, XLOWER and UX are: all the orbital parameters, all
+the transit parameters, all the secondary eclipse fields, and all the stellar
 properties and DIST and PAR.
 
-We also report the upper limits (XUL) for planet minimum mass (MSINI),
-eccentricity (ECC), and the radial velocity semi-amplitude (K) when
-the literature reports them. For example, the upper limits for ECC is
-reported when the orbit is consistent with a circular one, and the
-upper limits for K is reported when there is only upper-limit radial
-velocity detection. If only upper limits are given, we set the
-parameter field X to 0, the uncertainty XU to half of the upper limit,
-and the upper error bar XUPPER to the upper limits (same as XUL). For
-example, if the literature reports the upper limit for ECC, which we
-report in ECCUL, then we set ECC to be 0, ECCUPPER to ECCUL, and UECC
-to ECCUL/2. Since not all authors define the upper limits in the same
-way (e.g. 1$\sigma$ or some fixed percentile), we encourage the
-readers to refer to the original references for more information. Note that as of this writing, limits have not been incorporated into the EDE (see Section~\ref{sec:website}
+If only an upper limit is given, we set the parameter field X to 0,
+the uncertainty XU to half of the upper limit, and the upper error bar
+XUPPER to the upper limits (same as XUL). For example, if the
+literature reports the upper limit for ECC, which we report in ECCUL,
+then we set ECC to be 0, ECCUPPER to ECCUL, and UECC to ECCUL/2.  We
+are currently implementing a more precise upper limit scheme (see Section~\ref{sec:summary}.)
 
@@
 The fields {\bf XREF} and {\bf XURL} store the peer-reviewed reference
-and link to the publication for the data in field X. Previously, we only
-reported general references for certain sets of fields (e.g. FIRSTREF,
+and link to the publication for the data in field X. Previously, we 
+reported only general references for certain sets of fields (e.g. FIRSTREF,
 FIRSTURL, ORBREF, and ORBURL), but now we report the references for
@@
 
-The following fields do not have associated REF or URL fields.
-Except where we record these values directly from discovery papers, RA, DEC, and PAR are usually from the \textit{Hipparcos} re-reduction of \cite{van Leeuwen2009}; the $B-V$ (BMV) values
+The following fields do not have associated REF or URL fields. Except
+where we record these values directly from discovery papers, {\bf RA},
+{\bf DEC}, and PAR are usually from the \textit{Hipparcos}
+re-reduction of \cite{van Leeuwen2009}; the $B-V$ ({\bf BMV}) values
 are from the \textit{Hipparcos} catalog by \cite{Perryman1997};
-stellar magnitudes J H and KS are from the 2MASS
-\citep{Skrutskie2006} (as reduced from SIMBAD) and the KP magnitudes are from the Exoplanet
+stellar magnitudes {\bf J}, {\bf H}, and {\bf KS} (i.e.\ $K_{\rm s}$)
+are from the 2MASS catalog
+\citep{Skrutskie2006} (as reported in SIMBAD) and the {\bf KP} (i.e.\ $K_P$) magnitudes are from the Exoplanet
 Archive \citep{Akeson2013}.
 
-SHK and RHK are poorly maintained fields representing chromospheric emission measures and they unreferenced at the
-moment. We plan to include proper reference in the future. Most of the
-SHK and RHK values are from \cite{Butler2006}, and individual discovery papers.
+{\bf SHK} and {\bf RHK} represent the Mount Wilson S and
+$R^\prime_{HK}$ chromospheric
+emission measures.  These fields are poorly maintained fields and
+unreferenced, at the moment. We plan to include proper reference in
+the future. Most of the SHK and RHK values are from \cite{Butler2006},
+and individual discovery papers.
 
@@
 
-{\bf SPSTAR} field previously reported the stellar type of the host
-star, but it is removed since it is not well maintained.
+The {\bf SPSTAR} field previously reported the stellar type of the host
+star.  We have removed it since it can be difficult to verify with
+peer-reviewed references, and the field was not well maintained.  We encourage users
+to use TEFF and BMV instead.
 
-{\bf NSTEDID} field reported ID of host star in NStED and now it is
+The {\bf NSTEDID} field reported ID of host star in NStED, and now it is
 replaced by EANAME, which is the name of the star as appears on the
@@
 \centering
-\includegraphics[width=\textwidth]{../fig/wasp-14b.eps}
+\includegraphics[width=\textwidth]{fig/wasp-14b.eps}
 \caption{An example page for an individual exoplanet (WASP-14b in this
@@
 \section{Inclusion of the Kepler Planet Candidates \\
-  and Other Exoplanets on Exoplanets.org}\label{sec:kepler}
+  and Other Exoplanets on exoplanets.org}\label{sec:kepler}
 
 Since \cite{Wright2011}, \kepler\ has discovered many exoplanet
-candidates, and more planets were robustly discovered by various
-methods though not having very well characterized orbits, we have
+candidates, and more planets have been robustly discovered by various
+other methods, although not all have very well characterized orbits.  We have
 expanded the EDE to include those planets for the convenience of
-the users and also to keep our database complete in terms of confirmed
+our users, and also to keep exoplanets.org complete in terms of confirmed
 exoplanets.
@@
 % KOIs
-We have used broad definitions for SEP and MASS for this purpose. First, we now include the KOIs discovered by \kepler\ in the
+We now provide an option for users to include the KOIs discovered by \kepler\ in the
 EDE. Although KOIs are not counted as part of the EOD due to their
-status of being ``candidates", we include them in our website so that
-these KOIs are put into the context of all confirmed exoplanets. The
+status of being ``candidates", we include them on our website so that
+these KOIs are put into the context of all confirmed exoplanets. We
+have used broad definitions for SEP and MASS so that they may be
+compared to EOD planets, even though they share few strictly defined parameters.  The
 KOIs listed in our table include three \kepler\ data releases (as of
-March 2014), and we always keep up with the most up-to-date
-release. The original data are from the NASA Exoplanet Archive.
+July 2014), and exoplanets.org always provides the most up-to-date
+release through a partnership with the NASA Exoplanet Archive.
 
@@
 plots with the interactive plotting tool of EDE (see
-Figure~\ref{fig:koi} for an example plot).
+Figure~\ref{fig:koi} for an example plot).  All KOIs with a
+disposition other than ``FALSE POSITIVE'' are included in the EDE.
 
 % Other Planets
-Second, we now also include robustly detected imaging, microlensing,
-and timing planets, and our criteria for a `robust detection' are the
+We now also include robustly detected imaging, microlensing,
+and timing planets.  Our criteria for a ``robust detection'' for these
+planets are the
 following:
@@
 the EOD. These planets can be displayed by check the `Other' option
-for the EDE table. As of March 2014, no microlensing or imaging
-planets are in the EOD, while several timing exoplanets have
+for the EDE table. As of July 2014, no microlensing or imaging
+planets (except $\beta$ Pictoris) appear in the EOD, while several timing exoplanets have
 well-determined orbital parameters and are included in the
-EOD. Moreover, there have been no astrometric planets in the EOD but we
-plan to include them if any robust detections occur.
+EOD.
 
@@
 \centering
-\includegraphics[width=\textwidth]{../fig/mass-per-interactive.eps}
-\caption{ZZZ will change to mass-SEP plot once KOIs have SEP ZZZ
+\includegraphics[width=\textwidth]{fig/mass-per-interactive.eps}
+\caption{
   An example plot produced by the interactive plotting tools of
@@
   calculated using their radii based on mass-radius relations from the
-  literature (see Section~\ref{sec:orbit}).}
+  literature (see Section~\ref{sec:orbit}).  Note the
+  apples-to-oranges comparison enabled by the hybrid MASS field on the y-axis, which blends estimated
+  masses, minimum masses, and true masses on a single plot.}
 \label{fig:koi}
@@
 
-ZZZ add SE plots from Ming
-
 \begin{figure}[!htb]
 \centering
-\includegraphics[width=\textwidth]{../fig/senew.eps}
-\caption{An example plot that demonstrates the current secondary eclipse measurements.
-Each planet has a set of circles that stand for its available secondary eclipse measurements in the database, including Spitzer 8.0, 5.8, 4.5, \& 3.6 $\mu m$, and  ground-based $J$, $H$, and $Ks$ bands.
-\kepler\ secondary eclipse measurements are labeled as solid black dots.
-A few representative planets are also annotated.}
+\includegraphics[width=\textwidth]{fig/senew.eps}
+\caption{An example plot that demonstrates the current secondary
+  eclipse measurements. Each planet has a set of circles that stand
+  for its available secondary eclipse measurements in the database,
+  including Spitzer 8.0, 5.8, 4.5, \& 3.6 $\mu m$, and  ground-based
+  $J$, $H$, and $Ks$ bands. \kepler\ secondary eclipse measurements
+  are labeled as solid black dots. A few representative planets are
+  also annotated (a feature not offered by the EDE Plotter, but
+  trivially implemented by other image or presentation software).}
 \label{fig:se}
@@
 In the future, we hope to include images of directly imaged planets
-(where allowed under copyright law) and light curves for transits and microlensing planets.
-We plan to display RV curves whenever their RV data are available and include better incorporation of Kepler parameters in the EOD (such as KEPID).
-We also hope to include upper limits in the EDE table and plotter.
+and light curves for transits and
+microlensing planets. We plan to display RV curves whenever their RV
+data are available and include better incorporation of Kepler
+parameters in the EOD (such as KEPID).
+
+We also plan to report the upper limits (XUL) for planet minimum mass (MSINI),
+eccentricity (ECC), and the radial velocity semi-amplitude (K) when
+the literature reports them. For example, an upper limit for ECC is
+reported when the orbit is consistent with a circular one, and the
+upper limit for K is reported when there is only a null result from
+radial velocities. Since not all authors define the upper limits in the same
+way (e.g. 1$\sigma$ or some fixed percentile), we encourage the
+readers to refer to the original references for more information. We
+will also include proper rendering of upper limits in the EDE Table,
+proper upper limit symbols in the Plotter, and proper handling of
+upper limits in filters and queries in both cases.
+
+Omissions and errors to the EOD can be corrected by sending us an
+email at \url{datamaster@exoplanets.org}.
 
@@
 
-NSF funding? ZZZ will be added by Jason
+We acknowledge NSF grant AST-1211441 which supports exoplanets.org.
+Parts of this work was supported by a NASA Keck PI Data Award, administered by
+the NASA Exoplanet Science Institute.
 
-SXW acknowledges support from PSARC. This research has made use of
-NASA's Astrophysics Data System Bibliographic Services (ADS).
+We also thank NASA and NExScI for support via funds associated with
+the award of Keck time for monitoring the orbits of long-period and
+multi-planet systems.
 
-CEHW, SIMBAD, EA, and JS acknowledgement
+SXW acknowledges support from the Penn State Astrobiology Research
+Center, part of the NASA Astrobiology Institute. The Center for
+Exoplanets and Habitable Worlds is supported by the 
+Pennsylvania State University, the Eberly College of Science, and the
+Pennsylvania Space Grant Consortium.
+
+This research has made use of
+NASA's Astrophysics Data System Bibliographic Services (ADS) and the SIMBAD database,
+operated at CDS, Strasbourg, France.
+
+We thank Jean Schneider and the exoplanet.eu team, Rachel Akeson
+and the Exoplanet Archive team, and David Ciardi and the NStED team,
+for their hard work on their exoplanet compendia and for their
+occasional assistance and support.  Our parallel,
+independent, and complementary efforts improve all of our resources.
+We are especially grateful for the radial velocity archive compiled by
+NStED and currently maintained by the Exoplanet Archive, which enables
+many of the radial velocity plots at exoplanets.org.
+
+We thank Katie Peek, the information graphics editor at Popular
+Science magazine, for compiling the data to initially populate the
+MONTH field of the EOD and sharing it with us.
+
+We thank the many people who contributed bug reports and data
+errors to \url{datamaster@exoplanets.org}, which continue to improve
+the data quality of the EOD.
 
@@
 STAR\dotfill & String & Standard name for host star & \nodata & W11 \\
-BINARY\dotfill & Boolean & Star known ot be binary? & -REF, -URL & W11 \\
+BINARY\dotfill & Boolean & Star known to be binary? & -REF, -URL & W11 \\
 MSTAR\dotfill & Float & Mass of host star in solar mass & -UPPER, etc. & W11 \\
@@
 FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER, etc. & W11 \\
-TEFF\dotfill & Float & Effective temperature of host star & -UPPER, etc. & W11 \\
-RHOSTAR\dotfill & Float & Density of host star & -UPPER, etc. & \ref{sec:stellarprop} \\
+TEFF\dotfill & Float & Effective temperature of host star in Kelvins & -UPPER, etc. & W11 \\
+RHOSTAR\dotfill & Float & Density of host star in g/cm$^3$ & -UPPER, etc. & \ref{sec:stellarprop} \\
 LOGG\dotfill & Float & Spectroscopic $\log{g}$ (surface gravity) of

### 2014-07-22 draft/ms.tex
Incorporate Sharon's comments and update Ricker2014 in references.tex

@@
 
-The Exoplanet Orbit Database (EOD) compiles orbital, transit, host star, and other
-parameters of robustly detected exoplanets reported in the peer-reviewed
-literature. The EOD can be navigated through the Exoplanet Data
-Explorer (EDE) Plotter and Table, available on the World Wide Web at exoplanets.org. The EOD contains data for 1490 confirmed exoplanets as of March 2014.  
-The EOD descends from a table in \citet{Butler2002} and the Catalog of Nearby Exoplanets \citep{Butler2006}, and the first complete documentation for the EOD and the EDE was presented in 
-\cite{Wright2011}. In this work, we describe our work since then.  We have expanded the scope of the
-EOD to include secondary eclipse parameters, asymmetric uncertainties,
-and expanded the EDE to include
-the sample of over 3000 \kepler\ Objects of Interest (KOIs), and other
-real planets without good orbital parameters (such as many of those
-those detected by microlensing and imaging.) Users can download the
-latest version of the entire EOD as a single comma separated value
-file from the front page of exoplanets.org.
+The Exoplanet Orbit Database (EOD) compiles orbital, transit, host
+star, and other parameters of robustly detected exoplanets reported in
+the peer-reviewed literature. The EOD can be navigated through the
+Exoplanet Data Explorer (EDE) Plotter and Table, available on the
+World Wide Web at exoplanets.org. The EOD contains data for 1492
+confirmed exoplanets as of July 2014.  The EOD descends from a table
+in \citet{Butler2002} and the Catalog of Nearby Exoplanets
+\citep{Butler2006}, and the first complete documentation for the EOD
+and the EDE was presented in \cite{Wright2011}. In this work, we
+describe our work since then.  We have expanded the scope of the EOD
+to include secondary eclipse parameters, asymmetric uncertainties, and
+expanded the EDE to include the sample of over 3000 \kepler\ Objects
+of Interest (KOIs), and other real planets without good orbital
+parameters (such as many of those those detected by microlensing and
+imaging.) Users can download the latest version of the entire EOD as a
+single comma separated value file from the front page of
+exoplanets.org.
 
@@
 number of confirmed exoplanets has increased from about 300 to over
-1490 as of March 2014. \kepler\ contributed to a majority of these new discoveries ($> 800$) while providing an
-additional sample of over 4,000 exoplanet candidates (\kepler\ Objects
-of Interest, KOIs; e.g.~\citealt{Batalha2013}). The transit method has thus surpassed the radial velocity (RV) method to become the most fruitful
-means of detecting exoplanets. Meanwhile, great promise lies within
-the new and future exoplanet surveys and instruments with direct
-imaging (e.g., the Gemini Planet Imager, GPI,
-\citealt{Macintosh2014}) and microlensing (e.g., the Wide-Field
-InfraRed Survey Telescope, WFIRST, \citealt{Green2012}), while the
-fronts of RV and transit exoplanet searches keep expanding (e.g., the
-MINiature Exoplanet Radial Velocity Array, MINERVA,
-\citep{Wright2014}; the Habitable-zone Planet Finder, HPF, \cite{Mahadevan2012} and the
-Transiting Exoplanet Survey Satellit, TESS, \citealt{Ricker2014}).
+1490 as of July 2014. \kepler\ contributed to a majority of these new
+discoveries ($> 800$) while providing an additional sample of over
+3,000 exoplanet candidates (\kepler\ Objects of Interest, KOIs;
+e.g.~\citealt{Batalha2013}). The transit method has thus surpassed the
+radial velocity (RV) method to become the most fruitful means of
+detecting exoplanets. Meanwhile, great promise lies within the new and
+future exoplanet surveys and instruments with direct imaging (e.g.,
+the Gemini Planet Imager, GPI, \citealt{Macintosh2014}) and
+microlensing (e.g., the Wide-Field InfraRed Survey Telescope, WFIRST,
+\citealt{Green2012}), while the fronts of RV and transit exoplanet
+searches keep expanding (e.g., the MINiature Exoplanet Radial Velocity
+Array, MINERVA, \citealt{Wright2014}; the Habitable-zone Planet Finder,
+HPF, \citealt{Mahadevan2012} and the Transiting Exoplanet Survey
+Satellit, TESS, \citealt{Ricker2014}).
 
@@
 
-{\bf I} reports the orbital inclination of the planet. Previously, only transiting
-systems had $i$ measured, but now some non-transiting systems have
-dynamical or astrometric constraints on $i$ (for example, the
-microlensing system OGLE-2006-BLG-109L \citep{Bennett2010} and the imaged system, $\beta$ Pictoris \citep{Lagrange2009}).
+{\bf I} reports the orbital inclination of the planet. Previously,
+only transiting systems had $i$ measured, but now some non-transiting
+systems have dynamical or astrometric constraints on $i$ (for example,
+the microlensing system OGLE-2006-BLG-109L by \citealt{Bennett2010}
+and the imaged system, $\beta$ Pictoris by \citealt{Lagrange2009}).
 
@@
 
-{\bf SEDEPTHX} whereas X stands for one of ``J", ``H", ``KS", ``KP", ``36", ``45", ``58", ``80":
-these fields are the secondary eclipse depth measured in the
-corresponding wavelength band. SEDEPTHJ, H, and KS are the depths
-measured in the 2MASS wavelength bands in the near infrared, centered
-at 1.25~\micron, 1.65~\micron, and 2.15~\micron, respectively. KP is
-the depth measured in the \kepler\ photometric band which spans 400 to 865~nm. The other four represent the Spitzer IRAC and MIPS bands centered at
-3.6~\micron, 4.5~\micron, 5.8~\micron, and 8.0~\micron.
+{\bf SEDEPTHX} whereas X stands for one of ``J", ``H", ``KS", ``KP",
+``36", ``45", ``58", ``80": these fields are the secondary eclipse
+depth measured in the corresponding wavelength band. SEDEPTHJ, H, and
+KS are the depths measured in the 2MASS wavelength bands in the near
+infrared, centered at 1.25~\micron, 1.65~\micron, and 2.15~\micron,
+respectively. KP is the depth measured in the \kepler\ photometric
+band which spans 400 to 865~nm. The other four represent the
+\spitzer\ IRAC bands centered at 3.6~\micron, 4.5~\micron,
+5.8~\micron, and 8.0~\micron.
 
@@
 
-{\bf SET} is the epoch of secondary eclipse center, normally given in BJD but (as with other fields) when the literature reports HJD or UTC JD, we do not attempt a conversion to BJD.
+{\bf SET} is the epoch of secondary eclipse center, normally given in
+BJD but (as with other fields) when the literature reports HJD or UTC
+JD, we do not attempt a conversion to BJD.
 
@@
 2MASS $J$, $H$, and $K_s$ magnitudes and, we have added {\bf KP} for
-the \kepler\ photometric band. Notes that the definitions of $V$ and $B$ in the literature vary, and are often Hipparcos magnitudes.
+the \kepler\ photometric band. Note that the definitions of $V$ and $B$ in the literature vary, and are often Hipparcos magnitudes.
 
@@
 If only an upper limit is given, we set the parameter field X to 0,
-the uncertainty XU to half of the upper limit, and the upper error bar
-XUPPER to the upper limits (same as XUL). For example, if the
-literature reports the upper limit for ECC, which we report in ECCUL,
-then we set ECC to be 0, ECCUPPER to ECCUL, and UECC to ECCUL/2.  We
-are currently implementing a more precise upper limit scheme (see Section~\ref{sec:summary}.)
+and store the upper limit value in the field XUL. The uncertainty UX
+is set to half of the upper limit, and the upper error bar XUPPER to
+the upper limit value. For example, if the literature reports the
+upper limit for ECC, which we report in ECCUL, then we set ECC to be
+0, ECCUPPER to ECCUL, and UECC to ECCUL/2.  We are currently
+implementing a more precise upper limit scheme (see
+Section~\ref{sec:summary}.)
 
@@
 where we record these values directly from discovery papers, {\bf RA},
-{\bf DEC}, and PAR are usually from the \textit{Hipparcos}
+{\bf DEC}, and {\bf PAR} are usually from the \textit{Hipparcos}
 re-reduction of \cite{van Leeuwen2009}; the $B-V$ ({\bf BMV}) values
@@
 \centering
-\includegraphics[width=\textwidth]{fig/wasp-14b.eps}
+\includegraphics[width=\textwidth]{../fig/wasp-14b.eps}
 \caption{An example page for an individual exoplanet (WASP-14b in this
@@
 \centering
-\includegraphics[width=\textwidth]{fig/mass-per-interactive.eps}
+\includegraphics[width=\textwidth]{../fig/mass-per-interactive.eps}
 \caption{
@@
 \centering
-\includegraphics[width=\textwidth]{fig/senew.eps}
+\includegraphics[width=\textwidth]{../fig/senew.eps}
 \caption{An example plot that demonstrates the current secondary
@@
   for its available secondary eclipse measurements in the database,
-  including Spitzer 8.0, 5.8, 4.5, \& 3.6 $\mu m$, and  ground-based
-  $J$, $H$, and $Ks$ bands. \kepler\ secondary eclipse measurements
+  including \spitzer\ 8.0, 5.8, 4.5, \& 3.6 \micron, and ground-based
+  $J$, $H$, and $K_{\rm s}$ bands. \kepler\ secondary eclipse measurements
   are labeled as solid black dots. A few representative planets are

### 2014-07-22 draft/ms.tex
Remove upper limit from sec:unc and incorporate Ming's comments.

@@
 
-Also for plotting convenience, for transiting $Kepler$ planets without $m\sin{i}$ measured, we estimate their mass using 
-mass-radius relations from the literature. We follow a series of
-relations given by \footnote{As of the writing of this manuscript,
-  Kepler planet candidates on exoplanets.org ingested
-  from the Exoplanet Archive have their masses estimated in a slightly
-  different manner.  The Website uses the \citeauthor{Mordasini2012} relation for
-  planets with 6$\rearth < R < 1 $ \rjup, the \citeauthor{Lissauer2011}
-  relation between $1 \rearth < R < 6\rearth$, and $M = (1/R)^{0.306}$ in
-  Earth units for planets smaller than $\rearth$.  Updating this
-  relation to be consistent with the EOD (and updating the
-  corresponding MASSREF fields for these candidates) is a priority
-  upgrade for exoplanets.org.}
+Also for plotting convenience, for transiting $Kepler$ planets without
+$m\sin{i}$ measured, we estimate their mass using mass-radius
+relations from the literature. We follow a series of relations given
+by \footnote{As of the writing of this manuscript, Kepler planet
+  candidates on exoplanets.org ingested from the Exoplanet Archive
+  have their masses estimated in a slightly different manner.  The
+  Website uses the \citeauthor{Mordasini2012} relation for planets
+  with 6$\rearth < R < b$ ($b \sim 11 \rearth$ as defined by
+  \citeauthor{Mordasini2012}), the \citeauthor{Lissauer2011} relation
+  between $1 \rearth < R < 6\rearth$, and $M = (1/R)^{0.306}$ in Earth
+  units for planets smaller than $\rearth$.  Updating this relation to
+  be consistent with the EOD (and updating the corresponding MASSREF
+  fields for these candidates) is a priority upgrade for
+  exoplanets.org.}
 
@@
 %------------------------------------------------------------------------------
-\subsection{Uncertainties and Upper Limits}\label{sec:unc}
+%\subsection{Uncertainties and Upper Limits}\label{sec:unc}
+\subsection{Uncertainties}\label{sec:unc}
 
@@
 
+\begin{comment}
 If only an upper limit is given, we set the parameter field X to 0,
@@
 Section~\ref{sec:summary}.)
+\end{comment}
 
@@
   also annotated (a feature not offered by the EDE Plotter, but
-  trivially implemented by other image or presentation software).}
+  trivially implemented by other image or presentation software). The
+  planet name will appear when the user points the cursor at the
+  corresonding data point in the interactive plotting tools.}
 \label{fig:se}
@@
 AR\dotfill & Float & $(a/R_*)$ & -UPPER, etc. & W11 \\
-DEPTH\dotfill & Float & Transit depth, $(R_p/R_*)^2$ & -UPPER, etc. & W11 \\
+DEPTH\dotfill & Float & Transit depth, or $(R_p/R_*)^2$ when depth is
+not given & -UPPER, etc. & W11 \\
 DENSITY\dotfill & Float & Density of planet in g cc$^{-1}$ &

### 2014-07-22 draft/ms.tex
Typo fixes in abstract

@@
 of Interest (KOIs), and other real planets without good orbital
-parameters (such as many of those those detected by microlensing and
-imaging.) Users can download the latest version of the entire EOD as a
+parameters (such as many of those detected by microlensing and
+imaging). Users can download the latest version of the entire EOD as a
 single comma separated value file from the front page of

### 2014-07-22 draft/ms.tex
Formatting changes for compliance with PASP file name conventions

@@
 This paper describes our continuing efforts since \cite{Butler2006}
-and \cite{Wright2011} to maintain the Exoplanet Orbit Database\footnote{See \url{http://expoplanets.org}}(EOD)
-and the Exoplanets Data Explorer (EDE), to keep track of exoplanet
+and \cite{Wright2011} to maintain the Exoplanet Orbit
+Database\footnote{See \url{http://expoplanets.org}}(EOD) and the
+Exoplanets Data Explorer (EDE), to keep track of exoplanet
 discoveries, and to better catalog orbital parameters and host star
@@
 % data access and popularity
-The EOD is hosted at the Web domain exoplanets.org, which also hosts the EDE, an
-interactive table with plotting tools for all the EOD exoplanets, in
-addition to other confirmed exoplanets without good orbital
-parameters, and KOIs (except for those with a ``FALSE POSITIVE''
-disposition at the Exoplanet Archive). The entire dataset of exoplanets.org is available for download as a single comma separated value file from the Website front page.\footnote{At
+The EOD is hosted at the Web domain exoplanets.org, which also hosts
+the EDE, an interactive table with plotting tools for all the EOD
+exoplanets, in addition to other confirmed exoplanets without good
+orbital parameters, and KOIs (except for those with a ``FALSE
+POSITIVE'' disposition at the Exoplanet Archive). The entire dataset
+of exoplanets.org is available for download as a single comma
+separated value file from the Website front page.\footnote{At
   \url{http://exoplanets.org/csv-files/exoplanets.csv}.}  An example
-of this CSV file is available with the electronic version of this paper.
+of this CSV file is available with the electronic version of this
+paper.
 
@@
 exoplanets discovered by any other methods with robust detections and
-good orbital parameters, such as $\beta$ Pictoris $b$ \citep{Chauvin2012,Nielsen2014,Macintosh2014}.
+good orbital parameters, such as $\beta$ Pictoris $b$
+\citep{Chauvin2012,Nielsen2014,Macintosh2014}.
 
@@
 The rest of the selection criteria for the EOD remain unchanged. We
-still require the planets to have robust detections and well-determined
-orbits (though these are not strictly quantitative and sometimes subjective; see Section~2 of
-\citealt{Wright2011}). If new evidence comes to light and we are no
-longer confident about a planet, we may remove it from EOD, even if the
-new evidence is not peer reviewed.  The rationale for this scheme is,
-as it has been since the CNE, that the EOD represents our best, expert effort to produce a clean set of
-trustworthy parameters.  We do not report \textit{all} the announced
-exoplanets as we are not trying to provide ``an encyclopedic
-presentation of every claimed detection of an 
-exoplanet" \citep{Wright2011}.  More comprehensive sets of planet parameters
-are available from other exoplanet compendia on the Web.
+still require the planets to have robust detections and
+well-determined orbits (though these are not strictly quantitative and
+sometimes subjective; see Section~2 of \citealt{Wright2011}). If new
+evidence comes to light and we are no longer confident about a planet,
+we may remove it from EOD, even if the new evidence is not peer
+reviewed.  The rationale for this scheme is, as it has been since the
+CNE, that the EOD represents our best, expert effort to produce a
+clean set of trustworthy parameters.  We do not report \textit{all}
+the announced exoplanets as we are not trying to provide ``an
+encyclopedic presentation of every claimed detection of an exoplanet"
+\citep{Wright2011}.  More comprehensive sets of planet parameters are
+available from other exoplanet compendia on the Web.
 
@@
 fields since \cite{Wright2011}, and list all fields in
-Table~\ref{tab:par}. We divide the fields into categories consistent with the individual planet page on
+Table~\ref{tab:par}. We divide the fields into categories consistent
+with the individual planet page on
 exoplanets.org. (Figure~\ref{fig:individual} is an example of
-individual planet page, which is presented to website users who click on a planet's name). Some fields are not explicitly tabulated on
-the page (e.g., the URLs for ADS pages for papers providing the underlying data), but are explicitly listed in the
-downloadable {\tt .csv} file (see Section~\ref{sec:intro}). Though we
-focus on the EOD in this section, the fields apply to all planets on
-exoplanets.org. We follow the definition of orbital elements in
-\cite{Wright2013} unless indicated otherwise.
+individual planet page, which is presented to website users who click
+on a planet's name). Some fields are not explicitly tabulated on the
+page (e.g., the URLs for ADS pages for papers providing the underlying
+data), but are explicitly listed in the downloadable {\tt .csv} file
+(see Section~\ref{sec:intro}). Though we focus on the EOD in this
+section, the fields apply to all planets on exoplanets.org. We follow
+the definition of orbital elements in \cite{Wright2013} unless
+indicated otherwise.
 
@@
 We report general information of when, by whom and how the planets
-were discovered and first reported and provide the references for underlying data. We describe the added or
-revised fields since \cite{Wright2011} below.
+were discovered and first reported and provide the references for
+underlying data. We describe the added or revised fields since
+\cite{Wright2011} below.
 
@@
 detected by the radial velocity method, the semiamplitude, $K$, is
-reported, whereas the inclination of the orbit, $i$, is usually only known via the
-transit method (although planet-planet interactions and astrometry can also determine it). We describe the added fields since \cite{Wright2011}
-below.
+reported, whereas the inclination of the orbit, $i$, is usually only
+known via the transit method (although planet-planet interactions and
+astrometry can also determine it). We describe the added fields since
+\cite{Wright2011} below.
 
@@
 \citep[e.g.,][]{Winn2005} or planetary transits of star spots
-\citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is used because
-the true spin-orbit angle, defined as the angle between the
-stellar spin axis and the orbital axis, is normally not directly
-measurable. We follow \cite{Fabrycky2009} who defined the quantity as follows: the
-$z$-axis points toward the observer, the $x$-axis points along the
-intersection of the sky plane and the planet's orbital plane with the
-ascending node of the planet having $x<0$, and the $y$-axis completes
-a right handed-triad. $\lambda$ is measured clockwise on the sky from
-the $y$-axis to the projected stellar rotational axis. $\lambda$ is
-not a newly added field to the EOD but we describe it here because we did not
-previously report it consistently, since some literature report the ``projected
-spin-orbit misalignment" as $\beta = -\lambda$ instead\footnote{In some cases, \citep[e.g.][]{Moutou2011}, other conventions entirely appear to be used.}. We have sorted
-these cases out and made sure that our $\lambda$'s are following the
-definition of \cite{Fabrycky2009}.
+\citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is used because the true
+spin-orbit angle, defined as the angle between the stellar spin axis
+and the orbital axis, is normally not directly measurable. We follow
+\cite{Fabrycky2009} who defined the quantity as follows: the $z$-axis
+points toward the observer, the $x$-axis points along the intersection
+of the sky plane and the planet's orbital plane with the ascending
+node of the planet having $x<0$, and the $y$-axis completes a right
+handed-triad. $\lambda$ is measured clockwise on the sky from the
+$y$-axis to the projected stellar rotational axis. $\lambda$ is not a
+newly added field to the EOD but we describe it here because we did
+not previously report it consistently, since some literature report
+the ``projected spin-orbit misalignment" as $\beta = -\lambda$
+instead\footnote{In some cases, \citep[e.g.][]{Moutou2011}, other
+  conventions entirely appear to be used.}. We have sorted these cases
+out and made sure that our $\lambda$'s are following the definition of
+\cite{Fabrycky2009}.
 
@@
 stellar magnitudes {\bf J}, {\bf H}, and {\bf KS} (i.e.\ $K_{\rm s}$)
-are from the 2MASS catalog
-\citep{Skrutskie2006} (as reported in SIMBAD) and the {\bf KP} (i.e.\ $K_P$) magnitudes are from the Exoplanet
-Archive \citep{Akeson2013}.
+are from the 2MASS catalog \citep{Skrutskie2006} (as reported in
+SIMBAD) and the {\bf KP} (i.e.\ $K_P$) magnitudes are from the
+Exoplanet Archive \citep{Akeson2013}.
 
@@
 \centering
-\includegraphics[width=\textwidth]{../fig/wasp-14b.eps}
+%\includegraphics[width=\textwidth]{../fig/wasp-14b.eps}
+\includegraphics[width=\textwidth]{f1.eps}
 \caption{An example page for an individual exoplanet (WASP-14b in this
@@
 \centering
-\includegraphics[width=\textwidth]{../fig/mass-per-interactive.eps}
+%\includegraphics[width=\textwidth]{../fig/mass-per-interactive.eps}
+\includegraphics[width=\textwidth]{f2.eps}
 \caption{
@@
 \centering
-\includegraphics[width=\textwidth]{../fig/senew.eps}
+%\includegraphics[width=\textwidth]{../fig/senew.eps}
+\includegraphics[width=\textwidth]{f3.eps}
 \caption{An example plot that demonstrates the current secondary
@@
 \begin{enumerate}
-\item Plot parameters may be saved with browser cookies, so plots may be custom reproduced easily with updated data later.
-\item Tables may be generated and exported with custom fields computed.
-\item Plots may be exported with a variety of resolutions and aspects, including publication-quality vector graphics (SVG format). 
+\item Plot parameters may be saved with browser cookies, so plots may
+  be custom reproduced easily with updated data later. 
+\item Tables may be generated and exported with custom fields
+  computed. 
+\item Plots may be exported with a variety of resolutions and aspects,
+  including publication-quality vector graphics (SVG format).  
 \end{enumerate}
@@
 the secondary eclipse depths. We removed obsolete fields and revised
-some fields as necessary. We have included SEP and MASS with broad definitions so all planets may be plotted on common axes.
+some fields as necessary. We have included SEP and MASS with broad
+definitions so all planets may be plotted on common axes.
 
 Second, we included KOIs and other planets (the ones detected by
-microlensing, imaging, timing, and in the future, astrometry but do not have well characterized orbits) on
-exoplanets.org. Although they are not included in the EOD, we reported
-them on our website since the users might find them useful for
-purposes of statistical studies and comparison.
+microlensing, imaging, timing, and in the future, astrometry but do
+not have well characterized orbits) on exoplanets.org. Although they
+are not included in the EOD, we reported them on our website since the
+users might find them useful for purposes of statistical studies and
+comparison.
 
 In the future, we hope to include images of directly imaged planets
-and light curves for transits and
-microlensing planets. We plan to display RV curves whenever their RV
-data are available and include better incorporation of Kepler
-parameters in the EOD (such as KEPID).
+and light curves for transits and microlensing planets. We plan to
+display RV curves whenever their RV data are available and include
+better incorporation of Kepler parameters in the EOD (such as KEPID).
 
@@
 %\newpage
-\input{references.tex}
+%\input{references.tex}
+% List references here
+\begin{thebibliography}
+
+\bibitem[Akeson et al.(2013)]{Akeson2013} Akeson, R.~L., et al.\ 2013, 
+\pasp, 125, 989 % NASA Exoplanet Archive
+
+\bibitem[Batalha et al.(2013)]{Batalha2013} Batalha, N.~M., et al.\ 2013, 
+\apjs, 204, 24 % example of KOI release
+
+\bibitem[Bennett et al.(2010)]{Bennett2010} Bennett, D.~P., et al.\ 2010, 
+\apj, 713, 837 % OGLE microlensing planet with inclination measured
+
+\bibitem[Borucki et al.(2010)]{Borucki2010} Borucki, W.~J., et al.\ 2010, 
+Science, 327, 977 % Kepler instroduction and first results
+
+\bibitem[Butler et al.(2002)]{Butler2002} Butler, R.~P., et al.\ 2002, 
+\apj, 578, 565 % first peer-reviewed list of planets with robust orbits
+
+\bibitem[Butler et al.(2006)]{Butler2006} Butler, R.~P., et al.\ 2006, 
+\apj, 646, 505 % EOD first paper
+
+\bibitem[Collier Cameron et al.(2010)]{Collier Cameron2010} Collier 
+Cameron, A., et al.\ 2010, \mnras, 407, 507 % WASP-33b having no RV
+                                % detection and K upper limit
+
+\bibitem[Cosentino et al.(2012)]{Cosentino2012} Cosentino, R., et al.\ 
+2012, \procspie, 8446, 1V % HARPS-North
+
+\bibitem[Dawson \& Murray-Clay(2013)]{Dawson2013} Dawson, R.~I., \&
+  Murray-Clay, R.~A.\ 2013, \apjl, 767, L24  % use of EOD
+
+\bibitem[Fabrycky \& Winn(2009)]{Fabrycky2009} Fabrycky, D.~C., \&
+  Winn, J.~N.\ 2009, \apj, 696, 1230 % spin-orbit misalignment lambda definition
+
+\bibitem[Green et al.(2012)]{Green2012} Green, J., et al.\ 2012, 
+arXiv:1208.4012   % WFIRST
+
+\bibitem[Horner et al.(2012)]{Horner2012} Horner, J., Wittenmyer, R.~A., 
+Hinse, T.~C., \& Tinney, C.~G.\ 2012, \mnras, 425, 749 % dynamic
+                                % analysis on timing planet
+
+\bibitem[Howard(2013)]{Howard2013} Howard, A.~W.\ 2013, Science, 340,
+  572 % use of EOD
+
+\bibitem[Johnson et al.(2011)]{Johnson2011} Johnson, J.~A., et al.\ 2011, 
+\apjs, 197, 26 % HD 116029B having ECC upper limit (circular orbit)
+
+\bibitem[Kane(2014)]{Kane2014} Kane, S.~R.\ 2014, \apj, 782, 111 % use
+                                % of EOD
+
+\bibitem[Kipping(2013)]{Kipping2013} Kipping, D.~M.\ 2013, \mnras,
+  434, L51 % use of EOD
+
+\bibitem[Lagrange et al.(2009)]{Lagrange2009} Lagrange, A.-M., Gratadour, D., Chauvin, G., et al.\ 2009, \aap, 493, L21 %beta Pic b, imaging planet with I measured
+
+\bibitem[Lissauer et al.(2011)]{Lissauer2011} Lissauer, J.~J., et al.\ 
+2011, \apjs, 197, 8 % Mass-Radius for 1 Re < R < 6 Re
+
+\bibitem[Macintosh et al.(2014)]{Macintosh2014} Macintosh, B., Gemini 
+Planet Imager instrument team, Planet Imager Exoplanet Survey, G., 
+\& Observatory, G.\ 2014, American Astronomical Society Meeting
+Abstracts, 223, \#229.02  % GPI
+
+\bibitem[Marcy et al.(2014)]{Marcy2014} Marcy, G.~W., et al.\ 2014, \apjs, 
+210, 20 % 42 RV confirmed small Kepler planets
+
+\bibitem[Mahadevan et al.(2012)]{Mahadevan2012} Mahadevan, S., 
+Ramsey, L., Bender, C., et al.\ 2012, \procspie, 8446, %HPF
+
+\bibitem[Mordasini et al.(2012)]{Mordasini2012} Mordasini, C., Alibert, Y., 
+Georgy, C., Dittkrist, K.-M., Klahr, H., \& Henning, T.\ 2012, \aap, 547, A112
+% Mass-Radius for 6 Re < R < 11.684 Re
+
+\bibitem[Moutou et al.(2011)]{Moutou2011} Moutou, C., D{\'{\i}}az, R.~F., Udry, S., et al.\ 2011, \aap, 533, A113  %Lambda example
+
+\bibitem[Perryman \& ESA(1997)]{Perryman1997} Perryman, M.~A.~C., \&
+  ESA 1997, ESA Special Publication, 1200 % Hipparcos B-V reference
+
+\bibitem[Ricker(2014)]{Ricker2014} Ricker, G.~R.\ 2014, Journal of the 
+American Association of Variable Star Observers (JAAVSO), 42, 234 % TESS
+
+\bibitem[Rowe et al.(2014)]{Rowe2014} Rowe, J.~F., et al.\ 2014, 
+arXiv:1402.6534 % 715 new Kepler planets (multis)
+
+\bibitem[Sanchis-Ojeda et al.(2012)]{Sanchis-Ojeda2012} Sanchis-Ojeda, R., 
+et al.\ 2012, \nat, 487, 449 % Kepler 30 system lambda measurement
+                             % with star spot transit
+
+\bibitem[Schneider et al.(2011)]{Schneider2011} Schneider, J., Dedieu, C., 
+Le Sidaner, P., Savalle, R., \& Zolotukhin, I.\ 2011, \aap, 532, A79
+% exoplanet.eu
+
+\bibitem[Skrutskie et al.(2006)]{Skrutskie2006} Skrutskie, M.~F., et al.\ 
+2006, \aj, 131, 1163 % 2MASS
+
+\bibitem[Sotin et al.(2007)]{Sotin2007} Sotin, C., Grasset, O., 
+\& Mocquet, A.\ 2007, \icarus, 191, 337 % Mass-Radius for M<1Me, R<1Re
+
+\bibitem[van Leeuwen(2009)]{van Leeuwen2009} van Leeuwen, F.\ 2009, \aap, 
+497, 209 % Hipparcos catalog
+
+\bibitem[Weiss \& Marcy(2014)]{Weiss2014} Weiss, L.~M., \& Marcy,
+  G.~W.\ 2014, \apjl, 783, L6  % Mass-Radius for R < 4Re to be implemented
+
+\bibitem[Winn et al.(2005)]{Winn2005} Winn, J.~N., et al.\ 2005, \apj, 631, 
+1215 % HD 209458b, the first Rossiter-McLaughlin lambda measurement
+
+\bibitem[Wittenmyer et al.(2012)]{Wittenmyer2012} Wittenmyer, R.~A., 
+Horner, J., Marshall, J.~P., Butters, O.~W., 
+\& Tinney, C.~G.\ 2012, \mnras, 419, 3258 % dynamic analysis on timing
+                                % planets
+
+\bibitem[Wittenmyer et al.(2013)]{Wittenmyer2013} Wittenmyer, R.~A., 
+Horner, J., \& Marshall, J.~P.\ 2013, \mnras, 431, 2150 % dynamic
+                                % analysis on timing planets
+
+\bibitem[Wright et al.(2011)]{Wright2011} Wright, J.~T., et al.\ 2011,
+  \pasp, 123, 412 % EOD 2011 paper
+
+\bibitem[Wright \& Gaudi(2013)]{Wright2013} Wright, J.~T., \& Gaudi, B.~S.\ 2013,
+  Planets, Stars and Stellar Systems.~Volume 3: Solar and Stellar
+  Planetary Systems, 489 % Review article with definition of orbital elements
+
+\bibitem[Wright et al.(2014)]{Wright2014} Wright, J., et al.\ 2014, 
+American Astronomical Society Meeting Abstracts, 223, \#148.31
+
+\end{thebibliography}
 

### 2014-07-22 draft/references.tex
Incorporate Sharon's comments and update Ricker2014 in references.tex
Fix missing beta Pic b references.

@@
 \apj, 646, 505 % EOD first paper
+
+\bibitem[Chauvin et al.(2012)]{Chauvin2012} Chauvin, G., et al.\ 2012, 
+\aap, 542, A41 % beta Pic orbital pars
 
@@
 
+\bibitem[Nielsen et al.(2014)]{Nielsen2014} Nielsen, E.~L., et al.\ 2014, 
+arXiv:1403.7195 % beta Pic orbit pars
+
 \bibitem[Perryman \& ESA(1997)]{Perryman1997} Perryman, M.~A.~C., \&
@@
 
-\bibitem[Ricker et al.(2010)]{Ricker2010} Ricker, G.~R., et al.\ 2010, 
-Bulletin of the American Astronomical Society, 42, \#450.06 % TESS
+\bibitem[Ricker(2014)]{Ricker2014} Ricker, G.~R.\ 2014, Journal of the 
+American Association of Variable Star Observers (JAAVSO), 42, 234 % TESS
 

### 2014-09-26 draft/ms.tex
Fix missing beta Pic b references.
Fix errors in Section 2.2 on mass calculation based on radius.
Revise according to relevant proof corrections.

@@
   \url{http://exoplanetarchive.ipac.caltech.edu}.}
-\citep{Akeson2013}.  The natures of these efforts are complementary, and to the
+\citep{Akeson2013}.  The natures of these efforts are largely
+complementary to the EOD, and to the
 degree that they are redundant provide important cross-checking and
@@
 
-{\bf KEPID} stands for KEPler ID, which is the integer number assigned
+{\bf KEPID} stands for KEPler IDentification, which is the integer number assigned
 for a Kepler host star. KEPID is only available for unconfirmed
@@
 
-{\bf KOI} stands for Kepler Objects of Interest, which is an object
+{\bf KOI} stands for Kepler Object of Interest, which is an object
 with transit signals detected by \kepler\ that have not been validated
@@
 relations from the literature. We follow a series of relations given
-by \footnote{As of the writing of this manuscript, Kepler planet
+by
+\begin{comment}
+  % no longer true - already updated
+\footnote{As of the writing of this manuscript, Kepler planet
   candidates on exoplanets.org ingested from the Exoplanet Archive
@@
   exoplanets.org.}
+\end{comment}
 
@@
 M_L & 4 \rearth \leq R < 6 \rearth \\
-M_M &  6\rearth \leq R < b \\
+\min{(M_{\rm M},{\text \mjup})} &  6\rearth \leq R < b \\
 {\text \mjup} &  R \geq b
@@
 \begin{cases}
-2.69\left(\frac{R_{p}}{\rearth}\right)^{0.93} &  \rearth \leq R<1.5\rearth \\
-0.582\left(0.717+\frac{R_{p}}{\rearth}\right)\left(\frac{R_{p}}{\rearth}\right)^3 &  1.5\rearth\leq R<4\rearth
+0.615\left(0.717+\frac{R_{p}}{\rearth}\right)\left(\frac{R_{p}}{\rearth}\right)^3 &  R<1.5\rearth \\
+2.69\left(\frac{R_{p}}{\rearth}\right)^{0.93} &  1.5\rearth\leq R<4\rearth
 \end{cases}
@@
 \begin{tabular}{ c c c }
-  & $0.1<a/{\rm AU}$ & $0.1<a/{\rm AU} \leq 1$  \\ \hline $M_0[\mearth]$ & 1756.7 & 1308.7 \\
+  & $a/{\rm AU} \leq 0.1$ & $a/{\rm AU} > 0.1$  \\ \hline $M_0[\mearth]$ & 1756.7 & 1308.7 \\
 $b[\rearth]$ & 11.684 & 11.858 \\ $w$ & 1.646 & 1.635 \\ $p$ & 2.489 & 2.849 \\ 
@@
 
-{\bf I} reports the orbital inclination of the planet. Previously,
+The parameter {\bf I} reports the orbital inclination of the planet. Previously,
 only transiting systems had $i$ measured, but now some non-transiting
@@
 
+\begin{comment}
 {\bf SET} is the epoch of secondary eclipse center, normally given in
@@
 JD, we do not attempt a conversion to BJD.
+\end{comment}
 
@@
 
-The {\bf SPSTAR} field previously reported the stellar type of the host
+The {\bf SPTYPE} field previously reported the stellar type of the host
 star.  We have removed it since it can be difficult to verify with
@@
 way (e.g. 1$\sigma$ or some fixed percentile), we encourage the
-readers to refer to the original references for more information. We
+users to refer to the original references for more information. We
 will also include proper rendering of upper limits in the EDE Table,
@@
 SXW acknowledges support from the Penn State Astrobiology Research
-Center, part of the NASA Astrobiology Institute. The Center for
+Center, part of the NASA Astrobiology Institute (NNA09DA76A). The Center for
 Exoplanets and Habitable Worlds is supported by the 
@@
 
+We thank Jacob Bean for his referee report and suggestions to exoplanets.org.
+
 We thank the many people who contributed bug reports and data
@@
 
-\bibitem[Collier Cameron et al.(2010)]{Collier Cameron2010} Collier 
-Cameron, A., et al.\ 2010, \mnras, 407, 507 % WASP-33b having no RV
+\bibitem[Chauvin et al.(2012)]{Chauvin2012} Chauvin, G., et al.\ 2012, 
+\aap, 542, A41 % beta Pic orbital pars
+
+%\bibitem[Collier Cameron et al.(2010)]{Collier Cameron2010} Collier 
+%Cameron, A., et al.\ 2010, \mnras, 407, 507 % WASP-33b having no RV
                                 % detection and K upper limit
 
-\bibitem[Cosentino et al.(2012)]{Cosentino2012} Cosentino, R., et al.\ 
-2012, \procspie, 8446, 1V % HARPS-North
+%\bibitem[Cosentino et al.(2012)]{Cosentino2012} Cosentino, R., et al.\ 
+%2012, \procspie, 8446, 1V % HARPS-North
 
@@
 
-\bibitem[Johnson et al.(2011)]{Johnson2011} Johnson, J.~A., et al.\ 2011, 
-\apjs, 197, 26 % HD 116029B having ECC upper limit (circular orbit)
+%\bibitem[Johnson et al.(2011)]{Johnson2011} Johnson, J.~A., et al.\ 2011, 
+%\apjs, 197, 26 % HD 116029B having ECC upper limit (circular orbit)
 
@@
 
-\bibitem[Marcy et al.(2014)]{Marcy2014} Marcy, G.~W., et al.\ 2014, \apjs, 
-210, 20 % 42 RV confirmed small Kepler planets
+%\bibitem[Marcy et al.(2014)]{Marcy2014} Marcy, G.~W., et al.\ 2014, \apjs, 
+%210, 20 % 42 RV confirmed small Kepler planets
 
@@
 
-\bibitem[Rowe et al.(2014)]{Rowe2014} Rowe, J.~F., et al.\ 2014, 
-arXiv:1402.6534 % 715 new Kepler planets (multis)
+%\bibitem[Rowe et al.(2014)]{Rowe2014} Rowe, J.~F., et al.\ 2014, 
+%arXiv:1402.6534 % 715 new Kepler planets (multis)
 
@@
 
-\bibitem[Sotin et al.(2007)]{Sotin2007} Sotin, C., Grasset, O., 
-\& Mocquet, A.\ 2007, \icarus, 191, 337 % Mass-Radius for M<1Me, R<1Re
+%\bibitem[Sotin et al.(2007)]{Sotin2007} Sotin, C., Grasset, O., 
+%\& Mocquet, A.\ 2007, \icarus, 191, 337 % Mass-Radius for M<1Me, R<1Re
 
@@
 \spitzer\ IRAC4 8.0 \micron\ band & -UPPER, etc. & \ref{sec:se} \\
-SET\dotfill & Double & Epoch of secondary eclipse center in
-HJD\tablenotemark{c} & -UPPER, etc. & \ref{sec:se} \\
+%SET\dotfill & Double & Epoch of secondary eclipse center in
+%HJD\tablenotemark{c} & -UPPER, etc. & \ref{sec:se} \\
 %

### 2014-09-29 arxiv_newsletter/abstract_han2014.tex
Exoplanet newsletter and cool star newsletter files

% LaTeX-template for ExoPlanetNews abstract. v1.1 (March 2013)
% Please see the comments below. All lines beginning "%" are not processed or printed
%
%------------------------------------------------------------------------------------------------------------
%
% Remove the "%" from the following 3 lines to preview; please comment out these lines again prior to submission
%\documentclass{article}
%\usepackage{ep}
%\begin{document}
%
%------------------------------------------------------------------------------------------------------------
%
% Title of your paper and short author list (surnames only, no initials)
% Use: 'Author1 et al.' if more than three authors
\title{The Exoplanet Orbit Database \textsc{II}: Updates to
  exoplanets.org}{Han et al.}
%
% or for CONFERENCES use the style:
% \title{Conference Title}{Physical location of Conference}
%
% or for JOB ADVERTS use the style:
% \title{Post Title}{Institute at which post to be held}
%
% or for MISCELLANEOUS ANNOUNCEMENTS use the style:
% \title{Announcement Title}{Institute/Location to which announcement applies}
%
%------------------------------------------------------------------------------------------------------------
%
% Author(s) of your paper (initials then surnames)
% Use \inst{1} etc. for numbering of different institutes.
%{A. Author\inst{1,2}, B. Author\inst{1,3}, C. Author\inst{2} }
\author{Eunkyu Han\inst{1,2}, Sharon X.~Wang\inst{1,2,3}, Jason T.~Wright\inst{1,2,3}, Y.\
  Katherian Feng\inst{1,2}, Ming Zhao\inst{1,2}, Onsi Fakhouri\inst{4}, Jacob I.\ Brown\inst{1,2}, Colin Hancock\inst{1,2}}
%
% or for CONFERENCES use the style:
% \author(Conference Chair(s)}
%
% or for JOB ADVERTS use the style:
% \author{Person offering the job}
%
% or for MISCELLANEOUS ANNOUNCEMENTS use the style:
% \author{Person making the announcement}
%
% Institutes. In the first argument
% Give the numbers as used in the \author command above
%
\instlist{1}{Department of Astronomy \& Astrophysics, 525 Davey
  Lab, The Pennsylvania State University, University Park, PA 16802, USA}
\instlist{2}{Center for Exoplanets and Habitable Worlds, The
  Pennsylvania State University, University Park, PA 16802, USA}
\instlist{3}{Penn State Astrobiology Research Center, The
  Pennsylvania State University, University Park, PA 16802, USA}
\instlist{4}{Pivotal Labs, Cloud Foundry, 875 Howard St., Fourth
  Floor, San Francisco, CA 94103}  
%
% Alternately, if all authors are from the SAME single institute, use:
%\institute{My University, Down the Road, Any Town, UK}
%
%------------------------------------------------------------------------------------------------------------
%
% Status of your paper. 
%First Argument: The journal where it will appear.
% Second Argument. The state - should be one of: "in press" or "published".
%
% If it is already published, please provide us with the ADS-Bibcode,
% otherwise give the arXiv preprint code in the style: "arXiv:nnnn.mmmm"
%
\status{PASP}{in press, arXiv:}
%
% or for CONFERENCES use the style:
% \status{Location of Conference}{Dates of Conference}
%
% or for JOB ADVERTS use the style:
% \status{Location of Post}{Job start date}
%
% or for MISCELLANEOUS ANNOUNCEMENTS use the style:
% \status{Location of Announcement}{Relevant date for announcement}
%
% You should use the following abbreviations:
% \mnras   Monthly Notices of the Royal Astronomical Society
% \aj      Astronomical Journal
% \apj     Astrophysical Journal
% \apjl    Astrophysical Journal Letters
% \aa      Astronomy \& Astrophysics
% \aal     Astronomy \& Astrophysics Letters
% \pasp    Publications of the Astronomical Society of the Pacific
% \aas     American Astronomical Society Meeting
% \pasj    Publications of the Astronomical Society of Japan
%
%
%-----------------------------------------------------------------------------------------------------------
%
% The abstract body
%
\abstract{
The Exoplanet Orbit Database (EOD) compiles orbital, transit, host
star, and other parameters of robustly detected exoplanets reported in
the peer-reviewed literature. The EOD can be navigated through the
Exoplanet Data Explorer (EDE) Plotter and Table, available on the
World Wide Web at exoplanets.org. The EOD contains data for 1492
confirmed exoplanets as of July 2014.  The EOD descends from a table
in Butler et al.\ 2002 and the Catalog of Nearby Exoplanets
Butler et al.\ 2006, and the first complete documentation for the EOD
and the EDE was presented in Wright et al.\ 2011. In this work, we
describe our work since then.  We have expanded the scope of the EOD
to include secondary eclipse parameters, asymmetric uncertainties, and
expanded the EDE to include the sample of over 3000 \textit{Kepler} Objects
of Interest (KOIs), and other real planets without good orbital
parameters (such as many of those detected by microlensing and
imaging). Users can download the latest version of the entire EOD as a
single comma separated value file from the front page of
exoplanets.org.
}
%
% Optional Figure caption: (just paste in here - it will be typeset
% separately)
% Figure caption for han2014.eps
An example plot that demonstrates the current secondary eclipse
measurements. Each planet has a set of circles that stand for its
available secondary eclipse measurements in the database,
including \textit{Spitzer} 8.0, 5.8, 4.5, \& 3.6 $\mu$m, and ground-based
$J$, $H$, and $K_{\rm s}$ bands. \textit{Kepler} secondary eclipse
measurements are labeled as solid black dots. A few representative
planets are also annotated (a feature not offered by the EDE
Plotter, but trivially implemented by other image or presentation
software). The planet name will appear when the user points the
cursor at the corresonding data point in the interactive plotting
tools.
%
%------------------------------------------------------------------------------------------------------------
%
% Download: Website with the preprint and/or additional information/data (CHANGE this from the current value)
%
\download{http://exoplanets.org}
%
% Contact: E-Mail of the responsible person (CHANGE this from the current value)
%
\contact{jtwright@astro.psu.edu}
%
%------------------------------------------------------------------------------------------------------------
%
% Remove the "%" from the next line to preview; comment it out again before submission
%
% \end{document}
%
%------------------------------------------------------------------------------------------------------------

### 2014-09-29 arxiv_newsletter/coolnews_han2014.tex
Exoplanet newsletter and cool star newsletter files

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%                                                                       %%%
%%%            LaTeX MACRO FOR COOLNEWS (Journal Abstracts)               %%%
%%%                                                                       %%%
%%%    Simply fill in the information between the brackets { } below      %%%
%%%    and e-mail to coolnews@jila.colorado.edu.  Try not to use          %%%
%%%    specially-defined Latex commands, but if you must then include     %%% 
%%%    their definitions.                                                 %%%
%%%                                                                       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% To run Latex on your journal abstract, first remove the % sign in the
%% nine lines below, and in the \end{document} line.

%\documentstyle{article}
%\textwidth 18cm
%\textheight 23cm
%\oddsidemargin -1cm
%\topmargin 0cm
%\parskip 0.15cm
%\parindent 0pt
%\small
%\begin{document}

%%            ------ TITLE ---
%% Write the title of your paper between the brackets. Please
%% capitalize only the first letter of each word.
{\large\bf{The Exoplanet Orbit Database \textsc{II}: Updates to
  exoplanets.org}

%%            ------ AUTHORS -----
%% Here comes the author(s) of the paper, please indicate within $^...$ 
%% the number which corresponds to the institute of each author.
{\bf{Eunkyu Han$^{1,2}$, Sharon X.~Wang$^{1,2,3}$, Jason T.~Wright$^{1,2,3}$, Y.\
  Katherian Feng$^{1,2}$, Ming Zhao$^{1,2}$, Onsi
  Fakhouri$^{4}$, Jacob I.\ Brown$^{1,2}$, Colin Hancock$^{1,2}$}}

%%           ------INSTITUTIONS ---
%% Here write your institute name(s) and address(es), 
%% the number in $^..$ indicates your author number, for example:
$^1$ {Department of Astronomy \& Astrophysics, 525 Davey
  Lab, The Pennsylvania State University, University Park, PA 16802, USA}
$^2$ {Center for Exoplanets and Habitable Worlds, The
  Pennsylvania State University, University Park, PA 16802, USA}
$^3$ {Penn State Astrobiology Research Center, The
  Pennsylvania State University, University Park, PA 16802, USA}
$^4$ {Pivotal Labs, Cloud Foundry, 875 Howard St., Fourth
  Floor, San Francisco, CA 94103}

%%            ------ABSTRACT------
%% Enter the text of your abstract between these brackets:
{The Exoplanet Orbit Database (EOD) compiles orbital, transit, host
star, and other parameters of robustly detected exoplanets reported in
the peer-reviewed literature. The EOD can be navigated through the
Exoplanet Data Explorer (EDE) Plotter and Table, available on the
World Wide Web at exoplanets.org. The EOD contains data for 1492
confirmed exoplanets as of July 2014.  The EOD descends from a table
in Butler et al.\ 2002 and the Catalog of Nearby Exoplanets
Butler et al.\ 2006, and the first complete documentation for the EOD
and the EDE was presented in Wright et al.\ 2011. In this work, we
describe our work since then.  We have expanded the scope of the EOD
to include secondary eclipse parameters, asymmetric uncertainties, and
expanded the EDE to include the sample of over 3000 \textit{Kepler} Objects
of Interest (KOIs), and other real planets without good orbital
parameters (such as many of those detected by microlensing and
imaging). Users can download the latest version of the entire EOD as a
single comma separated value file from the front page of
exoplanets.org.}

%%            -----PUBLICATION STATUS---
%% Here give the  publication status (Accepted by, Submitted to) 
%% and the name of journal, for example:
{ PASP in press, arXiv: }

%%            -----E-MAIL ADDRESS-----
%% Here give the e-mail address for preprint requests, for example:
{{\em For preprints contact}: jtwright@astro.psu.edu}
%%

%%            ----FTP or WWW ADDRESS (optional)----
%% If your preprint is available via ftp or WWW, uncomment
%% the line below by removing the % sign in first column
%% and enter the ftp or WWW address.

%{{\em For preprints via ftp or WWW}: http://www.myaddress } 
%% 
%%             ----CATEGORY------
%% Below give the subject category of the abstract (stellar, solar).
%% If you aren't sure, then give Category: uncertain.  
%% The category will only be used for sorting, and wont be printed     
%% in the newsletter.
{ Category: stellar }
%
%\vspace*{0.3cm}
%\end{document}
